---
title: "One Pattern Sims"
author: "Lizzy Gibson"
date: "6/09/2020"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    toc_depth: 5
---

```{r setup, include=FALSE}
require("knitr")
opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
options(scipen = 999)
library(R.matlab)
library(tidyverse)
library(gridExtra)
library(Matrix)
library(matconv)
library(patchwork)
library(janitor)
library(ggcorrplot)
library(ggfortify)  
library(factoextra)
library(knitr)
library(haven)
library(rlist)
library(mvtnorm)
library(reshape2)
library(GGally)
library(grDevices)
library(pcpr)
```

## Simulate

```{r, scores}
# Simulate independent scores
set.seed(1988)
scores <- exp(rnorm(100))
# summary(scores)
# sd(scores)

# scores %>%
#   as_tibble() %>% 
#   ggplot(aes(x = value)) +
#   geom_histogram() + 
#   theme_minimal()

# Simulate 1 pattern
pattern <- t(c(1,1,1,1,1,1,0,0,0,0))

# Add noise
noise <- matrix(NA, nrow = 100, ncol = 10)
seeds <- 1:10
for (i in 1:length(seeds)) {
  set.seed(seeds[i])
  noise[,i] <- exp(rnorm(100, mean = 0, sd = 1))
}

# Multiply scores by pattern
sim_all <- as_tibble((scores %*% pattern) + noise)
#summary(sim_all)
sim_all[sim_all < 0] <- 0 # non-negative
sim_all <- as_tibble(scale(sim_all, center = FALSE, 
                           scale = apply(sim_all, 2, sd, na.rm = TRUE))) # standardize do not center
#sim_all

sim_all %>%
  mutate(id = 1:nrow(.)) %>% 
  gather(key = pop, value = value, -id) %>% 
  ggplot(aes(x = value)) +
  geom_histogram() + facet_wrap(~pop) +
  theme_minimal()

ggcorr(sim_all, method = c("everything", "spearman"), limits = FALSE,
       label = TRUE, label_size = 3, label_alpha = TRUE,
       hjust = 0.85, size = 3, color = "grey50", layout.exp = 1)
```

```{r, neg}
mix_data_lod_10 <- sim_all %>%
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .10), -1, V1)) %>% as.matrix()
  
# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20 <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .20), -1, V1)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30 <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .30), -1, V1)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40 <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .40), -1, V1)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50 <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .50), -1, V1)) %>% as.matrix()

# Create version with 10% lowest values for each variable as below the LOD
mix_data_lod_10_sqrt2 <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .10), (quantile(V1, probs = .10)/sqrt(2)), V1)) %>% as.matrix()

# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20_sqrt2 <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .20), (quantile(V1, probs = .20)/sqrt(2)), V1)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30_sqrt2 <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .30), (quantile(V1, probs = .30)/sqrt(2)), V1)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40_sqrt2 <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .40), (quantile(V1, probs = .40)/sqrt(2)), V1)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50_sqrt2 <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .50), (quantile(V1, probs = .50)/sqrt(2)), V1)) %>% as.matrix()

# LODs
delta10 <- c(quantile(sim_all$V1, probs = 0.10), rep(0, times = 9))

delta20 <- c(quantile(sim_all$V1, probs = 0.20), rep(0, times = 9))

delta30 <- c(quantile(sim_all$V1, probs = 0.30), rep(0, times = 9))

delta40 <- c(quantile(sim_all$V1, probs = 0.40), rep(0, times = 9))

delta50 <- c(quantile(sim_all$V1, probs = 0.50), rep(0, times = 9))
```

```{r, jingkai_leave, cache = TRUE, include=FALSE}
m <- nrow(sim_all)
p <- ncol(sim_all)

lambda_mix <- 1/sqrt(m)
mu_mix <- sqrt(p/(2*log(m*p)))

mix <- as.matrix(sim_all)

dim(mix)
length(delta10)

results_0  <- pcp_lod(mix,             lambda_mix, mu_mix, 0)
results_10 <- pcp_lod(mix_data_lod_10, lambda_mix, mu_mix, delta10)
results_20 <- pcp_lod(mix_data_lod_20, lambda_mix, mu_mix, delta20)
results_30 <- pcp_lod(mix_data_lod_30, lambda_mix, mu_mix, delta30)
results_40 <- pcp_lod(mix_data_lod_40, lambda_mix, mu_mix, delta40)
results_50 <- pcp_lod(mix_data_lod_50, lambda_mix, mu_mix, delta50)

L_lod0 <- results_0[[1]]
S_lod0 <- results_0[[2]]
L_lod10 <- results_10[[1]]
S_lod10 <- results_10[[2]]
L_lod20 <- results_20[[1]]
S_lod20 <- results_20[[2]]
L_lod30 <- results_30[[1]]
S_lod30 <- results_30[[2]]
L_lod40 <- results_40[[1]]
S_lod40 <- results_40[[2]]
L_lod50 <- results_50[[1]]
S_lod50 <- results_50[[2]]

# svd(L_lod50)$d
# rankMatrix(L_lod50)
```

```{r, original, cache = TRUE, include=FALSE}
results_0_sqrt2  <- pcp_lod(mix,                   lambda_mix, mu_mix, 0)
results_10_sqrt2 <- pcp_lod(mix_data_lod_10_sqrt2, lambda_mix, mu_mix, 0)
results_20_sqrt2 <- pcp_lod(mix_data_lod_20_sqrt2, lambda_mix, mu_mix, 0)
results_30_sqrt2 <- pcp_lod(mix_data_lod_30_sqrt2, lambda_mix, mu_mix, 0)
results_40_sqrt2 <- pcp_lod(mix_data_lod_40_sqrt2, lambda_mix, mu_mix, 0)
results_50_sqrt2 <- pcp_lod(mix_data_lod_50_sqrt2, lambda_mix, mu_mix, 0)

L_lod0_sqrt2 <- results_0_sqrt2[[1]]
S_lod0_sqrt2 <- results_0_sqrt2[[2]]
L_lod10_sqrt2 <- results_10_sqrt2[[1]]
S_lod10_sqrt2 <- results_10_sqrt2[[2]]
L_lod20_sqrt2 <- results_20_sqrt2[[1]]
S_lod20_sqrt2 <- results_20_sqrt2[[2]]
L_lod30_sqrt2 <- results_30_sqrt2[[1]]
S_lod30_sqrt2 <- results_30_sqrt2[[2]]
L_lod40_sqrt2 <- results_40_sqrt2[[1]]
S_lod40_sqrt2 <- results_40_sqrt2[[2]]
L_lod50_sqrt2 <- results_50_sqrt2[[1]]
S_lod50_sqrt2 <- results_50_sqrt2[[2]]
```

## PCA

```{r}
pca_0  <- prcomp(mix)
pca_10 <- prcomp(mix_data_lod_10_sqrt2)
pca_20 <- prcomp(mix_data_lod_20_sqrt2)
pca_30 <- prcomp(mix_data_lod_30_sqrt2)
pca_40 <- prcomp(mix_data_lod_40_sqrt2)
pca_50 <- prcomp(mix_data_lod_50_sqrt2)
```

```{r, pca}
#pca_50$sdev
plot(pca_50)
```

### Predicted Values

```{r}
# Create mean vector for un-centering
sim_means_sqrt2 <- apply(sim_all, 2, mean)
mix_10_means_sqrt2 <- apply(mix_data_lod_10_sqrt2, 2, mean)
mix_20_means_sqrt2 <- apply(mix_data_lod_20_sqrt2, 2, mean)
mix_30_means_sqrt2 <- apply(mix_data_lod_30_sqrt2, 2, mean)
mix_40_means_sqrt2 <- apply(mix_data_lod_40_sqrt2, 2, mean)
mix_50_means_sqrt2 <- apply(mix_data_lod_50_sqrt2, 2, mean)
```

```{r, echo = TRUE}
# prcomp centers, does not scale
# need to UNCENTER predictions to compare
# REMOVE SV

rep.row<-function(x,n){
  matrix(rep(x,each=n),nrow=n)
}

pca_pred_0  <- pca_0$x[,1:5] %*% t(pca_0$rotation)[1:5,]   + rep.row(sim_means_sqrt2, 100)
pca_pred_10 <- pca_10$x[,1:5] %*% t(pca_10$rotation)[1:5,] + rep.row(mix_10_means_sqrt2, 100)
pca_pred_20 <- pca_20$x[,1:5] %*% t(pca_20$rotation)[1:5,] + rep.row(mix_20_means_sqrt2, 100)
pca_pred_30 <- pca_30$x[,1:5] %*% t(pca_30$rotation)[1:5,] + rep.row(mix_30_means_sqrt2, 100)
pca_pred_40 <- pca_40$x[,1:5] %*% t(pca_40$rotation)[1:5,] + rep.row(mix_40_means_sqrt2, 100)
pca_pred_50 <- pca_50$x[,1:5] %*% t(pca_50$rotation)[1:5,] + rep.row(mix_50_means_sqrt2, 100)
```

```{r, tp_lod}
pred_sim <- sim_all %>% 
  mutate(id = 1:100) %>% 
  pivot_longer(cols = V1:V10,
               names_to = "Variable",
               values_to = "Simulated")

add_lods <- as_tibble(rbind(c("0%",0), 
      c("10%", quantile(mix[,1], .10)), 
      c("20%", quantile(mix[,1], .20)),
      c("30%", quantile(mix[,1], .30)), 
      c("40%", quantile(mix[,1], .40)),
      c("50%", quantile(mix[,1], .50)))) %>% rename(Percent = 1, LOD = 2) %>% 
  mutate(LOD = as.numeric(LOD),
         Variable = "V1")

pca_pred <- (pca_pred_0) %>% as_tibble() %>% mutate(Percent = "0%") %>% 
  rbind(., (pca_pred_10) %>% as_tibble() %>% mutate(Percent = "10%")) %>% 
  rbind(., (pca_pred_20) %>% as_tibble() %>% mutate(Percent = "20%")) %>% 
  rbind(., (pca_pred_30) %>% as_tibble() %>% mutate(Percent = "30%")) %>% 
  rbind(., (pca_pred_40) %>% as_tibble() %>% mutate(Percent = "40%")) %>% 
  rbind(., (pca_pred_50) %>% as_tibble() %>% mutate(Percent = "50%")) %>%
  mutate(id = rep(1:100, 6)) %>% 
  pivot_longer(cols = V1:V10,
               names_to = "Variable",
               values_to = "Predicted") %>% 
  left_join(., pred_sim, by = c("id", "Variable")) %>% 
  left_join(., add_lods, by = c("Percent", "Variable")) %>% 
  replace_na(list(LOD = 0)) %>% 
  mutate(Value = ifelse(Simulated < LOD, "< LOD", "> LOD"),
         Method = "PCA")
```

## Metrics

```{r, pred_all}
pcp_pred_pcplod <- (L_lod0 + S_lod0) %>% as_tibble() %>% mutate(Percent = "0%") %>% 
  rbind(., (L_lod10 + S_lod10) %>% as_tibble() %>% mutate(Percent = "10%")) %>% 
  rbind(., (L_lod20 + S_lod20) %>% as_tibble() %>% mutate(Percent = "20%")) %>% 
  rbind(., (L_lod30 + S_lod30) %>% as_tibble() %>% mutate(Percent = "30%")) %>% 
  rbind(., (L_lod40 + S_lod40) %>% as_tibble() %>% mutate(Percent = "40%")) %>% 
  rbind(., (L_lod50 + S_lod50) %>% as_tibble() %>% mutate(Percent = "50%")) %>%
  mutate(id = rep(1:100, 6)) %>% 
  pivot_longer(cols = V1:V10,
               names_to = "Variable",
               values_to = "Predicted") %>% 
  left_join(., pred_sim, by = c("id", "Variable")) %>% 
  left_join(., add_lods, by = c("Percent", "Variable")) %>% 
  replace_na(list(LOD = 0)) %>% 
  mutate(Value = ifelse(Simulated < LOD, "< LOD", "> LOD"),
         Method = "PCP-LOD")

lowrank_pcplod <- (L_lod0) %>% as_tibble() %>% mutate(Percent = "0%") %>% 
  rbind(., (L_lod10) %>% as_tibble() %>% mutate(Percent = "10%")) %>% 
  rbind(., (L_lod20) %>% as_tibble() %>% mutate(Percent = "20%")) %>% 
  rbind(., (L_lod30) %>% as_tibble() %>% mutate(Percent = "30%")) %>% 
  rbind(., (L_lod40) %>% as_tibble() %>% mutate(Percent = "40%")) %>% 
  rbind(., (L_lod50) %>% as_tibble() %>% mutate(Percent = "50%")) %>%
  mutate(id = rep(1:100, 6)) %>% 
  pivot_longer(cols = V1:V10,
               names_to = "Variable",
               values_to = "Low_Rank") %>% 
  left_join(., pred_sim, by = c("id", "Variable")) %>% 
  left_join(., add_lods, by = c("Percent", "Variable")) %>% 
  replace_na(list(LOD = 0)) %>% 
  mutate(Value = ifelse(Simulated < LOD, "< LOD", "> LOD"),
         Method = "PCP-LOD")

sparse_pcplod <- (S_lod0) %>% as_tibble() %>% mutate(Percent = "0%") %>% 
  rbind(., (S_lod10) %>% as_tibble() %>% mutate(Percent = "10%")) %>% 
  rbind(., (S_lod20) %>% as_tibble() %>% mutate(Percent = "20%")) %>% 
  rbind(., (S_lod30) %>% as_tibble() %>% mutate(Percent = "30%")) %>% 
  rbind(., (S_lod40) %>% as_tibble() %>% mutate(Percent = "40%")) %>% 
  rbind(., (S_lod50) %>% as_tibble() %>% mutate(Percent = "50%")) %>%
  mutate(id = rep(1:100, 6)) %>% 
  pivot_longer(cols = V1:V10,
               names_to = "Variable",
               values_to = "Sparse") %>% 
  left_join(., pred_sim, by = c("id", "Variable")) %>% 
  left_join(., add_lods, by = c("Percent", "Variable")) %>% 
  replace_na(list(LOD = 0)) %>% 
  mutate(Value = ifelse(Simulated < LOD, "< LOD", "> LOD"),
         Method = "PCP-LOD")

pcp_pred_original <- (L_lod0_sqrt2 + S_lod0_sqrt2) %>% as_tibble() %>% mutate(Percent = "0%") %>% 
  rbind(., (L_lod10_sqrt2 + S_lod10_sqrt2) %>% as_tibble() %>% mutate(Percent = "10%")) %>% 
  rbind(., (L_lod20_sqrt2 + S_lod20_sqrt2) %>% as_tibble() %>% mutate(Percent = "20%")) %>% 
  rbind(., (L_lod30_sqrt2 + S_lod30_sqrt2) %>% as_tibble() %>% mutate(Percent = "30%")) %>% 
  rbind(., (L_lod40_sqrt2 + S_lod40_sqrt2) %>% as_tibble() %>% mutate(Percent = "40%")) %>% 
  rbind(., (L_lod50_sqrt2 + S_lod50_sqrt2) %>% as_tibble() %>% mutate(Percent = "50%")) %>%
  mutate(id = rep(1:100, 6)) %>% 
  pivot_longer(cols = V1:V10,
               names_to = "Variable",
               values_to = "Predicted") %>% 
  left_join(., pred_sim, by = c("id", "Variable")) %>% 
  left_join(., add_lods, by = c("Percent", "Variable")) %>% 
  replace_na(list(LOD = 0)) %>% 
  mutate(Value = ifelse(Simulated < LOD, "< LOD", "> LOD"),
         Method = "Original PCP")

lowrank_original <- (L_lod0_sqrt2) %>% as_tibble() %>% mutate(Percent = "0%") %>% 
  rbind(., (L_lod10_sqrt2) %>% as_tibble() %>% mutate(Percent = "10%")) %>% 
  rbind(., (L_lod20_sqrt2) %>% as_tibble() %>% mutate(Percent = "20%")) %>% 
  rbind(., (L_lod30_sqrt2) %>% as_tibble() %>% mutate(Percent = "30%")) %>% 
  rbind(., (L_lod40_sqrt2) %>% as_tibble() %>% mutate(Percent = "40%")) %>% 
  rbind(., (L_lod50_sqrt2) %>% as_tibble() %>% mutate(Percent = "50%")) %>%
  mutate(id = rep(1:100, 6)) %>% 
  pivot_longer(cols = V1:V10,
               names_to = "Variable",
               values_to = "Low_Rank") %>% 
  left_join(., pred_sim, by = c("id", "Variable")) %>% 
  left_join(., add_lods, by = c("Percent", "Variable")) %>% 
  replace_na(list(LOD = 0)) %>% 
  mutate(Value = ifelse(Simulated < LOD, "< LOD", "> LOD"),
         Method = "Original PCP")

sparse_original <- (S_lod0_sqrt2) %>% as_tibble() %>% mutate(Percent = "0%") %>% 
  rbind(., (S_lod10_sqrt2) %>% as_tibble() %>% mutate(Percent = "10%")) %>% 
  rbind(., (S_lod20_sqrt2) %>% as_tibble() %>% mutate(Percent = "20%")) %>% 
  rbind(., (S_lod30_sqrt2) %>% as_tibble() %>% mutate(Percent = "30%")) %>% 
  rbind(., (S_lod40_sqrt2) %>% as_tibble() %>% mutate(Percent = "40%")) %>% 
  rbind(., (S_lod50_sqrt2) %>% as_tibble() %>% mutate(Percent = "50%")) %>%
  mutate(id = rep(1:100, 6)) %>% 
  pivot_longer(cols = V1:V10,
               names_to = "Variable",
               values_to = "Sparse") %>% 
  left_join(., pred_sim, by = c("id", "Variable")) %>% 
  left_join(., add_lods, by = c("Percent", "Variable")) %>% 
  replace_na(list(LOD = 0)) %>% 
  mutate(Value = ifelse(Simulated < LOD, "< LOD", "> LOD"),
         Method = "Original PCP")

pcp_pred <- rbind(pcp_pred_pcplod, pcp_pred_original)
lowrank_pred <- rbind(lowrank_pcplod, lowrank_original)
sparse_pred <- rbind(sparse_pcplod, sparse_original)

pcp_pred <- full_join(pcp_pred, lowrank_pred, 
                       by = c("Percent", "id", "Variable", "Simulated", "LOD", "Value", "Method")) %>% 
            full_join(., sparse_pred, 
                       by = c("Percent", "id", "Variable", "Simulated", "LOD", "Value", "Method")) 

base <- pcp_pred %>% filter(Percent == "0%") %>% 
  mutate(base_low = Low_Rank, base_sparse = Sparse) %>% 
  select(id, Variable, Method, base_low, base_sparse)

pcp_pred <- pcp_pred %>% 
  left_join(., base)

all_pred <- pcp_pred %>% select(-(Low_Rank:base_sparse)) %>% 
  rbind(., pca_pred)
```

### X - L - S

* X = simulated dataset
* L = low rank solution matrix
* S = sparse solution matrix

```{r}
all_pred %>%
  mutate(l2 = (Simulated - Predicted)^2,
         l1 = abs(Simulated - Predicted)) %>%
  group_by(Percent, Method) %>% 
           summarise(Fro = sqrt(sum(l2))/sqrt(sum(Simulated^2)),
                     l1 = sqrt(sum(l1))/sqrt(sum(Simulated)),
                     linf = max(l1)/max(Simulated)) %>% 
  ggplot(aes(x = Percent, y = Fro, group = Method, color = Method)) + 
  geom_point() + geom_path() + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(X-L-S) / norm(X)",
       title = "Relative Prediction Error")

pcp_pred %>%
  mutate(l2 = (Simulated - Predicted)^2,
         l1 = abs(Simulated - Predicted)) %>%
  group_by(Percent, Method) %>% 
           summarise(Fro = sqrt(sum(l2))/sqrt(sum(Simulated^2)),
                     l1 = sqrt(sum(l1))/sqrt(sum(Simulated)),
                     linf = max(l1)/max(Simulated)) %>% 
  ggplot(aes(x = Percent, y = Fro, group = Method, color = Method)) + 
  geom_point() + geom_path() + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(X-L-S) / norm(X)",
       title = "Relative Prediction Error")
```

### Individual Solution Matrices

* Reference is solution matix with 0\% \<LOD  
* Low rank solution matrices compared with low rank solution with 0\% \<LOD
* Sparse solution matrices compared with sparse solution with 0\% \<LOD

```{r}
pcp_pred %>% 
  pivot_longer(cols = Low_Rank:Sparse,
               names_to = "Matrix",
               values_to = "low_sparse") %>% 
  pivot_longer(cols = base_low:base_sparse,
               names_to = "Matrix2",
               values_to = "Base") %>% 
  filter((Matrix == "Low_Rank" & Matrix2 == "base_low") |
           (Matrix == "Sparse" & Matrix2 == "base_sparse")) %>%
  mutate(l2 = (Base - low_sparse)^2,
         l1 = abs(Base - low_sparse)) %>% 
  group_by(Percent, Method, Matrix) %>% 
           summarise(Fro = sqrt(sum(l2))/sqrt(sum(Base^2)),
                     l1 = sqrt(sum(l1))/sqrt(sum(Base)),
                     linf = max(l1)/max(Base)) %>% 
  ggplot(aes(x = Percent, y = Fro, group = interaction(Method, Matrix), color = Method)) + 
  geom_point() + geom_path(aes(linetype = Matrix)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(difference) / norm(lod0))",
       title = "Relative Error in Solution Matrices")
```

### Values \<LOD vs \>LOD

* Values \> and \< LOD stratified
* Sum of low rank and sparse solution matrices (L \+ S) compared to simulated data (X)

```{r}
all_pred %>% 
  mutate(l2 = (Simulated - Predicted)^2,
         l1 = abs(Simulated - Predicted)) %>% 
  group_by(Percent, Method, Value) %>% 
           summarise(Fro = sqrt(sum(l2))/sqrt(sum(Simulated^2)),
                     l1 = sqrt(sum(l1))/sqrt(sum(Simulated)),
                     linf = max(l1)/max(Simulated)) %>%
  ggplot(aes(x = Percent, y = Fro, group = interaction(Method, Value), color = Method)) + 
  geom_point() + geom_path(aes(linetype = Value)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "norm(X-L-S) / norm(X)",
       title = "Relative Error in Values < LOD & > LOD")
```

```{r}
pcp_pred %>% 
  mutate(l2 = (Simulated - Predicted)^2,
         l1 = abs(Simulated - Predicted)) %>% 
  group_by(Percent, Method, Value) %>% 
           summarise(Fro = sqrt(sum(l2))/sqrt(sum(Simulated^2)),
                     l1 = sqrt(sum(l1))/sqrt(sum(Simulated)),
                     linf = max(l1)/max(Simulated)) %>%
  ggplot(aes(x = Percent, y = Fro, group = interaction(Method, Value), color = Method)) + 
  geom_point() + geom_path(aes(linetype = Value)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "norm(X-L-S) / norm(X)",
       title = "Relative Error in Values < LOD & > LOD")
```

## True v. Predicted

```{r}
pcp_pred %>%
  filter(Variable == "V1" & Method == "PCP-LOD") %>%
  ggplot(aes(x = Simulated, y = Predicted)) + 
  geom_hline(yintercept = 0, color = 'grey', linetype = 'dashed') +
  geom_rect(aes(xmin = 0, xmax = LOD, ymin = 0, ymax = LOD),
                   fill = "pink", alpha = 0.03) +
  geom_abline(intercept = 0, slope = 1, color = 'grey', linetype = 'dashed') +
  geom_point(aes(color = Percent)) +
  facet_wrap(~Percent) +
  theme_bw() + theme(legend.position = "none") +
  labs(title= "PCP-LOD Simulated v. Predicted Values (L + S) for POP V1")

pcp_pred %>%
  filter(Variable == "V1" & Method == "PCP-LOD") %>%
  filter(Simulated <= LOD) %>% 
  ggplot(aes(x = Simulated, y = Predicted)) + 
  geom_hline(yintercept = 0, color = 'grey', linetype = 'dashed') +
  geom_rect(aes(xmin = 0, xmax = LOD, ymin = 0, ymax = LOD),
                   fill = "pink", alpha = 0.03) +
  geom_abline(intercept = 0, slope = 1, color = 'grey', linetype = 'dashed') +
  geom_point(aes(color = Percent)) +
  facet_wrap(~Percent) +
  theme_bw() + theme(legend.position = "none") +
  labs(title= "PCP-LOD Simulated v. Predicted Values (L + S) for POP V1 <LOD")

pcp_pred %>%
  filter(Variable == "V1" & Method == "Original PCP") %>%
  ggplot(aes(x = Simulated, y = Predicted)) + 
  geom_hline(yintercept = 0, color = 'grey', linetype = 'dashed') +
  geom_rect(aes(xmin = 0, xmax = LOD, ymin = 0, ymax = LOD),
                   fill = "pink", alpha = 0.03) +
  geom_abline(intercept = 0, slope = 1, color = 'grey', linetype = 'dashed') +
  geom_point(aes(color = Percent)) +
  facet_wrap(~Percent) +
  theme_bw() + theme(legend.position = "none") +
  labs(title= "Original PCP w/ LOD/sqrt(2) Simulated v. Predicted Values (L + S) for POP V1")

pcp_pred %>%
  filter(Variable == "V1" & Method == "Original PCP") %>%
  filter(Simulated <= LOD) %>% 
  ggplot(aes(x = Simulated, y = Predicted)) + 
  geom_hline(yintercept = 0, color = 'grey', linetype = 'dashed') +
  geom_rect(aes(xmin = 0, xmax = LOD, ymin = 0, ymax = LOD),
                   fill = "pink", alpha = 0.03) +
  geom_abline(intercept = 0, slope = 1, color = 'grey', linetype = 'dashed') +
  geom_point(aes(color = Percent)) +
  facet_wrap(~Percent) +
  theme_bw() + theme(legend.position = "none") +
  labs(title= "Original PCP w/ LOD/sqrt(2) Simulated v. Predicted Values (L + S) for POP V1 <LOD")

pca_pred %>% 
  filter(Variable == "V1") %>% 
  ggplot(aes(x = Simulated, y = Predicted)) + 
  geom_hline(yintercept = 0, color = 'grey', linetype = 'dashed') +
  geom_rect(aes(xmin = 0, xmax = LOD, ymin = 0, ymax = LOD),
                   fill = "pink", alpha = 0.03) +
  geom_abline(intercept = 0, slope = 1, color = 'grey', linetype = 'dashed') +
  geom_point(aes(color = Percent)) +
  facet_wrap(~Percent) +
  theme_bw() + theme(legend.position = "none") +
  labs(title= "PCA Simulated v. Predicted Values for POP V1")

pca_pred %>% 
  filter(Variable == "V1" & Simulated <= LOD) %>% 
  ggplot(aes(x = Simulated, y = Predicted)) + 
  geom_hline(yintercept = 0, color = 'grey', linetype = 'dashed') +
  geom_rect(aes(xmin = 0, xmax = LOD, ymin = 0, ymax = LOD),
                   fill = "pink", alpha = 0.03) +
  geom_abline(intercept = 0, slope = 1, color = 'grey', linetype = 'dashed') +
  geom_point(aes(color = Percent)) +
  facet_wrap(~Percent) +
  theme_bw() + theme(legend.position = "none") +
  labs(title= "PCA Simulated v. Predicted Values for POP V1 <LOD")
```

## Values \<LOD

```{r}
pcp_pred %>% 
  filter(Simulated < LOD) %>% 
  drop_na(.) %>% 
  mutate(above_lod = ifelse(Low_Rank > LOD, 1, 0)) %>%
  group_by(Method, Percent) %>% 
  summarise(above = sum(above_lod),
            total = n()) %>% 
  mutate(Proportion = round(above/total, 2)) %>% 
  ungroup(.) %>% 
  select(Method, Percent, Proportion) %>% 
  kable(., caption = "Low Rank Solution Values >LOD for TRUE POP V1 <LOD")

pcp_pred %>% 
  filter(Simulated < LOD) %>% 
  drop_na(.) %>% 
  group_by(Method, Percent) %>% 
  summarise(Min = min(Sparse),
            Ave = mean(Sparse),
            Max = max(Sparse)) %>% 
  ungroup(.) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  kable(., caption = "PCP Sparse Solutions for TRUE POP V1 <LOD")
```

* Plus sign (\+) indicates LOD for each chemical

```{r}
pcp_pred %>% 
  filter(Simulated < LOD) %>% 
  pivot_longer(cols = c(Predicted, Simulated, Low_Rank, Sparse),
               names_to = "Compare") %>% 
  ggplot(aes(x = Method, y = value)) + 
  #geom_jitter(aes(color = Compare), alpha = 0.5, width = 0.10, height = 0) + 
  geom_boxplot(aes(color = Compare), width = 0.5, size = 0.75) +
  theme_bw() +
  geom_point(aes(y = LOD), shape = 3, size = 2) +
  facet_wrap(.~Percent) +
  labs(x = "% < LOD", 
       y = "Solution Value",
       title = "PCP Solution Values <LOD + Original Values for POP V1") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))
```


