---
title: "NHANES POP Simulations"
author: "Lizzy Gibson"
date: "4/8/2020"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    toc_depth: 5
    code_folding: 'hide'
---

```{r setup, include=FALSE}
require("knitr")
opts_chunk$set(echo = TRUE)
options(scipen = 999)
library(R.matlab)
library(tidyverse)
library(gridExtra)
library(Matrix)
library(matconv)
library(patchwork)
library(janitor)
library(ggcorrplot)
library(ggfortify)  
library(factoextra)
library(knitr)
library(haven)
library(rlist)
library(mvtnorm)
library(reshape2)
library(GGally)
library(grDevices)
library(plotly)
library(Cairo)
```

## NHANES

NHANES 2001-2002 POP data.

```{r}
nhanes <- read_sas(here::here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names()

head(nhanes)[1:7]
```

LA = lipid adjusted  
LC = comment code  

### Select

CDC imputes values \<LOD as LOD/sqrt(2). Here, if comment code = "below detectable limit", LC = 1.

```{r}
prop <- function (x) {1 - (sum(x, na.rm = TRUE)/nrow(nhanes))}

names <- nhanes %>% select(names(.)[grep("lc", names(.))]) %>% 
  summarize_all(prop) %>% select_if(~. > 0.6) %>% names() %>% str_sub(., 4, 6) %>% str_c("lbx", ., "la") %>% as.vector()

pops <- nhanes %>% 
  select(!!names) %>% na.omit(.)

names(pops) <- str_sub(names(pops), 1, 6)
names(pops) <- str_replace(names(pops), "lbxd", "D")
names(pops) <- str_replace(names(pops), "lbxf", "F")
names(pops) <- str_replace(names(pops), "lbx", "PCB")
pops

ggcorr(pops, method = c("everything", "spearman"), limits = FALSE,
       label = TRUE, label_size = 3, label_alpha = TRUE,
       hjust = 0.85, size = 3, color = "grey50", layout.exp = 1) + ggtitle("Persistent organic pollutants \n in NHANES 2001-2002")
```

### Simulate

Remove comment codes for simulations.  
Remove NA for simulations.

```{r}
# Vector of NHANES means
# log to approx normal dist
means <- as_vector(map(log(pops), function(x) mean(x, na.rm = TRUE)))

# Covariance matrix from NHANES
# log to approx normal dist
covs <- cov(log(pops))

# Simulate with multivariate normal function
# exp multi-normal to get multi-log normal
set.seed(1988)
sim_all <- exp(rmvnorm(1000, mean = means, sigma = covs)) %>% as_tibble()
```

```{r}
ggcorr(sim_all, method = c("everything", "spearman"), limits = FALSE,
       label = TRUE, label_size = 3, label_alpha = TRUE,
       hjust = 0.85, size = 3, color = "grey50", layout.exp = 1) + ggtitle("Simulated Data")
```

### Scale Simulations

Divide by standard deviation, do not mean center.  

```{r}
sim_all <- sim_all %>% 
  mutate_all(scale, center = FALSE)
```

### Create \<LOD Datasets

```{r, neg}
# Create version with 10% lowest values for each variable as below the LOD
mix_data_lod_10 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .10), -1, .)) %>% as.matrix()

# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .20), -1, .)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .30), -1, .)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .40), -1, .)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .50), -1, .)) %>% as.matrix()
#write_csv(as_tibble(mix_data_lod_50), "sim_nhanes_lod50.csv")

# Create version with 10% lowest values for each variable as below the LOD
mix_data_lod_10_0 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .10), 0, .)) %>% as.matrix()

# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20_0 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .20), 0, .)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30_0 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .30), 0, .)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40_0 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .40), 0, .)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50_0 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .50), 0, .)) %>% as.matrix()

# Create version with 10% lowest values for each variable as below the LOD
mix_data_lod_10_sqrt2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .10), (quantile(., probs = .10)/sqrt(2)), .)) %>% as.matrix()

# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20_sqrt2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .20), (quantile(., probs = .20)/sqrt(2)), .)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30_sqrt2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .30), (quantile(., probs = .30)/sqrt(2)), .)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40_sqrt2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .40), (quantile(., probs = .40)/sqrt(2)), .)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50_sqrt2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .50), (quantile(., probs = .50)/sqrt(2)), .)) %>% as.matrix()

# Create version with 10% lowest values for each variable as below the LOD
mix_data_lod_10_2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .10), (quantile(., probs = .10)/2), .)) %>% as.matrix()

# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20_2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .20), (quantile(., probs = .20)/2), .)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30_2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .30), (quantile(., probs = .30)/2), .)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40_2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .40), (quantile(., probs = .40)/2), .)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50_2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .50), (quantile(., probs = .50)/2), .)) %>% as.matrix()
```

### Quantiles = LOD

```{r}
delta10 <- sim_all %>% 
  summarise_all(quantile, probs = .10) %>% as_vector()

delta20 <- sim_all %>% 
  summarise_all(quantile, probs = .20) %>% as_vector()

delta30 <- sim_all %>% 
  summarise_all(quantile, probs = .30) %>% as_vector()

delta40 <- sim_all %>% 
  summarise_all(quantile, probs = .40) %>% as_vector()

delta50 <- sim_all %>% 
  summarise_all(quantile, probs = .50) %>% as_vector()
```

## Fuctions

```{r, nn_function}
prox_l1 <- function(Y, c) {
  
  myzero <- matrix(data = 0, ncol = ncol(Y), nrow = nrow(Y))
  X <- sign(Y) * pmax(abs(Y) - c, myzero, na.rm = TRUE)
  X
} 

############################################################

prox_nuclear <- function(Y, c) {
  
  USV <- svd(Y)
  U <- USV$u
  S <- USV$d
  V <- USV$v
  
  myzero <- vector("numeric", length = length(S))
  S_new <- sign(S) * pmax(abs(S) - c, myzero, na.rm = TRUE)
  X <- U %*% diag(S_new) %*% t(V)
  nuclearX  <- sum(abs(S_new))

    list(X = X, nuclearX = nuclearX)
}

############################################################

is_same <- function(SAME_THRESH, ...) {
  flag <- TRUE
  varargin <- list(...)
  if (length(varargin) == 2) {
    if (max(abs(varargin[[1]] - varargin[[2]])) > SAME_THRESH) {
      flag <- FALSE
    }
  }
  else if (length(varargin) == 3) {
    if ((max(abs(varargin[[1]] - varargin[[2]])) > SAME_THRESH) |
        (max(abs(varargin[[1]] - varargin[[3]])) > SAME_THRESH) |
        (max(abs(varargin[[2]] - varargin[[3]])) > SAME_THRESH)) {
      flag <- FALSE
    }
  }
  flag
}

```

```{r, older}
loss_lod <- function(X, D, LOD) {

    X_lod <- ((X - D)     * (D >= 0)) +
             ((X - LOD)   * (D < 0 & (X > LOD))) +
              (X          * (D < 0 & X < 0))
  
  l <- sum(X_lod^2) / 2
  l
}

############################################################

pcp_lod <- function(D, lambda, mu, LOD) {
  
  m <- nrow(D)
  n <- ncol(D)
  rho <- 1 # Augmented Lagrangian coefficient (rate)
  
  L1 <- matrix(0, m, n)
  L2 <- matrix(0, m, n)
  L3 <- matrix(0, m, n)
  
  S1 <- matrix(0, m, n)
  S2 <- matrix(0, m, n)
  
  Z1 <- matrix(0, m, n)
  Z2 <- matrix(0, m, n)
  Z3 <- matrix(0, m, n)
  
  # Max iteration
  MAX_ITER <- 5000
  
  # Convergence Thresholds
  LOSS_THRESH <- 1e-5
  SAME_THRESH <- 1e-4
  
  if (is.vector(LOD)) {
  #tf = ifelse(D < 0, TRUE, FALSE)
  #LOD = t(t(tf) * LOD)
    empty = matrix(1, nrow = nrow(D), ncol = ncol(D))
    LOD = t(t(empty) * LOD)
    }
  
  loss <- vector("numeric", MAX_ITER)
  
  for (i in 1:MAX_ITER) {
    
    nuc <- prox_nuclear( ((L2 + L3 - (Z1 + Z2)/rho)/2), 1/2/rho)
    L1 <- nuc[[1]]
    nuclearL1 <- nuc[[2]] #nuclearX
    
    S1 <- prox_l1((S2 - Z3/rho), lambda/rho)
    
      L2_opt1 <- (mu*rho*D     + (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)
      L2_opt2 <- L1 + Z1/rho
      L2_opt3 <- ((mu*rho*LOD + (((mu + rho)*Z1) - (mu*Z3) + ((mu + rho)*rho*L1) - (mu*rho*S1)))) / ((2*mu*rho) + (rho^2))
      L2_opt4 <- (               (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)

      L2_new <- (L2_opt1 * (D >= 0)) +
        (L2_opt2 * ((D < 0) & (((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
        (L2_opt3 * ((D < 0) & (((L2 + S2) > LOD)))) +
        (L2_opt4 * ((D < 0) & (((L2 + S2) < 0))))

      S2_opt1 <- (mu*rho*D     + (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)
      S2_opt2 <- S1 + (Z3/rho)
      S2_opt3 <- (((mu*rho*LOD) + (((mu + rho)*Z3) - (mu*Z1) + ((mu + rho)*rho*S1) - (mu*rho*L1)))) / ((2*mu*rho) + (rho^2))
      S2_opt4 <- (               (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)

      S2 <- (S2_opt1 * (D >= 0)) +
        (S2_opt2 * (((D < 0) & ((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
        (S2_opt3 * (((D < 0) & ((L2 + S2) > LOD)))) +
        (S2_opt4 * (((D < 0) & ((L2 + S2) < 0))))
   
    L2 <- L2_new
    
    L3 <- pmax(L1 + Z2/rho, 0, na.rm = TRUE)
    # % Non-Negativity constraint!
    
    Z1 <- Z1 + rho*(L1 - L2)
    Z2 <- Z2 + rho*(L1 - L3)
    Z3 <- Z3 + rho*(S1 - S2)
    # % Z accumulate differnces between L and L and between S and S
    
    loss[i] <- nuclearL1 + 
      (lambda*sum(abs(S1))) +
      (mu*loss_lod((L2 + S2), D, LOD)) +
      sum(Z1*(L1 - L2)) +
      sum(Z2*(L1 - L3)) +
      sum(Z3*(S1 - S2)) +
      (rho/2 * (sum((L1-L2)^2) + sum((L1 - L3)^2) + sum((S1 - S2)^2)))
    # % The code block above takes LOD into account.
    
    print(str_c(i, " Obj: ", loss[i]))
        
    if ((i != 1) && 
        (abs(loss[i-1] - loss[i]) < LOSS_THRESH) && 
        is_same(SAME_THRESH, L1, L2, L3) &&
        is_same(SAME_THRESH, S1, S2)) {
      break} # % Convergence criteria!
  }
  
  L <- L3 # (L1 + L2 + L3) / 3
  S <- S1 #(S1 + S2) / 2
  list(L = L, S = S, loss = loss)
}
```

## PCP

```{r, jingkai_leave}
m <- nrow(sim_all)
p <- ncol(sim_all)

lambda_mix <- 1/sqrt(m)
mu_mix <- sqrt(p/(2*log(m*p)))

mix <- as.matrix(sim_all)
  
results_0  <- pcp_lod(mix,             lambda_mix, mu_mix, 0)
results_10 <- pcp_lod(mix_data_lod_10, lambda_mix, mu_mix, delta10)
results_20 <- pcp_lod(mix_data_lod_20, lambda_mix, mu_mix, delta20)
results_30 <- pcp_lod(mix_data_lod_30, lambda_mix, mu_mix, delta30)
results_40 <- pcp_lod(mix_data_lod_40, lambda_mix, mu_mix, delta40)
results_50 <- pcp_lod(mix_data_lod_50, lambda_mix, mu_mix, delta50)

L_lod0 <- results_0[[1]]
S_lod0 <- results_0[[2]]
L_lod10 <- results_10[[1]]
S_lod10 <- results_10[[2]]
L_lod20 <- results_20[[1]]
S_lod20 <- results_20[[2]]
L_lod30 <- results_30[[1]]
S_lod30 <- results_30[[2]]
L_lod40 <- results_40[[1]]
S_lod40 <- results_40[[2]]
L_lod50 <- results_50[[1]]
S_lod50 <- results_50[[2]]

sum(L_lod50)
sum(S_lod50)
```

## X - L - S

```{r}
F_norm <- as_tibble(cbind(`0%` = norm((mix - L_lod0 - S_lod0), type = "F")/norm((mix), type = "F"),
      `10%` = norm((mix - L_lod10 - S_lod10), type = "F")/norm((mix), type = "F"),
      `20%` = norm((mix - L_lod20 - S_lod20), type = "F")/norm((mix), type = "F"),
      `30%` = norm((mix - L_lod30 - S_lod30), type = "F")/norm((mix), type = "F"),
      `40%` = norm((mix - L_lod40 - S_lod40), type = "F")/norm((mix), type = "F"),
      `50%` = norm((mix - L_lod50 - S_lod50), type = "F")/norm((mix), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "LOD PCP")
```

### Viz

```{r, fig.height = 5, fig.width = 4, fig.align = "center"}
F_norm %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point(aes(color = Method)) + geom_path(aes(group = Method, color = Method)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(X-L-S) / norm(X)",
       title = "Relative Prediction Error")
```

## Individual Solution Matrices

```{r}
L_diff <- as_tibble(cbind(`0%` = norm((L_lod0 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      `10%` = norm((L_lod10 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      `20%` = norm((L_lod20 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      `30%` = norm((L_lod30 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      `40%` = norm((L_lod40 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      `50%` = norm((L_lod50 - L_lod0), type = "F")/norm((L_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank",
         Method = "LOD PCP")

S_diff <- as_tibble(cbind(`0%` = norm((S_lod0 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      `10%` = norm((S_lod10 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      `20%` = norm((S_lod20 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      `30%` = norm((S_lod30 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      `40%` = norm((S_lod40 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      `50%` = norm((S_lod50 - S_lod0), type = "F")/norm((S_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse",
         Method = "LOD PCP")
```

### Viz

```{r, fig.height = 5, fig.width = 4, fig.align = "center"}
rbind(L_diff, S_diff) %>% ggplot(aes(x = percent_blod, y = norm, group = interaction(Matrix,Method), color = Method)) + 
  geom_point() + geom_path(aes(linetype = Matrix)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(difference) / norm(lod0))",
       title = "Relative Error in \nSolution Matrices")
```

## Values \<LOD

```{r, l22s}
t_na_lod_0 <- sim_all %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_0_na <- as_tibble(t_na_lod_0*L_lod0)
s_blod_0_na <- as_tibble(t_na_lod_0*S_lod0)
blod_0_na <- as_tibble(sim_all*t_na_lod_0)

t_na_lod_10 <- mix_data_lod_10 %>% 
  as_tibble() %>%
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_10_na <- as_tibble(t_na_lod_10*L_lod10)
s_blod_10_na <- as_tibble(t_na_lod_10*S_lod10)
blod_10_na <- as_tibble(sim_all*t_na_lod_10)

t_na_lod_20 <- mix_data_lod_20 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_20_na <- as_tibble(t_na_lod_20*L_lod20)
s_blod_20_na <- as_tibble(t_na_lod_20*S_lod20)
blod_20_na <- as_tibble(sim_all*t_na_lod_20)

t_na_lod_30 <- mix_data_lod_30 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_30_na <- as_tibble(t_na_lod_30*L_lod30)
s_blod_30_na <- as_tibble(t_na_lod_30*S_lod30)
blod_30_na <- as_tibble(sim_all*t_na_lod_30)

t_na_lod_40 <- mix_data_lod_40 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_40_na <- as_tibble(t_na_lod_40*L_lod40)
s_blod_40_na <- as_tibble(t_na_lod_40*S_lod40)
blod_40_na <- as_tibble(sim_all*t_na_lod_40)

t_na_lod_50 <- mix_data_lod_50 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_50_na <- as_tibble(t_na_lod_50*L_lod50)
s_blod_50_na <- as_tibble(t_na_lod_50*S_lod50)
blod_50_na <- as_tibble(sim_all*t_na_lod_50) 
```

```{r}
LOD10 <- delta10 %>% as.matrix() %>% t() %>% as_tibble() %>% rename_all(., list(~str_sub(., start = 1, end = -5))) %>% gather(POP, LOD) %>% mutate(Percent = "10%")
LOD20 <- delta20 %>% as.matrix() %>% t() %>% as_tibble() %>% rename_all(., list(~str_sub(., start = 1, end = -5))) %>% gather(POP, LOD) %>% mutate(Percent = "20%")
LOD30 <- delta30 %>% as.matrix() %>% t() %>% as_tibble() %>% rename_all(., list(~str_sub(., start = 1, end = -5))) %>% gather(POP, LOD) %>% mutate(Percent = "30%")
LOD40 <- delta40 %>% as.matrix() %>% t() %>% as_tibble() %>% rename_all(., list(~str_sub(., start = 1, end = -5))) %>% gather(POP, LOD) %>% mutate(Percent = "40%")
LOD50 <- delta50 %>% as.matrix() %>% t() %>% as_tibble() %>% rename_all(., list(~str_sub(., start = 1, end = -5))) %>% gather(POP, LOD) %>% mutate(Percent = "50%")
LODall <- rbind(LOD10, LOD20, LOD30, LOD40, LOD50)
  
plot_10 <- blod_10_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Original, -rowid) %>% mutate(Percent = "10%")
plotl_10 <- l_blod_10_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))
plots_10 <- s_blod_10_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))
plotall_10 <- (l_blod_10_na + s_blod_10_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))

plot_20 <- blod_20_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Original, -rowid) %>% mutate(Percent = "20%") 
plotl_20 <- l_blod_20_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent"))
plots_20 <- s_blod_20_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent"))
plotall_20 <- (l_blod_20_na + s_blod_20_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent")) 

plot_30 <- blod_30_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Original, -rowid) %>% mutate(Percent = "30%")
plotl_30 <- l_blod_30_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent"))
plots_30 <- s_blod_30_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent")) 
plotall_30 <- (l_blod_30_na + s_blod_30_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent")) 

plot_40 <- blod_40_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Original, -rowid) %>% mutate(Percent = "40%") 
plotl_40 <- l_blod_40_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))
plots_40 <- s_blod_40_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))
plotall_40 <- (l_blod_40_na + s_blod_40_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))

plot_50 <- blod_50_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Original, -rowid) %>% mutate(Percent = "50%") 
plotl_50 <- l_blod_50_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent"))
plots_50 <- s_blod_50_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent")) 
plotall_50 <- (l_blod_50_na + s_blod_50_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent"))

org <- rbind(plot_10,
        plot_20,
        plot_30,
        plot_40,
        plot_50) %>% rename(Value = Original) %>% 
  mutate(Compare = "Original") %>% 
  left_join(., LODall, by = c("POP", "Percent"))

plotall <- rbind(plotl_10,
      plots_10,
      plotall_10,
      plotl_20,
      plots_20,
      plotall_20,
      plotl_30,
      plots_30,
      plotall_30, 
      plotl_40,
      plots_40,
      plotall_40,
      plotl_50,
      plots_50,
      plotall_50)
```

```{r}
plotall %>% 
  drop_na(.) %>% 
  mutate(above_lod = ifelse(Value > LOD, 1, 0)) %>%
  group_by(Compare, Percent) %>% 
  summarise(above = sum(above_lod),
            total = n()) %>% 
  mutate(above_prop = above/total) %>% 
  select(-above, -total) %>% 
  kable(.)

rbind(plots_10,
      plots_20,
      plots_30,
      plots_40,
      plots_50) %>% 
  drop_na(.) %>% 
  group_by(Compare, Percent) %>% 
  summarise(Min = min (Value),
            Ave = mean(Value),
            Max = max(Value)) %>% kable(.)
```

### Correlation

```{r}
cor(as.matrix(blod_50_na), use = "complete.obs", method = "spearman")
cor(as.matrix(l_blod_50_na), use = "complete.obs", method = "spearman")
cor(as.matrix(s_blod_50_na), use = "complete.obs", method = "spearman")
```

### Viz

```{r}
plotall %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  #filter(Compare != "Original") %>% 
  # with and without Original
  mutate(Compare = fct_relevel(Compare, "Low Rank Solution",
                            "Sparse Solution",
                            "Model Prediction",
                            "Original")) %>% 
  ggplot(aes(x = POP, y = Value)) + 
  geom_jitter(aes(color = Compare), alpha = 0.1, width = 0.3, height = 0) + 
  theme_bw() +
  geom_point(aes(y = LOD), shape = 3, size = 0.5) +
  facet_wrap(.~Percent) +
  labs(x = "POP", 
       y = "Solution Value",
       title = "Values <LOD") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, hjust = 1))

plotall %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  filter(Compare != "Original") %>% 
  # with and without Original
  mutate(Compare = fct_relevel(Compare, "Low Rank Solution",
                            "Sparse Solution",
                            "Model Prediction")) %>% 
  ggplot(aes(x = POP, y = Value)) + 
  geom_jitter(aes(color = Compare), alpha = 0.1, width = 0.3, height = 0) + 
  theme_bw() +
  geom_point(aes(y = LOD), shape = 3, size = 0.5) +
  facet_wrap(.~Percent) +
  labs(x = "POP", 
       y = "Solution Value",
       title = "Values <LOD") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
plotall %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  mutate(Value_SD = Value - LOD) %>%
  filter(Compare != "Sparse Solution") %>% 
  ggplot(aes(x = Value)) + 
  geom_density(aes(fill = Compare, color = Compare), alpha = 0.25) + 
  theme_bw() +
  facet_wrap(.~Percent, scales = "free") +
  labs(x = "Solution Value", 
       y = "Density",
       title = "Values <LOD") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, hjust = 1))
```

