---
title: "Compare PCA w/ NA"
author: "Lizzy Gibson"
date: "6/09/2020"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    toc_depth: 5
---

```{r setup, include=FALSE}
require("knitr")
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(scipen = 999)
library(R.matlab)
library(tidyverse)
library(gridExtra)
library(Matrix)
library(matconv)
library(patchwork)
library(janitor)
library(ggcorrplot)
library(ggfortify)  
library(factoextra)
library(knitr)
library(haven)
library(rlist)
library(mvtnorm)
library(reshape2)
library(GGally)
library(grDevices)
library(pcpr)
```

```{r, scores}
# Simulate independent scores
set.seed(1988)
scores <- exp(rnorm(100))

# Simulate 1 pattern
pattern <- t(c(1,1,1,1,1,1,0,0,0,0))

# Add noise
noise <- matrix(NA, nrow = 100, ncol = 10)
seeds <- 1:10
for (i in 1:length(seeds)) {
  set.seed(seeds[i])
  noise[,i] <- exp(rnorm(100, mean = 0, sd = 1))
}

# Multiply scores by pattern
sim_all <- as_tibble((scores %*% pattern) + noise)
#summary(sim_all)
sim_all[sim_all < 0] <- 0 # non-negative
sim_all <- as_tibble(scale(sim_all, center = FALSE, 
                           scale = apply(sim_all, 2, sd, na.rm = TRUE))) # standardize do not center
sim_all_pca <- as_tibble(scale(sim_all, center = TRUE, 
                           scale = FALSE)) # standardize do not center
```

```{r, neg}
# Create version with 10% lowest values for each variable as below the LOD
mix_data_lod_10_sqrt2 <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .10), (quantile(V1, probs = .10)/sqrt(2)), V1)) %>% as.matrix()

# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20_sqrt2 <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .20), (quantile(V1, probs = .20)/sqrt(2)), V1)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30_sqrt2 <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .30), (quantile(V1, probs = .30)/sqrt(2)), V1)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40_sqrt2 <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .40), (quantile(V1, probs = .40)/sqrt(2)), V1)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50_sqrt2 <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .50), (quantile(V1, probs = .50)/sqrt(2)), V1)) %>% as.matrix()

# Create version with 10% lowest values for each variable as below the LOD
mix_data_lod_10_sqrt2_pca <- sim_all_pca %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .10), (quantile(V1, probs = .10)/sqrt(2)), V1)) %>% as.matrix()

# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20_sqrt2_pca <- sim_all_pca %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .20), (quantile(V1, probs = .20)/sqrt(2)), V1)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30_sqrt2_pca <- sim_all_pca %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .30), (quantile(V1, probs = .30)/sqrt(2)), V1)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40_sqrt2_pca <- sim_all_pca %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .40), (quantile(V1, probs = .40)/sqrt(2)), V1)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50_sqrt2_pca <- sim_all_pca %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .50), (quantile(V1, probs = .50)/sqrt(2)), V1)) %>% as.matrix()

# LODs
delta10 <- c(quantile(sim_all$V1, probs = 0.10), rep(0, times = 9))

delta20 <- c(quantile(sim_all$V1, probs = 0.20), rep(0, times = 9))

delta30 <- c(quantile(sim_all$V1, probs = 0.30), rep(0, times = 9))

delta40 <- c(quantile(sim_all$V1, probs = 0.40), rep(0, times = 9))

delta50 <- c(quantile(sim_all$V1, probs = 0.50), rep(0, times = 9))

mix_data_lod_10_na <- sim_all_pca %>%
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .10), NA, V1)) %>% as.matrix()
  
# Create version with 20% lowest value below the LOD
mix_data_lod_20_na <- sim_all_pca %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .20), NA, V1)) %>% as.matrix()

# Create version with 30% lowest value below the LOD
mix_data_lod_30_na <- sim_all_pca %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .30), NA, V1)) %>% as.matrix()

# Create version with 40% lowest value below the LOD
mix_data_lod_40_na <- sim_all_pca %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .40), NA, V1)) %>% as.matrix()

# Create version with 50% lowest value below the LOD
mix_data_lod_50_na <- sim_all_pca %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .50), NA, V1)) %>% as.matrix()
```

## PCA w/ LOD/sqrt2

```{r}
mix <- as.matrix(sim_all)
mix_pca <- as.matrix(sim_all_pca)

pca_0  <- prcomp(mix)
pca_10 <- prcomp(mix_data_lod_10_sqrt2)
pca_20 <- prcomp(mix_data_lod_20_sqrt2)
pca_30 <- prcomp(mix_data_lod_30_sqrt2)
pca_40 <- prcomp(mix_data_lod_40_sqrt2)
pca_50 <- prcomp(mix_data_lod_50_sqrt2)
```

### Predicted Values

```{r}
# Create mean vector for un-centering
sim_means_sqrt2 <- apply(sim_all, 2, mean)
mix_10_means_sqrt2 <- apply(mix_data_lod_10_sqrt2, 2, mean)
mix_20_means_sqrt2 <- apply(mix_data_lod_20_sqrt2, 2, mean)
mix_30_means_sqrt2 <- apply(mix_data_lod_30_sqrt2, 2, mean)
mix_40_means_sqrt2 <- apply(mix_data_lod_40_sqrt2, 2, mean)
mix_50_means_sqrt2 <- apply(mix_data_lod_50_sqrt2, 2, mean)
```

```{r, echo = TRUE}
rep.row<-function(x,n){
  matrix(rep(x,each=n),nrow=n)
}

pca_pred_0  <- pca_0$x[,1:5] %*% t(pca_0$rotation)[1:5,]   + rep.row(sim_means_sqrt2, 100)
pca_pred_10 <- pca_10$x[,1:5] %*% t(pca_10$rotation)[1:5,] + rep.row(mix_10_means_sqrt2, 100)
pca_pred_20 <- pca_20$x[,1:5] %*% t(pca_20$rotation)[1:5,] + rep.row(mix_20_means_sqrt2, 100)
pca_pred_30 <- pca_30$x[,1:5] %*% t(pca_30$rotation)[1:5,] + rep.row(mix_30_means_sqrt2, 100)
pca_pred_40 <- pca_40$x[,1:5] %*% t(pca_40$rotation)[1:5,] + rep.row(mix_40_means_sqrt2, 100)
pca_pred_50 <- pca_50$x[,1:5] %*% t(pca_50$rotation)[1:5,] + rep.row(mix_50_means_sqrt2, 100)
```

```{r, tp_lod2, include=FALSE}
pred_sim <- sim_all %>% 
  mutate(id = 1:100) %>% 
  pivot_longer(cols = V1:V10,
               names_to = "Variable",
               values_to = "Simulated")

pred_sim_pca <- sim_all_pca %>% 
  mutate(id = 1:100) %>% 
  pivot_longer(cols = V1:V10,
               names_to = "Variable",
               values_to = "Simulated")

add_lods <- as_tibble(rbind(c("0%",0), 
      c("10%", quantile(mix[,1], .10)), 
      c("20%", quantile(mix[,1], .20)),
      c("30%", quantile(mix[,1], .30)), 
      c("40%", quantile(mix[,1], .40)),
      c("50%", quantile(mix[,1], .50)))) %>% rename(Percent = 1, LOD = 2) %>% 
  mutate(LOD = as.numeric(LOD),
         Variable = "V1")

add_lods_pca <- as_tibble(rbind(c("0%",min(mix_pca[,1])-0.0001), 
      c("10%", quantile(mix_pca[,1], .10)), 
      c("20%", quantile(mix_pca[,1], .20)),
      c("30%", quantile(mix_pca[,1], .30)), 
      c("40%", quantile(mix_pca[,1], .40)),
      c("50%", quantile(mix_pca[,1], .50)))) %>% rename(Percent = 1, LOD = 2) %>% 
  mutate(LOD = as.numeric(LOD),
         Variable = "V1")

pca_pred <- (pca_pred_0) %>% as_tibble() %>% mutate(Percent = "0%") %>% 
  rbind(., (pca_pred_10) %>% as_tibble() %>% mutate(Percent = "10%")) %>% 
  rbind(., (pca_pred_20) %>% as_tibble() %>% mutate(Percent = "20%")) %>% 
  rbind(., (pca_pred_30) %>% as_tibble() %>% mutate(Percent = "30%")) %>% 
  rbind(., (pca_pred_40) %>% as_tibble() %>% mutate(Percent = "40%")) %>% 
  rbind(., (pca_pred_50) %>% as_tibble() %>% mutate(Percent = "50%")) %>%
  mutate(id = rep(1:100, 6)) %>% 
  pivot_longer(cols = V1:V10,
               names_to = "Variable",
               values_to = "Predicted") %>% 
  left_join(., pred_sim, by = c("id", "Variable")) %>% 
  left_join(., add_lods, by = c("Percent", "Variable")) %>% 
  replace_na(list(LOD = 0)) %>% 
  mutate(Value = ifelse(Simulated < LOD, "< LOD", "> LOD"),
         Method = "PCA w/ LOD/sqrt2")
```

## PCA w/ NA

```{r}
# Covariance
cov0 <- cov(mix_pca, use = "pairwise.complete.obs")

values0 <- eigen(cov0)$values
vectors0 <- eigen(cov0)$vectors # loadings

mixt <- t(mix_pca)

colnames(vectors0) <- paste0("PC", 1:10)

full <- as_tibble(cbind(mixt, vectors0))
colnames(full)[1:100] <- paste0("person", 1:100)

scores0r <- matrix(NA, nrow = nrow(mix), ncol = ncol(mix))
for (i in 1:100) {
  p1 <- paste0("person", i)
  model <- lm(as.formula(paste(p1, "~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10")), data = full)
  scores0r[i,] <- as.data.frame(model$coefficient) %>% t()
  }
```

### Same steps with NA

```{r}
# Covariance
cov10 <- cov(mix_data_lod_10_na, use = "pairwise.complete.obs")

# Eigen decomposition of covariance
values10 <- eigen(cov10)$values
vectors10 <- eigen(cov10)$vectors # loadings

mix10t <- t(mix_data_lod_10_na)
colnames(vectors10) <- paste0("PC", 1:10)

full10 <- as_tibble(cbind(mix10t, vectors10))
colnames(full10)[1:100] <- paste0("person", 1:100)

scores10r <- matrix(NA, nrow = nrow(mix), ncol = ncol(mix))
for (i in 1:100) {
  p1 <- paste0("person", i)
  model <- lm(as.formula(paste(p1, "~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10")), data = full10)
  scores10r[i,] <- as.data.frame(model$coefficient) %>% t()
  }
```

```{r}
# Covariance
cov20 <- cov(mix_data_lod_20_na, use = "pairwise.complete.obs")

# Eigen decomposition of covariance
values20 <- eigen(cov20)$values
vectors20 <- eigen(cov20)$vectors # loadings

mix20t <- t(mix_data_lod_20_na)
colnames(vectors20) <- paste0("PC", 1:10)

full20 <- as_tibble(cbind(mix20t, vectors20))
colnames(full20)[1:100] <- paste0("person", 1:100)

scores20r <- matrix(NA, nrow = nrow(mix), ncol = ncol(mix))
for (i in 1:100) {
  p1 <- paste0("person", i)
  model <- lm(as.formula(paste(p1, "~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10")), data = full20)
  scores20r[i,] <- as.data.frame(model$coefficient) %>% t()
  }
```

```{r}
# Covariance
cov30 <- cov(mix_data_lod_30_na, use = "pairwise.complete.obs")

# Eigen decomposition of covariance
values30 <- eigen(cov30)$values
vectors30 <- eigen(cov30)$vectors # loadings

mix30t <- t(mix_data_lod_30_na)
colnames(vectors30) <- paste0("PC", 1:10)

full30 <- as_tibble(cbind(mix30t, vectors30))
colnames(full30)[1:100] <- paste0("person", 1:100)

scores30r <- matrix(NA, nrow = nrow(mix), ncol = ncol(mix))
for (i in 1:100) {
  p1 <- paste0("person", i)
  model <- lm(as.formula(paste(p1, "~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10")), data = full30)
  scores30r[i,] <- as.data.frame(model$coefficient) %>% t()
  }
```

```{r}
# Covariance
cov40 <- cov(mix_data_lod_40_na, use = "pairwise.complete.obs")

# Eigen decomposition of covariance
values40 <- eigen(cov40)$values
vectors40 <- eigen(cov40)$vectors # loadings

mix40t <- t(mix_data_lod_40_na)
colnames(vectors40) <- paste0("PC", 1:10)

full40 <- as_tibble(cbind(mix40t, vectors40))
colnames(full40)[1:100] <- paste0("person", 1:100)

scores40r <- matrix(NA, nrow = nrow(mix), ncol = ncol(mix))
for (i in 1:100) {
  p1 <- paste0("person", i)
  model <- lm(as.formula(paste(p1, "~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10")), data = full40)
  scores40r[i,] <- as.data.frame(model$coefficient) %>% t()
  }
```

#### 50%

```{r, echo=TRUE}
# Covariance
cov50 <- cov(mix_data_lod_50_na, use = "pairwise.complete.obs")

# Eigen decomposition of covariance
values50 <- eigen(cov50)$values
vectors50 <- eigen(cov50)$vectors # loadings

mix50t <- t(mix_data_lod_50_na)
colnames(vectors50) <- paste0("PC", 1:10)

full50 <- as_tibble(cbind(mix50t, vectors50))
colnames(full50)[1:100] <- paste0("person", 1:100)

scores50r <- matrix(NA, nrow = nrow(mix), ncol = ncol(mix))
for (i in 1:100) {
  p1 <- paste0("person", i)
  model <- lm(as.formula(paste(p1, "~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10")), data = full50)
  scores50r[i,] <- as.data.frame(model$coefficient) %>% t()
  }
```

### Predicted Values

```{r, echo = TRUE}
pca_pred_0_na  <- scores0r[,1:5] %*% t(vectors0)[1:5,]
pca_pred_10_na <- scores10r[,1:5] %*% t(vectors10)[1:5,]
pca_pred_20_na <- scores20r[,1:5] %*% t(vectors20)[1:5,]
pca_pred_30_na <- scores30r[,1:5] %*% t(vectors30)[1:5,]
pca_pred_40_na <- scores40r[,1:5] %*% t(vectors40)[1:5,]
pca_pred_50_na <- scores50r[,1:5] %*% t(vectors50)[1:5,]
```

```{r, tp_lod, include=FALSE}
pca_pred_na <- (pca_pred_0_na) %>% as_tibble() %>% mutate(Percent = "0%") %>% 
  rbind(., (pca_pred_10_na) %>% as_tibble() %>% mutate(Percent = "10%")) %>% 
  rbind(., (pca_pred_20_na) %>% as_tibble() %>% mutate(Percent = "20%")) %>% 
  rbind(., (pca_pred_30_na) %>% as_tibble() %>% mutate(Percent = "30%")) %>% 
  rbind(., (pca_pred_40_na) %>% as_tibble() %>% mutate(Percent = "40%")) %>% 
  rbind(., (pca_pred_50_na) %>% as_tibble() %>% mutate(Percent = "50%")) %>%
  mutate(id = rep(1:100, 6)) %>% 
  pivot_longer(cols = V1:V10,
               names_to = "Variable",
               values_to = "Predicted") %>% 
  left_join(., pred_sim_pca, by = c("id", "Variable")) %>% 
  left_join(., add_lods_pca, by = c("Percent", "Variable")) %>% 
  mutate(LOD = ifelse(is.na(LOD), min(Simulated), LOD)) %>% 
  # replace_na(list(LOD = 0)) %>%
  mutate(Value = ifelse(Simulated < LOD, "< LOD", "> LOD"),
         Method = "PCA w/ NA")
```

## Metrics

```{r, pred_all}
all_pred <- rbind(pca_pred, pca_pred_na)
```

### X - L - S

* X = simulated dataset
* L = low rank solution matrix
* S = sparse solution matrix

```{r}
all_pred %>%
  mutate(l2 = (Simulated - Predicted)^2,
         l1 = abs(Simulated - Predicted)) %>%
  group_by(Percent, Method) %>% 
           summarise(Fro = sqrt(sum(l2))/sqrt(sum(Simulated^2)),
                     l1 = sqrt(sum(l1))/sqrt(sum(Simulated)),
                     linf = max(l1)/max(Simulated)) %>% 
  ggplot(aes(x = Percent, y = Fro, group = Method, color = Method)) + 
  geom_point() + geom_path() + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(X-L-S) / norm(X)",
       title = "Relative Prediction Error")

all_pred %>%
  mutate(l2 = (Simulated - Predicted)^2) %>%
  group_by(Percent, Method) %>% 
           summarise(l2 = mean(l2)) %>% 
  ggplot(aes(x = Percent, y = l2, group = Method, color = Method)) + 
  geom_point() + geom_path() + theme_bw() +
  labs(x = "Percent Below LOD", y = "mean((X-L-S)^2)",
       title = "MSE")
```

### Values \<LOD vs \>LOD

* Values \> and \< LOD stratified
* Sum of low rank and sparse solution matrices (L \+ S) compared to simulated data (X)

```{r}
all_pred %>% 
  mutate(l2 = (Simulated - Predicted)^2) %>% 
  group_by(Percent, Method, Value) %>% 
           summarise(Fro = sqrt(sum(l2))/sqrt(sum(Simulated^2))) %>%
  ggplot(aes(x = Percent, y = Fro, group = interaction(Method, Value), color = Method)) + 
  geom_point() + geom_path(aes(linetype = Value)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "norm(X-L-S) / norm(X)",
       title = "Relative Error in Values < LOD & > LOD")
```



