---
title: "PCA w/ NA"
author: "Lizzy Gibson"
date: "7/09/2020"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    toc_depth: 5
---

```{r setup, include=FALSE}
require("knitr")
opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
options(scipen = 999)
library(nlme)
library(lme4)
library(R.matlab)
library(tidyverse)
library(gridExtra)
library(Matrix)
library(matlib)
library(matconv)
library(patchwork)
library(janitor)
library(ggcorrplot)
library(ggfortify)  
library(factoextra)
library(knitr)
library(haven)
library(rlist)
library(mvtnorm)
library(reshape2)
library(GGally)
library(grDevices)
```

## Simulate

Independent scores.  
```{r, scores}
set.seed(1988)
scores <- exp(rnorm(100))
```

One pattern.  
```{r}
pattern <- t(c(1,1,1,1,1,1,0,0,0,0))
```

Add noise (sparse matrix).  
```{r}
noise <- matrix(NA, nrow = 100, ncol = 10)
seeds <- 1:10
for (i in 1:length(seeds)) {
  set.seed(seeds[i])
  noise[,i] <- exp(rnorm(100, mean = 0, sd = 1))
}
```

Multiply scores by pattern.
```{r}
sim_all <- as_tibble((scores %*% pattern) + noise)
sim_all[sim_all < 0] <- 0 # non-negative
sim_all <- as_tibble(scale(sim_all, center = FALSE, 
                           scale = apply(sim_all, 2, sd, na.rm = TRUE))) # standardize do not center
```

Add NA.  
```{r, neg}
summary(sim_all)
sim_all <- scale(sim_all, center = TRUE, scale = apply(sim_all, 2, sd, na.rm = TRUE)) %>% as_tibble()
summary(sim_all)

mix_data_lod_10_na <- sim_all %>%
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .10), NA, V1)) %>% as.matrix()
  
# Create version with 20% lowest value below the LOD
mix_data_lod_20_na <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .20), NA, V1)) %>% as.matrix()

# Create version with 30% lowest value below the LOD
mix_data_lod_30_na <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .30), NA, V1)) %>% as.matrix()

# Create version with 40% lowest value below the LOD
mix_data_lod_40_na <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .40), NA, V1)) %>% as.matrix()

# Create version with 50% lowest value below the LOD
mix_data_lod_50_na <- sim_all %>% 
  mutate(V1 = ifelse(V1 < quantile(V1, probs = .50), NA, V1)) %>% as.matrix()
```

## PCA w/ no NA
```{r}
mix <- as.matrix(sim_all)

pca_0 <- prcomp(mix)
plot(pca_0)
```

Get covariance.  
```{r}
# Covariance
cov0 <- cov(mix, use = "pairwise.complete.obs")
```

Eigen decomposition of covariance.  
Eigenvalues = (singular values)^2.  
Eigenvectors = right singular vectors.  
```{r}
svd(mix)
pca_0$rotation
values0 <- eigen(cov0)$values
vectors0 <- eigen(cov0)$vectors # loadings
```

Put vectors in same direction as PCA results.  
```{r}
# cor(pca_0$rotation, vectors0)
# vectors0[,1:2] <- -vectors0[,1:2]
# vectors0[,3] <- -vectors0[,3]
# vectors0[,5] <- -vectors0[,5]
# vectors0[,8:9] <- -vectors0[,8:9]
```

Scores = data %*% loadings.  
Doesn't work with missing data.  
```{r}
scores0 <- mix %*% vectors0
```

Scores are the same.
```{r}
norm(pca_0$x - scores0, "F")/norm(pca_0$x, "F")
```

Loadings are the same.  
```{r}
norm(pca_0$rotation - vectors0, "F")/norm(pca_0$rotation, "F")
```

Get scores through linear regression.  
y = a + b * x   
person = 0 + score*loading  
```{r}
mixt <- t(mix)

colnames(vectors0) <- paste0("PC", 1:10)

full <- as_tibble(cbind(mixt, vectors0))
colnames(full)[1:100] <- paste0("person", 1:100)

scores0r <- matrix(NA, nrow = nrow(mix), ncol = ncol(mix))
for (i in 1:100) {
  p1 <- paste0("person", i)
  model <- lm(as.formula(paste(p1, "~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10")), data = full)
  scores0r[i,] <- as.data.frame(model$coefficient) %>% t()
  }
```

Regression scores are the same.  
```{r}
norm(pca_0$x - scores0r, "F")/norm(pca_0$x, "F")
norm(scores0 - scores0r, "F")/norm(scores0, "F")
```

Get scores through MULTILEVEL linear regression.  
y = a + b * x   
person = 0 + score*loading  

```{r}
full_long <- full %>%
  mutate(variable = paste0("V",1:10)) %>% 
  dplyr::select(variable, everything()) %>% 
  pivot_longer(cols = person1:person100) %>% 
  mutate(name = str_sub(name, 7, -1)) %>%
  mutate(name = as.integer(name),
         variable = as.factor(variable))
  
full_longer <- full_long %>% 
  pivot_longer(PC1:PC10,
               names_to = "PC",
               values_to = "pred")

# lmer(value ~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10 +
#       (0 + PC1 + PC2 + PC3 + PC4 || name), data = full_long)

# Random effect for all 10 PC crashes R
# Random effect for first 6 PC works fine
# Random effect for first 7 PC takes 10 min
# Random effect for first 8 PC does not converge
# lme_out <- lme(value ~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10,
#     random = ~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 | name,
#     data = full_long)
# 
# fixed <- varIdent(c("PC1" = values0[1], "PC2" = values0[2],
#                                     "PC3" = values0[3], "PC4" = values0[4],
#                                     "PC5" = values0[5], "PC6" = values0[6],
#                                     "PC7" = values0[7], "PC8" = values0[8],
#                                     "PC9" = values0[9], "PC10" = values0[10]))
# 
# (fix <- Initialize(fixed, full_long))

# head(Orthodont)
# val <- c("10"=1.10,"14"=1.14)
# vf <- varIdent(value=val, form=~1|age, fixed=c("12"=1.12))
# vfi <- Initialize(vf,Orthodont)
# vfi
# 
# lme_ou <- lme(value ~ 0 + PC,
#     random = ~ 0 + PC | name,
#     data = full_longer)

# lme_pc <- lme(fixed = value ~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10,
#     random = ~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 | name,
#     weights = varIdent(fixed = list(PC1 = values0[1], PC2 = values0[2],
#                                     PC3 = values0[3], PC4 = values0[4],
#                                     PC5 = values0[5], PC6 = values0[6],
#                                     PC7 = values0[7], PC8 = values0[8],
#                                     PC9 = values0[9], PC10 = values0[10])),
#     data = full_long)
# 
# summary(lme_out)
# summary(lme_pc)
# 
# lme_out$varFix
# 
# head(ranef(lme_out))
# head(ranef(lme_pc))
# head(pca_0$x)
```

## Same steps with NA

### 10%
```{r}
# Covariance
cov10 <- cov(mix_data_lod_10_na, use = "pairwise.complete.obs")

# Eigen decomposition of covariance
values10 <- eigen(cov10)$values
vectors10 <- eigen(cov10)$vectors # loadings

# Put vectors in same direction as PCA results
# cor(pca_0$rotation, vectors10)
# vectors10[,1:3] <- -vectors10[,1:3]
# vectors10[,6:9] <- -vectors10[,6:9]
```

Are loadings are the same?
```{r}
norm(pca_0$rotation - vectors10, "F")/norm(pca_0$rotation, "F")
```

Scores through linear regression.  
```{r}
mix10t <- t(mix_data_lod_10_na)
colnames(vectors10) <- paste0("PC", 1:10)

full10 <- as_tibble(cbind(mix10t, vectors10))
colnames(full10)[1:100] <- paste0("person", 1:100)

scores10r <- matrix(NA, nrow = nrow(mix), ncol = ncol(mix))
for (i in 1:100) {
  p1 <- paste0("person", i)
  model <- lm(as.formula(paste(p1, "~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10")), data = full10)
  scores10r[i,] <- as.data.frame(model$coefficient) %>% t()
  }
```

Are regression scores the same?
```{r}
norm(pca_0$x - scores10r, "F")/norm(pca_0$x, "F")
norm(pca_0$x[,1:9] - scores10r[,1:9], "F")/norm(pca_0$x[,1:9], "F")
```

Still some NA scores.  
```{r}
lm(person3 ~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10, data = full10)
mix_data_lod_10_na[3,]
```

Loadings are not the same.  
```{r}
norm(pca_0$rotation - vectors10, "F")/norm(pca_0$rotation, "F")
```

### 20%

```{r}
# Covariance
cov20 <- cov(mix_data_lod_20_na, use = "pairwise.complete.obs")

# Eigen decomposition of covariance
values20 <- eigen(cov20)$values
vectors20 <- eigen(cov20)$vectors # loadings

# Put vectors in same direction as PCA results
# cor(pca_0$rotation, vectors20)
# vectors20[,1:3] <- -vectors20[,1:3]
# vectors20[,8] <- -vectors20[,8]
# vectors20[,10] <- -vectors20[,10]
```

Scores through linear regression.  
```{r}
mix20t <- t(mix_data_lod_20_na)
colnames(vectors20) <- paste0("PC", 1:10)

full20 <- as_tibble(cbind(mix20t, vectors20))
colnames(full20)[1:100] <- paste0("person", 1:100)

scores20r <- matrix(NA, nrow = nrow(mix), ncol = ncol(mix))
for (i in 1:100) {
  p1 <- paste0("person", i)
  model <- lm(as.formula(paste(p1, "~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10")), data = full20)
  scores20r[i,] <- as.data.frame(model$coefficient) %>% t()
  }
```

Are regression scores the same?
```{r}
norm(pca_0$x[,1:9] - scores20r[,1:9], "F")/norm(pca_0$x[,1:9], "F")
```

Loadings are not the same.  
```{r}
norm(pca_0$rotation - vectors20, "F")/norm(pca_0$rotation, "F")
```

### 30%

```{r}
# Covariance
cov30 <- cov(mix_data_lod_30_na, use = "pairwise.complete.obs")

# Eigen decomposition of covariance
values30 <- eigen(cov30)$values
vectors30 <- eigen(cov30)$vectors # loadings

# Put vectors in same direction as PCA results
# cor(pca_0$rotation, vectors30)
# vectors30[,1] <- -vectors30[,1]
# vectors30[,9:10] <- -vectors30[,9:10]
```

Scores through linear regression.  
```{r}
mix30t <- t(mix_data_lod_30_na)
colnames(vectors30) <- paste0("PC", 1:10)

full30 <- as_tibble(cbind(mix30t, vectors30))
colnames(full30)[1:100] <- paste0("person", 1:100)

scores30r <- matrix(NA, nrow = nrow(mix), ncol = ncol(mix))
for (i in 1:100) {
  p1 <- paste0("person", i)
  model <- lm(as.formula(paste(p1, "~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10")), data = full30)
  scores30r[i,] <- as.data.frame(model$coefficient) %>% t()
  }
```

Are regression scores the same?
```{r}
norm(pca_0$x[,1:9] - scores30r[,1:9], "F")/norm(pca_0$x[,1:9], "F")
```

Loadings are not the same.  
```{r}
norm(pca_0$rotation - vectors30, "F")/norm(pca_0$rotation, "F")
```

### 40%

```{r}
# Covariance
cov40 <- cov(mix_data_lod_40_na, use = "pairwise.complete.obs")

# Eigen decomposition of covariance
values40 <- eigen(cov40)$values
vectors40 <- eigen(cov40)$vectors # loadings

# Put vectors in same direction as PCA results
# cor(pca_0$rotation, vectors40)
# vectors40[,1:3] <- -vectors40[,1:3]
# vectors40[,7] <- -vectors40[,7]
# vectors40[,10] <- -vectors40[,10]
```

Scores through linear regression.  
```{r}
mix40t <- t(mix_data_lod_40_na)
colnames(vectors40) <- paste0("PC", 1:10)

full40 <- as_tibble(cbind(mix40t, vectors40))
colnames(full40)[1:100] <- paste0("person", 1:100)

scores40r <- matrix(NA, nrow = nrow(mix), ncol = ncol(mix))
for (i in 1:100) {
  p1 <- paste0("person", i)
  model <- lm(as.formula(paste(p1, "~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10")), data = full40)
  scores40r[i,] <- as.data.frame(model$coefficient) %>% t()
  }
```

Are regression scores the same?
```{r}
norm(pca_0$x[,1:9] - scores40r[,1:9], "F")/norm(pca_0$x[,1:9], "F")
```

Loadings are not the same.  
```{r}
norm(pca_0$rotation - vectors40, "F")/norm(pca_0$rotation, "F")
```

### 50%

```{r}
# Covariance
cov50 <- cov(mix_data_lod_50_na, use = "pairwise.complete.obs")

# Eigen decomposition of covariance
values50 <- eigen(cov50)$values
vectors50 <- eigen(cov50)$vectors # loadings

# Put vectors in same direction as PCA results
# cor(pca_0$rotation, vectors50)
vectors50[,1:3] <- -vectors50[,1:3]
vectors50[,5:10] <- -vectors50[,5:10]
```

Scores through linear regression.  
```{r}
mix50t <- t(mix_data_lod_50_na)
colnames(vectors50) <- paste0("PC", 1:10)

full50 <- as_tibble(cbind(mix50t, vectors50))
colnames(full50)[1:100] <- paste0("person", 1:100)

scores50r <- matrix(NA, nrow = nrow(mix), ncol = ncol(mix))
for (i in 1:100) {
  p1 <- paste0("person", i)
  model <- lm(as.formula(paste(p1, "~ 0 + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10")), data = full50)
  scores50r[i,] <- as.data.frame(model$coefficient) %>% t()
  }
```

Are regression scores the same?
```{r}
norm(pca_0$x[,1:9] - scores50r[,1:9], "F")/norm(pca_0$x[,1:9], "F")
```

Loadings are not the same.  
```{r}
norm(pca_0$rotation - vectors50, "F")/norm(pca_0$rotation, "F")
```

## PCA Predicted Values

```{r}
# Create mean vector for un-centering
sim_means_na <- apply(sim_all, 2, mean)
mix_10_means_na <- apply(mix_data_lod_10_na, 2, mean, na.rm = TRUE)
mix_20_means_na <- apply(mix_data_lod_20_na, 2, mean, na.rm = TRUE)
mix_30_means_na <- apply(mix_data_lod_30_na, 2, mean, na.rm = TRUE)
mix_40_means_na <- apply(mix_data_lod_40_na, 2, mean, na.rm = TRUE)
mix_50_means_na <- apply(mix_data_lod_50_na, 2, mean, na.rm = TRUE)
```

```{r, echo = TRUE}
# prcomp centers, does not scale
# need to UNCENTER predictions to compare
# REMOVE SV

rep.row<-function(x,n){
  matrix(rep(x,each=n),nrow=n)
}

pca_pred_0_na  <- scores0r[,1:5] %*% t(vectors0)[1:5,]
pca_pred_10_na <- scores10r[,1:5] %*% t(vectors10)[1:5,]
pca_pred_20_na <- scores20r[,1:5] %*% t(vectors20)[1:5,]
pca_pred_30_na <- scores30r[,1:5] %*% t(vectors30)[1:5,]
pca_pred_40_na <- scores40r[,1:5] %*% t(vectors40)[1:5,]
pca_pred_50_na <- scores50r[,1:5] %*% t(vectors50)[1:5,]
```

```{r, tp_lod, include=FALSE}
pred_sim_na <- sim_all %>% 
  mutate(id = 1:100) %>% 
  pivot_longer(cols = V1:V10,
               names_to = "Variable",
               values_to = "Simulated")

add_lods <- as_tibble(rbind(c("0%",0), 
      c("10%", quantile(mix[,1], .10)), 
      c("20%", quantile(mix[,1], .20)),
      c("30%", quantile(mix[,1], .30)), 
      c("40%", quantile(mix[,1], .40)),
      c("50%", quantile(mix[,1], .50)))) %>% rename(Percent = 1, LOD = 2) %>% 
  mutate(LOD = as.numeric(LOD),
         Variable = "V1")

pca_pred_na <- (pca_pred_0_na) %>% as_tibble() %>% mutate(Percent = "0%") %>% 
  rbind(., (pca_pred_10_na) %>% as_tibble() %>% mutate(Percent = "10%")) %>% 
  rbind(., (pca_pred_20_na) %>% as_tibble() %>% mutate(Percent = "20%")) %>% 
  rbind(., (pca_pred_30_na) %>% as_tibble() %>% mutate(Percent = "30%")) %>% 
  rbind(., (pca_pred_40_na) %>% as_tibble() %>% mutate(Percent = "40%")) %>% 
  rbind(., (pca_pred_50_na) %>% as_tibble() %>% mutate(Percent = "50%")) %>%
  mutate(id = rep(1:100, 6)) %>% 
  pivot_longer(cols = V1:V10,
               names_to = "Variable",
               values_to = "Predicted") %>% 
  left_join(., pred_sim_na, by = c("id", "Variable")) %>% 
  left_join(., add_lods, by = c("Percent", "Variable")) %>% 
  replace_na(list(LOD = 0)) %>% 
  mutate(Value = ifelse(Simulated < LOD, "< LOD", "> LOD"),
         Method = "PCA w/ NA")
```

### X - L - S

* X = simulated dataset
* L = low rank solution matrix
* S = sparse solution matrix

```{r}
pca_pred_na %>%
  mutate(l2 = (Simulated - Predicted)^2) %>%
  group_by(Percent, Method) %>% 
           summarise(Fro = sqrt(sum(l2))/sqrt(sum(Simulated^2))) %>% 
  ggplot(aes(x = Percent, y = Fro, group = Method, color = Method)) + 
  geom_point() + geom_path() + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(X-L-S) / norm(X)",
       title = "Relative Prediction Error")
```

### Values \<LOD vs \>LOD

* Values \> and \< LOD stratified
* Sum of low rank and sparse solution matrices (L \+ S) compared to simulated data (X)

```{r}
pca_pred_na %>% 
  mutate(l2 = (Simulated - Predicted)^2) %>% 
  group_by(Percent, Method, Value) %>% 
           summarise(Fro = sqrt(sum(l2))/sqrt(sum(Simulated^2))) %>%
  ggplot(aes(x = Percent, y = Fro, group = interaction(Method, Value), color = Method)) + 
  geom_point() + geom_path(aes(linetype = Value)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "norm(X-L-S) / norm(X)",
       title = "Relative Error in Values < LOD & > LOD")
```
