---
title: "One Pattern Sims"
author: "Lizzy Gibson"
date: "6/09/2020"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    toc_depth: 5
---

```{r setup, include=FALSE}
require("knitr")
opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
options(scipen = 999)
library(R.matlab)
library(tidyverse)
library(gridExtra)
library(Matrix)
library(matconv)
library(patchwork)
library(janitor)
library(ggcorrplot)
library(ggfortify)  
library(factoextra)
library(knitr)
library(haven)
library(rlist)
library(mvtnorm)
library(reshape2)
library(GGally)
library(grDevices)
library(pcpr)
```

## Simulate

```{r, scores}
# Simulate independent scores
set.seed(1988)
#scores <- exp(rnorm(100))
n = 100
scores <- matrix(exp(rnorm(n)), nrow = n, ncol = 1)
# Simulate 1 pattern
pattern <- t(c(1,1,1,1,1,1,0,0,0,0))

noise <- 
  mvtnorm::rmvnorm(n, mean = rep(0, 10), sigma = diag(.1, 10, 10)) %>% 
  exp()

# Multiply scores by pattern
sim_all_check <- as_tibble((scores %*% pattern) + noise)
sim_all_check[sim_all_check < 0] <- 0 # non-negative
sim_all_check <- as_tibble(scale(sim_all_check, center = FALSE, 
                           scale = apply(sim_all_check, 2, sd, na.rm = TRUE))) # standardize do not center
#sim_all_check
```

```{r, jeff_functions}
create_lod_mat = function(df, quant) {
  df %>%
    mutate(V1 = ifelse(V1 < quantile(V1, probs = quant), -1, V1)) %>% 
    as.matrix()
}

create_lod_imp_mat = function(df, quant) {
  df = 
    df %>%
    mutate(V1 = ifelse(V1 < quantile(V1, probs = quant), NA, V1))
  mod = lm(V1 ~ V2 + V3 + V4 + V5, data = df)
  
  df %>%
    modelr::add_predictions(mod) %>% 
    mutate(
      V1 = case_when(
        is.na(V1) ~ pred,
        TRUE      ~ V1
      )) %>% 
    select(-pred) %>% 
    as.matrix()
}

create_lod_sqrt2_mat = function(df, quant) {
  df %>%
    mutate(V1 = ifelse(
      V1 < quantile(V1, probs = quant), 
      (quantile(V1, probs = quant)/sqrt(2)), V1)) %>%
    as.matrix()
}

create_v1_missing_ind = function(mat) {
  tibble(below_lod = (mat[,1] == -1))
}

col_residual = function(fit, target_mat) {
  if (is.matrix(fit)) {
    as_tibble(target_mat - fit) %>% 
      select(resid = V1)
  }
  
  else {
#    as_tibble(target_mat - fit$L - fit$S) %>% 
    as_tibble(target_mat - fit$L ) %>% 
      select(resid = V1)
  }
}
```

```{r}
lod_mat_df = 
  tibble(
    quant = seq(0, .5, by = .1)
  ) %>% 
  mutate(
    lod_mat =     map(quant, ~create_lod_mat(df = sim_all_check, quant = .x)), # -1 for pcp
    lod_imp_mat = map(quant, ~create_lod_imp_mat(df = sim_all_check, quant = .x)),
    lod_sq2_mat = map(quant, ~create_lod_sqrt2_mat(df = sim_all_check, quant = .x)),
    delta =       map(quant, ~c(quantile(sim_all_check$V1, probs = .x), rep(0, times = 9))),
    below_lod   = map(lod_mat, create_v1_missing_ind))
```

```{r}
m <- nrow(sim_all_check)
p <- ncol(sim_all_check)

lambda_mix <- 1/sqrt(m)
mu_mix <- sqrt(p/(2*log(m*p)))

fit_df = 
  lod_mat_df %>% 
  pivot_longer(
    lod_mat:lod_sq2_mat,
    names_to = "mechanism",
    values_to = "mat"
  ) %>% 
  mutate(
    pca_jg = map(mat, pca_jg),
    pcp = map2(mat, delta, ~pcpr::pcp_lod(.x, lambda_mix, mu_mix, .y)),
  )

fit_pca <- fit_df %>% 
  filter(mechanism == "lod_sq2_mat") %>% 
  mutate(
    pca_lz = map(mat, pca_lz)) %>% 
  select(quant, mechanism, pca_lz)

pca_lz <- fit_pca %>% 
  mutate(pca_lz = map(pca_lz, as_tibble),
         number = 1:nrow(.)) %>% 
  unnest(pca_lz) %>% 
  group_by(number) %>% 
  mutate(id = 1:n()) %>% 
  pivot_longer(grep("V", colnames(.)),
               values_to = "Predicted",
               names_to = "Variable") %>% 
  mutate(model = "pca_reg")
```

```{r}
target = scores %*% pattern
# target = as.matrix(sim_all_check)

pred_lz <- fit_df %>% 
  mutate(pcp_l = map(pcp, function(x) as_tibble(x$L)),
         pcp_s = map(pcp, function(x) as_tibble(x$S)),
         pcp_pred = map2(pcp_l, pcp_s, function(x,y) x + y),
         number = 1:nrow(.)) %>% #number is lod*mechanism
  pivot_longer(c(pca_jg, pcp_l, pcp_s, pcp_pred),
               names_to = "model") %>% 
  mutate(value = map(value, as_tibble)) %>% 
  unnest(value) %>% 
  group_by(number, model) %>% 
  mutate(id = 1:n()) %>% 
  select(-pcp, -delta, -mat, -below_lod) %>% 
  pivot_longer(grep("V", colnames(.)),
               values_to = "Predicted",
               names_to = "Variable")

pred_lz <- full_join(pca_lz, pred_lz)
```

### Predicted Values

```{r, tp_lod}
pred_sim_check <- sim_all_check %>% 
  mutate(id = 1:100) %>% 
  pivot_longer(cols = V1:V10,
               names_to = "Variable",
               values_to = "Simulated")

pred_target_check <- target %>% as_tibble() %>% 
  mutate(id = 1:100) %>% 
  pivot_longer(cols = V1:V10,
               names_to = "Variable",
               values_to = "Target") %>% 
  full_join(., pred_sim_check)
```

## Metrics

```{r}
all_pred2 <-  full_join(pred_target_check, pred_lz) %>% 
  select(Percent = quant, everything()) %>% 
  filter(mechanism != "lod_imp_mat") %>%
  filter(!(model == "pca_jg" & mechanism == "lod_mat")) %>% 
  mutate(Method = case_when(model == "pca_reg" ~ "pca_lz",
                            model == "pca_jg" & mechanism == "lod_sq2_mat" ~ "pca_jg",
                            model == "pcp_l" & mechanism == "lod_mat"~ "pcp_lod_l",
                            model == "pcp_s" & mechanism == "lod_mat"~ "pcp_lod_s",
                            model == "pcp_l" & mechanism == "lod_sq2_mat"~ "pcp_sq2_l",
                            model == "pcp_s" & mechanism == "lod_sq2_mat"~ "pcp_sq2_s",
                            model == "pcp_pred" & mechanism == "lod_mat"~ "pcp_lod_pred",
                            model == "pcp_pred" & mechanism == "lod_sq2_mat"~ "pcp_sq2_pred")) %>% 
  select(-mechanism, -model)

all_pred2 %>% 
  #filter(Method == "pcp_pred" & mechanism == "lod_mat") %>% 
  #filter(Method == "pcp_pred" & mechanism == "lod_sq2_mat") %>% 
  filter(Method == "pca_lz") %>% 
  #filter(Method == "pca_reg") %>% 
  arrange(Percent, Method)
```

### X - L - S

* X = simulated dataset
* L = low rank solution matrix
* S = sparse solution matrix

```{r}
all_pred2 %>%
  filter(Method != "pca_lz") %>% 
  filter(!grepl("_s$", Method)) %>% 
  mutate(l2 = (Simulated - Predicted)^2,
         l1 = abs(Simulated - Predicted)) %>%
  group_by(Percent, Method) %>% 
           summarise(Fro = sqrt(sum(l2))/sqrt(sum(Simulated^2)),
                     l1 = sqrt(sum(l1))/sqrt(sum(Simulated)),
                     linf = max(l1)/max(Simulated)) %>% 
  ggplot(aes(x = Percent, y = Fro, color = Method)) + 
  geom_point() + geom_path() + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(X-L-S) / norm(X)",
       title = "Relative Prediction Error")

all_pred2 %>%
  filter(Method != "pca_lz") %>% 
  filter(!grepl("_s$", Method)) %>% 
  mutate(l2 = (Target - Predicted)^2,
         l1 = abs(Target - Predicted)) %>%
  group_by(Percent, Method) %>% 
           summarise(Fro = sqrt(sum(l2))/sqrt(sum(Target^2)),
                     l1 = sqrt(sum(l1))/sqrt(sum(Target)),
                     linf = max(l1)/max(Simulated)) %>% 
  ggplot(aes(x = Percent, y = Fro, color = Method)) + 
  geom_point() + geom_path() + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(X-L-S) / norm(X)",
       title = "Relative Prediction Error")
```

### Values \<LOD vs \>LOD

* Values \> and \< LOD stratified
* Sum of low rank and sparse solution matrices (L \+ S) compared to simulated data (X)

```{r}
all_pred %>% 
  mutate(l2 = (Simulated - Predicted)^2,
         l1 = abs(Simulated - Predicted)) %>% 
  group_by(Percent, Method, Value) %>% 
           summarise(Fro = sqrt(sum(l2))/sqrt(sum(Simulated^2)),
                     l1 = sqrt(sum(l1))/sqrt(sum(Simulated)),
                     linf = max(l1)/max(Simulated)) %>%
  ggplot(aes(x = Percent, y = Fro, group = interaction(Method, Value), color = Method)) + 
  geom_point() + geom_path(aes(linetype = Value)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "norm(X-L-S) / norm(X)",
       title = "Relative Error in Values < LOD & > LOD")
```

```{r}
pcp_pred %>% 
  mutate(l2 = (Simulated - Predicted)^2,
         l1 = abs(Simulated - Predicted)) %>% 
  group_by(Percent, Method, Value) %>% 
           summarise(Fro = sqrt(sum(l2))/sqrt(sum(Simulated^2)),
                     l1 = sqrt(sum(l1))/sqrt(sum(Simulated)),
                     linf = max(l1)/max(Simulated)) %>%
  ggplot(aes(x = Percent, y = Fro, group = interaction(Method, Value), color = Method)) + 
  geom_point() + geom_path(aes(linetype = Value)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "norm(X-L-S) / norm(X)",
       title = "Relative Error in Values < LOD & > LOD")
```

