---
title: "PCP w/ <LOD Penalty"
subtitle: "Boston air pollution example"
author: "Lizzy Gibson"
date: "7/16/2019"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: 'hide'
---

```{r setup, include=FALSE}
require("knitr")
opts_chunk$set(echo = TRUE)
options(scipen = 999)
library(R.matlab)
library(tidyverse)
library(gridExtra)
library(Matrix)
```

## Data

* 20 air pollution species
* 2,478 days (~6.7 years)

```{r}
# Read air pollution data
mixture <- readMat("./Data/mixtures_data.mat")

mixture_data <- as.data.frame(mixture) %>% as_tibble() %>% 
  select(Al, As, Ba, bc, Br, Ca, Cl,
         Cr, Cu, Fe, K,  Mn,  Ni,  Pb,  S,  Se,  Si,
         Ti,  V, Zn) %>% 
  drop_na()

mixture_data
```

## Steps

1. Run Jingkai's PCP version on original air pollution data (MATLAB).
2. Artificially assign increasing LOD's (10%, 20%, 30%, 40%, and 50% <LOD) to separate test datasets (R).
3. Run Jingkai's PCP version on all 5 <LOD datasets, save L and S matrices from each (MATLAB).
4. Evaluate relative error -- compare results from <LOD datasets with original (R).

## Create \<LOD Datasets

```{r}
# Create version with 10% lowest values for each variable as below the LOD
mix_data_lod_10 <- mixture_data %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .10), -1, .))

#write_csv(as_tibble(mix_data_lod_10), "./Below_LOD/R/BLOD_airpol_data/mix_data_lod_10.csv")

# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20 <- mixture_data %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .20), -1, .))

#write_csv(as_tibble(mix_data_lod_20), "./Below_LOD/R/BLOD_airpol_data/mix_data_lod_20.csv")

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30 <- mixture_data %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .30), -1, .))

#write_csv(as_tibble(mix_data_lod_30), "./Below_LOD/R/BLOD_airpol_data/mix_data_lod_30.csv")

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40 <- mixture_data %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .40), -1, .))

#write_csv(as_tibble(mix_data_lod_40), "./Below_LOD/R/BLOD_airpol_data/mix_data_lod_40.csv")

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50 <- mixture_data %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .50), -1, .))

#write_csv(as_tibble(mix_data_lod_50), "./Below_LOD/R/BLOD_airpol_data/mix_data_lod_50.csv")
```

## Read MATLAB Output

Run PCP on separate datasets in MATLAB, load results L and S matrices from file.

*Low Rank Matrices*
```{r}
L_lod0 <- readMat("./Below_LOD/MATLAB/LOD_demo_output/lowrank_lod0.mat") %>% as.data.frame() %>% as_tibble() %>% as.matrix()
L_lod10 <- readMat("./Below_LOD/MATLAB/LOD_demo_output/lowrank_lod10.mat") %>% as.data.frame() %>% as_tibble() %>% as.matrix()
L_lod20 <- readMat("./Below_LOD/MATLAB/LOD_demo_output/lowrank_lod20.mat") %>% as.data.frame() %>% as_tibble() %>% as.matrix()
L_lod30 <- readMat("./Below_LOD/MATLAB/LOD_demo_output/lowrank_lod30.mat") %>% as.data.frame() %>% as_tibble() %>% as.matrix()
L_lod40 <- readMat("./Below_LOD/MATLAB/LOD_demo_output/lowrank_lod40.mat") %>% as.data.frame() %>% as_tibble() %>% as.matrix()
L_lod50 <- readMat("./Below_LOD/MATLAB/LOD_demo_output/lowrank_lod50.mat") %>% as.data.frame() %>% as_tibble() %>% as.matrix()
```

*Sparse Matrices*
```{r}
S_lod0 <- readMat("./Below_LOD/MATLAB/LOD_demo_output/sparse_lod0.mat") %>% as.data.frame() %>% as_tibble() %>% as.matrix()
S_lod10 <- readMat("./Below_LOD/MATLAB/LOD_demo_output/sparse_lod10.mat") %>% as.data.frame() %>% as_tibble() %>% as.matrix()
S_lod20 <- readMat("./Below_LOD/MATLAB/LOD_demo_output/sparse_lod20.mat") %>% as.data.frame() %>% as_tibble() %>% as.matrix()
S_lod30 <- readMat("./Below_LOD/MATLAB/LOD_demo_output/sparse_lod30.mat") %>% as.data.frame() %>% as_tibble() %>% as.matrix()
S_lod40 <- readMat("./Below_LOD/MATLAB/LOD_demo_output/sparse_lod40.mat") %>% as.data.frame() %>% as_tibble() %>% as.matrix()
S_lod50 <- readMat("./Below_LOD/MATLAB/LOD_demo_output/sparse_lod50.mat") %>% as.data.frame() %>% as_tibble() %>% as.matrix()
```

## Compare Results

### X - L - S

```{r}
X <- as.matrix(mixture_data)

F_norm <- as_tibble(cbind(lod0 = norm((X - L_lod0 - S_lod0), type = "F")/norm((X), type = "F"),
      lod10 = norm((X - L_lod10 - S_lod10), type = "F")/norm((X), type = "F"),
      lod20 = norm((X - L_lod20 - S_lod20), type = "F")/norm((X), type = "F"),
      lod30 = norm((X - L_lod30 - S_lod30), type = "F")/norm((X), type = "F"),
      lod40 = norm((X - L_lod40 - S_lod40), type = "F")/norm((X), type = "F"),
      lod50 = norm((X - L_lod50 - S_lod50), type = "F")/norm((X), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Both")

F_norm_s <- as_tibble(cbind(lod0 = norm((X - S_lod0), type = "F")/norm((X), type = "F"),
      lod10 = norm((X - S_lod10), type = "F")/norm((X), type = "F"),
      lod20 = norm((X - S_lod20), type = "F")/norm((X), type = "F"),
      lod30 = norm((X - S_lod30), type = "F")/norm((X), type = "F"),
      lod40 = norm((X - S_lod40), type = "F")/norm((X), type = "F"),
      lod50 = norm((X - S_lod50), type = "F")/norm((X), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse")

F_norm_l <- as_tibble(cbind(lod0 = norm((X - L_lod0), type = "F")/norm((X), type = "F"),
      lod10 = norm((X - L_lod10), type = "F")/norm((X), type = "F"),
      lod20 = norm((X - L_lod20), type = "F")/norm((X), type = "F"),
      lod30 = norm((X - L_lod30), type = "F")/norm((X), type = "F"),
      lod40 = norm((X - L_lod40), type = "F")/norm((X), type = "F"),
      lod50 = norm((X - L_lod50), type = "F")/norm((X), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank")

#pdf("new_penalty_Fnorm.pdf")
F_norm %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point() + geom_path(aes(group = 1)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "Relative Error\n(norm(X-L-S) / norm(X))",
       title = "PCP with <LOD Penalty")
#dev.off()

rbind(F_norm, F_norm_l, F_norm_s) %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point(aes(color = Matrix)) + geom_path(aes(group = Matrix, color = Matrix)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "Relative Error\n(norm(X - .) / norm(X))")
```

### Individual Solution Matrices

```{r}
L_diff <- as_tibble(cbind(lod0 = norm((L_lod0 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      lod10 = norm((L_lod10 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      lod20 = norm((L_lod20 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      lod30 = norm((L_lod30 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      lod40 = norm((L_lod40 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      lod50 = norm((L_lod50 - L_lod0), type = "F")/norm((L_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank")

S_diff <- as_tibble(cbind(lod0 = norm((S_lod0 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      lod10 = norm((S_lod10 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      lod20 = norm((S_lod20 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      lod30 = norm((S_lod30 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      lod40 = norm((S_lod40 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      lod50 = norm((S_lod50 - S_lod0), type = "F")/norm((S_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse")

#pdf("new_penalty_LandS.pdf")
rbind(L_diff, S_diff) %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point(aes(color = Matrix)) + geom_path(aes(group = Matrix, color = Matrix)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "Relative Error in Solution Matrices\n(norm(difference) / norm(lod0))",
       title = "PCP with <LOD Penalty")
#dev.off()
```

### SVD low rank vs. no \<LOD

```{r}
# Extract right singular vectors from each low rank solution matrix
V_lod0  <-  svd(L_lod0)$v[,1:5]
V_lod10 <- svd(L_lod10)$v[,1:5]
V_lod20 <- svd(L_lod20)$v[,1:5]
V_lod30 <- svd(L_lod30)$v[,1:5]
V_lod40 <- svd(L_lod40)$v[,1:5]
V_lod50 <- svd(L_lod50)$v[,1:5]

dim(V_lod0)
dim(svd(L_lod0)$v)

V_diff <- as_tibble(cbind(lod0 =norm((V_lod0 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      lod10 =norm((V_lod10 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      lod20 =norm((V_lod20 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      lod30 =norm((V_lod30 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      lod40 =norm((V_lod40 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      lod50 =norm((V_lod50 - V_lod0), type = "F")/norm((V_lod0), type = "F"))) %>% 
  gather(percent_blod, norm)

#pdf("new_penalty_singular_vectors.pdf")
V_diff %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point() + geom_path(aes(group = 1)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "Relative Error in Low-Rank Solution Singular Vectors\n(norm(SV - SV_lod0) / norm(SV_lod0))",
       title = "PCP with <LOD Penalty")
#dev.off()
```

### SVD low rank vs. original

```{r}
# Extract right singular vectors from original matrix
V_orig <- svd(X)$v[,1:5]

V_diff2 <- as_tibble(cbind(lod0 =norm((V_lod0 - V_orig), type = "F")/norm((V_orig), type = "F"),
      lod10 =norm((V_lod10 - V_orig), type = "F")/norm((V_orig), type = "F"),
      lod20 =norm((V_lod20 - V_orig), type = "F")/norm((V_orig), type = "F"),
      lod30 =norm((V_lod30 - V_orig), type = "F")/norm((V_orig), type = "F"),
      lod40 =norm((V_lod40 - V_orig), type = "F")/norm((V_orig), type = "F"),
      lod50 =norm((V_lod50 - V_orig), type = "F")/norm((V_orig), type = "F"))) %>% 
  gather(percent_blod, norm)

#pdf("new_penalty_singular_vectors_vs_original.pdf")
V_diff2 %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point() + geom_path(aes(group = 1)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "Relative Error in Low-Rank Solution Singular Vectors\n(norm(SV - SV_orig) / norm(SV_orig))",
       title = "PCP with <LOD Penalty")
#dev.off()
```

### Values \<LOD vs \>LOD

* Are values \<LOD estimated more poorly than those \>LOD? Are \<LOD driving the increased error?
* Rescale by range/variance of values \<LOD.
    * Wider range -> more error

```{r}
# This one is all zeros bc nothing is <LOD to begin with
tf_lod_0 <- mixture_data %>% 
  mutate_all(~ifelse(. == -1, TRUE, FALSE))
l_blod_0 <- as.matrix(tf_lod_0*L_lod0)
s_blod_0 <- as.matrix(tf_lod_0*S_lod0)
true_0 <- as.matrix(mixture_data*tf_lod_0)


tf_lod_10 <- mix_data_lod_10 %>% 
  mutate_all(~ifelse(. == -1, TRUE, FALSE))
# T/F dataset, T = <LOD
l_blod_10 <- as.matrix(tf_lod_10*L_lod10)
s_blod_10 <- as.matrix(tf_lod_10*S_lod10)
# keep <LOD predictions, >LOD predictions are zero
# Solution L matrix with >LOD values as zero
true_10 <- as.matrix(mixture_data*tf_lod_10)
# keep 10% lowest true values, push >LOD values to zero
# Original matrix with only bottom 10percent, all >LOD set to zero

tf_lod_20 <- mix_data_lod_20 %>% 
  mutate_all(~ifelse(. == -1, TRUE, FALSE))
l_blod_20 <- as.matrix(tf_lod_20*L_lod20)
s_blod_20 <- as.matrix(tf_lod_20*S_lod20)
true_20 <- as.matrix(mixture_data*tf_lod_20)

tf_lod_30 <- mix_data_lod_30 %>% 
  mutate_all(~ifelse(. == -1, TRUE, FALSE))
l_blod_30 <- as.matrix(tf_lod_30*L_lod30)
s_blod_30 <- as.matrix(tf_lod_30*S_lod30)
true_30 <- as.matrix(mixture_data*tf_lod_30)

tf_lod_40 <- mix_data_lod_40 %>% 
  mutate_all(~ifelse(. == -1, TRUE, FALSE))
l_blod_40 <- as.matrix(tf_lod_40*L_lod40)
s_blod_40 <- as.matrix(tf_lod_40*S_lod40)
true_40 <- as.matrix(mixture_data*tf_lod_40)

tf_lod_50 <- mix_data_lod_50 %>% 
  mutate_all(~ifelse(. == -1, TRUE, FALSE))
l_blod_50 <- as.matrix(tf_lod_50*L_lod50)
s_blod_50 <- as.matrix(tf_lod_50*S_lod50)
true_50 <- as.matrix(mixture_data*tf_lod_50) 

#Subtract true values and divide by norm of true
less_diff <- as_tibble(cbind(lod0 = norm((true_0 - l_blod_0 - s_blod_0), type = "F"), #/norm((true_0), type = "F"),
      lod10 = norm((true_10 - l_blod_10 - s_blod_10), type = "F")/norm((true_10), type = "F"),
      lod20 = norm((true_20 - l_blod_20 - s_blod_20), type = "F")/norm((true_20), type = "F"),
      lod30 = norm((true_30 - l_blod_30 - s_blod_30), type = "F")/norm((true_30), type = "F"),
      lod40 = norm((true_40 - l_blod_40 - s_blod_40), type = "F")/norm((true_40), type = "F"),
      lod50 = norm((true_50 - l_blod_50 - s_blod_50), type = "F")/norm((true_50), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "< LOD")
```

```{r}
above_lod_0 <- mixture_data %>% 
  mutate_all(~ifelse(. == -1, FALSE, TRUE))
l_above_blod_0 <- as.matrix(above_lod_0*L_lod0)
s_above_blod_0 <- as.matrix(above_lod_0*S_lod0)
above_true_0 <- as.matrix(mixture_data*above_lod_0)

above_lod_10 <- mix_data_lod_10 %>% 
  mutate_all(~ifelse(. == -1, FALSE, TRUE))
# T/F dataset, T = >LOD
l_above_blod_10 <- as.matrix(above_lod_10*L_lod10)
s_above_blod_10 <- as.matrix(above_lod_10*S_lod10)
# keep >LOD predictions, BLOD predictions are zero
above_true_10 <- as.matrix(mixture_data*above_lod_10)
# keep 10% lowest true values, push >LOD values to zero

above_lod_20 <- mix_data_lod_20 %>% 
  mutate_all(~ifelse(. == -1, FALSE, TRUE))
l_above_blod_20 <- as.matrix(above_lod_20*L_lod20)
s_above_blod_20 <- as.matrix(above_lod_20*S_lod20)
above_true_20 <- as.matrix(mixture_data*above_lod_20)

above_lod_30 <- mix_data_lod_30 %>% 
  mutate_all(~ifelse(. == -1, FALSE, TRUE))
l_above_blod_30 <- as.matrix(above_lod_30*L_lod30)
s_above_blod_30 <- as.matrix(above_lod_30*S_lod30)
above_true_30 <- as.matrix(mixture_data*above_lod_30)

above_lod_40 <- mix_data_lod_40 %>% 
  mutate_all(~ifelse(. == -1, FALSE, TRUE))
l_above_blod_40 <- as.matrix(above_lod_40*L_lod40)
s_above_blod_40 <- as.matrix(above_lod_40*S_lod40)
above_true_40 <- as.matrix(mixture_data*above_lod_40)

above_lod_50 <- mix_data_lod_50 %>% 
  mutate_all(~ifelse(. == -1, FALSE, TRUE))
l_above_blod_50 <- as.matrix(above_lod_50*L_lod50)
s_above_blod_50 <- as.matrix(above_lod_50*S_lod50)
above_true_50 <- as.matrix(mixture_data*above_lod_50) 
summary(above_lod_50)
```

```{r}
#divide by true values
above_diff <- as_tibble(cbind(
  lod0  = norm((above_true_0  - l_above_blod_0  - s_above_blod_0),  type = "F")/norm(above_true_0,  type = "F"),
  lod10 = norm((above_true_10 - l_above_blod_10 - s_above_blod_10), type = "F")/norm(above_true_10, type = "F"),
  lod20 = norm((above_true_20 - l_above_blod_20 - s_above_blod_20), type = "F")/norm(above_true_20, type = "F"),
  lod30 = norm((above_true_30 - l_above_blod_30 - s_above_blod_30), type = "F")/norm(above_true_30, type = "F"),
  lod40 = norm((above_true_40 - l_above_blod_40 - s_above_blod_40), type = "F")/norm(above_true_40, type = "F"),
  lod50 = norm((above_true_50 - l_above_blod_50 - s_above_blod_50), type = "F")/norm(above_true_50, type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "> LOD")

#pdf("new_penalty_above_below.pdf")
rbind(above_diff, less_diff) %>% 
  ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point(aes(color = Values)) + geom_path(aes(group = Values, color = Values)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "Relative Error in Values < LOD & > LOD\n(norm(X-L-S) / norm(X))",
       title = "PCP with <LOD Penalty")
#dev.off()
```

### SVD compare scores - low rank vs. no \<LOD

```{r}
# Extract left singular vectors from each low rank solution matrix
u_lod0  <-  svd(L_lod0)$u
u_lod10 <- svd(L_lod10)$u
u_lod20 <- svd(L_lod20)$u
u_lod30 <- svd(L_lod30)$u
u_lod40 <- svd(L_lod40)$u
u_lod50 <- svd(L_lod50)$u

u_diff <- as_tibble(cbind(lod0 =norm((u_lod0 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      lod10 =norm((u_lod10 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      lod20 =norm((u_lod20 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      lod30 =norm((u_lod30 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      lod40 =norm((u_lod40 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      lod50 =norm((u_lod50 - u_lod0), type = "F")/norm((u_lod0), type = "F"))) %>% 
  gather(percent_blod, norm)

#pdf("new_penalty_score_vectors.pdf")
u_diff %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point() + geom_path(aes(group = 1)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "Relative Error in Low-Rank Solution Singular Vectors\n(norm(SV - SV_lod0) / norm(SV_lod0))",
       title = "PCP with <LOD Penalty")
#dev.off()
```

### SVD compare scores - low rank vs. original

```{r}
# Extract right singular vectors from original matrix
u_orig <- svd(X)$u

u_diff2 <- as_tibble(cbind(lod0 =norm((u_lod0 - u_orig), type = "F")/norm((u_orig), type = "F"),
      lod10 =norm((u_lod10 - u_orig), type = "F")/norm((u_orig), type = "F"),
      lod20 =norm((u_lod20 - u_orig), type = "F")/norm((u_orig), type = "F"),
      lod30 =norm((u_lod30 - u_orig), type = "F")/norm((u_orig), type = "F"),
      lod40 =norm((u_lod40 - u_orig), type = "F")/norm((u_orig), type = "F"),
      lod50 =norm((u_lod50 - u_orig), type = "F")/norm((u_orig), type = "F"))) %>% 
  gather(percent_blod, norm)

#pdf("new_penalty_score_vectors_vs_original.pdf")
u_diff2 %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point() + geom_path(aes(group = 1)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "Relative Error in Low-Rank Solution Singular Vectors\n(norm(SV - SV_orig) / norm(SV_orig))",
       title = "PCP with <LOD Penalty")
#dev.off()
```

### SVD compare singular values - low rank vs. no \<LOD

```{r}
# Extract left singular vectors from each low rank solution matrix
d_lod0  <-  svd(L_lod0)$d
d_lod10 <- svd(L_lod10)$d
d_lod20 <- svd(L_lod20)$d
d_lod30 <- svd(L_lod30)$d
d_lod40 <- svd(L_lod40)$d
d_lod50 <- svd(L_lod50)$d
norm_vec <- function(x) sqrt(sum(x^2))

d_diff <- as_tibble(cbind(lod0 = norm_vec(d_lod0 - d_lod0)/norm_vec(d_lod0),
      lod10 = norm_vec(d_lod10 - d_lod0)/norm_vec(d_lod0),
      lod20 = norm_vec(d_lod20 - d_lod0)/norm_vec(d_lod0),
      lod30 = norm_vec(d_lod30 - d_lod0)/norm_vec(d_lod0),
      lod40 = norm_vec(d_lod40 - d_lod0)/norm_vec(d_lod0),
      lod50 = norm_vec(d_lod50 - d_lod0)/norm_vec(d_lod0))) %>% 
  gather(percent_blod, norm)

#pdf("new_penalty_sv.pdf")
d_diff %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point() + geom_path(aes(group = 1)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "Relative Error in Low-Rank Solution Singular Values\n(norm(SV - SV_lod0) / norm(SV_lod0))",
       title = "PCP with <LOD Penalty")
#dev.off()
```

### SVD compare singular values - low rank vs. original

```{r}
# Extract right singular vectors from original matrix
d_orig <- svd(X)$d

d_diff2 <- as_tibble(cbind(lod0 = norm_vec(d_lod0 - d_orig)/norm_vec(d_orig),
      lod10 =norm_vec(d_lod10 - d_orig)/norm_vec(d_orig),
      lod20 =norm_vec(d_lod20 - d_orig)/norm_vec(d_orig),
      lod30 =norm_vec(d_lod30 - d_orig)/norm_vec(d_orig),
      lod40 =norm_vec(d_lod40 - d_orig)/norm_vec(d_orig),
      lod50 =norm_vec(d_lod50 - d_orig)/norm_vec(d_orig))) %>% 
  gather(percent_blod, norm)

#pdf("new_penalty_sv_vs_original.pdf")
d_diff2 %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point() + geom_path(aes(group = 1)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "Relative Error in Low-Rank Solution Singular Values\n(norm(SV - SV_orig) / norm(SV_orig))",
       title = "PCP with <LOD Penalty")
#dev.off()
```

## Sanity Check

SVD results should produce original matrix solution.

```{r}
dim(svd(X)$u)
length(svd(X)$d)
dim(svd(X)$v)

# Does svd give v or v' ?
# Should = zero
norm((X - (svd(X)$u %*% diag(svd(X)$d) %*% t(svd(X)$v))), type = "F")
norm((X - (svd(X)$u %*% diag(svd(X)$d) %*% svd(X)$v)), type = "F")

svd_diff <- as_tibble(cbind(
      lod0  = norm((L_lod0 - (u_lod0  %*% diag(d_lod0)  %*% t(svd(L_lod0)$v))),  type = "F")/norm((L_lod0),  type = "F"),
      lod10 =norm((L_lod10 - (u_lod10 %*% diag(d_lod10) %*% t(svd(L_lod10)$v))), type = "F")/norm((L_lod10), type = "F"),
      lod20 =norm((L_lod20 - (u_lod20 %*% diag(d_lod20) %*% t(svd(L_lod20)$v))), type = "F")/norm((L_lod20), type = "F"),
      lod30 =norm((L_lod30 - (u_lod30 %*% diag(d_lod30) %*% t(svd(L_lod30)$v))), type = "F")/norm((L_lod30), type = "F"),
      lod40 =norm((L_lod40 - (u_lod40 %*% diag(d_lod40) %*% t(svd(L_lod40)$v))), type = "F")/norm((L_lod40), type = "F"),
      lod50 =norm((L_lod50 - (u_lod50 %*% diag(d_lod50) %*% t(svd(L_lod50)$v))), type = "F")/norm((L_lod50), type = "F"))) %>% 
  gather(percent_blod, norm)

# Basically zero
svd_diff %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point() + geom_path(aes(group = 1)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "Relative Error in Low-Rank SVD Solution",
       title = "PCP with <LOD Penalty")
```
