---
title: "<LOD Penalty PCP -- vary $\\lambda$ and $\\mu$"
author: "Lizzy Gibson"
date: "9/3/2019"
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_depth: 4
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
options(scipen = 999)
library(tidyverse)
library(janitor)
library(reshape2)
library(ggcorrplot)
library(ggfortify)  
library(gridExtra)
library(factoextra)
library(Matrix)
library(rlist)
library(ggrepel)
library(broom)
library(R.matlab)
library(pcpr)
```

## Read Data

Read Boston air pollution data.

```{r read}
# Read air pollution data
mixture <- readMat(here::here("Data/mixtures_data.mat"))

mix <- as.data.frame(mixture) %>% as_tibble() %>% 
  select(Al, As, Ba, bc, Br, Ca, Cl,
         Cr, Cu, Fe, K,  Mn,  Ni,  Pb,  S,  Se,  Si,
         Ti,  V, Zn) %>% 
  drop_na(.) %>% 
  as.matrix(.)

m <- nrow(mix)
n <- ncol(mix)

lambda_mix = 1/sqrt(m)
#This is the default lambda
```

## Vary $\mu$

Create function to output new low rank matrix, sparse matrix, singular values and rank of new low rank matrix, and $\lambda$ and $\mu$ parameters used

```{r mu_lam}
mu_value <- seq(0.01, 20, by = 0.5)
# Every mu > 3 has all 17 non-zero singular values.

make_L_mu_l <- function(mu){ 
  mixture_mu <- pcp_lod(mix, 1/sqrt(m), mu, 0)
  L <- mixture_mu$L
  S <- mixture_mu$S
  sv_diag <- svd(L)$d # singular values on new low rank matrix
  sv_count <- sum(sv_diag > 0.0001) # rank of new low rank matrix
  list(L = L, SV = sv_diag, S = S, Count = sv_count, Mu = mu, Lambda = 1/sqrt(m))
}
```

Loop over $\lambda$, $\mu$ pairs.

```{r looop, results = FALSE, cache = TRUE}
range_out <- map(.x = mu_value, ~make_L_mu_l(mu = .x))
```

### Changing Low Rank Matrix

Examine how rank of low rank matrix changes with varying $\lambda$ and $\mu$.

```{r rank_ml}
singular_value_count <- range_out %>% list.map(.[4]) %>% unlist() %>% 
  cbind(sv_count = ., mu = mu_value) %>% as_tibble() 
```

```{r rank2}
singular_value_count %>% summary()
```

```{r}
singular_value_count %>% 
  ggplot(aes(x = mu, y = sv_count)) +
  geom_point() + geom_line() +
  theme_bw() +
  labs(y = "Rank",
       x = expression(mu),
       title = expression(paste("Changing rank of low rank matrix with varying ", mu))) +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 70, hjust = 1))
```

### Changing Sparse Matrix

Examine how sparsity of sparse matrix changes with varying $\lambda$ and $\mu$.

```{r mu_sparse2}
sparse <- range_out %>% list.map(.[3])
# Extract all sparse matrices

loop.vector2 <- 1:length(mu_value)

cells <- nrow(mix)*ncol(mix)
prop_not_zero <- vector(length = length(mu_value))

for (i in loop.vector2) { # Loop over loop.vector2

 not_zeros <- sum(sparse[[i]]$S != 0)
  # Create proportion of non-zero values across all cells in sparse matrix
  prop_not_zero[i] <- not_zeros/cells
}

sparseness <- cbind(prop_not_zero, singular_value_count) %>% as_tibble()
```

```{r plot_sparse2}
sparseness %>% summary()
```

```{r}
sparseness %>% 
  ggplot(aes(x = mu, y = prop_not_zero)) +
  geom_point() + geom_line() +
  theme_bw() +
  labs(y = "Proportion Non-Zero",
       x = expression(mu),
       title = expression(paste("Changing sparsity of sparse matrix with varying ", mu))) +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 70, hjust = 1))
```

## Error

Each PCP creates a low rank L matrix and a sparse matrix that sum to the original D matrix with some error. To choose the best value for $\lambda$ and $\mu$, we add the L and S matrices to form D', then subtract D - D' to get an error matrix for each $\lambda$ and $\mu$ pair. We then take the RMSE of the low rank matrix and the F norm of each error matrix, divided by the norm of the original matrix, to get relative error.

```{r cv_both}
# low_rank and sparse are lists of L and S matrices for each 

loop.vector2 <- 1:length(mu_value)
rmse <- vector(length = length(mu_value))
rel_error <- vector(length = length(mu_value))
new_ml <- list()

low_rank_ml <- range_out %>% list.map(.[1])
sparse_ml <- range_out %>% list.map(.[3])

for (i in loop.vector2) { # Loop over loop.vector
  new_ml[[i]]  <- low_rank_ml[[i]]$L + sparse_ml[[i]]$S
  rmse[i]      <- sqrt(mean((mix - new_ml[[i]])^2))
  rel_error[i] <- norm((mix - new_ml[[i]]), type = "F")/norm(mix, type = "F")
  }

cv <- cbind(mu_value, rmse, rel_error) %>% as_tibble()
```

### Plot Error

```{r plot_both}
cv %>% summary()
```

Below is the cross-section at $\lambda = 1/\sqrt{n}$, same as only varying $\mu$.

```{r}
cv %>% 
  ggplot(aes(y = rmse, x = mu_value)) + 
  geom_point() + geom_line() +
  theme_bw() +
  labs(y = "Root Mean Squared Error",
       x = expression(mu),
       title = expression(paste("Changing RMSE with varying ", mu)))
```
