---
title: "Impute Zero: Increasing LOD in NHANES POPs"
author: "Lizzy Gibson"
date: "2/1/2020"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("tidyverse")
library(tidyverse)
#install.packages("janitor")
library(janitor)
#install.packages("ggcorrplot")
library(ggcorrplot)
#install.packages("ggfortify")
library(ggfortify)  
#install.packages("gridExtra")
library(gridExtra)
#install.packages("factoextra")
library(factoextra)
#install.packages("knitr")
library(knitr)

options(scipen = 999)
```

# Data Import and Cleaning

```{r data preping}
studypop <- read_csv(here::here("Data/studypop.csv")) %>% 
  clean_names() %>% 
  select(names(.)[grep("la", names(.))] ) %>% 
    na.omit(.)

#check dimensions of dataset
dim(studypop)

#summary statistics on dataset
summary(studypop)

# Scale bc way different ranges
mixture_data <- studypop %>% 
  mutate_all(scale, center = FALSE, scale = TRUE)

summary(mixture_data)
```

Probably don't want log.

```{r}
#create a new data frame with my.x and convert values for the predictor variables to its natural log.
#log.x <- data.frame(apply(studypop, 2, FUN = function(x) log(x))) %>%
 # setNames(paste(my.x, "log", sep = ".")) #add suffix 12 to the predictors' name

#check dimensions of dataset
#dim(log.x)

#summary statistics on dataset
#summary(log.x)
```

## Steps

1. Artificially assign increasing LOD's (10%, 20%, 30%, 40%, and 50% <LOD) to separate test datasets.
3. Run origina PCP (with zero imputed) on all 5 <LOD datasets, save L and S matrices from each.
4. Evaluate relative error -- compare results from <LOD datasets with PCP-LOD and original (imputed with LOD/sqrt(2).

## Create \<LOD Datasets

*Push values \<LOD to zero*

```{r}
# Create version with 10% lowest values for each variable as below the LOD
mix_data_lod_10 <- mixture_data %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .10), 0, .)) %>% as.matrix()

# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20 <- mixture_data %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .20), 0, .)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30 <- mixture_data %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .30), 0, .)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40 <- mixture_data %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .40), 0, .)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50 <- mixture_data %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .50), 0, .)) %>% as.matrix()
```

## Original PCP

```{r}
soft_thresholding <- function(v, lambda) {
  myzero <- matrix(data = 0, ncol = ncol(v), nrow = nrow(v))
  w <- sign(v) * pmax(abs(v) - lambda, myzero)
  w
} 

soft_thresholding_diag <- function(v, lambda) {
  myzero <- vector("numeric", length = length(v))
  w <- sign(v) * pmax(abs(v) - lambda, myzero)
  w
} 

singular_value_threshold <- function(M, lambda) {
  
  USV <- svd(M)
  U <- USV$u
  S <- USV$d
  V <- USV$v
    
  N <- U %*% diag(soft_thresholding_diag(S, lambda)) %*% t(V)
  
  v  <- sum(soft_thresholding_diag(S, lambda))
  
  svt <- list(N = N, v = v) 
  svt
}

original_pcp <- function(D, lambda, mu) {
  
  m <- nrow(D)
  n <- ncol(D)
  
  S <- matrix(0, nrow = m, ncol = n)
  L <- matrix(0, nrow = m, ncol = n)
  
  iter <- 0
  MAX_ITER <- 100
  done <- FALSE
  
  while (!done) {
    
    iter <- iter + 1
    
    svt <- singular_value_threshold((D - S), 1/mu)
    L <- svt[[1]] #svt$N
    v <- svt[[2]]
    
    S <- soft_thresholding((D - L), lambda/mu)
    
    obj <- v + lambda * sum(abs(S)) + (mu/2) * norm((D - L - S), type = "F")^2
    
    print(str_c(iter, " Obj: ", obj))
    
    if (iter >= MAX_ITER) {done <- TRUE}
    
  }
  list(L = L, S = S, Lambda = lambda, Mu = mu, obj_value = obj)
}
```

## Run PCP

Run ORIGINAL PCP on separate datasets.

```{r}
m <- nrow(mixture_data)
n <- ncol(mixture_data)

results_0  <- original_pcp(as.matrix(mixture_data), 1/sqrt(m), 1/sqrt(n))
results_10 <- original_pcp(mix_data_lod_10, 1/sqrt(m), 1/sqrt(n))
results_20 <- original_pcp(mix_data_lod_20, 1/sqrt(m), 1/sqrt(n))
results_30 <- original_pcp(mix_data_lod_30, 1/sqrt(m), 1/sqrt(n))
results_40 <- original_pcp(mix_data_lod_40, 1/sqrt(m), 1/sqrt(n))
results_50 <- original_pcp(mix_data_lod_50, 1/sqrt(m), 1/sqrt(n))

L_lod0 <- results_0[[1]]
S_lod0 <- results_0[[2]]
L_lod10 <- results_10[[1]]
S_lod10 <- results_10[[2]]
L_lod20 <- results_20[[1]]
S_lod20 <- results_20[[2]]
L_lod30 <- results_30[[1]]
S_lod30 <- results_30[[2]]
L_lod40 <- results_40[[1]]
S_lod40 <- results_40[[2]]
L_lod50 <- results_50[[1]]
S_lod50 <- results_50[[2]]
```


## Compare Results

## X - L - S

```{r}
X <- as.matrix(mixture_data)

F_norm <- as_tibble(cbind(lod0 = norm((X - L_lod0 - S_lod0), type = "F")/norm((X), type = "F"),
      lod10 = norm((X - L_lod10 - S_lod10), type = "F")/norm((X), type = "F"),
      lod20 = norm((X - L_lod20 - S_lod20), type = "F")/norm((X), type = "F"),
      lod30 = norm((X - L_lod30 - S_lod30), type = "F")/norm((X), type = "F"),
      lod40 = norm((X - L_lod40 - S_lod40), type = "F")/norm((X), type = "F"),
      lod50 = norm((X - L_lod50 - S_lod50), type = "F")/norm((X), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Both")

F_norm_s <- as_tibble(cbind(lod0 = norm((X - S_lod0), type = "F")/norm((X), type = "F"),
      lod10 = norm((X - S_lod10), type = "F")/norm((X), type = "F"),
      lod20 = norm((X - S_lod20), type = "F")/norm((X), type = "F"),
      lod30 = norm((X - S_lod30), type = "F")/norm((X), type = "F"),
      lod40 = norm((X - S_lod40), type = "F")/norm((X), type = "F"),
      lod50 = norm((X - S_lod50), type = "F")/norm((X), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse")

F_norm_l <- as_tibble(cbind(lod0 = norm((X - L_lod0), type = "F")/norm((X), type = "F"),
      lod10 = norm((X - L_lod10), type = "F")/norm((X), type = "F"),
      lod20 = norm((X - L_lod20), type = "F")/norm((X), type = "F"),
      lod30 = norm((X - L_lod30), type = "F")/norm((X), type = "F"),
      lod40 = norm((X - L_lod40), type = "F")/norm((X), type = "F"),
      lod50 = norm((X - L_lod50), type = "F")/norm((X), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank")

F_norm %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point() + geom_path(aes(group = 1)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "Relative Error\n(norm(X-L-S) / norm(X))")

rbind(F_norm, F_norm_l, F_norm_s) %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point(aes(color = Matrix)) + geom_path(aes(group = Matrix, color = Matrix)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "Relative Error\n(norm(X - .) / norm(X))")
```

## Individual Solution Matrices

```{r}
L_diff <- as_tibble(cbind(lod0 = norm((L_lod0 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      lod10 = norm((L_lod10 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      lod20 = norm((L_lod20 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      lod30 = norm((L_lod30 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      lod40 = norm((L_lod40 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      lod50 = norm((L_lod50 - L_lod0), type = "F")/norm((L_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank")

S_diff <- as_tibble(cbind(lod0 = norm((S_lod0 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      lod10 = norm((S_lod10 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      lod20 = norm((S_lod20 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      lod30 = norm((S_lod30 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      lod40 = norm((S_lod40 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      lod50 = norm((S_lod50 - S_lod0), type = "F")/norm((S_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse")

rbind(L_diff, S_diff) %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point(aes(color = Matrix)) + geom_path(aes(group = Matrix, color = Matrix)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "Relative Error in Solution Matrices\n(norm(difference) / norm(lod0))")
```

## PCA loadings

```{r}
# Extract right singular vectors from each low rank solution matrix
V_lod0  <-  prcomp(L_lod0)$rotation[,1:3]
V_lod10 <- prcomp(L_lod10)$rotation[,1:3]
V_lod20 <- prcomp(L_lod20)$rotation[,1:3]
V_lod30 <- prcomp(L_lod30)$rotation[,1:3]
V_lod40 <- prcomp(L_lod40)$rotation[,1:3]
V_lod50 <- prcomp(L_lod50)$rotation[,1:3]

V_diff <- as_tibble(cbind(lod0 =norm((V_lod0 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      lod10 =norm((V_lod10 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      lod20 =norm((V_lod20 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      lod30 =norm((V_lod30 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      lod40 =norm((V_lod40 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      lod50 =norm((V_lod50 - V_lod0), type = "F")/norm((V_lod0), type = "F"))) %>% 
  gather(percent_blod, norm)

V_diff %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point() + geom_path(aes(group = 1)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "Relative Error in Low-Rank Solution Singular Vectors\n(norm(SV - SV_lod0) / norm(SV_lod0))")
```

## PCA scores

```{r}
# Extract left singular vectors from each low rank solution matrix
u_lod0  <-  prcomp(L_lod0)$x[,1:3]
u_lod10 <- prcomp(L_lod10)$x[,1:3]
u_lod20 <- prcomp(L_lod20)$x[,1:3]
u_lod30 <- prcomp(L_lod30)$x[,1:3]
u_lod40 <- prcomp(L_lod40)$x[,1:3]
u_lod50 <- prcomp(L_lod50)$x[,1:3]

u_diff <- as_tibble(cbind(lod0 =norm((u_lod0 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      lod10 =norm((u_lod10 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      lod20 =norm((u_lod20 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      lod30 =norm((u_lod30 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      lod40 =norm((u_lod40 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      lod50 =norm((u_lod50 - u_lod0), type = "F")/norm((u_lod0), type = "F"))) %>% 
  gather(percent_blod, norm)

#pdf("edc_new_penalty_score_vectors.pdf")
u_diff %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point() + geom_path(aes(group = 1)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "Relative Error in Low-Rank Solution Singular Vectors\n(norm(SV - SV_lod0) / norm(SV_lod0))",
       title = "PCP w/ <LOD Penalty")
#dev.off()
```

## PCA singular values

```{r}
# Extract left singular vectors from each low rank solution matrix
d_lod0  <-  prcomp(L_lod0)$sdev[1:3]
d_lod10 <- prcomp(L_lod10)$sdev[1:3]
d_lod20 <- prcomp(L_lod20)$sdev[1:3]
d_lod30 <- prcomp(L_lod30)$sdev[1:3]
d_lod40 <- prcomp(L_lod40)$sdev[1:3]
d_lod50 <- prcomp(L_lod50)$sdev[1:3]
norm_vec <- function(x) sqrt(sum(x^2))

d_diff <- as_tibble(cbind(lod0 = norm_vec(d_lod0 - d_lod0)/norm_vec(d_lod0),
      lod10 = norm_vec(d_lod10 - d_lod0)/norm_vec(d_lod0),
      lod20 = norm_vec(d_lod20 - d_lod0)/norm_vec(d_lod0),
      lod30 = norm_vec(d_lod30 - d_lod0)/norm_vec(d_lod0),
      lod40 = norm_vec(d_lod40 - d_lod0)/norm_vec(d_lod0),
      lod50 = norm_vec(d_lod50 - d_lod0)/norm_vec(d_lod0))) %>% 
  gather(percent_blod, norm)

#pdf("edc_new_lod_penalty_sv.pdf")
d_diff %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point() + geom_path(aes(group = 1)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "Relative Error in Low-Rank Solution Singular Values\n(norm(SV - SV_lod0) / norm(SV_lod0))",
       title = "PCP w/ <LOD Penalty")
#dev.off()
```

## Values \<LOD vs \>LOD

* Are values \<LOD estimated more poorly than those \>LOD? Are \<LOD driving the increased error?
* Rescale by range/variance of values \<LOD.
    * Wider range -> more error

```{r}
# This one is all zeros bc nothing is <LOD to begin with
tf_lod_0 <- mixture_data %>% 
  mutate_all(~ifelse(. == 0, FALSE, FALSE))
# T/F dataset, T = <LOD
l_blod_0 <- as.matrix(tf_lod_0*L_lod0)
s_blod_0 <- as.matrix(tf_lod_0*S_lod0)
# keep <LOD predictions, >LOD predictions are zero
# Solution matrices with >LOD values as zero
true_0 <- as.matrix(mixture_data*tf_lod_0)
# keep zeros as values, push >LOD values to zero
# Original matrix with only zeros, all >LOD set to zero

tf_lod_10 <- mix_data_lod_10 %>% 
  as_tibble(.) %>% 
  mutate_all(~ifelse(. == 0, TRUE, FALSE))
# T/F dataset, T = <LOD
l_blod_10 <- as.matrix(tf_lod_10*L_lod10)
s_blod_10 <- as.matrix(tf_lod_10*S_lod10)
# keep <LOD predictions, >LOD predictions are zero
# Solution matrice with >LOD values as zero
true_10 <- as.matrix(mixture_data*tf_lod_10)
# keep 10% lowest true values, push >LOD values to zero
# Original matrix with only bottom 10percent, all >LOD set to zero

tf_lod_20 <- mix_data_lod_20 %>% as_tibble(.) %>% 
  mutate_all(~ifelse(. == 0, TRUE, FALSE))
l_blod_20 <- as.matrix(tf_lod_20*L_lod20)
s_blod_20 <- as.matrix(tf_lod_20*S_lod20)
true_20 <- as.matrix(mixture_data*tf_lod_20)

tf_lod_30 <- mix_data_lod_30 %>% as_tibble(.) %>% 
  mutate_all(~ifelse(. == 0, TRUE, FALSE))
l_blod_30 <- as.matrix(tf_lod_30*L_lod30)
s_blod_30 <- as.matrix(tf_lod_30*S_lod30)
true_30 <- as.matrix(mixture_data*tf_lod_30)

tf_lod_40 <- mix_data_lod_40 %>% as_tibble(.) %>% 
  mutate_all(~ifelse(. == 0, TRUE, FALSE))
l_blod_40 <- as.matrix(tf_lod_40*L_lod40)
s_blod_40 <- as.matrix(tf_lod_40*S_lod40)
true_40 <- as.matrix(mixture_data*tf_lod_40)

tf_lod_50 <- mix_data_lod_50 %>% as_tibble(.) %>% 
  mutate_all(~ifelse(. == 0, TRUE, FALSE))
l_blod_50 <- as.matrix(tf_lod_50*L_lod50)
s_blod_50 <- as.matrix(tf_lod_50*S_lod50)
true_50 <- as.matrix(mixture_data*tf_lod_50) 

#Subtract true values and divide by norm of true
less_diff <- as_tibble(cbind(lod0 = norm((true_0 - l_blod_0 - s_blod_0), type = "F"), #/norm((true_0), type = "F"),
      lod10 = norm((true_10 - l_blod_10 - s_blod_10), type = "F")/norm((true_10), type = "F"),
      lod20 = norm((true_20 - l_blod_20 - s_blod_20), type = "F")/norm((true_20), type = "F"),
      lod30 = norm((true_30 - l_blod_30 - s_blod_30), type = "F")/norm((true_30), type = "F"),
      lod40 = norm((true_40 - l_blod_40 - s_blod_40), type = "F")/norm((true_40), type = "F"),
      lod50 = norm((true_50 - l_blod_50 - s_blod_50), type = "F")/norm((true_50), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "< LOD")
```

```{r}
#All TRUE
l_above_blod_0 <- L_lod0
s_above_blod_0 <- S_lod0
above_true_0 <- as.matrix(mixture_data)

above_lod_10 <- mix_data_lod_10 %>% as_tibble(.) %>% 
  mutate_all(~ifelse(. == 0, FALSE, TRUE))
# T/F dataset, T = >LOD
l_above_blod_10 <- as.matrix(above_lod_10*L_lod10)
s_above_blod_10 <- as.matrix(above_lod_10*S_lod10)
# keep >LOD predictions, BLOD predictions are zero
above_true_10 <- as.matrix(mixture_data*above_lod_10)
# keep 10% lowest true values, push >LOD values to zero

above_lod_20 <- mix_data_lod_20 %>% as_tibble(.) %>% 
  mutate_all(~ifelse(. == 0, FALSE, TRUE))
l_above_blod_20 <- as.matrix(above_lod_20*L_lod20)
s_above_blod_20 <- as.matrix(above_lod_20*S_lod20)
above_true_20 <- as.matrix(mixture_data*above_lod_20)

above_lod_30 <- mix_data_lod_30 %>% as_tibble(.) %>% 
  mutate_all(~ifelse(. == 0, FALSE, TRUE))
l_above_blod_30 <- as.matrix(above_lod_30*L_lod30)
s_above_blod_30 <- as.matrix(above_lod_30*S_lod30)
above_true_30 <- as.matrix(mixture_data*above_lod_30)

above_lod_40 <- mix_data_lod_40 %>% as_tibble(.) %>% 
  mutate_all(~ifelse(. == 0, FALSE, TRUE))
l_above_blod_40 <- as.matrix(above_lod_40*L_lod40)
s_above_blod_40 <- as.matrix(above_lod_40*S_lod40)
above_true_40 <- as.matrix(mixture_data*above_lod_40)

above_lod_50 <- mix_data_lod_50 %>% as_tibble(.) %>% 
  mutate_all(~ifelse(. == 0, FALSE, TRUE))
l_above_blod_50 <- as.matrix(above_lod_50*L_lod50)
s_above_blod_50 <- as.matrix(above_lod_50*S_lod50)
above_true_50 <- as.matrix(mixture_data*above_lod_50) 
```

```{r}
#divide by true values
above_diff <- as_tibble(cbind(
  lod0  = norm((above_true_0  - l_above_blod_0  - s_above_blod_0),  type = "F")/norm(above_true_0,  type = "F"),
  lod10 = norm((above_true_10 - l_above_blod_10 - s_above_blod_10), type = "F")/norm(above_true_10, type = "F"),
  lod20 = norm((above_true_20 - l_above_blod_20 - s_above_blod_20), type = "F")/norm(above_true_20, type = "F"),
  lod30 = norm((above_true_30 - l_above_blod_30 - s_above_blod_30), type = "F")/norm(above_true_30, type = "F"),
  lod40 = norm((above_true_40 - l_above_blod_40 - s_above_blod_40), type = "F")/norm(above_true_40, type = "F"),
  lod50 = norm((above_true_50 - l_above_blod_50 - s_above_blod_50), type = "F")/norm(above_true_50, type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "> LOD")

#pdf("edc_original_lod_subzero_above_below.pdf")
rbind(above_diff, less_diff) %>% 
  ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point(aes(color = Values)) + geom_path(aes(group = Values, color = Values)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "Relative Error in Values < LOD & > LOD\n(norm(X-L-S) / norm(X))",
       title = "Original PCP w/ 0")
#dev.off()
```
