---
title: "PCP-LOD: Increasing LOD in NHANES POPs"
author: "Lizzy Gibson"
date: "2/1/2020"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(NMF)
library(janitor)
library(ggcorrplot)
library(ggfortify)  
library(gridExtra)
library(factoextra)
library(knitr)
library(haven)
library(rlist)
library(Matrix)
library(matconv)
library(patchwork)
library(mvtnorm)
library(reshape2)
library(GGally)
library(grDevices)
library(gplots)

options(scipen = 999)
```

## NHANES

CDC imputes values \<LOD as LOD/sqrt(2). Here, if comment code = "below detectable limit", set value to -1.

```{r}
nhanes <- read_sas(here::here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  mutate(lbx074la = ifelse(lbd074lc == 1, -1, lbx074la),
         lbx099la = ifelse(lbd099lc == 1, -1, lbx099la),
         lbx105la = ifelse(lbd105lc == 1, -1, lbx105la),
         lbx118la = ifelse(lbd118lc == 1, -1, lbx118la),
         lbx138la = ifelse(lbd138lc == 1, -1, lbx138la),
         lbx153la = ifelse(lbd153lc == 1, -1, lbx153la),
         lbx156la = ifelse(lbd156lc == 1, -1, lbx156la),
         lbx157la = ifelse(lbd157lc == 1, -1, lbx157la),
         lbx167la = ifelse(lbd167lc == 1, -1, lbx167la),
         lbx170la = ifelse(lbd170lc == 1, -1, lbx170la),
         lbx180la = ifelse(lbd180lc == 1, -1, lbx180la),
         lbx187la = ifelse(lbd187lc == 1, -1, lbx187la),
         lbxd01la = ifelse(lbdd01lc == 1, -1, lbxd01la),
         lbxd03la = ifelse(lbdd03lc == 1, -1, lbxd03la),
         lbxd04la = ifelse(lbdd04lc == 1, -1, lbxd04la),
         lbxd05la = ifelse(lbdd05lc == 1, -1, lbxd05la),
         lbxd07la = ifelse(lbdd07lc == 1, -1, lbxd07la),
         lbxf01la = ifelse(lbdf01lc == 1, -1, lbxf01la),
         lbxf02la = ifelse(lbdf02lc == 1, -1, lbxf02la),
         lbxf03la = ifelse(lbdf03lc == 1, -1, lbxf03la),
         lbxf04la = ifelse(lbdf04lc == 1, -1, lbxf04la),
         lbxf05la = ifelse(lbdf05lc == 1, -1, lbxf05la),
         lbxf06la = ifelse(lbdf06lc == 1, -1, lbxf06la),
         lbxf07la = ifelse(lbdf07lc == 1, -1, lbxf07la),
         lbxf08la = ifelse(lbdf08lc == 1, -1, lbxf08la),
         lbxpcbla = ifelse(lbdpcblc == 1, -1, lbxpcbla),
         lbxtcdla = ifelse(lbdtcdlc == 1, -1, lbxtcdla),
         lbxhxcla = ifelse(lbdhxclc == 1, -1, lbxhxcla),
         lbx189la = ifelse(lbd189lc == 1, -1, lbx189la),
         lbx194la = ifelse(lbd194lc == 1, -1, lbx194la),
         lbx196la = ifelse(lbd196lc == 1, -1, lbx196la),
         lbx199la = ifelse(lbd199lc == 1, -1, lbx199la),
         lbxd02la = ifelse(lbdd02lc == 1, -1, lbxd02la),
         lbxf09la = ifelse(lbdf09lc == 1, -1, lbxf09la))
```

```{r}
prop <- function (x) {1 - (sum(x, na.rm = TRUE)/nrow(nhanes))}

names <- nhanes %>% select(names(.)[grep("lc", names(.))]) %>% 
  summarize_all(prop) %>% select_if(~. > 0.2) %>% names() %>% str_sub(., 4, 6) %>% str_c("lbx", ., "la") %>% as.vector()

pops <- nhanes %>% 
  select(!!names) %>% na.omit(.)

names(pops) <- str_sub(names(pops), 1, 6)
names(pops) <- str_replace(names(pops), "lbxd", "D")
names(pops) <- str_replace(names(pops), "lbxf", "F")
names(pops) <- str_replace(names(pops), "lbxtcd", "TCDD")
names(pops) <- str_replace(names(pops), "lbx", "PCB")
pops <- pops %>% rename(PCB169 = PCBhxc, PCB126 = PCBpcb)
#pops

ggcorr(pops, method = c("everything", "spearman"), limits = FALSE,
       label = TRUE, label_size = 3, label_alpha = TRUE,
       hjust = 0.85, size = 3, color = "grey50", layout.exp = 1) + ggtitle("Persistent organic pollutants \n in NHANES 2001-2002")
```

Here, make matrix of LODs to use in LOD PCP. Comment code = 1 means "below detectable limit". CDC imputes values <LOD as LOD/sqrt(2).

```{r}
# Matrix of 0/1
lod_names <- nhanes %>% select(names(.)[grep("lc", names(.))]) %>% 
  summarize_all(prop) %>% select_if(~. > 0.2) %>% names() %>% as.vector()

lods <- read_sas(here::here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  select(!!lod_names) %>% 
  na.omit()

# Matrix of all values (with CDC imputed values)
imputed <- read_sas(here::here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  select(!!names) %>% 
  na.omit()

# Element-wise multiplication by 1/0
# Keep values <LOD
# Values >LOD == 0
# Multiply by sqrt(2) to get back LOD
lod_matrix <- (lods * imputed) * sqrt(2)
lod_matrix <- as.matrix(lod_matrix)
#summary(lod_matrix)
```

**Need to scale LODs, too!**

Need to scale PCBs because they have super different ranges. Need to get rid of values less than LOD to scale and then add them back.

```{r}
#summary(pops)

# make <LOD NA so they dont affect the scaling
pops[pops < 0] <- NA

# Get stand dev of values > LDO
pop_sd <- as.vector(apply(as.matrix(pops), 2, sd, na.rm = TRUE))

# head(pops[,5])
# head(pop_sd[5])
# head(pops[,5]/pop_sd[5])

# Scale bc way different ranges
# Scale by sd vector of length equal to the number of columns of x.
pops <- scale(pops, center = FALSE, scale = pop_sd)

# make <LOD negative again
pops[is.na(pops)] <- -1
mixture_data <- pops

#summary(mixture_data)
```

Also want to scale the LODS!

```{r}
# Scale lod matrix by stand dev of measurements
lod_matrix <- scale(lod_matrix, center = FALSE, scale = pop_sd)

#summary(lod_matrix)
```

## Function

```{r, jingkai}
prox_l1 <- function(Y, c) {
  
  myzero <- matrix(data = 0, ncol = ncol(Y), nrow = nrow(Y))
  X <- sign(Y) * pmax(abs(Y) - c, myzero, na.rm = TRUE)
  X
} 

############################################################

prox_nuclear <- function(Y, c) {
  
  USV <- svd(Y)
  U <- USV$u
  S <- USV$d
  V <- USV$v
  
  myzero <- vector("numeric", length = length(S))
  S_new <- sign(S) * pmax(abs(S) - c, myzero, na.rm = TRUE)
  X <- U %*% diag(S_new) %*% t(V)
  nuclearX  <- sum(abs(S_new))

    list(X = X, nuclearX = nuclearX)
}

############################################################

is_same <- function(SAME_THRESH, ...) {
  flag <- TRUE
  varargin <- list(...)
  if (length(varargin) == 2) {
    if (max(abs(varargin[[1]] - varargin[[2]])) > SAME_THRESH) {
      flag <- FALSE
    }
  }
  else if (length(varargin) == 3) {
    if ((max(abs(varargin[[1]] - varargin[[2]])) > SAME_THRESH) |
        (max(abs(varargin[[1]] - varargin[[3]])) > SAME_THRESH) |
        (max(abs(varargin[[2]] - varargin[[3]])) > SAME_THRESH)) {
      flag <- FALSE
    }
  }
  flag
}

loss_lod <- function(X, D, LOD) {

    X_lod <- ((X - D)     * (D >= 0)) +
             ((X - LOD)   * (D < 0 & (X > LOD))) +
              (X          * (D < 0 & X < 0))
  
  l <- sum(X_lod^2) / 2
  l
}

############################################################

pcp_lod_nnS <- function(D, lambda, mu, LOD) {
  
  m <- nrow(D)
  n <- ncol(D)
  rho <- 1 # Augmented Lagrangian coefficient (rate)
  
  L1 <- matrix(0, m, n)
  L2 <- matrix(0, m, n)
  L3 <- matrix(0, m, n)
  
  S1 <- matrix(0, m, n)
  S2 <- matrix(0, m, n)
  S3 <- matrix(0, m, n) # ADDED
  
  Z1 <- matrix(0, m, n)
  Z2 <- matrix(0, m, n)
  Z3 <- matrix(0, m, n)
  Z4 <- matrix(0, m, n) # ADDED
  
  # Max iteration
  MAX_ITER <- 5000
  
  # Convergence Thresholds
  LOSS_THRESH <- 1e-5
  SAME_THRESH <- 1e-4
  
  if (is.vector(LOD)) {
  #tf = ifelse(D < 0, TRUE, FALSE)
  #LOD = t(t(tf) * LOD)
    empty = matrix(1, nrow = nrow(D), ncol = ncol(D))
    LOD = t(t(empty) * LOD)
    }
  
  loss <- vector("numeric", MAX_ITER)
  
  for (i in 1:MAX_ITER) {
    
    nuc <- prox_nuclear(((L2 + L3 - (Z1 + Z2)/rho)/2), 1/2/rho)
    L1 <- nuc[[1]]
    nuclearL1 <- nuc[[2]] #nuclearX
    
    S1 <- prox_l1(((S2 + S3 - (Z3 + Z4)/rho)/2), lambda/rho) # ADDED
      #prox_l1(S2 - Z3/rho, lambda/rho)
    
    L2_opt1 <- (mu*rho*D     + (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)
    L2_opt2 <- L1 + Z1/rho
    L2_opt3 <- ((mu*rho*LOD + (((mu + rho)*Z1) - (mu*Z3) + ((mu + rho)*rho*L1) - (mu*rho*S1)))) / ((2*mu*rho) + (rho^2))
    L2_opt4 <- (               (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)

    L2 <- (L2_opt1 * (D >= 0)) +
        (L2_opt2 * ((D < 0) & (((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
        (L2_opt3 * ((D < 0) & (((L2 + S2) > LOD)))) +
        (L2_opt4 * ((D < 0) & (((L2 + S2) < 0))))

    S2_opt1 <- (mu*rho*D     + (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)
    S2_opt2 <- S1 + (Z3/rho)
    S2_opt3 <- (((mu*rho*LOD) + (((mu + rho)*Z3) - (mu*Z1) + ((mu + rho)*rho*S1) - (mu*rho*L1)))) / ((2*mu*rho) + (rho^2))
    S2_opt4 <- (               (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)

    S2 <- (S2_opt1 * (D >= 0)) +
        (S2_opt2 * (((D < 0) & ((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
        (S2_opt3 * (((D < 0) & ((L2 + S2) > LOD)))) +
        (S2_opt4 * (((D < 0) & ((L2 + S2) < 0))))
      
    L3 <- pmax(L1 + Z2/rho, 0, na.rm = TRUE)
    # % Non-Negativity constraint!
    
    ## ADDED
    S3 <- pmax(S1 + Z4/rho, 0, na.rm = TRUE)
    
    Z1 <- Z1 + rho*(L1 - L2)
    Z2 <- Z2 + rho*(L1 - L3)
    Z3 <- Z3 + rho*(S1 - S2)
    Z4 <- Z4 + rho*(S1 - S3) # ADDED
    # % Z accumulate differnces between L and L and between S and S
    
    loss[i] <- nuclearL1 + 
      (lambda*sum(abs(S1))) +
      (mu*loss_lod((L2 + S2), D, LOD)) +
      sum(Z1*(L1 - L2)) +
      sum(Z2*(L1 - L3)) +
      sum(Z3*(S1 - S2)) +
      sum(Z4*(S1 - S3)) + # ADDED
      (rho/2 * (sum((L1-L2)^2) + sum((L1 - L3)^2) + sum((S1 - S2)^2)) + sum((S1 - S3)^2)) # ADDED
    # % The code block above takes LOD into account.
    
    print(str_c(i, " Obj: ", loss[i]))
        
    if ((i != 1) && 
        (abs(loss[i-1] - loss[i]) < LOSS_THRESH) && 
        is_same(SAME_THRESH, L1, L2, L3) &&
        is_same(SAME_THRESH, S1, S2, S3)) { # ADDED
      break} # % Convergence criteria!
  }
  
  L <- L3 #(L1 + L2 + L3) / 3
  S <- S3 #(S1 + S2 + S3) / 3
  list(L = L, S = S, loss = loss)
}
```

## Run PCP

```{r, best}
m <- nrow(mixture_data)
p <- ncol(mixture_data)

lambda_mix <- 1/sqrt(m)
mu_mix <- sqrt(p/(2*log(m*p)))

results_0  <- pcp_lod_nnS(D = mixture_data, lambda = lambda_mix, mu = mu_mix, LOD = lod_matrix)

L_lod0 <- results_0[[1]]
S_lod0 <- results_0[[2]]

rankMatrix(L_lod0)
prcomp(L_lod0)$sdev

S_lod0 %>% as_tibble() %>% mutate_all(function(x) ifelse(x > 0.001, 1, 0)) %>% 
  as.matrix(.) %>% sum(.)/(1007*18)
```

## Best $\mu$

### Sparse Matrix

```{r}
plot_sparse <- S_lod0 %>% as_tibble() %>% 
  mutate(id = 1:nrow(S_lod0)) %>% 
  select(id, everything()) %>% 
  gather(key = exposure, value = value, -id) %>%
  mutate(binary = ifelse(value < 0.001, 0, 1))

sparse_matrix <- plot_sparse %>% 
  select(id, exposure, binary) %>% 
  spread(exposure, binary) %>% 
  select(-id) %>% as.matrix()

sum(sparse_matrix)/(nrow(sparse_matrix)*ncol(sparse_matrix))
```

```{r fig.width = 10}
## Plot heatmap 
heatmap.2(sparse_matrix, key.xlab = "Sparsity", cexCol = 0.75, cexRow = 0.01,
                               margins =c(4,4), keysize = 1.25,
          col = c("white", "red"), density.info="none", trace="none", dendrogram = "column", key.title = "")
dev.off()

plot_sparse %>% 
ggplot(aes(x = exposure, y = id)) +
  geom_tile(aes(fill = as.factor(binary))) + 
  labs(x = "Exposure", y = "Participant", title = "Sparse matrix of rare events", legend = "Magnitude") + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")
```

### Patterns

```{r}
rankMatrix(L_lod0)
# rank 7

length(L_lod0[L_lod0 >= 0])/length(L_lod0)
# all non-negative

length(S_lod0[S_lod0 > 0])/length(S_lod0)
# 65% sparsity
```

```{r}
colnames(L_lod0) <- colnames(mixture_data)

ggcorr(L_lod0, method = c("everything", "spearman"), limits = FALSE,
       label = TRUE, label_size = 3, label_alpha = TRUE,
       hjust = 0.85, size = 3, color = "grey50", layout.exp = 1) + ggtitle("Low Rank Matrix from LOD PCP")
```

```{r}
pcp_pca <- prcomp(L_lod0)
pcp_pca$sdev

fviz_eig(pcp_pca, main = "PCA on Low Rank Matrix",
         xlab = "Principal components") 

pcp_pca$rotation %>% 
  as_tibble() %>% 
  mutate(Chemicals = colnames(mixture_data)) %>% 
  select(Chemicals, PC1:PC7) %>% 
  gather(key = Component, value = Loadings, -Chemicals) %>%
  mutate(Chemicals = fct_inorder(Chemicals)) %>% 
  mutate(Group = ifelse(grepl("D|TCDD", Chemicals), "Dioxins", 
                  ifelse(grepl("F", Chemicals), "Furans",
                    ifelse(grepl("126|169", Chemicals), "Non-Ortho PCBs",
                     ifelse(grepl("105|118|156|157|167|198", Chemicals), "Mono-Ortho PCBs", "Non-Dioxin-like PCBs"))))) %>%
  ggplot(aes(x = Chemicals, y = Loadings, color = Group)) + geom_point() +
  geom_segment(aes(yend=0, xend = Chemicals)) +
  facet_wrap(.~Component) + theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "bottom",
        strip.background = element_blank())
```

### Scores

```{r}
scores <- pcp_pca$x
```

### NMF

```{r, nmf, cache = TRUE}
any(L_lod0 < 0)
any(is.na(L_lod0))

L_nmf <- L_lod0 %>% as_tibble() %>% drop_na() %>% 
  filter(PCB074 != PCB099)

pcp_nmf <- nmf(L_nmf, rank = 7, nrun = 50)
```

```{r}
nmf_loadings <- coef(pcp_nmf)
mnf_scores <- basis(pcp_nmf)
```

```{r}
nmf_loadings %>% 
  t() %>% 
  as_tibble() %>% 
  mutate(Chemicals = colnames(mixture_data)) %>% 
  gather(key = Factor, value = Loadings, -Chemicals) %>%
  mutate(Chemicals = fct_inorder(Chemicals)) %>% 
  mutate(Group = ifelse(grepl("D|TCDD", Chemicals), "Dioxins", 
                  ifelse(grepl("F", Chemicals), "Furans",
                    ifelse(grepl("126|169", Chemicals), "Non-Ortho PCBs",
                     ifelse(grepl("105|118|156|157|167|198", Chemicals), "Mono-Ortho PCBs", "Non-Dioxin-like PCBs"))))) %>%
  ggplot(aes(x = Chemicals, y = Loadings, color = Group)) + geom_point() +
  geom_segment(aes(yend=0, xend = Chemicals)) +
  facet_wrap(.~Factor) + theme_bw(base_size = 15) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "bottom",
        strip.background = element_blank())
```

## PCA

```{r}
just_pca <- prcomp(mixture_data)
```

```{r}
rankMatrix(mixture_data)
# rank 7

rankMatrix(just_pca$rotation)
rankMatrix(just_pca$x)

just_pca$sdev
```

```{r}
fviz_eig(just_pca, main = "PCA on Original Matrix",
         xlab = "Principal components") 

just_pca$rotation %>% 
  as_tibble() %>% 
  mutate(Chemicals = colnames(mixture_data)) %>% 
  select(Chemicals, PC1:PC7) %>% 
  gather(key = Component, value = Loadings, -Chemicals) %>%
  mutate(Chemicals = fct_inorder(Chemicals)) %>% 
  mutate(Group = ifelse(grepl("D|TCDD", Chemicals), "Dioxins", 
                  ifelse(grepl("F", Chemicals), "Furans",
                    ifelse(grepl("126|169", Chemicals), "Non-Ortho PCBs",
                     ifelse(grepl("105|118|156|157|167|198", Chemicals), "Mono-Ortho PCBs", "Non-Dioxin-like PCBs"))))) %>%
  ggplot(aes(x = Chemicals, y = Loadings, color = Group)) + geom_point() +
  geom_segment(aes(yend=0, xend = Chemicals)) +
  facet_wrap(.~Component) + theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "bottom",
        strip.background = element_blank())
```

### Scores

```{r}
scores_pca <- just_pca$x
```

## PCP v PCA

```{r}
PCP <- pcp_pca$sdev^2/sum(pcp_pca$sdev^2) *100
PCA <- just_pca$sdev^2/sum(just_pca$sdev^2) *100
round(cbind(Component = 1:18, PCP, PCA), 4) %>% stargazer::stargazer(., summary = NULL)
```


