---
title: "PCP-LOD: NHANES POPs"
author: "Lizzy Gibson"
date: "6/18/2020"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(NMF)
library(janitor)
library(ggcorrplot)
library(ggfortify)  
library(gridExtra)
library(factoextra)
library(knitr)
library(haven)
library(rlist)
library(Matrix)
library(matconv)
library(patchwork)
library(mvtnorm)
library(reshape2)
library(GGally)
library(grDevices)
library(gplots)
library(pcpr)
library(here)
options(scipen = 999)
```

## NHANES

CDC imputes values \<LOD as LOD/sqrt(2). Here, if comment code = "below detectable limit", set value to -1.

```{r}
nhanes <- read_sas(here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  mutate(lbx074la = ifelse(lbd074lc == 1, -1, lbx074la),
         lbx099la = ifelse(lbd099lc == 1, -1, lbx099la),
         lbx105la = ifelse(lbd105lc == 1, -1, lbx105la),
         lbx118la = ifelse(lbd118lc == 1, -1, lbx118la),
         lbx138la = ifelse(lbd138lc == 1, -1, lbx138la),
         lbx153la = ifelse(lbd153lc == 1, -1, lbx153la),
         lbx156la = ifelse(lbd156lc == 1, -1, lbx156la),
         lbx157la = ifelse(lbd157lc == 1, -1, lbx157la),
         lbx167la = ifelse(lbd167lc == 1, -1, lbx167la),
         lbx170la = ifelse(lbd170lc == 1, -1, lbx170la),
         lbx180la = ifelse(lbd180lc == 1, -1, lbx180la),
         lbx187la = ifelse(lbd187lc == 1, -1, lbx187la),
         lbxd01la = ifelse(lbdd01lc == 1, -1, lbxd01la),
         lbxd03la = ifelse(lbdd03lc == 1, -1, lbxd03la),
         lbxd04la = ifelse(lbdd04lc == 1, -1, lbxd04la),
         lbxd05la = ifelse(lbdd05lc == 1, -1, lbxd05la),
         lbxd07la = ifelse(lbdd07lc == 1, -1, lbxd07la),
         lbxf01la = ifelse(lbdf01lc == 1, -1, lbxf01la),
         lbxf02la = ifelse(lbdf02lc == 1, -1, lbxf02la),
         lbxf03la = ifelse(lbdf03lc == 1, -1, lbxf03la),
         lbxf04la = ifelse(lbdf04lc == 1, -1, lbxf04la),
         lbxf05la = ifelse(lbdf05lc == 1, -1, lbxf05la),
         lbxf06la = ifelse(lbdf06lc == 1, -1, lbxf06la),
         lbxf07la = ifelse(lbdf07lc == 1, -1, lbxf07la),
         lbxf08la = ifelse(lbdf08lc == 1, -1, lbxf08la),
         lbxpcbla = ifelse(lbdpcblc == 1, -1, lbxpcbla),
         lbxtcdla = ifelse(lbdtcdlc == 1, -1, lbxtcdla),
         lbxhxcla = ifelse(lbdhxclc == 1, -1, lbxhxcla),
         lbx189la = ifelse(lbd189lc == 1, -1, lbx189la),
         lbx194la = ifelse(lbd194lc == 1, -1, lbx194la),
         lbx196la = ifelse(lbd196lc == 1, -1, lbx196la),
         lbx199la = ifelse(lbd199lc == 1, -1, lbx199la),
         lbxd02la = ifelse(lbdd02lc == 1, -1, lbxd02la),
         lbxf09la = ifelse(lbdf09lc == 1, -1, lbxf09la))
```

```{r}
# this takes proportion detected (1 - proportion nondetect)
prop <- function (x) {1 - (sum(x, na.rm = TRUE)/length(x))}

names <- nhanes %>% select(names(.)[grep("lc", names(.))]) %>% 
  summarize_all(prop) %>% select_if(~. > 0.6) %>% names() %>% str_sub(., 4, 6) %>% str_c("lbx", ., "la") %>% as.vector()

pops <- nhanes %>% 
  select(!!names) %>% na.omit(.)

names(pops) <- str_sub(names(pops), 1, 6)
names(pops) <- str_replace(names(pops), "lbxd", "D")
names(pops) <- str_replace(names(pops), "lbxf", "F")
names(pops) <- str_replace(names(pops), "lbxtcd", "TCDD")
names(pops) <- str_replace(names(pops), "lbx", "PCB")
pops <- pops %>% rename(PCB169 = PCBhxc, PCB126 = PCBpcb)

ggcorr(pops, method = c("everything", "spearman"), limits = FALSE,
       label = TRUE, label_size = 3, label_alpha = TRUE,
       hjust = 0.85, size = 3, color = "grey50", layout.exp = 1) + ggtitle("Persistent organic pollutants \n in NHANES 2001-2002")
```

Here, make matrix of LODs to use in LOD PCP. Comment code = 1 means "below detectable limit". CDC imputes values <LOD as LOD/sqrt(2).

```{r}
# Matrix of 0/1
lod_names <- nhanes %>% select(names(.)[grep("lc", names(.))]) %>% 
  summarize_all(prop) %>% select_if(~. > 0.6) %>% names() %>% as.vector()

lods <- read_sas(here::here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  select(!!lod_names) %>% 
  na.omit()

# Matrix of all values (with CDC imputed values)
imputed <- read_sas(here::here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  select(!!names) %>% 
  na.omit()

# Element-wise multiplication by 1/0
# Keep values <LOD
# Values >LOD == 0
# Multiply by sqrt(2) to get back LOD
lod_matrix <- (lods * imputed) * sqrt(2)
lod_matrix <- as.matrix(lod_matrix)
#summary(lod_matrix)
```

Need to scale POPs because they have super different ranges. Need to get rid of values less than LOD to scale and then add them back.

```{r}
#summary(pops)

# make <LOD NA so they dont affect the scaling
pops[pops < 0] <- NA

# Scale bc way different ranges
# Scale by sd vector of length equal to the number of columns of x.
pops <- scale(pops, center = FALSE, scale = apply(pops, 2, sd, na.rm = TRUE))

# make <LOD negative again
pops[is.na(pops)] <- -1
mixture_data <- pops

#summary(mixture_data)
```

Also want to scale the LODS!

```{r}
# Get stand dev of values > LDO
pop_sd <- as.vector(apply(as.matrix(pops), 2, sd, na.rm = TRUE))

# Scale lod matrix by stand dev of measurements
lod_matrix <- scale(lod_matrix, center = FALSE, scale = pop_sd)

#summary(lod_matrix)
```

## Function

**Input function here if package pcpr doens't work.**

## Run PCP

```{r, best, cache = TRUE}
m <- nrow(mixture_data)
p <- ncol(mixture_data)

lambda_mix <- 1/sqrt(m) # these are default parameter values
mu_mix <- sqrt(p/(2*log(m*p)))

pcp_out  <- pcp_lod(D = mixture_data, lambda = lambda_mix, mu = mu_mix, LOD = lod_matrix)

# low rank matrix
L_lod0 <- pcp_out[[1]]

#sparse matrix
S_lod0 <- pcp_out[[2]]
```

### Sparse Matrix

```{r}
plot_sparse <- S_lod0 %>% as_tibble() %>% 
  mutate(id = 1:nrow(S_lod0)) %>% 
  select(id, everything()) %>% 
  gather(key = exposure, value = value, -id) %>%
  mutate(binary = ifelse(value < 0.00001, 0, 1)) # sparse event (0) vs non-sparse event (not zero)
# this isn't exactly right bc sparse matrix can have negative values, this treats negative as sparse event, too

sparse_matrix <- plot_sparse %>% 
  select(id, exposure, binary) %>% 
  spread(exposure, binary) %>% 
  select(-id) %>% as.matrix()

sum(sparse_matrix)/(nrow(sparse_matrix)*ncol(sparse_matrix))
```

```{r fig.width = 10}
## Plot heatmap 
heatmap.2(sparse_matrix, key.xlab = "Sparsity", 
                               margins =c(4,8), keysize = 1.25,
          col = c("white", "red"), density.info="none", trace="none", dendrogram = "column", key.title = "")

# Similar plot in ggplot but without clustering of axes
# plot_sparse %>% 
# ggplot(aes(x = exposure, y = id)) +
#   geom_tile(aes(fill = as.factor(binary))) + 
#   labs(x = "Exposure", y = "Participant", title = "Sparse matrix of rare events", legend = "Magnitude") + 
#   theme_classic() +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1),
#         legend.position = "bottom")
```

### Patterns

```{r}
rankMatrix(L_lod0)
# rank 6

length(L_lod0[L_lod0 >= 0])/length(L_lod0)
# all non-negative 

length(S_lod0[S_lod0 > 0])/length(S_lod0)
# 69% sparsity is not that sparse
```

```{r}
colnames(L_lod0) <- colnames(mixture_data)

ggcorr(L_lod0, method = c("everything", "spearman"), limits = FALSE,
       label = TRUE, label_size = 3, label_alpha = TRUE,
       hjust = 0.85, size = 3, color = "grey50", layout.exp = 1) + ggtitle("Low Rank Matrix from LOD PCP")
```

#### PCA of low rank matrix

```{r}
# Default is scale = false but this is ok bc we scaled data to begin with
pcp_pca <- prcomp(L_lod0)
pcp_pca$sdev

fviz_eig(pcp_pca, main = "PCA on Low Rank Matrix",
         xlab = "Principal components") 

# plot rotations (loadings) of chemicals on patterns in low rank matrix
pcp_pca$rotation %>% 
  as_tibble() %>% 
  mutate(Chemicals = colnames(mixture_data)) %>% 
  select(Chemicals, PC1:PC7) %>% 
  gather(key = Component, value = Loadings, -Chemicals) %>%
  mutate(Chemicals = fct_inorder(Chemicals)) %>% 
  mutate(Group = ifelse(grepl("D|TCDD", Chemicals), "Dioxins", # this groups chemicals based on expert knowledge
                  ifelse(grepl("F", Chemicals), "Furans",
                    ifelse(grepl("126|169", Chemicals), "Non-Ortho PCBs",
                     ifelse(grepl("105|118|156|157|167|198", Chemicals), "Mono-Ortho PCBs", "Non-Dioxin-like PCBs"))))) %>%
  ggplot(aes(x = Chemicals, y = Loadings, color = Group)) + geom_point() +
  geom_segment(aes(yend=0, xend = Chemicals)) +
  facet_wrap(.~Component) + theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "bottom",
        strip.background = element_blank())
```

##### Scores

```{r}
scores <- pcp_pca$x
```

## PCA

```{r}
just_pca <- prcomp(mixture_data)
```

```{r}
rankMatrix(mixture_data)
# rank 18

rankMatrix(just_pca$rotation)
rankMatrix(just_pca$x)
# still rank 18

just_pca$sdev
```

```{r}
fviz_eig(just_pca, main = "PCA on Original Matrix",
         xlab = "Principal components") 

just_pca$rotation %>% 
  as_tibble() %>% 
  mutate(Chemicals = colnames(mixture_data)) %>% 
  select(Chemicals, PC1:PC7) %>% 
  gather(key = Component, value = Loadings, -Chemicals) %>%
  mutate(Chemicals = fct_inorder(Chemicals)) %>% 
  mutate(Group = ifelse(grepl("D|TCDD", Chemicals), "Dioxins", 
                  ifelse(grepl("F", Chemicals), "Furans",
                    ifelse(grepl("126|169", Chemicals), "Non-Ortho PCBs",
                     ifelse(grepl("105|118|156|157|167|198", Chemicals), "Mono-Ortho PCBs", "Non-Dioxin-like PCBs"))))) %>%
  ggplot(aes(x = Chemicals, y = Loadings, color = Group)) + geom_point() +
  geom_segment(aes(yend=0, xend = Chemicals)) +
  facet_wrap(.~Component) + theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "bottom",
        strip.background = element_blank())
```

### Scores

```{r}
scores_pca <- just_pca$x
```

## PCP v PCA

```{r}
PCP_PCA <- pcp_pca$sdev^2/sum(pcp_pca$sdev^2) *100
just_PCA <- just_pca$sdev^2/sum(just_pca$sdev^2) *100
round(cbind(Component = 1:18, PCP_PCA, just_PCA), 4) %>% kable()
```

