---
title: "PCP -- vary $\\lambda$ and $\\mu$"
author: "Lizzy Gibson"
date: "3/26/2019"
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_depth: 4
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
options(scipen = 999)
library(tidyverse)
library(janitor)
library(reshape2)
library(tableone)
library(ggcorrplot)
library(ggfortify)  
library(gridExtra)
library(factoextra)
library(Matrix)
library(rlist)
library(ggrepel)
library(broom)
library(R.matlab)
```

## Read Data

Read Boston air pollution data.

```{r read}
# Read air pollution data
mixture <- readMat(here::here("Data/mixtures_data.mat"))

mix <- as.data.frame(mixture) %>% as_tibble() %>% 
  select(Al, As, Ba, bc, Br, Ca, Cl,
         Cr, Cu, Fe, K,  Mn,  Ni,  Pb,  S,  Se,  Si,
         Ti,  V, Zn) %>% 
  drop_na(.) %>% 
  as.matrix(.)

m <- nrow(mix)
n <- ncol(mix)

lambda_mix = 1/sqrt(m)
#This is the default lambda
```

### Import PCP Function

```{r import}
soft_thresholding <- function(v, lambda) {
  myzero <- matrix(data = 0, ncol = ncol(v), nrow = nrow(v))
  w <- sign(v) * pmax(abs(v) - lambda, myzero)
  w
} 

soft_thresholding_diag <- function(v, lambda) {
  myzero <- vector("numeric", length = length(v))
  w <- sign(v) * pmax(abs(v) - lambda, myzero)
  w
} 

singular_value_threshold <- function(M, lambda) {
  
  USV <- svd(M)
  U <- USV$u
  S <- USV$d
  V <- USV$v
    
  N <- U %*% diag(soft_thresholding_diag(S, lambda)) %*% t(V)
  
  v  <- sum(soft_thresholding_diag(S, lambda))
  
  svt <- list(N = N, v = v) 
  svt
}

stable_pcp_alternating <- function(D, lambda, mu) {
  
  m <- nrow(D)
  n <- ncol(D)
  
  S <- matrix(0, nrow = m, ncol = n)
  L <- matrix(0, nrow = m, ncol = n)
  
  iter <- 0
  MAX_ITER <- 20
  done <- FALSE
  
  while (!done) {
    
    iter <- iter + 1
    
    svt <- singular_value_threshold((D - S), 1/mu)
    L <- svt[[1]] #svt$N
    v <- svt[[2]]
    
    S <- soft_thresholding((D - L), lambda/mu)
    
    obj <- v + lambda * sum(abs(S)) + (mu/2) * norm((D - L - S), type = "F")^2
    
    print(str_c(iter, " Obj: ", obj))
    
    if (iter >= MAX_ITER) {done <- TRUE}
    
  }
  list(L = L, S = S, Lambda = lambda, Mu = mu, obj_value = obj)
}
```

## Vary $\lambda$ and $\mu$

Create function to output new low rank matrix, sparse matrix, singular values and rank of new low rank matrix, and $\lambda$ and $\mu$ parameters used. Create grid of $\lambda$ and $\mu$ values to loop over.

```{r mu_lam}
mu_value <- seq(0.01, 11, by = 0.1)
# Every mu > 3 has all 17 non-zero singular values.

lambda_value <- c(seq(0.00001, 1/sqrt(m), by = 0.01), seq(1/sqrt(m), 0.15, by = 0.01))
# center lambda = 1/sqrt(n)

parameters <- expand.grid(mu_value, lambda_value)
# combo of all mu and lambda pairs
mu_value <- parameters[,1]
lambda_value <- parameters[,2]

make_L_mu_l <- function(lambda, mu){ 
  mixture_mu <- stable_pcp_alternating(mix, lambda, mu)
  L <- mixture_mu$L
  S <- mixture_mu$S
  sv_diag <- svd(L)$d # singular values on new low rank matrix
  sv_count <- sum(sv_diag > 0.001) # rank of new low rank matrix
  list(L = L, SV = sv_diag, S = S, Count = sv_count, Mu = mu, Lambda = lambda)
}
```

Loop over $\lambda$, $\mu$ pairs.

```{r looop, results = FALSE, cache = TRUE}
range_out <- map2(.x = lambda_value, .y = mu_value, ~make_L_mu_l(lambda = .x, mu = .y))
```

### Changing Low Rank Matrix

Examine how rank of low rank matrix changes with varying $\lambda$ and $\mu$.

```{r rank_ml}
singular_value_count <- range_out %>% list.map(.[4]) %>% unlist() %>% 
  cbind(sv_count = ., parameters) %>% as_tibble() %>% rename(mu = Var1, lambda = Var2)
```

```{r rank2}
singular_value_count %>% summary()

singular_value_count %>% 
  mutate(lambda = round(lambda, 5)) %>% 
  mutate_at(vars(2:3), as.factor) %>% 
  ggplot(aes(x = mu, y = lambda)) +
  geom_tile(aes(fill = sv_count), color = "white") +
  scale_fill_gradientn(colours = rainbow(10), 
                      na.value = "transparent", limits = c(0, 17)) +
  theme_bw() + labs(fill = "Rank", 
                    y = expression(lambda),
                    x = expression(mu),
                    title = expression(paste("Changing low rank matrix rank with varying ", mu, " and ", lambda))) +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 70, hjust = 1))
```

```{r}
singular_value_count %>% 
  filter(lambda == lambda_mix) %>% 
  ggplot(aes(x = mu, y = sv_count)) +
  geom_point() + geom_line() +
  theme_bw() +
  labs(y = "Rank",
       x = expression(mu),
       title = expression(paste("Changing rank of low rank matrix with varying ", mu))) +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 70, hjust = 1))
```

### Changing Sparse Matrix

Examine how sparsity of sparse matrix changes with varying $\lambda$ and $\mu$.

```{r mu_sparse2}
sparse <- range_out %>% list.map(.[3])
# Extract all sparse matrices

loop.vector2 <- 1:length(parameters[,1])

cells <- nrow(mix)*ncol(mix)
prop_not_zero <- vector(length = length(parameters[,1]))

for (i in loop.vector2) { # Loop over loop.vector2

 not_zeros <- sum(sparse[[i]]$S != 0)
  # Create proportion of non-zero values across all cells in sparse matrix
  prop_not_zero[i] <- not_zeros/cells
}

sparseness <- cbind(prop_not_zero, singular_value_count) %>% as_tibble()
```

```{r plot_sparse2}
sparseness %>% summary()

sparseness %>%
  mutate(lambda = round(lambda, 5)) %>% 
  mutate_at(vars(3:4), as.factor) %>% 
  ggplot(aes(y = lambda, x = mu)) + 
  geom_tile(aes(fill = prop_not_zero), color = "white") +
  scale_fill_gradientn(colours = rainbow(10), 
                      na.value = "transparent", limits = c(0, 1)) +
  theme_bw() + labs(fill = "Not Zero", 
                    y = expression(lambda),
                    x = expression(mu),
                    title = expression(paste("Changing sparse matrix sparsity with varying ", mu, " and ", lambda))) +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 70, hjust = 1))
```

```{r}
sparseness %>% 
  filter(lambda == lambda_mix) %>% 
  ggplot(aes(x = mu, y = prop_not_zero)) +
  geom_point() + geom_line() +
  theme_bw() +
  labs(y = "Proportion Non-Zero",
       x = expression(mu),
       title = expression(paste("Changing sparsity of sparse matrix with varying ", mu))) +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 70, hjust = 1))
```

## Error

Each PCP creates a low rank L matrix and a sparse matrix that sum to the original D matrix with some error. To choose the best value for $\lambda$ and $\mu$, we add the L and S matrices to form D', then subtract D - D' to get an error matrix for each $\lambda$ and $\mu$ pair. We then take the RMSE of the low rank matrix and the F norm of each error matrix, divided by the norm of the original matrix, to get relative error.

```{r cv_both}
# low_rank and sparse are lists of L and S matrices for each 

loop.vector2 <- 1:length(parameters[,1])
rmse <- vector(length = length(parameters[,1]))
rel_error <- vector(length = length(parameters[,1]))
new_ml <- list()

low_rank_ml <- range_out %>% list.map(.[1])
sparse_ml <- range_out %>% list.map(.[3])

for (i in loop.vector2) { # Loop over loop.vector
  new_ml[[i]]  <- low_rank_ml[[i]]$L + sparse_ml[[i]]$S
  rmse[i]      <- sqrt(mean((mix - new_ml[[i]])^2))
  rel_error[i] <- norm((mix - new_ml[[i]]), type = "F")/norm(mix, type = "F")
  }

cv <- cbind(parameters, rmse, rel_error) %>% as_tibble() %>% 
  rename(mu = Var1, lambda = Var2)
```

### Plot Error

```{r plot_both}
cv %>% summary()

cv %>% 
  mutate(lambda = round(lambda, 5)) %>% 
  mutate_at(vars(1:2), as.factor) %>% 
  ggplot(aes(x = mu, y = lambda)) +
  geom_tile(aes(fill = rmse), color = "white") +
  scale_fill_gradientn(colours = rainbow(10), 
                      na.value = "transparent", limits = c(0, 1.01)) +
  theme_bw() + labs(fill = "RMSE", 
                    y = expression(lambda),
                    x = expression(mu),
                    title = expression(paste("Changing RMSE with varying ", mu, " and ", lambda))) +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 70, hjust = 1))
```

```{r}
cv %>% 
  #filter(rel_error > 0.01) %>% 
  mutate(lambda = round(lambda, 5)) %>% 
  mutate_at(vars(1:2), as.factor) %>% 
  ggplot(aes(x = mu, y = lambda)) +
  geom_tile(aes(fill = rel_error), color = "white") +
  scale_fill_gradientn(colours = rainbow(10), 
                      na.value = "transparent", limits = c(0, 1.01)) +
  theme_bw() + labs(fill = "Relative Error", 
                    y = expression(lambda),
                    x = expression(mu),
                    title = "Relative Error norm(X - L - S)/norm(X)") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 70, hjust = 1))
```

Below is the cross-section at $\lambda = 1/\sqrt{n}$, same as only varying $\mu$.

```{r}
cv %>% 
  filter(lambda == lambda_mix) %>% 
  ggplot(aes(y = rmse, x = mu)) + 
  geom_point() + geom_line() +
  theme_bw() +
  labs(y = "Root Mean Squared Error",
       x = expression(mu),
       title = expression(paste("Changing RMSE with varying ", mu)))
```
