---
title: "PCP-LOD: NHANES POPs"
author: "Lizzy Gibson"
date: "6/18/2020"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(NMF)
library(janitor)
library(ggcorrplot)
library(ggfortify)  
library(gridExtra)
library(factoextra)
library(knitr)
library(haven)
library(rlist)
library(Matrix)
library(matconv)
library(patchwork)
library(mvtnorm)
library(reshape2)
library(GGally)
library(grDevices)
library(gplots)
library(pcpr)
library(here)
library(PCPhelpers)
options(scipen = 999)
```

## NHANES

* **Info:** https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/L28POC_B.htm  

* CDC imputes values \<LOD as LOD/sqrt(2).  
* Here, if comment code = "below detectable limit", set value to -1.  
* All values are measured in blood and lipid-adjusted.  
* Make matrix of LODs to use in LOD PCP. 

```{r, clean, include=FALSE}
nhanes <- read_sas(here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  mutate(lbx074la = ifelse(lbd074lc == 1, -1, lbx074la),
         lbx099la = ifelse(lbd099lc == 1, -1, lbx099la),
         lbx105la = ifelse(lbd105lc == 1, -1, lbx105la),
         lbx118la = ifelse(lbd118lc == 1, -1, lbx118la),
         lbx138la = ifelse(lbd138lc == 1, -1, lbx138la),
         lbx153la = ifelse(lbd153lc == 1, -1, lbx153la),
         lbx156la = ifelse(lbd156lc == 1, -1, lbx156la),
         lbx157la = ifelse(lbd157lc == 1, -1, lbx157la),
         lbx167la = ifelse(lbd167lc == 1, -1, lbx167la),
         lbx170la = ifelse(lbd170lc == 1, -1, lbx170la),
         lbx180la = ifelse(lbd180lc == 1, -1, lbx180la),
         lbx187la = ifelse(lbd187lc == 1, -1, lbx187la),
         lbxd01la = ifelse(lbdd01lc == 1, -1, lbxd01la),
         lbxd03la = ifelse(lbdd03lc == 1, -1, lbxd03la),
         lbxd04la = ifelse(lbdd04lc == 1, -1, lbxd04la),
         lbxd05la = ifelse(lbdd05lc == 1, -1, lbxd05la),
         lbxd07la = ifelse(lbdd07lc == 1, -1, lbxd07la),
         lbxf01la = ifelse(lbdf01lc == 1, -1, lbxf01la),
         lbxf02la = ifelse(lbdf02lc == 1, -1, lbxf02la),
         lbxf03la = ifelse(lbdf03lc == 1, -1, lbxf03la),
         lbxf04la = ifelse(lbdf04lc == 1, -1, lbxf04la),
         lbxf05la = ifelse(lbdf05lc == 1, -1, lbxf05la),
         lbxf06la = ifelse(lbdf06lc == 1, -1, lbxf06la),
         lbxf07la = ifelse(lbdf07lc == 1, -1, lbxf07la),
         lbxf08la = ifelse(lbdf08lc == 1, -1, lbxf08la),
         lbxpcbla = ifelse(lbdpcblc == 1, -1, lbxpcbla),
         lbxtcdla = ifelse(lbdtcdlc == 1, -1, lbxtcdla),
         lbxhxcla = ifelse(lbdhxclc == 1, -1, lbxhxcla),
         lbx189la = ifelse(lbd189lc == 1, -1, lbx189la),
         lbx194la = ifelse(lbd194lc == 1, -1, lbx194la),
         lbx196la = ifelse(lbd196lc == 1, -1, lbx196la),
         lbx199la = ifelse(lbd199lc == 1, -1, lbx199la),
         lbxd02la = ifelse(lbdd02lc == 1, -1, lbxd02la),
         lbxf09la = ifelse(lbdf09lc == 1, -1, lbxf09la))
```

```{r, func, include=FALSE}
pop_rename_lc = function(name) {
  name = str_to_upper(name)
         name = fct_recode(name,'PCB 74' = 'LBD074LC',
                                'PCB 99' = 'LBD099LC',
                                'PCB 118' = 'LBD118LC',
                                'PCB 138' = 'LBD138LC',
                                'PCB 153' = 'LBD153LC',
                                'PCB 170' = 'LBD170LC',
                                'PCB 180' = 'LBD180LC',
                                'PCB 187' = 'LBD187LC',
                                'PCB 194' = 'LBD194LC',
                                '1,2,3,6,7,8-hxcdd' = 'LBDD03LC',
                                '1,2,3,4,6,7,8-hpcdd' = 'LBDD05LC',
                                '1,2,3,4,6,7,8,9-ocdd' = 'LBDD07LC',
                                '2,3,4,7,8-pncdf' = 'LBDF03LC',
                                '1,2,3,4,7,8-hxcdf' = 'LBDF04LC',
                                '1,2,3,6,7,8-hxcdf' = 'LBDF05LC',
                                '1,2,3,4,6,7,8-hxcdf' = 'LBDF08LC',
                                'PCB 169' = 'LBDHXCLC',
                                'PCB 126' = 'LBDPCBLC')
         name
}

pop_rename_la = function(name) {
  name = str_to_upper(name)
         name = fct_recode(name,'PCB 74' = 'LBX074LA',
                                'PCB 99' = 'LBX099LA',
                                'PCB 118' = 'LBX118LA',
                                'PCB 138' = 'LBX138LA',
                                'PCB 153' = 'LBX153LA',
                                'PCB 170' = 'LBX170LA',
                                'PCB 180' = 'LBX180LA',
                                'PCB 187' = 'LBX187LA',
                                'PCB 194' = 'LBX194LA',
                                '1,2,3,6,7,8-hxcdd' = 'LBXD03LA',
                                '1,2,3,4,6,7,8-hpcdd' = 'LBXD05LA',
                                '1,2,3,4,6,7,8,9-ocdd' = 'LBXD07LA',
                                '2,3,4,7,8-pncdf' = 'LBXF03LA',
                                '1,2,3,4,7,8-hxcdf' = 'LBXF04LA',
                                '1,2,3,6,7,8-hxcdf' = 'LBXF05LA',
                                '1,2,3,4,6,7,8-hxcdf' = 'LBXF08LA',
                                'PCB 169' = 'LBXHXCLA',
                                'PCB 126' = 'LBXPCBLA')
         name
}

re_name = function(pops) {
      names(pops) <- str_sub(names(pops), 1, 6)
      names(pops) <- str_replace(names(pops), "lbxd", "D")
      names(pops) <- str_replace(names(pops), "lbxf", "F")
      names(pops) <- str_replace(names(pops), "lbxtcd", "TCDD")
      names(pops) <- str_replace(names(pops), "lbx", "PCB")
      if ("pops$PCBpcb" %in% colnames(pops)) {
      pops = pops %>% rename(PCB169 = PCBhxc, PCB126 = PCBpcb)}
      return(pops)
      }


# this takes proportion detected (1 - proportion nondetect)
prop <- function (x) {1 - (sum(x, na.rm = TRUE)/length(x[!is.na(x)]))}
```

```{r}
nhanes %>% dplyr::select(grep("lc", names(.))) %>% 
            summarize_all(prop) %>% 
  pivot_longer(lbd074lc:lbdf09lc) %>%
  mutate(name = str_to_upper(name),
         name = pop_rename_lc(name),
         name = fct_reorder(name, value)) %>% 
  ggplot(aes(x = name, y = value)) +
  geom_segment( aes(x=name, xend=name, y=0, yend=value), color="grey") +
  geom_point( color="orange", size=2) +
  theme_light() +
  theme(panel.grid.major.x = element_blank(),
        panel.border = element_blank(),
       axis.ticks.x = element_blank(),
       axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "% > LOD", n = "")
```

```{r, clean_func, include=FALSE}
# Select pops with detection above a certain limit
props <- nhanes %>% dplyr::select(grep("lc", names(.))) %>% 
            summarize_all(prop) 

# x is a proportion
# take all variables > x and preprocess them
# scale them and save their lods
process_pops = function(x) {
  names = props %>% select_if(~. > x) %>%
            names() %>% str_sub(., 4, 6) %>% str_c("lbx", ., "la") %>% as.vector()  

  pops <- nhanes %>% dplyr::select(all_of(names)) %>% na.omit(.)
  pops = re_name(pops)
  
  # Matrix of 0/1
  lod_names <- nhanes %>% 
               select(names(.)[grep("lc", names(.))]) %>% 
               summarize_all(prop) %>% select_if(~. > x) %>% names() %>% as.vector()
  
  lods <- read_sas(here::here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  select(lod_names) %>% 
  na.omit()

  # Matrix of all values (with CDC imputed values)
  imputed <- read_sas(here::here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  select(all_of(names)) %>% 
  na.omit() %>% as.matrix()

  # Element-wise multiplication by 1/0
  # Keep values <LOD
  # Values >LOD == 0
  # Multiply by sqrt(2) to get back LOD
  lod_matrix <- (lods * imputed) * sqrt(2)
  lod_matrix <- as.matrix(lod_matrix)
  #summary(lod_matrix)

  # Need to scale POPs because they have super different ranges. 
  # Need to get rid of values less than LOD to scale and then add them back.

  #summary(pops)

  # make <LOD NA so they dont affect the scaling
  pops[pops < 0] <- NA

  # Scale bc way different ranges
  # Get stand dev of values > LDO
  denoms = apply(pops, 2, function(a) sd(a, na.rm = T))
  pops_scaled = apply(pops, 2, function(a) a/sd(a, na.rm = T))
  
  # make <LOD negative again
  pops_scaled[is.na(pops_scaled)] <- -1
  pops_scaled = as.matrix(pops_scaled)

  # Also want to scale the LODS!
  # Scale lod matrix by stand dev of measurements
  lod_matrix <- lod_matrix/denoms

  return(list(scaled_data = pops_scaled, lods = lod_matrix, sqrt2_data = imputed))
}
```

## 50% > LOD

```{r}
fifty_percent = process_pops(.5)

data_50  = as.matrix(fifty_percent$scaled_data)
delta_50 = fifty_percent$lods
imputed_50 = fifty_percent$sqrt2_data

#write_csv(as.data.frame(data_50), "./Data/nhanes_50.csv")
#write_csv(as.data.frame(delta_50), "./Data/nhanes_50_lods.csv")
```

## PCP

### CV

```{r}
lambda <- seq(.1, 5, length.out = 5)
mu <-  seq(.1, 5, length.out = 5)
rank <- 1:5

grid.pop <- expand.grid(lambda = lambda, mu = mu, r = rank)
# a grid searching through lambda, mu and rank (for non-convex PCP)
nrow(grid.pop)

noncvx_search <- bayes_search_cv(mat = data_50, 
                                 pcp_func = root_pcp_noncvx_nonnegL_na_lod, 
                                 grid_df = grid.pop,
                                 init_evals = 5, bayes_evals = 5, 
                                 cores = 2, runs = 5, LOD = delta_50) # <- here we hold LOD constant
```

```{r}
print_gs(noncvx_search$formatted)
noncvx_search$formatted
```

```{r}
best.idx <- which.min(noncvx_search$formatted$value)
optimal.lambda <- noncvx_search$formatted$lambda[best.idx]
optimal.mu <- noncvx_search$formatted$mu[best.idx]
optimal.r <- noncvx_search$formatted$r[best.idx]

pcp_out <- root_pcp_noncvx_nonnegL_na_lod(D = data_50, 
                                   lambda = optimal.lambda, mu = optimal.mu, 
                                   r = optimal.r, LOD = delta_50,
                                           verbose = TRUE)

```

```{r, best, cache = TRUE}
m <- nrow(data_50)
p <- ncol(data_50)

lambda_mix <- 1/sqrt(m) # these are default parameter values
mu_mix <- sqrt(p/(2*log(m*p)))

data_50[data_50 == -1] = NA

pcp_out <- root_pcp_na_nonnegL_lod(D = data_50, lambda = lambda_mix, 
                                           mu = mu_mix, LOD = delta_50,
                                           verbose = TRUE)

# low rank matrix
L_lod0 <- pcp_out[[1]]

#sparse matrix
S_lod0 <- pcp_out[[2]]
```

### Sparse Matrix

```{r}
plot_sparse <- S_lod0 %>% as_tibble() %>% 
  mutate(id = 1:nrow(S_lod0)) %>% 
  select(id, everything()) %>% 
  gather(key = exposure, value = value, -id) %>%
  mutate(binary = ifelse(value < 0.00001, 0, 1)) # sparse event (0) vs non-sparse event (not zero)
# this isn't exactly right bc sparse matrix can have negative values, this treats negative as sparse event, too

sparse_matrix <- plot_sparse %>% 
  select(id, exposure, binary) %>% 
  spread(exposure, binary) %>% 
  select(-id) %>% as.matrix()

sum(sparse_matrix)/(nrow(sparse_matrix)*ncol(sparse_matrix))
```

```{r fig.width = 10}
## Plot heatmap 
heatmap.2(sparse_matrix, key.xlab = "Sparsity", 
                               margins =c(4,8), keysize = 1.25,
          col = c("white", "red"), density.info="none", trace="none", dendrogram = "column", key.title = "")

# Similar plot in ggplot but without clustering of axes
plot_sparse %>%
ggplot(aes(x = exposure, y = id)) +
  geom_tile(aes(fill = as.factor(binary))) +
  labs(x = "Exposure", y = "Participant", title = "Sparse matrix of rare events", legend = "Magnitude") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")
```

### Patterns

```{r}
rankMatrix(L_lod0)
# rank 6

length(L_lod0[L_lod0 >= 0])/length(L_lod0)
# all non-negative 

length(S_lod0[S_lod0 > 0])/length(S_lod0)
# 69% sparsity is not that sparse
```

```{r}
colnames(L_lod0) <- colnames(data_50)

ggcorr(L_lod0, method = c("everything", "spearman"), limits = FALSE,
       label = TRUE, label_size = 3, label_alpha = TRUE,
       hjust = 0.85, size = 3, color = "grey50", layout.exp = 1) + ggtitle("Low Rank Matrix from LOD PCP")
```

#### PCA of low rank matrix

```{r}
# Default is scale = false but this is ok bc we scaled data to begin with
pcp_pca <- prcomp(L_lod0)
pcp_pca$sdev

fviz_eig(pcp_pca, main = "PCA on Low Rank Matrix",
         xlab = "Principal components") 

# plot rotations (loadings) of chemicals on patterns in low rank matrix
pcp_pca$rotation %>% 
  as_tibble() %>% 
  mutate(Chemicals = colnames(data_50)) %>% 
  select(Chemicals, PC1:PC7) %>% 
  gather(key = Component, value = Loadings, -Chemicals) %>%
  mutate(Chemicals = fct_inorder(Chemicals)) %>% 
  mutate(Group = ifelse(grepl("D|TCDD", Chemicals), "Dioxins", # this groups chemicals based on expert knowledge
                  ifelse(grepl("F", Chemicals), "Furans",
                    ifelse(grepl("126|169", Chemicals), "Non-Ortho PCBs",
                     ifelse(grepl("105|118|156|157|167|198", Chemicals), "Mono-Ortho PCBs", "Non-Dioxin-like PCBs"))))) %>%
  ggplot(aes(x = Chemicals, y = Loadings, color = Group)) + geom_point() +
  geom_segment(aes(yend=0, xend = Chemicals)) +
  facet_wrap(.~Component) + theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "bottom",
        strip.background = element_blank())
```

##### Scores

```{r}
scores <- pcp_pca$x
```

## PCA

```{r}
dim(fifty_percent$sqrt2_data)
pca_50 <- prcomp(log(fifty_percent$sqrt2_data))
```

```{r}
pca_50$sdev

summary(pca_50)

pca_50$sdev^2/sum(pca_50$sdev^2)
```

```{r}
fviz_eig(pca_50, main = "PCA on Original Matrix",
         xlab = "Principal components") 

pca_50$rotation %>% 
  as_tibble() %>% 
  mutate(Chemicals = colnames(fifty_percent$sqrt2_data)) %>% 
  select(Chemicals, PC1:PC3) %>% 
  gather(key = Component, value = Loadings, -Chemicals) %>%
  mutate(Chemicals = fct_inorder(Chemicals),
         Chemicals = pop_rename_la(Chemicals),
         Group = ifelse(grepl("(d$|TCDD)", Chemicals), "Dioxins", 
                  ifelse(grepl("f$", Chemicals), "Furans",
                    ifelse(grepl("(126|169)", Chemicals), "Non-Ortho PCBs",
                     ifelse(grepl("(105|118|156|157|167|198)", Chemicals), "Mono-Ortho PCBs", "Non-Dioxin-like PCBs"))))) %>%
  ggplot(aes(x = Chemicals, y = Loadings, color = Group)) + geom_point() +
  geom_segment(aes(yend=0, xend = Chemicals)) +
  facet_wrap(.~Component) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        strip.background = element_blank())
```

### Scores

```{r}
scores_pca <- pca_50$x
```

## PCP v PCA

```{r}
PCP_PCA <- pcp_pca$sdev^2/sum(pcp_pca$sdev^2) *100
just_PCA <- just_pca$sdev^2/sum(just_pca$sdev^2) *100
round(cbind(Component = 1:18, PCP_PCA, just_PCA), 4) %>% kable()
```


