---
title: "PCP-LOD: NHANES POPs"
author: "Lizzy Gibson"
date: "6/18/2020"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(NMF)
library(janitor)
library(ggcorrplot)
library(ggfortify)  
library(gridExtra)
library(factoextra)
library(knitr)
library(haven)
library(rlist)
library(Matrix)
library(matconv)
library(patchwork)
library(mvtnorm)
library(reshape2)
library(GGally)
library(grDevices)
library(gplots)
library(pcpr)
library(here)
library(PCPhelpers)
options(scipen = 999)
```

## NHANES

* **Info:** https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/L28POC_B.htm  

* CDC imputes values \<LOD as LOD/sqrt(2).  
* Here, if comment code = "below detectable limit", set value to -1.  
* All values are measured in blood and lipid-adjusted.  
* Make matrix of LODs to use in LOD PCP. 

```{r, data, include=FALSE}
nhanes <- read_sas(here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  mutate(lbx074la = ifelse(lbd074lc == 1, -1, lbx074la),
         lbx099la = ifelse(lbd099lc == 1, -1, lbx099la),
         lbx105la = ifelse(lbd105lc == 1, -1, lbx105la),
         lbx118la = ifelse(lbd118lc == 1, -1, lbx118la),
         lbx138la = ifelse(lbd138lc == 1, -1, lbx138la),
         lbx153la = ifelse(lbd153lc == 1, -1, lbx153la),
         lbx156la = ifelse(lbd156lc == 1, -1, lbx156la),
         lbx157la = ifelse(lbd157lc == 1, -1, lbx157la),
         lbx167la = ifelse(lbd167lc == 1, -1, lbx167la),
         lbx170la = ifelse(lbd170lc == 1, -1, lbx170la),
         lbx180la = ifelse(lbd180lc == 1, -1, lbx180la),
         lbx187la = ifelse(lbd187lc == 1, -1, lbx187la),
         lbxd01la = ifelse(lbdd01lc == 1, -1, lbxd01la),
         lbxd03la = ifelse(lbdd03lc == 1, -1, lbxd03la),
         lbxd04la = ifelse(lbdd04lc == 1, -1, lbxd04la),
         lbxd05la = ifelse(lbdd05lc == 1, -1, lbxd05la),
         lbxd07la = ifelse(lbdd07lc == 1, -1, lbxd07la),
         lbxf01la = ifelse(lbdf01lc == 1, -1, lbxf01la),
         lbxf02la = ifelse(lbdf02lc == 1, -1, lbxf02la),
         lbxf03la = ifelse(lbdf03lc == 1, -1, lbxf03la),
         lbxf04la = ifelse(lbdf04lc == 1, -1, lbxf04la),
         lbxf05la = ifelse(lbdf05lc == 1, -1, lbxf05la),
         lbxf06la = ifelse(lbdf06lc == 1, -1, lbxf06la),
         lbxf07la = ifelse(lbdf07lc == 1, -1, lbxf07la),
         lbxf08la = ifelse(lbdf08lc == 1, -1, lbxf08la),
         lbxpcbla = ifelse(lbdpcblc == 1, -1, lbxpcbla),
         lbxtcdla = ifelse(lbdtcdlc == 1, -1, lbxtcdla),
         lbxhxcla = ifelse(lbdhxclc == 1, -1, lbxhxcla),
         lbx189la = ifelse(lbd189lc == 1, -1, lbx189la),
         lbx194la = ifelse(lbd194lc == 1, -1, lbx194la),
         lbx196la = ifelse(lbd196lc == 1, -1, lbx196la),
         lbx199la = ifelse(lbd199lc == 1, -1, lbx199la),
         lbxd02la = ifelse(lbdd02lc == 1, -1, lbxd02la),
         lbxf09la = ifelse(lbdf09lc == 1, -1, lbxf09la))
```

```{r, functions, include=FALSE}
pop_rename_lc = function(name) {
  name = str_to_upper(name)
         name = fct_recode(name,'PCB 74' = 'LBD074LC', 'PCB 99' = 'LBD099LC', 'PCB 118' = 'LBD118LC', 
                           'PCB 138' = 'LBD138LC', 'PCB 153' = 'LBD153LC', 'PCB 170' = 'LBD170LC', 
                           'PCB 180' = 'LBD180LC', 'PCB 187' = 'LBD187LC', 'PCB 194' = 'LBD194LC',
                           '1,2,3,6,7,8-hxcdd' = 'LBDD03LC', '1,2,3,4,6,7,8-hpcdd' = 'LBDD05LC',
                           '1,2,3,4,6,7,8,9-ocdd' = 'LBDD07LC', '2,3,4,7,8-pncdf' = 'LBDF03LC',
                           '1,2,3,4,7,8-hxcdf' = 'LBDF04LC', '1,2,3,6,7,8-hxcdf' = 'LBDF05LC',
                           '1,2,3,4,6,7,8-hxcdf' = 'LBDF08LC', 'PCB 169' = 'LBDHXCLC', 
                           'PCB 126' = 'LBDPCBLC', "PCB 105" = "LBD105LC",     "PCB 156" = "LBD156LC", 
                           "PCB 157" = "LBD157LC",  "PCB 167" = "LBD167LC", "Dioxin 1" = "LBDD01LC",  
                           "Dioxin 4" = "LBDD04LC",    "Furan 1" = "LBDF01LC", "Furan 2" = "LBDF02LC",  
                           "Furan 4" = "LBDF04LC",   "Furan 6" = "LBDF06LC",  "Furan 7" = "LBDF07LC",   
                           "TCDD" = "LBDTCDLC", "PCB 189" = "LBD189LC",   "PCB 196" = "LBD196LC",  
                           "PCB 199" = "LBD199LC",  "Dioxin 2" = "LBDD02LC",  "Furan 9" = "LBDF09LC")
         name
}

pop_rename_la = function(name) {
  name = str_to_upper(name)
         name = fct_recode(name,'PCB 74' = 'LBX074LA',
                                'PCB 99' = 'LBX099LA',
                                'PCB 118' = 'LBX118LA',
                                'PCB 138' = 'LBX138LA',
                                'PCB 153' = 'LBX153LA',
                                'PCB 170' = 'LBX170LA',
                                'PCB 180' = 'LBX180LA',
                                'PCB 187' = 'LBX187LA',
                                'PCB 194' = 'LBX194LA',
                                '1,2,3,6,7,8-hxcdd' = 'LBXD03LA',
                                '1,2,3,4,6,7,8-hpcdd' = 'LBXD05LA',
                                '1,2,3,4,6,7,8,9-ocdd' = 'LBXD07LA',
                                '2,3,4,7,8-pncdf' = 'LBXF03LA',
                                '1,2,3,4,7,8-hxcdf' = 'LBXF04LA',
                                '1,2,3,6,7,8-hxcdf' = 'LBXF05LA',
                                '1,2,3,4,6,7,8-hxcdf' = 'LBXF08LA',
                                'PCB 169' = 'LBXHXCLA',
                                'PCB 126' = 'LBXPCBLA',
                                "PCB 105" = "LBX105LA",    
                                "PCB 156" = "LBX156LA", 
                                "PCB 157" = "LBX157LA", 
                                "PCB 167" = "LBX167LA",
                                "Dioxin 1" = "LBXD01LA",  
                                "Dioxin 4" = "LBXD04LA",   
                                "Furan 1" = "LBXF01LA",
                                "Furan 2" = "LBXF02LA",  
                                "Furan 4" = "LBXF04LA",  
                                "Furan 6" = "LBXF06LA", 
                                "Furan 7" = "LBXF07LA",   
                                "TCDD" = "LBXTCDLA",
                                "PCB 189" = "LBX189LA",  
                                "PCB 196" = "LBX196LA", 
                                "PCB 199" = "LBX199LA", 
                                "Dioxin 2" = "LBXD02LA", 
                                "Furan 9" = "LBXF09LA")
         name
}

pop_rename_col = function(name) {
  name = str_to_upper(name)
         name = fct_recode(name,'PCB 74' = 'PCB074',
                                'PCB 99' = 'PCB099',
                                'PCB 118' = 'PCB118',
                                'PCB 138' = 'PCB138',
                                'PCB 153' = 'PCB153',
                                'PCB 170' = 'PCB170',
                                'PCB 180' = 'PCB180',
                                'PCB 187' = 'PCB187',
                                'PCB 194' = 'PCB194',
                                '1,2,3,6,7,8-hxcdd' = 'D03',
                                '1,2,3,4,6,7,8-hpcdd' = 'D05',
                                '1,2,3,4,6,7,8,9-ocdd' = 'D07',
                                '2,3,4,7,8-pncdf' = 'F03',
                                '1,2,3,4,7,8-hxcdf' = 'F04',
                                '1,2,3,6,7,8-hxcdf' = 'F05',
                                '1,2,3,4,6,7,8-hxcdf' = 'F08',
                                'PCB 169' = 'PCBHXC',
                                'PCB 126' = 'PCBPCB',
                                "PCB 105" = "PCB105",    
                                "PCB 156" = "PCB156", 
                                "PCB 157" = "PCB157", 
                                "PCB 167" = "PCB167",
                                "Dioxin 1" = "D01",  
                                "Dioxin 4" = "D04",   
                                "Furan 1" = "F01",
                                "Furan 2" = "F02",  
                                "Furan 4" = "F04",  
                                "Furan 6" = "F06", 
                                "Furan 7" = "F07",   
                                "TCDD" = "TCD",
                                "PCB 189" = "189",  
                                "PCB 196" = "196", 
                                "PCB 199" = "199", 
                                "Dioxin 2" = "D02", 
                                "Furan 9" = "F09")
         name
}

re_name = function(pops) {
      names(pops) <- str_sub(names(pops), 1, 6)
      names(pops) <- str_replace(names(pops), "lbxd", "D")
      names(pops) <- str_replace(names(pops), "lbxf", "F")
      names(pops) <- str_replace(names(pops), "lbxtcd", "TCDD")
      names(pops) <- str_replace(names(pops), "lbx", "PCB")
      if ("pops$PCBpcb" %in% colnames(pops)) {
      pops = pops %>% rename(PCB169 = PCBhxc, PCB126 = PCBpcb)}
      return(pops)
      }


# this takes proportion detected (1 - proportion nondetect)
prop <- function (x) {1 - (sum(x, na.rm = TRUE)/length(x[!is.na(x)]))}
```

```{r}
nhanes %>% dplyr::select(grep("lc", names(.))) %>% 
            summarize_all(prop) %>% 
  pivot_longer(lbd074lc:lbdf09lc) %>%
  mutate(name = str_to_upper(name),
         name = pop_rename_lc(name),
         name = fct_reorder(name, value)) %>% 
  ggplot(aes(x = name, y = value)) +
  geom_segment( aes(x=name, xend=name, y=0, yend=value), color="grey") +
  geom_point( color="orange", size=2) +
  theme_light() +
  theme(panel.grid.major.x = element_blank(),
        panel.border = element_blank(),
       axis.ticks.x = element_blank(),
       axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "% > LOD", n = "")
```

```{r, process, include=FALSE}
# Select pops with detection above a certain limit
props <- nhanes %>% dplyr::select(grep("lc", names(.))) %>% 
            summarize_all(prop) 

# x is a proportion
# take all variables > x and preprocess them
# scale them and save their lods
process_pops = function(x) {
  names = props %>% select_if(~. > x) %>%
            names() %>% str_sub(., 4, 6) %>% str_c("lbx", ., "la") %>% as.vector()  

  pops <- nhanes %>% dplyr::select(all_of(names)) %>% na.omit(.)
  pops = re_name(pops)
  
  # Matrix of 0/1
  lod_names <- nhanes %>% 
               select(names(.)[grep("lc", names(.))]) %>% 
               summarize_all(prop) %>% select_if(~. > x) %>% names() %>% as.vector()
  
  lods <- read_sas(here::here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  select(lod_names) %>% 
  na.omit()

  # Matrix of all values (with CDC imputed values)
  imputed <- read_sas(here::here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  select(all_of(names)) %>% 
  na.omit() %>% as.matrix()

  # Element-wise multiplication by 1/0
  # Keep values <LOD
  # Values >LOD == 0
  # Multiply by sqrt(2) to get back LOD
  lod_matrix <- (lods * imputed) * sqrt(2)
  lod_matrix <- as.matrix(lod_matrix)
  #summary(lod_matrix)

  # Need to scale POPs because they have super different ranges. 
  # Need to get rid of values less than LOD to scale and then add them back.

  #summary(pops)

  # make <LOD NA so they dont affect the scaling
  pops[pops < 0] <- NA

  # Scale bc way different ranges
  # Get stand dev of values > LDO
  denoms = apply(pops, 2, function(a) sd(a, na.rm = T))
  pops_scaled = apply(pops, 2, function(a) a/sd(a, na.rm = T))
  
  # make <LOD negative again
  pops_scaled[is.na(pops_scaled)] <- -1
  pops_scaled = as.matrix(pops_scaled)

  # Also want to scale the LODS!
  # Scale lod matrix by stand dev of measurements
  lod_matrix <- lod_matrix/denoms

  return(list(scaled_data = pops_scaled, lods = lod_matrix, sqrt2_data = imputed))
}
```

## 50% > LOD

```{r}
fifty_percent = process_pops(.5)

data_50  = as.matrix(fifty_percent$scaled_data)
delta_50 = fifty_percent$lods
imputed_50 = fifty_percent$sqrt2_data
colnames(data_50)

#write_csv(as.data.frame(data_50), "./experiments/law_experiments/PCPhelpers/Data/nhanes_50.csv")
#write_csv(as.data.frame(delta_50), "./experiments/law_experiments/PCPhelpers/Data/nhanes_50_lods.csv")
```

## PCP

### CV

```{r}
n = nrow(data_50)
p = ncol(data_50)

m = sqrt(p/2)
lam = 1/n

mu <- c(seq(m, 20, length.out = 20))
lambda <- c(seq(lam, 10, length.out = 10))
rank <- 1:10

grid.pop <- expand.grid(lambda = lambda, mu = mu)
nrow(grid.pop)
evals = ceiling(.07*nrow(grid.pop))

noncvx_search <- bayes_search_cv(mat = data_50, 
                                 pcp_func = root_pcp_na_nonnegL_lod, 
                                 grid_df = grid.pop,
                                 init_evals = evals, bayes_evals = evals, 
                                 cores = 2, runs = 5, LOD = delta_50)
```

```{r}
print_gs(noncvx_search$formatted)

noncvx_search$formatted %>%
  arrange(desc(value)) %>% 
  drop_na()

noncvx_search$formatted %>%
  ggplot(aes(y = lambda, x = mu)) +
  geom_tile(aes(fill = value)) +
  theme_bw()
```

```{r}
best.idx <- which.min(noncvx_search$formatted$value)
optimal.lambda <- noncvx_search$formatted$lambda[best.idx]
optimal.mu <- noncvx_search$formatted$mu[best.idx]
optimal.r <- noncvx_search$formatted$r[best.idx]

pcp_out <- root_pcp_na_nonnegL_lod(D = data_50, 
                                   lambda = optimal.lambda, mu = optimal.mu, 
                                   LOD = delta_50,
                                           verbose = TRUE)

# low rank matrix
L <- pcp_out[[1]]

#sparse matrix
S <- pcp_out[[2]]
```

### Sparse Matrix

```{r}
sum(S == 0)/(nrow(S)*ncol(S))
sum(S < 0)/(nrow(S)*ncol(S))
sum(S < 0.00001)/(nrow(S)*ncol(S))
colnames(S)

plot_sparse <- S %>% as_tibble() %>% 
  mutate(id = 1:nrow(.)) %>% 
  select(id, everything()) %>% 
  gather(key = exposure, value = value, -id) %>%
  mutate(exposure = pop_rename_col(exposure),
          binary = ifelse(value < 0.00001, 0, 1)) 
# sparse event (0) vs non-sparse event (not zero)
# this treats negative as sparse      event, too
```

```{r fig.width = 10}
## Plot heatmap 
plot_sparse %>%
ggplot(aes(x = exposure, y = id)) +
  geom_tile(aes(fill = as.factor(binary))) +
  labs(x = "Exposure", y = "Participant", 
       title = "Sparse matrix of rare events", fill = "Magnitude") +
  theme_test() +
  scale_fill_manual(values = c("white", "red")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")
```

### Patterns

```{r}
rankMatrix(L)
```

```{r}
ggcorr(L, method = c("everything", "spearman"), limits = FALSE,
       label = TRUE, label_size = 3, label_alpha = TRUE,
       hjust = 0.85, size = 3, color = "grey50", layout.exp = 1) + 
        ggtitle("Low Rank Matrix from LOD PCP")
```

#### PCA of low rank matrix

```{r}
# Default is scale = false but this is ok bc we scaled data to begin with
pcp_pca <- prcomp(L)
pcp_pca$sdev

fviz_eig(pcp_pca, main = "PCA on Low Rank Matrix",
         xlab = "Principal components") 

# plot rotations (loadings) of chemicals on patterns in low rank matrix
pcp_plot = pcp_pca$rotation %>% 
  as_tibble() %>% 
  mutate(Chemicals = colnames(data_50)) %>% 
  select(Chemicals, PC1:PC3) %>% 
  gather(key = Component, value = Loadings, -Chemicals) %>%
  mutate(Group = ifelse(grepl("(D|TCDD)", Chemicals), "Dioxins",
                  ifelse(grepl("F", Chemicals), "Furans",
                    ifelse(grepl("(126|169|pcb|hxc)", Chemicals), "Non-Ortho PCBs",
                     ifelse(grepl("(105|118|156|157|167|198)", Chemicals), "Mono-Ortho PCBs", "Non-Dioxin-like PCBs"))))) %>%
  mutate(Chemicals = pop_rename_col(Chemicals),
         Chemicals = fct_inorder(Chemicals)) %>% 
  ggplot(aes(x = Chemicals, y = Loadings, color = Group)) + geom_point() +
  geom_segment(aes(yend=0, xend = Chemicals)) +
  facet_wrap(.~Component) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        strip.background = element_blank())
pcp_plot
```

## PCA

```{r}
dim(imputed_50)
pca_50 <- prcomp(imputed_50)
```

```{r}
pca_50$sdev

summary(pca_50)

pca_50$sdev^2/sum(pca_50$sdev^2)
```

```{r}
fviz_eig(pca_50, main = "PCA on Original Matrix",
         xlab = "Principal components") 

pca_plot = pca_50$rotation %>% 
  as_tibble() %>% 
  mutate(Chemicals = colnames(fifty_percent$sqrt2_data)) %>% 
  select(Chemicals, PC1:PC3) %>% 
  gather(key = Component, value = Loadings, -Chemicals) %>%
  mutate(Chemicals = pop_rename_la(Chemicals),
         Group = ifelse(grepl("(d$|TCDD)", Chemicals), "Dioxins", 
                  ifelse(grepl("(^F|f$)", Chemicals), "Furans",
                    ifelse(grepl("(126|169)", Chemicals), "Non-Ortho PCBs",
                     ifelse(grepl("(105|118|156|157|167|198)", Chemicals), "Mono-Ortho PCBs", "Non-Dioxin-like PCBs"))))) %>%
  mutate(Chemicals = fct_inorder(Chemicals)) %>% 
  ggplot(aes(x = Chemicals, y = Loadings, color = Group)) + geom_point() +
  geom_segment(aes(yend=0, xend = Chemicals)) +
  facet_wrap(.~Component) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        strip.background = element_blank())
pca_plot
```

## PCP v PCA

```{r}
pcp_plot / pca_plot
```

```{r}
PCP_PCA <- pcp_pca$sdev^2/sum(pcp_pca$sdev^2) *100
just_PCA <- pca_50$sdev^2/sum(pca_50$sdev^2) *100
round(cbind(Component = 1:21, PCP_PCA, just_PCA), 4) %>% kable()
```

## Relative error

```{r}
data_50
delta_50
imputed_50

mask = data_50 != -1
data_above = data_50 * mask

L_above = L*mask
S_above = S*mask

norm(data_above-L_above, "F")/norm(data_above, "F")

pca_pred = pca_50$x %*% t(pca_50$rotation) +
        matrix(rep(apply(imputed_50, 2, mean), each= nrow(pca_50$x)), nrow = nrow(pca_50$x))

norm(imputed_50-pca_pred, "F")/norm(imputed_50, "F")
norm(data_above-pca_pred, "F")/norm(imputed_50, "F")
```

