---
title: "PCP-LOD: NHANES POPs"
author: "Lizzy Gibson"
date: "6/18/2020"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(NMF)
library(janitor)
library(ggcorrplot)
library(ggfortify)  
library(gridExtra)
library(factoextra)
library(knitr)
library(haven)
library(rlist)
library(Matrix)
library(matconv)
library(patchwork)
library(mvtnorm)
library(reshape2)
library(GGally)
library(grDevices)
library(gplots)
library(pcpr)
library(here)
library(PCPhelpers)
options(scipen = 999)
```

## NHANES

* **Info:** https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/L28POC_B.htm  

* CDC imputes values \<LOD as LOD/sqrt(2).  
* Here, if comment code = "below detectable limit", set value to -1.  
* All values are measured in blood and lipid-adjusted.  
* Make matrix of LODs to use in LOD PCP. 

```{r, data, include=FALSE}
nhanes <- read_sas(here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  mutate(lbx074la = ifelse(lbd074lc == 1, -1, lbx074la),
         lbx099la = ifelse(lbd099lc == 1, -1, lbx099la),
         lbx105la = ifelse(lbd105lc == 1, -1, lbx105la),
         lbx118la = ifelse(lbd118lc == 1, -1, lbx118la),
         lbx138la = ifelse(lbd138lc == 1, -1, lbx138la),
         lbx153la = ifelse(lbd153lc == 1, -1, lbx153la),
         lbx156la = ifelse(lbd156lc == 1, -1, lbx156la),
         lbx157la = ifelse(lbd157lc == 1, -1, lbx157la),
         lbx167la = ifelse(lbd167lc == 1, -1, lbx167la),
         lbx170la = ifelse(lbd170lc == 1, -1, lbx170la),
         lbx180la = ifelse(lbd180lc == 1, -1, lbx180la),
         lbx187la = ifelse(lbd187lc == 1, -1, lbx187la),
         lbxd01la = ifelse(lbdd01lc == 1, -1, lbxd01la),
         lbxd03la = ifelse(lbdd03lc == 1, -1, lbxd03la),
         lbxd04la = ifelse(lbdd04lc == 1, -1, lbxd04la),
         lbxd05la = ifelse(lbdd05lc == 1, -1, lbxd05la),
         lbxd07la = ifelse(lbdd07lc == 1, -1, lbxd07la),
         lbxf01la = ifelse(lbdf01lc == 1, -1, lbxf01la),
         lbxf02la = ifelse(lbdf02lc == 1, -1, lbxf02la),
         lbxf03la = ifelse(lbdf03lc == 1, -1, lbxf03la),
         lbxf04la = ifelse(lbdf04lc == 1, -1, lbxf04la),
         lbxf05la = ifelse(lbdf05lc == 1, -1, lbxf05la),
         lbxf06la = ifelse(lbdf06lc == 1, -1, lbxf06la),
         lbxf07la = ifelse(lbdf07lc == 1, -1, lbxf07la),
         lbxf08la = ifelse(lbdf08lc == 1, -1, lbxf08la),
         lbxpcbla = ifelse(lbdpcblc == 1, -1, lbxpcbla),
         lbxtcdla = ifelse(lbdtcdlc == 1, -1, lbxtcdla),
         lbxhxcla = ifelse(lbdhxclc == 1, -1, lbxhxcla),
         lbx189la = ifelse(lbd189lc == 1, -1, lbx189la),
         lbx194la = ifelse(lbd194lc == 1, -1, lbx194la),
         lbx196la = ifelse(lbd196lc == 1, -1, lbx196la),
         lbx199la = ifelse(lbd199lc == 1, -1, lbx199la),
         lbxd02la = ifelse(lbdd02lc == 1, -1, lbxd02la),
         lbxf09la = ifelse(lbdf09lc == 1, -1, lbxf09la))
```

```{r, functions, include=FALSE}
pop_label_groups <- function(names) {
 case_when(grepl("(^D|d$|TCDD)", names) ~ "Dioxins", 
           grepl("(^F|f$)", names) ~ "Furans",
           grepl("(126|169|hxc|pcb|HXC|PCBPCB)", names) ~ "Non-Ortho PCBs",
           grepl("(105|118|156|157|167|198)", names) ~ "Mono-Ortho PCBs",
           TRUE ~ "Non-Dioxin-like PCBs")
}

pop_rename = function(name) {
  name = str_to_upper(name)
  name = case_when(grepl('074', name) ~ 'PCB 74',
                   grepl('099', name) ~ 'PCB 99',
                   grepl('118', name) ~ 'PCB 118',
                   grepl('138', name) ~ 'PCB 138',
                   grepl('153', name) ~ 'PCB 153',
                   grepl('170', name) ~ 'PCB 170',
                   grepl('180', name) ~ 'PCB 180',
                   grepl('187', name) ~ 'PCB 187',
                   grepl('194', name) ~ 'PCB 194',
                   grepl('D03', name) ~   '1,2,3,6,7,8-hxcdd',
                   grepl('D05', name) ~ '1,2,3,4,6,7,8-hpcdd',
                   grepl('D07', name) ~'1,2,3,4,6,7,8,9-ocdd',
                   grepl('F03', name) ~     '2,3,4,7,8-pncdf',
                   grepl('F04', name) ~   '1,2,3,4,7,8-hxcdf',
                   grepl('F05', name) ~   '1,2,3,6,7,8-hxcdf',
                   grepl('F08', name) ~ '1,2,3,4,6,7,8-hxcdf',
                   grepl('(hxc|HXC)', name) ~ 'PCB 169',
                   grepl('(LBDPCBLC|PCBPCB|LBXPCBLA)', name) ~ 'PCB 126', 
                   grepl("105", name) ~ "PCB 105",    
                   grepl("156", name) ~ "PCB 156", 
                   grepl("157", name) ~ "PCB 157", 
                   grepl("167", name) ~ "PCB 167",
                   grepl("D01", name) ~ "Dioxin 1",  
                   grepl("D04", name) ~ "Dioxin 4",   
                   grepl("F01", name) ~  "Furan 1",
                   grepl("F02", name) ~  "Furan 2",  
                   grepl("F04", name) ~  "Furan 4",  
                   grepl("F06", name) ~  "Furan 6", 
                   grepl("F07", name) ~  "Furan 7",   
                   grepl("TCD", name) ~     "TCDD",
                   grepl("189", name) ~  "PCB 189",  
                   grepl("196", name) ~  "PCB 196", 
                   grepl("199", name) ~  "PCB 199", 
                   grepl("D02", name) ~ "Dioxin 2", 
                   grepl("F09", name) ~  "Furan 9"  )
         name
}

col_rename = function(pops) {
      colnames(pops) <- str_sub(colnames(pops), 1, 6)
      colnames(pops) <- str_replace(colnames(pops), "lbxd", "D")
      colnames(pops) <- str_replace(colnames(pops), "lbxf", "F")
      colnames(pops) <- str_replace(colnames(pops), "lbxtcd", "TCDD")
      colnames(pops) <- str_replace(colnames(pops), "lbx", "PCB")
      if ("pops$PCBpcb" %in% colnames(pops)) {
      pops = pops %>% rename(PCB169 = PCBhxc, PCB126 = PCBpcb)}
      return(pops)
      }

# this takes proportion detected (1 - proportion nondetect)
prop <- function (x) {1 - (sum(x, na.rm = TRUE)/length(x[!is.na(x)]))}
```

```{r}
nhanes %>% dplyr::select(grep("lc", names(.))) %>% 
            summarize_all(prop) %>% 
  pivot_longer(lbd074lc:lbdf09lc) %>%
  mutate(name = str_to_upper(name),
         name = pop_rename(name),
         name = fct_reorder(name, value)) %>% 
  ggplot(aes(x = name, y = value)) +
  geom_segment( aes(x=name, xend=name, y=0, yend=value), color="grey") +
  geom_point( color="orange", size=2) +
  theme_light() +
  theme(panel.grid.major.x = element_blank(),
        panel.border = element_blank(),
       axis.ticks.x = element_blank(),
       axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "% > LOD", n = "")

detected = nhanes %>% dplyr::select(grep("lc", names(.))) %>% 
            summarize_all(prop) %>% 
  pivot_longer(lbd074lc:lbdf09lc) %>%
  mutate(name = str_to_upper(name),
         name = pop_rename(name),
         name = fct_reorder(name, value)) %>% rename(Chemicals = name, detected = value)
```

```{r, process, include=FALSE}
# Select pops with detection above a certain limit
props <- nhanes %>% dplyr::select(grep("lc", names(.))) %>% 
            summarize_all(prop) 

# x is a proportion
# take all variables > x and preprocess them
# scale them and save their lods
process_pops = function(x) {
  names = props %>% select_if(~. > x) %>%
            names() %>% str_sub(., 4, 6) %>% str_c("lbx", ., "la") %>% as.vector()  

  pops <- nhanes %>% dplyr::select(all_of(names)) %>% na.omit(.)
  pops = col_rename(pops)
  
  # Matrix of 0/1
  lod_names <- nhanes %>% 
               select(names(.)[grep("lc", names(.))]) %>% 
               summarize_all(prop) %>% select_if(~. > x) %>% names() %>% as.vector()
  
  lods <- read_sas(here::here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  select(lod_names) %>% 
  na.omit()
  
  # Matrix of all values (with CDC imputed values)
  imputed <- read_sas(here::here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  select(all_of(names)) %>% 
  na.omit() %>% as.matrix()
  imputed = col_rename(imputed)
  
  # Element-wise multiplication by 1/0
  # Keep values <LOD
  # Values >LOD == 0
  # Multiply by sqrt(2) to get back LOD
  lod_matrix <- (lods * imputed) * sqrt(2)
  lod_matrix <- as.matrix(lod_matrix)
  lod_matrix <- col_rename(lod_matrix)
  #summary(lod_matrix)

  # Need to scale POPs because they have super different ranges. 
  # Need to get rid of values less than LOD to scale and then add them back.
  
  # make <LOD NA so they dont affect the scaling
  pops[pops < 0] <- NA

  # Get stand dev of values > LDO
  denoms = apply(pops, 2, function(a) sd(a, na.rm = T))
  pops_scaled = apply(pops, 2, function(a) a/sd(a, na.rm = T))
  
  # make <LOD negative again
  pops_scaled[is.na(pops_scaled)] <- -1
  pops_scaled = as.matrix(pops_scaled)

  # Also want to scale the LODS!
  # Scale lod matrix by stand dev of measurements
  lod_matrix <- lod_matrix/denoms

  # and scale imputed
  imputed = apply(imputed, 2, function(a) a/sd(a, na.rm = T))
  
  return(list(scaled_data = pops_scaled, lods = lod_matrix, sqrt2_data = imputed))
}
```

## 50% > LOD

```{r}
fifty_percent = process_pops(.5)

data_50  = as.matrix(fifty_percent$scaled_data)
delta_50 = fifty_percent$lods
imputed_50 = fifty_percent$sqrt2_data

#write_csv(as.data.frame(data_50), "./experiments/law_experiments/PCPhelpers/Data/nhanes_50.csv")
#write_csv(as.data.frame(delta_50), "./experiments/law_experiments/PCPhelpers/Data/nhanes_50_lods.csv")
```

## CV

```{r}
n = nrow(data_50)
p = ncol(data_50)

m = sqrt(p/2)
lam = 1/sqrt(n)

lambda <- c(seq(0, lam, length.out = 10)[-c(1,10)], seq(lam, 1, length.out = 5))
rank <- 1:10

grid.pop <- expand.grid(lambda = lambda, r = rank)
evals = ceiling(.07*nrow(grid.pop))

# noncvx_search <- bayes_search_cv(mat = data_50, 
#                                  pcp_func = root_pcp_noncvx_nonnegL_na_lod, 
#                                  grid_df = grid.pop,
#                                  init_evals = evals, bayes_evals = evals, 
#                                  cores = 2, runs = 5, LOD = delta_50, mu = sqrt(p/2))
# to_save = noncvx_search$formatted
# save(to_save, file = "./rootPCP-lod/nhanes_cv.rda")

# we can even continue the search by passing bayes the formatted results from the last one:
noncvx_search4 <- bayes_search_cv(mat = data_50, pcp_func = root_pcp_noncvx_nonnegL_na_lod, 
                                  grid_df = new.grid,
                                  init_evals = evals, bayes_evals = 100, 
                                  cores = 2, runs = 5, LOD = delta_50, mu = sqrt(p/2))
save2 = noncvx_search4$formatted
save(save2, file = "./rootPCP-lod/nhanes_cv.rda")
```

```{r}
new.grid = noncvx_search3$formatted %>% distinct()

print_gs(noncvx_search3$formatted)

noncvx_search3$formatted %>%
  arrange(desc(value)) %>% 
  drop_na() %>% 
  filter(r == 2) %>% arrange(lambda) %>% distinct()

new.grid %>%
  mutate(lambda = as_factor(round(lambda, 4)),
         r = as_factor(r)) %>% 
  ggplot(aes(y = lambda, x = r)) +
  geom_tile(aes(fill = value)) +
  scale_fill_viridis_c() +
  theme_test()
```

## PCP

```{r}
best.idx <- which.min(noncvx_search3$formatted$value)
optimal.lambda <- noncvx_search3$formatted$lambda[best.idx]
optimal.mu <- noncvx_search3$formatted$mu[best.idx]
optimal.r <- noncvx_search3$formatted$r[best.idx]

pcp_out <- root_pcp_noncvx_nonnegL_na_lod(D = data_50, 
                                   lambda = optimal.lambda, mu = m, 
                                   r = optimal.r, LOD = delta_50,
                                           verbose = TRUE)
#save(pcp_out, file = "./rootPCP-lod/nhanes_pcp_out.rda")
#load("./rootPCP-lod/nhanes_pcp_out.rda")
# "Converged in 10795 iterations."

L = pcp_out$L
S = pcp_out$S
```

### Sparse Matrix

```{r}
sum(S == 0)/(nrow(S)*ncol(S))
sum(S < 0)/(nrow(S)*ncol(S))
sum(S < 0.001)/(nrow(S)*ncol(S))
colnames(S)

plot_sparse <- S %>% as_tibble() %>% 
  mutate(id = 1:nrow(.)) %>% 
  select(id, everything()) %>% 
  gather(key = exposure, value = value, -id) %>%
  mutate(exposure = pop_rename(exposure),
          binary = ifelse(value < 0.001, 0, 1)) 
# sparse event (0) vs non-sparse event (not zero)
# this treats negative as sparse      event, too
```

```{r fig.width = 10}
plot_sparse %>%
ggplot(aes(x = exposure, y = id)) +
  geom_tile(aes(fill = as.factor(binary))) +
  labs(x = "Exposure", y = "Participant", 
       title = "Sparse matrix of rare events", fill = "Magnitude") +
  theme_test() +
  scale_fill_manual(values = c("white", "red")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")
```

### Patterns

```{r}
ggcorr(L, method = c("everything", "spearman"), limits = FALSE,
       label = TRUE, label_size = 3, label_alpha = TRUE,
       hjust = 0.85, size = 3, color = "grey50", layout.exp = 1) + ggtitle("Low Rank Matrix from LOD PCP")
```

### PCA of low rank matrix

```{r}
# Default is scale = false but this is ok bc we scaled data to begin with
pcp_pca <- prcomp(L)
pcp_pca$sdev

fviz_eig(pcp_pca, main = "PCA on Low Rank Matrix",
         xlab = "Principal components") 

# plot rotations (loadings) of chemicals on patterns in low rank matrix
pcp_plot = pcp_pca$rotation %>% 
  as_tibble() %>% 
  mutate(Chemicals = colnames(data_50)) %>% 
  select(Chemicals, PC1:PC3) %>% 
  gather(key = Component, value = Loadings, -Chemicals) %>%
  mutate(Group = pop_label_groups(Chemicals)) %>%
  mutate(Chemicals = pop_rename(Chemicals),
         Chemicals = fct_reorder(Chemicals, Group)) %>% 
  ggplot(aes(x = Chemicals, y = Loadings, color = Group)) + geom_point() +
  geom_segment(aes(yend=0, xend = Chemicals)) +
  facet_wrap(.~Component) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        strip.background = element_blank()) + labs(title = "PCA on PCP L matrix")
pcp_plot
```

## PCA

```{r}
# data already scaled
pca_50 <- prcomp(imputed_50)

pca_50$sdev

summary(pca_50)

pca_50$sdev^2/sum(pca_50$sdev^2)
```

```{r}
fviz_eig(pca_50, main = "PCA on Original Matrix",
         xlab = "Principal components") 

pca_plot = 
  pca_50$rotation %>% 
  as_tibble() %>% 
  mutate(Chemicals = colnames(fifty_percent$sqrt2_data)) %>% 
  select(Chemicals, PC1:PC3) %>% 
  gather(key = Component, value = Loadings, -Chemicals) %>%
  mutate(Group = pop_label_groups(Chemicals),
        Chemicals = pop_rename(Chemicals),
        Chemicals = fct_reorder(Chemicals, Group)) %>% 
  ggplot(aes(x = Chemicals, y = Loadings, color = Group)) + geom_point() +
  geom_segment(aes(yend=0, xend = Chemicals)) +
  facet_wrap(.~Component) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        strip.background = element_blank()) + labs(title = "PCA on original data (LOD/sqrt2)")
```

## PCP & PCA

```{r}
(pcp_plot + theme(axis.text.x = element_blank())) / (pca_plot + theme(legend.position = "none"))
```

```{r}
PCP_PCA <- pcp_pca$sdev^2/sum(pcp_pca$sdev^2) *100
just_PCA <- pca_50$sdev^2/sum(pca_50$sdev^2) *100
round(cbind(Component = 1:21, PCP_PCA, just_PCA), 4) %>% kable()
```

## Relative error

```{r}
mask = data_50 != -1
data_above = data_50 * mask

L_above = L*mask
S_above = S*mask

norm(data_above-L_above, "F")/norm(data_above, "F")

pca_pred = pca_50$x %*% t(pca_50$rotation) #+ kronecker(matrix(1, nrow(imputed_50), 1), t(apply(imputed_50, 2, mean)))
pca_pred_above = pca_pred*mask

imputed_50_sc = scale(imputed_50)
norm(imputed_50_sc - pca_pred, "F")/norm(imputed_50_sc, "F")

data_above_sc = scale(data_above)
norm(data_above_sc - pca_pred, "F")/norm(data_above_sc, "F") # all 21 PC

pca_pred_3 = scale(pca_50$x[,1:3] %*% t(pca_50$rotation)[1:3,])
norm(data_above_sc - pca_pred_3, "F")/norm(data_above_sc, "F") # first 3 PC
```

## NMF

#### On L matrix

```{r}
L[L < 0] = 0
any(is.null(L))
any(is.na(L))

summary(L)
L[220:221,] # one row ALL zero

L_less = L[-221,]

L_nmf = nmf(L_less, 3, method = "lee", nrun = 100)
```

```{r}
nmf_plot = coef(L_nmf) %>% 
  t() %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "Chemicals") %>% 
  pivot_longer(V1:V3) %>% 
  mutate(Chemicals = pop_rename(Chemicals),
         Group = pop_label_groups(Chemicals)) %>%
  mutate(Chemicals = fct_reorder(Chemicals, Group)) %>% 
  ggplot(aes(x = Chemicals, y = value, color = Group)) + geom_point() +
  geom_segment(aes(yend=0, xend = Chemicals)) +
  facet_wrap(.~name) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        strip.background = element_blank()) +
  labs(y = "Loadings", title = "NMF on PCP L matrix")
```

#### On original

```{r}
nmf_out = nmf(imputed_50, 3, method = "lee", nrun = 100)

plot_nmf_total = coef(nmf_out) %>% 
  t() %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "Chemicals") %>% 
  pivot_longer(V1:V3) %>% 
  mutate(name = case_when(name == "V1" ~ "V3",
                          name == "V2" ~ "V1",
                          name == "V3" ~ "V2"),
         Chemicals = pop_rename(Chemicals),
         Group = pop_label_groups(Chemicals)) %>%
  mutate(Chemicals = fct_reorder(Chemicals, Group)) %>% 
  ggplot(aes(x = Chemicals, y = value, color = Group)) + geom_point() +
  geom_segment(aes(yend=0, xend = Chemicals)) +
  facet_wrap(.~name) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        strip.background = element_blank()) +
  labs(y = "Loadings", title = "NMF on original data (LOD/sqrt2)")
```

## Viz

```{r}
(nmf_plot + theme(axis.text.x = element_blank(), legend.position = "none")) /
  (pcp_plot + theme(axis.text.x = element_blank(), legend.position = "none")) / 
  (pca_plot)

(nmf_plot + theme(axis.text.x = element_blank(), legend.position = "none")) / plot_nmf_total
```
