---
title: "NHANES POP Simulations"
author: "Lizzy Gibson"
date: "4/8/2020"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    toc_depth: 5
    code_folding: 'hide'
---

```{r setup, include=FALSE}
require("knitr")
opts_chunk$set(echo = TRUE)
options(scipen = 999)
library(R.matlab)
library(tidyverse)
library(gridExtra)
library(Matrix)
library(matconv)
library(patchwork)
library(janitor)
library(ggcorrplot)
library(ggfortify)  
library(factoextra)
library(knitr)
library(haven)
library(rlist)
library(mvtnorm)
library(reshape2)
library(GGally)
library(grDevices)
```

## NHANES

NHANES 2001-2002 POP data.

```{r}
nhanes <- read_sas(here::here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names()

head(nhanes)[1:7]
```

LA = lipid adjusted  
LC = comment code  

### Select

CDC imputes values \<LOD as LOD/sqrt(2). Here, if comment code = "below detectable limit", LC = 1.

```{r}
prop <- function (x) {1 - (sum(x, na.rm = TRUE)/nrow(nhanes))}

names <- nhanes %>% select(names(.)[grep("lc", names(.))]) %>% 
  summarize_all(prop) %>% select_if(~. > 0.2) %>% names() %>% str_sub(., 4, 6) %>% str_c("lbx", ., "la") %>% as.vector()

pops <- nhanes %>% 
  select(!!names) %>% na.omit(.)

names(pops) <- str_sub(names(pops), 1, 6)
names(pops) <- str_replace(names(pops), "lbxd", "D")
names(pops) <- str_replace(names(pops), "lbxf", "F")
names(pops) <- str_replace(names(pops), "lbx", "PCB")
pops

ggcorr(pops, method = c("everything", "spearman"), limits = FALSE,
       label = TRUE, label_size = 3, label_alpha = TRUE,
       hjust = 0.85, size = 3, color = "grey50", layout.exp = 1) + ggtitle("Persistent organic pollutants \n in NHANES 2001-2002")
```

### Simulate

Remove comment codes for simulations.  
Remove NA for simulations.

```{r}
# Vector of NHANES means
# log to approx normal dist
means <- as_vector(map(log(pops), function(x) mean(x, na.rm = TRUE)))

# Covariance matrix from NHANES
# log to approx normal dist
covs <- cov(log(pops))

# Simulate with multivariate normal function
# exp multi-normal to get multi-log normal
set.seed(1988)
sim_all <- exp(rmvnorm(1000, mean = means, sigma = covs)) %>% as_tibble()
```

```{r}
ggcorr(sim_all, method = c("everything", "spearman"), limits = FALSE,
       label = TRUE, label_size = 3, label_alpha = TRUE,
       hjust = 0.85, size = 3, color = "grey50", layout.exp = 1) + ggtitle("Simulated Data")
```

### Scale Simulations

Divide by standard deviation, do not mean center.  

```{r}
sim_all <- sim_all %>% 
  mutate_all(scale, center = FALSE)
```

### Create \<LOD Datasets

```{r, neg}
# Create version with 10% lowest values for each variable as below the LOD
mix_data_lod_10 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .10), -1, .)) %>% as.matrix()

# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .20), -1, .)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .30), -1, .)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .40), -1, .)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .50), -1, .)) %>% as.matrix()

# Create version with 10% lowest values for each variable as below the LOD
mix_data_lod_10_0 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .10), 0, .)) %>% as.matrix()

# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20_0 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .20), 0, .)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30_0 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .30), 0, .)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40_0 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .40), 0, .)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50_0 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .50), 0, .)) %>% as.matrix()

# Create version with 10% lowest values for each variable as below the LOD
mix_data_lod_10_sqrt2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .10), (quantile(., probs = .10)/sqrt(2)), .)) %>% as.matrix()

# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20_sqrt2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .20), (quantile(., probs = .20)/sqrt(2)), .)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30_sqrt2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .30), (quantile(., probs = .30)/sqrt(2)), .)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40_sqrt2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .40), (quantile(., probs = .40)/sqrt(2)), .)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50_sqrt2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .50), (quantile(., probs = .50)/sqrt(2)), .)) %>% as.matrix()
```

### Quantiles = LOD

```{r}
delta10 <- sim_all %>% 
  summarise_all(quantile, probs = .10) %>% as_vector()

delta20 <- sim_all %>% 
  summarise_all(quantile, probs = .20) %>% as_vector()

delta30 <- sim_all %>% 
  summarise_all(quantile, probs = .30) %>% as_vector()

delta40 <- sim_all %>% 
  summarise_all(quantile, probs = .40) %>% as_vector()

delta50 <- sim_all %>% 
  summarise_all(quantile, probs = .50) %>% as_vector()
```

## Fuctions

```{r, nn_function}
prox_l1 <- function(Y, c) {
  
  myzero <- matrix(data = 0, ncol = ncol(Y), nrow = nrow(Y))
  X <- sign(Y) * pmax(abs(Y) - c, myzero, na.rm = TRUE)
  X
} 

############################################################

prox_nuclear <- function(Y, c) {
  
  USV <- svd(Y)
  U <- USV$u
  S <- USV$d
  V <- USV$v
  
  myzero <- vector("numeric", length = length(S))
  S_new <- sign(S) * pmax(abs(S) - c, myzero, na.rm = TRUE)
  X <- U %*% diag(S_new) %*% t(V)
  nuclearX  <- sum(abs(S_new))

    list(X = X, nuclearX = nuclearX)
}

############################################################

is_same <- function(SAME_THRESH, ...) {
  flag <- TRUE
  varargin <- list(...)
  if (length(varargin) == 2) {
    if (max(abs(varargin[[1]] - varargin[[2]])) > SAME_THRESH) {
      flag <- FALSE
    }
  }
  else if (length(varargin) == 3) {
    if ((max(abs(varargin[[1]] - varargin[[2]])) > SAME_THRESH) |
        (max(abs(varargin[[1]] - varargin[[3]])) > SAME_THRESH) |
        (max(abs(varargin[[2]] - varargin[[3]])) > SAME_THRESH)) {
      flag <- FALSE
    }
  }
  flag
}

############################################################

loss_lod_NN <- function(X, D, LOD) {

    X_lod <- ((X - D)     * (D >= LOD)) +
            ((X - LOD)  * ((D < LOD) & (X > LOD))) +
              (X          * ((D < LOD) & (X < 0)))
  
  l <- sum(X_lod^2) / 2
  l
}

############################################################

pcp_lod_NN <- function(D, lambda, mu, LOD) {
  
  if( any(D < matrix(0, nrow = nrow(D), ncol = ncol(D))) ) stop("Physical concentration measurements cannot be negative.")
  
  m <- nrow(D)
  n <- ncol(D)
  rho <- 1 # Augmented Lagrangian coefficient (rate)
  
  L1 <- matrix(0, m, n)
  L2 <- matrix(0, m, n)
  L3 <- matrix(0, m, n)
  
  S1 <- matrix(0, m, n)
  S2 <- matrix(0, m, n)
  
  Z1 <- matrix(0, m, n)
  Z2 <- matrix(0, m, n)
  Z3 <- matrix(0, m, n)
  
  # Max iteration
  MAX_ITER <- 5000
  
  # Convergence Thresholds
  LOSS_THRESH <- 1e-5
  SAME_THRESH <- 1e-4
  
  if (is.vector(LOD)) {
    empty = matrix(TRUE, nrow = nrow(D), ncol = ncol(D))
    LOD = t(t(empty) * LOD)
  }
  
  if( any(LOD < matrix(0, nrow = nrow(LOD), ncol = ncol(LOD))) ) stop("Physical Limits of Detection (LOD) cannot be negative.")
  
  loss <- vector("numeric", MAX_ITER)
  
  for (i in 1:MAX_ITER) {
    
    nuc <- prox_nuclear( ((L2 + L3 - (Z1 + Z2)/rho)/2), 1/2/rho)
    L1 <- nuc[[1]]
    nuclearL1 <- nuc[[2]] #nuclearX
    # % L, Z, S all start at zero, and change each iteration
    # % Prox_nuc is singular value thresholding
    # % L is low rank matrix
    
    S1 <- prox_l1((S2 - Z3/rho), lambda/rho)
    # % S is sparse matrix
    
      L2_opt1 <- (mu*rho*D     + (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)
      L2_opt2 <- L1 + Z1/rho
      L2_opt3 <- ((mu*rho*LOD + (((mu + rho)*Z1) - (mu*Z3) + ((mu + rho)*rho*L1) - (mu*rho*S1)))) / ((2*mu*rho) + (rho^2))
      L2_opt4 <- (               (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)

      L2_new <- (L2_opt1 * (( D >= LOD))) +
                (L2_opt2 * (((D < LOD) & ((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
                (L2_opt3 * (((D < LOD) & ((L2 + S2) > LOD)))) +
                (L2_opt4 * (((D < LOD) & ((L2 + S2) < 0))))

      S2_opt1 <- (mu*rho*D     + (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)
      S2_opt2 <- S1 + (Z3/rho)
      S2_opt3 <- (((mu*rho*LOD) + (((mu + rho)*Z3) - (mu*Z1) + ((mu + rho)*rho*S1) - (mu*rho*L1)))) / ((2*mu*rho) + (rho^2))
      S2_opt4 <- (               (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)

      S2 <- (S2_opt1 * (( D >= LOD))) +
            (S2_opt2 * (((D < LOD) & ((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
            (S2_opt3 * (((D < LOD) & ((L2 + S2) > LOD)))) +
            (S2_opt4 * (((D < LOD) & ((L2 + S2) < 0))))
   
    L2 <- L2_new
    
    L3 <- pmax(L1 + Z2/rho, 0, na.rm = TRUE)
    # % Non-Negativity constraint!
    
    Z1 <- Z1 + rho*(L1 - L2)
    Z2 <- Z2 + rho*(L1 - L3)
    Z3 <- Z3 + rho*(S1 - S2)
    # % Z accumulate differnces between L and L and between S and S
    
    loss[i] <- nuclearL1 + 
      (lambda*sum(abs(S1))) +
      (mu*loss_lod_NN((L2 + S2), D, LOD)) +
      sum(Z1*(L1 - L2)) +
      sum(Z2*(L1 - L3)) +
      sum(Z3*(S1 - S2)) +
      (rho/2 * (sum((L1-L2)^2) + sum((L1 - L3)^2) + sum((S1 - S2)^2)))
    # % The code block above takes LOD into account.
    
    print(str_c(i, " Obj: ", loss[i]))
      
    if ((i != 1) && 
        (abs(loss[i-1] - loss[i]) < LOSS_THRESH) && 
        is_same(SAME_THRESH, L1, L2, L3) &&
        is_same(SAME_THRESH, S1, S2)) {
      break} # % Convergence criteria!
  }
  
  L <- L3 # (L1 + L2 + L3) / 3
  S <- S1 #(S1 + S2) / 2
  list(L = L, S = S, loss = loss)
}
```

```{r, older}
loss_lod <- function(X, D, LOD) {

    X_lod <- ((X - D)     * (D >= 0)) +
             ((X - LOD)   * (D < 0 & (X > LOD))) +
              (X          * (D < 0 & X < 0))
  
  l <- sum(X_lod^2) / 2
  l
}

############################################################

pcp_lod <- function(D, lambda, mu, LOD) {
  
  m <- nrow(D)
  n <- ncol(D)
  rho <- 1 # Augmented Lagrangian coefficient (rate)
  
  L1 <- matrix(0, m, n)
  L2 <- matrix(0, m, n)
  L3 <- matrix(0, m, n)
  
  S1 <- matrix(0, m, n)
  S2 <- matrix(0, m, n)
  
  Z1 <- matrix(0, m, n)
  Z2 <- matrix(0, m, n)
  Z3 <- matrix(0, m, n)
  
  # Max iteration
  MAX_ITER <- 5000
  
  # Convergence Thresholds
  LOSS_THRESH <- 1e-5
  SAME_THRESH <- 1e-4
  
  if (is.vector(LOD)) {
    empty = matrix(1, nrow = nrow(D), ncol = ncol(D))
    LOD = t(t(empty) * LOD)
  }
  
  loss <- vector("numeric", MAX_ITER)
  
  for (i in 1:MAX_ITER) {
    
    nuc <- prox_nuclear( ((L2 + L3 - (Z1 + Z2)/rho)/2), 1/2/rho)
    L1 <- nuc[[1]]
    nuclearL1 <- nuc[[2]] #nuclearX
    
    S1 <- prox_l1((S2 - Z3/rho), lambda/rho)
    
      L2_opt1 <- (mu*rho*D     + (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)
      L2_opt2 <- L1 + Z1/rho
      L2_opt3 <- ((mu*rho*LOD + (((mu + rho)*Z1) - (mu*Z3) + ((mu + rho)*rho*L1) - (mu*rho*S1)))) / ((2*mu*rho) + (rho^2))
      L2_opt4 <- (               (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)

      L2_new <- (L2_opt1 * (D >= 0)) +
        (L2_opt2 * ((D < 0) & (((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
        (L2_opt3 * ((D < 0) & (((L2 + S2) > LOD)))) +
        (L2_opt4 * ((D < 0) & (((L2 + S2) < 0))))

      S2_opt1 <- (mu*rho*D     + (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)
      S2_opt2 <- S1 + (Z3/rho)
      S2_opt3 <- (((mu*rho*LOD) + (((mu + rho)*Z3) - (mu*Z1) + ((mu + rho)*rho*S1) - (mu*rho*L1)))) / ((2*mu*rho) + (rho^2))
      S2_opt4 <- (               (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)

      S2 <- (S2_opt1 * (D >= 0)) +
        (S2_opt2 * (((D < 0) & ((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
        (S2_opt3 * (((D < 0) & ((L2 + S2) > LOD)))) +
        (S2_opt4 * (((D < 0) & ((L2 + S2) < 0))))
   
    L2 <- L2_new
    
    L3 <- pmax(L1 + Z2/rho, 0, na.rm = TRUE)
    # % Non-Negativity constraint!
    
    Z1 <- Z1 + rho*(L1 - L2)
    Z2 <- Z2 + rho*(L1 - L3)
    Z3 <- Z3 + rho*(S1 - S2)
    # % Z accumulate differnces between L and L and between S and S
    
    loss[i] <- nuclearL1 + 
      (lambda*sum(abs(S1))) +
      (mu*loss_lod((L2 + S2), D, LOD)) +
      sum(Z1*(L1 - L2)) +
      sum(Z2*(L1 - L3)) +
      sum(Z3*(S1 - S2)) +
      (rho/2 * (sum((L1-L2)^2) + sum((L1 - L3)^2) + sum((S1 - S2)^2)))
    # % The code block above takes LOD into account.
    
    print(str_c(i, " Obj: ", loss[i]))
        
    if ((i != 1) && 
        (abs(loss[i-1] - loss[i]) < LOSS_THRESH) && 
        is_same(SAME_THRESH, L1, L2, L3) &&
        is_same(SAME_THRESH, S1, S2)) {
      break} # % Convergence criteria!
  }
  
  L <- L3 # (L1 + L2 + L3) / 3
  S <- S1 #(S1 + S2) / 2
  list(L = L, S = S, loss = loss)
}
```

```{r}
soft_thresholding <- function(v, lambda) {
  myzero <- matrix(data = 0, ncol = ncol(v), nrow = nrow(v))
  w <- sign(v) * pmax(abs(v) - lambda, myzero)
  w
} 

soft_thresholding_diag <- function(v, lambda) {
  myzero <- vector("numeric", length = length(v))
  w <- sign(v) * pmax(abs(v) - lambda, myzero)
  w
} 

singular_value_threshold <- function(M, lambda) {
  
  USV <- svd(M)
  U <- USV$u
  S <- USV$d
  V <- USV$v
    
  N <- U %*% diag(soft_thresholding_diag(S, lambda)) %*% t(V)
  
  v  <- sum(soft_thresholding_diag(S, lambda))
  
  svt <- list(N = N, v = v) 
  svt
}

original_pcp <- function(D, lambda, mu) {
  
  m <- nrow(D)
  n <- ncol(D)
  
  S <- matrix(0, nrow = m, ncol = n)
  L <- matrix(0, nrow = m, ncol = n)
  
  iter <- 0
  MAX_ITER <- 5000
  done <- FALSE
  
  # Convergence Thresholds
  LOSS_THRESH <- 1e-4
  loss <- vector("numeric", MAX_ITER)
  
  while (!done) {
    
    iter <- iter + 1
    
    svt <- singular_value_threshold((D - S), 1/mu)
    L <- svt[[1]] #svt$N
    v <- svt[[2]]
    
    S <- soft_thresholding((D - L), lambda/mu)
    
    obj <- v + lambda * sum(abs(S)) + (mu/2) * norm((D - L - S), type = "F")^2
    loss[iter] <- obj
    
    print(str_c(iter, " Obj: ", obj))
    
    if (iter >= MAX_ITER | 
        (iter != 1) && (abs(loss[iter-1] - loss[iter]) < LOSS_THRESH)) {done <- TRUE}
    
  }
  list(L = L, S = S, Lambda = lambda, Mu = mu, obj_value = obj)
}
```

## PCP

```{r, jingkai_leave, cache = TRUE}
m <- nrow(sim_all)
p <- ncol(sim_all)

lambda_mix <- 1/sqrt(m)
mu_mix <- sqrt(p/(2*log(m*p)))

mix <- as.matrix(sim_all)
  
results_0  <- pcp_lod(mix,             lambda_mix, mu_mix, 0)
results_10 <- pcp_lod(mix_data_lod_10, lambda_mix, mu_mix, delta10)
results_20 <- pcp_lod(mix_data_lod_20, lambda_mix, mu_mix, delta20)
results_30 <- pcp_lod(mix_data_lod_30, lambda_mix, mu_mix, delta30)
results_40 <- pcp_lod(mix_data_lod_40, lambda_mix, mu_mix, delta40)
results_50 <- pcp_lod(mix_data_lod_50, lambda_mix, mu_mix, delta50)

nn_results_0  <- pcp_lod_NN(mix, lambda_mix, mu_mix, 0)
nn_results_10 <- pcp_lod_NN(mix, lambda_mix, mu_mix, delta10)
nn_results_20 <- pcp_lod_NN(mix, lambda_mix, mu_mix, delta20)
nn_results_30 <- pcp_lod_NN(mix, lambda_mix, mu_mix, delta30)
nn_results_40 <- pcp_lod_NN(mix, lambda_mix, mu_mix, delta40)
nn_results_50 <- pcp_lod_NN(mix, lambda_mix, mu_mix, delta50)

L_lod0 <- results_0[[1]]
S_lod0 <- results_0[[2]]
L_lod10 <- results_10[[1]]
S_lod10 <- results_10[[2]]
L_lod20 <- results_20[[1]]
S_lod20 <- results_20[[2]]
L_lod30 <- results_30[[1]]
S_lod30 <- results_30[[2]]
L_lod40 <- results_40[[1]]
S_lod40 <- results_40[[2]]
L_lod50 <- results_50[[1]]
S_lod50 <- results_50[[2]]

nn_L_lod0 <- nn_results_0[[1]]
nn_S_lod0 <- nn_results_0[[2]]
nn_L_lod10 <- nn_results_10[[1]]
nn_S_lod10 <- nn_results_10[[2]]
nn_L_lod20 <- nn_results_20[[1]]
nn_S_lod20 <- nn_results_20[[2]]
nn_L_lod30 <- nn_results_30[[1]]
nn_S_lod30 <- nn_results_30[[2]]
nn_L_lod40 <- nn_results_40[[1]]
nn_S_lod40 <- nn_results_40[[2]]
nn_L_lod50 <- nn_results_50[[1]]
nn_S_lod50 <- nn_results_50[[2]]

# all_equal(nn_L_lod0, L_lod0)
# all_equal(nn_L_lod10, L_lod10)
# all_equal(nn_L_lod20, L_lod20)
# all_equal(nn_L_lod30, L_lod30)
# all_equal(nn_L_lod40, L_lod40)
# all_equal(nn_L_lod50, L_lod50)
```

```{r, subzero_old, cache = TRUE}
results_0_0  <- original_pcp(mix,               lambda_mix, mu_mix)
results_10_0 <- original_pcp(mix_data_lod_10_0, lambda_mix, mu_mix)
results_20_0 <- original_pcp(mix_data_lod_20_0, lambda_mix, mu_mix)
results_30_0 <- original_pcp(mix_data_lod_30_0, lambda_mix, mu_mix)
results_40_0 <- original_pcp(mix_data_lod_40_0, lambda_mix, mu_mix)
results_50_0 <- original_pcp(mix_data_lod_50_0, lambda_mix, mu_mix)

L_lod0_0 <- results_0_0[[1]]
S_lod0_0 <- results_0_0[[2]]
L_lod10_0 <- results_10_0[[1]]
S_lod10_0 <- results_10_0[[2]]
L_lod20_0 <- results_20_0[[1]]
S_lod20_0 <- results_20_0[[2]]
L_lod30_0 <- results_30_0[[1]]
S_lod30_0 <- results_30_0[[2]]
L_lod40_0 <- results_40_0[[1]]
S_lod40_0 <- results_40_0[[2]]
L_lod50_0 <- results_50_0[[1]]
S_lod50_0 <- results_50_0[[2]]

results_0_sqrt2  <- original_pcp(mix,                   lambda_mix, mu_mix)
results_10_sqrt2 <- original_pcp(mix_data_lod_10_sqrt2, lambda_mix, mu_mix)
results_20_sqrt2 <- original_pcp(mix_data_lod_20_sqrt2, lambda_mix, mu_mix)
results_30_sqrt2 <- original_pcp(mix_data_lod_30_sqrt2, lambda_mix, mu_mix)
results_40_sqrt2 <- original_pcp(mix_data_lod_40_sqrt2, lambda_mix, mu_mix)
results_50_sqrt2 <- original_pcp(mix_data_lod_50_sqrt2, lambda_mix, mu_mix)

L_lod0_sqrt2 <- results_0_sqrt2[[1]]
S_lod0_sqrt2 <- results_0_sqrt2[[2]]
L_lod10_sqrt2 <- results_10_sqrt2[[1]]
S_lod10_sqrt2 <- results_10_sqrt2[[2]]
L_lod20_sqrt2 <- results_20_sqrt2[[1]]
S_lod20_sqrt2 <- results_20_sqrt2[[2]]
L_lod30_sqrt2 <- results_30_sqrt2[[1]]
S_lod30_sqrt2 <- results_30_sqrt2[[2]]
L_lod40_sqrt2 <- results_40_sqrt2[[1]]
S_lod40_sqrt2 <- results_40_sqrt2[[2]]
L_lod50_sqrt2 <- results_50_sqrt2[[1]]
S_lod50_sqrt2 <- results_50_sqrt2[[2]]
```

## X - L - S

```{r}
F_norm <- as_tibble(cbind(lod0 = norm((mix - L_lod0 - S_lod0), type = "F")/norm((mix), type = "F"),
      lod10 = norm((mix - L_lod10 - S_lod10), type = "F")/norm((mix), type = "F"),
      lod20 = norm((mix - L_lod20 - S_lod20), type = "F")/norm((mix), type = "F"),
      lod30 = norm((mix - L_lod30 - S_lod30), type = "F")/norm((mix), type = "F"),
      lod40 = norm((mix - L_lod40 - S_lod40), type = "F")/norm((mix), type = "F"),
      lod50 = norm((mix - L_lod50 - S_lod50), type = "F")/norm((mix), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "LOD PCP")

nn_F_norm <- as_tibble(cbind(lod0 = norm((mix - nn_L_lod0 - nn_S_lod0), type = "F")/norm((mix), type = "F"),
      lod10 = norm((mix - nn_L_lod10 - nn_S_lod10), type = "F")/norm((mix), type = "F"),
      lod20 = norm((mix - nn_L_lod20 - nn_S_lod20), type = "F")/norm((mix), type = "F"),
      lod30 = norm((mix - nn_L_lod30 - nn_S_lod30), type = "F")/norm((mix), type = "F"),
      lod40 = norm((mix - nn_L_lod40 - nn_S_lod40), type = "F")/norm((mix), type = "F"),
      lod50 = norm((mix - nn_L_lod50 - nn_S_lod50), type = "F")/norm((mix), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Both")

F_norm_0 <- as_tibble(cbind(lod0 = norm((mix - L_lod0_0 - S_lod0_0), type = "F")/norm((mix), type = "F"),
      lod10 = norm((mix - L_lod10_0 - S_lod10_0), type = "F")/norm((mix), type = "F"),
      lod20 = norm((mix - L_lod20_0 - S_lod20_0), type = "F")/norm((mix), type = "F"),
      lod30 = norm((mix - L_lod30_0 - S_lod30_0), type = "F")/norm((mix), type = "F"),
      lod40 = norm((mix - L_lod40_0 - S_lod40_0), type = "F")/norm((mix), type = "F"),
      lod50 = norm((mix - L_lod50_0 - S_lod50_0), type = "F")/norm((mix), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP w/ 0")

F_norm_sqrt2 <- as_tibble(cbind(lod0 = norm((mix - L_lod0_sqrt2 - S_lod0_sqrt2), type = "F")/norm((mix), type = "F"),
      lod10 = norm((mix - L_lod10_sqrt2 - S_lod10_sqrt2), type = "F")/norm((mix), type = "F"),
      lod20 = norm((mix - L_lod20_sqrt2 - S_lod20_sqrt2), type = "F")/norm((mix), type = "F"),
      lod30 = norm((mix - L_lod30_sqrt2 - S_lod30_sqrt2), type = "F")/norm((mix), type = "F"),
      lod40 = norm((mix - L_lod40_sqrt2 - S_lod40_sqrt2), type = "F")/norm((mix), type = "F"),
      lod50 = norm((mix - L_lod50_sqrt2 - S_lod50_sqrt2), type = "F")/norm((mix), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))
```

### Viz

```{r, fig.height = 5, fig.width = 5, fig.align = "center"}
rbind(F_norm_sqrt2, F_norm_0, F_norm) %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point(aes(color = Method)) + geom_path(aes(group = Method, color = Method)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(X-L-S) / norm(X)",
       title = "Relative Prediction Error")
```

## Individual Solution Matrices

```{r}
L_diff <- as_tibble(cbind(lod0 = norm((L_lod0 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      lod10 = norm((L_lod10 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      lod20 = norm((L_lod20 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      lod30 = norm((L_lod30 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      lod40 = norm((L_lod40 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      lod50 = norm((L_lod50 - L_lod0), type = "F")/norm((L_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank",
         Method = "LOD PCP")

S_diff <- as_tibble(cbind(lod0 = norm((S_lod0 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      lod10 = norm((S_lod10 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      lod20 = norm((S_lod20 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      lod30 = norm((S_lod30 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      lod40 = norm((S_lod40 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      lod50 = norm((S_lod50 - S_lod0), type = "F")/norm((S_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse",
         Method = "LOD PCP")

nn_L_diff <- as_tibble(cbind(lod0 = norm((nn_L_lod0 - nn_L_lod0), type = "F")/norm((nn_L_lod0), type = "F"),
      lod10 = norm((nn_L_lod10 - nn_L_lod0), type = "F")/norm((nn_L_lod0), type = "F"),
      lod20 = norm((nn_L_lod20 - nn_L_lod0), type = "F")/norm((nn_L_lod0), type = "F"),
      lod30 = norm((nn_L_lod30 - nn_L_lod0), type = "F")/norm((nn_L_lod0), type = "F"),
      lod40 = norm((nn_L_lod40 - nn_L_lod0), type = "F")/norm((nn_L_lod0), type = "F"),
      lod50 = norm((nn_L_lod50 - nn_L_lod0), type = "F")/norm((nn_L_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank")

nn_S_diff <- as_tibble(cbind(lod0 = norm((nn_S_lod0 - nn_S_lod0), type = "F")/norm((nn_S_lod0), type = "F"),
      lod10 = norm((nn_S_lod10 - nn_S_lod0), type = "F")/norm((nn_S_lod0), type = "F"),
      lod20 = norm((nn_S_lod20 - nn_S_lod0), type = "F")/norm((nn_S_lod0), type = "F"),
      lod30 = norm((nn_S_lod30 - nn_S_lod0), type = "F")/norm((nn_S_lod0), type = "F"),
      lod40 = norm((nn_S_lod40 - nn_S_lod0), type = "F")/norm((nn_S_lod0), type = "F"),
      lod50 = norm((nn_S_lod50 - nn_S_lod0), type = "F")/norm((nn_S_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse")

L_diff_0 <- as_tibble(cbind(lod0 = norm((L_lod0_0 - L_lod0_0), type = "F")/norm((L_lod0_0), type = "F"),
      lod10 = norm((L_lod10_0 - L_lod0_0), type = "F")/norm((L_lod0_0), type = "F"),
      lod20 = norm((L_lod20_0 - L_lod0_0), type = "F")/norm((L_lod0_0), type = "F"),
      lod30 = norm((L_lod30_0 - L_lod0_0), type = "F")/norm((L_lod0_0), type = "F"),
      lod40 = norm((L_lod40_0 - L_lod0_0), type = "F")/norm((L_lod0_0), type = "F"),
      lod50 = norm((L_lod50_0 - L_lod0_0), type = "F")/norm((L_lod0_0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank",
         Method = "PCP w/ 0")

S_diff_0 <- as_tibble(cbind(lod0 = norm((S_lod0_0 - S_lod0_0), type = "F")/norm((S_lod0_0), type = "F"),
      lod10 = norm((S_lod10_0 - S_lod0_0), type = "F")/norm((S_lod0_0), type = "F"),
      lod20 = norm((S_lod20_0 - S_lod0_0), type = "F")/norm((S_lod0_0), type = "F"),
      lod30 = norm((S_lod30_0 - S_lod0_0), type = "F")/norm((S_lod0_0), type = "F"),
      lod40 = norm((S_lod40_0 - S_lod0_0), type = "F")/norm((S_lod0_0), type = "F"),
      lod50 = norm((S_lod50_0 - S_lod0_0), type = "F")/norm((S_lod0_0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse",
         Method = "PCP w/ 0")

L_diff_sqrt2 <- as_tibble(cbind(lod0 = norm((L_lod0_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"),
      lod10 = norm((L_lod10_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"),
      lod20 = norm((L_lod20_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"),
      lod30 = norm((L_lod30_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"),
      lod40 = norm((L_lod40_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"),
      lod50 = norm((L_lod50_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank",
         Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))

S_diff_sqrt2 <- as_tibble(cbind(lod0 = norm((S_lod0_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"),
      lod10 = norm((S_lod10_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"),
      lod20 = norm((S_lod20_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"),
      lod30 = norm((S_lod30_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"),
      lod40 = norm((S_lod40_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"),
      lod50 = norm((S_lod50_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse",
         Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))
```

### Viz

```{r, fig.height = 5, fig.width = 5, fig.align = "center"}
rbind(L_diff_sqrt2, S_diff_sqrt2,
      L_diff, S_diff,
      L_diff_0, S_diff_0) %>% ggplot(aes(x = percent_blod, y = norm, group = interaction(Matrix,Method), color = Method)) + 
  geom_point() + geom_path(aes(linetype = Matrix)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(difference) / norm(lod0))",
       title = "Relative Error in Solution Matrices")
```

## Values \<LOD vs \>LOD

```{r}
# BELOW LOD
# TRUE = <LOD
tf_lod_0 <- sim_all %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_0 <- as.matrix(tf_lod_0*L_lod0)
s_blod_0 <- as.matrix(tf_lod_0*S_lod0)
blod_0 <- as.matrix(sim_all*tf_lod_0)

tf_lod_10 <- mix_data_lod_10 %>% 
  as_tibble() %>%
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_10 <- as.matrix(tf_lod_10*L_lod10)
s_blod_10 <- as.matrix(tf_lod_10*S_lod10)
blod_10 <- as.matrix(sim_all*tf_lod_10)

tf_lod_20 <- mix_data_lod_20 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_20 <- as.matrix(tf_lod_20*L_lod20)
s_blod_20 <- as.matrix(tf_lod_20*S_lod20)
blod_20 <- as.matrix(sim_all*tf_lod_20)

tf_lod_30 <- mix_data_lod_30 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_30 <- as.matrix(tf_lod_30*L_lod30)
s_blod_30 <- as.matrix(tf_lod_30*S_lod30)
blod_30 <- as.matrix(sim_all*tf_lod_30)

tf_lod_40 <- mix_data_lod_40 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_40 <- as.matrix(tf_lod_40*L_lod40)
s_blod_40 <- as.matrix(tf_lod_40*S_lod40)
blod_40 <- as.matrix(sim_all*tf_lod_40)

tf_lod_50 <- mix_data_lod_50 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_50 <- as.matrix(tf_lod_50*L_lod50)
s_blod_50 <- as.matrix(tf_lod_50*S_lod50)
blod_50 <- as.matrix(sim_all*tf_lod_50) 

#Subtract true values and divide by norm of true
less_diff <- as_tibble(cbind(lod0 = norm((blod_0 - l_blod_0 - s_blod_0), type = "F"), #/norm((mix), type = "F"),
      lod10 = norm((blod_10 - l_blod_10 - s_blod_10), type = "F")/norm((blod_10), type = "F"),
      lod20 = norm((blod_20 - l_blod_20 - s_blod_20), type = "F")/norm((blod_20), type = "F"),
      lod30 = norm((blod_30 - l_blod_30 - s_blod_30), type = "F")/norm((blod_30), type = "F"),
      lod40 = norm((blod_40 - l_blod_40 - s_blod_40), type = "F")/norm((blod_40), type = "F"),
      lod50 = norm((blod_50 - l_blod_50 - s_blod_50), type = "F")/norm((blod_50), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "< LOD",
         Method = "LOD PCP")

l_above_blod_0 <- as.matrix((!tf_lod_0)*L_lod0)
s_above_blod_0 <- as.matrix((!tf_lod_0)*S_lod0)

l_above_blod_10 <- as.matrix((!tf_lod_10)*L_lod10)
s_above_blod_10 <- as.matrix((!tf_lod_10)*S_lod10)

l_above_blod_20 <- as.matrix((!tf_lod_20)*L_lod20)
s_above_blod_20 <- as.matrix((!tf_lod_20)*S_lod20)

l_above_blod_30 <- as.matrix((!tf_lod_30)*L_lod30)
s_above_blod_30 <- as.matrix((!tf_lod_30)*S_lod30)

l_above_blod_40 <- as.matrix((!tf_lod_40)*L_lod40)
s_above_blod_40 <- as.matrix((!tf_lod_40)*S_lod40)

l_above_blod_50 <- as.matrix((!tf_lod_50)*L_lod50)
s_above_blod_50 <- as.matrix((!tf_lod_50)*S_lod50)

#divide by true values
above_diff <- as_tibble(cbind(
  lod0  = norm((mix  - l_above_blod_0  - s_above_blod_0),  type = "F")/norm(mix,  type = "F"),
  lod10 = norm((mix_data_lod_10_0 - l_above_blod_10 - s_above_blod_10), type = "F")/norm(mix_data_lod_10_0, type = "F"),
  lod20 = norm((mix_data_lod_20_0 - l_above_blod_20 - s_above_blod_20), type = "F")/norm(mix_data_lod_20_0, type = "F"),
  lod30 = norm((mix_data_lod_30_0 - l_above_blod_30 - s_above_blod_30), type = "F")/norm(mix_data_lod_30_0, type = "F"),
  lod40 = norm((mix_data_lod_40_0 - l_above_blod_40 - s_above_blod_40), type = "F")/norm(mix_data_lod_40_0, type = "F"),
  lod50 = norm((mix_data_lod_50_0 - l_above_blod_50 - s_above_blod_50), type = "F")/norm(mix_data_lod_50_0, type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "> LOD",
         Method = "LOD PCP")

nn_l_blod_0 <- as.matrix(tf_lod_0*nn_L_lod0)
nn_s_blod_0 <- as.matrix(tf_lod_0*nn_S_lod0)

nn_l_blod_10 <- as.matrix(tf_lod_10*nn_L_lod10)
nn_s_blod_10 <- as.matrix(tf_lod_10*nn_S_lod10)

nn_l_blod_20 <- as.matrix(tf_lod_20*nn_L_lod20)
nn_s_blod_20 <- as.matrix(tf_lod_20*nn_S_lod20)

nn_l_blod_30 <- as.matrix(tf_lod_30*nn_L_lod30)
nn_s_blod_30 <- as.matrix(tf_lod_30*nn_S_lod30)

nn_l_blod_40 <- as.matrix(tf_lod_40*nn_L_lod40)
nn_s_blod_40 <- as.matrix(tf_lod_40*nn_S_lod40)

nn_l_blod_50 <- as.matrix(tf_lod_50*nn_L_lod50)
nn_s_blod_50 <- as.matrix(tf_lod_50*nn_S_lod50)

#Subtract true values and divide by norm of true
nn_less_diff <- as_tibble(cbind(lod0 = norm((blod_0 - nn_l_blod_0 - nn_s_blod_0), type = "F"), #/norm((mix), type = "F"),
      lod10 = norm((blod_10 - nn_l_blod_10 - nn_s_blod_10), type = "F")/norm((blod_10), type = "F"),
      lod20 = norm((blod_20 - nn_l_blod_20 - nn_s_blod_20), type = "F")/norm((blod_20), type = "F"),
      lod30 = norm((blod_30 - nn_l_blod_30 - nn_s_blod_30), type = "F")/norm((blod_30), type = "F"),
      lod40 = norm((blod_40 - nn_l_blod_40 - nn_s_blod_40), type = "F")/norm((blod_40), type = "F"),
      lod50 = norm((blod_50 - nn_l_blod_50 - nn_s_blod_50), type = "F")/norm((blod_50), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "< LOD")

nn_l_above_blod_0 <- as.matrix((!tf_lod_0)*nn_L_lod0)
nn_s_above_blod_0 <- as.matrix((!tf_lod_0)*nn_S_lod0)

nn_l_above_blod_10 <- as.matrix((!tf_lod_10)*nn_L_lod10)
nn_s_above_blod_10 <- as.matrix((!tf_lod_10)*nn_S_lod10)

nn_l_above_blod_20 <- as.matrix((!tf_lod_20)*nn_L_lod20)
nn_s_above_blod_20 <- as.matrix((!tf_lod_20)*nn_S_lod20)

nn_l_above_blod_30 <- as.matrix((!tf_lod_30)*nn_L_lod30)
nn_s_above_blod_30 <- as.matrix((!tf_lod_30)*nn_S_lod30)

nn_l_above_blod_40 <- as.matrix((!tf_lod_40)*nn_L_lod40)
nn_s_above_blod_40 <- as.matrix((!tf_lod_40)*nn_S_lod40)

nn_l_above_blod_50 <- as.matrix((!tf_lod_50)*nn_L_lod50)
nn_s_above_blod_50 <- as.matrix((!tf_lod_50)*nn_S_lod50)

#divide by true values
nn_above_diff <- as_tibble(cbind(
  lod0  = norm((mix  - nn_l_above_blod_0  - nn_s_above_blod_0),  type = "F")/norm(mix,  type = "F"),
  lod10 = norm((mix_data_lod_10_0 - nn_l_above_blod_10 - nn_s_above_blod_10), type = "F")/norm(mix_data_lod_10_0, type = "F"),
  lod20 = norm((mix_data_lod_20_0 - nn_l_above_blod_20 - nn_s_above_blod_20), type = "F")/norm(mix_data_lod_20_0, type = "F"),
  lod30 = norm((mix_data_lod_30_0 - nn_l_above_blod_30 - nn_s_above_blod_30), type = "F")/norm(mix_data_lod_30_0, type = "F"),
  lod40 = norm((mix_data_lod_40_0 - nn_l_above_blod_40 - nn_s_above_blod_40), type = "F")/norm(mix_data_lod_40_0, type = "F"),
  lod50 = norm((mix_data_lod_50_0 - nn_l_above_blod_50 - nn_s_above_blod_50), type = "F")/norm(mix_data_lod_50_0, type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "> LOD")

l_blod_0_0 <- as.matrix(tf_lod_0*L_lod0_0)
s_blod_0_0 <- as.matrix(tf_lod_0*S_lod0_0)

l_blod_10_0 <- as.matrix(tf_lod_10*L_lod10_0)
s_blod_10_0 <- as.matrix(tf_lod_10*S_lod10_0)

l_blod_20_0 <- as.matrix(tf_lod_20*L_lod20_0)
s_blod_20_0 <- as.matrix(tf_lod_20*S_lod20_0)

l_blod_30_0 <- as.matrix(tf_lod_30*L_lod30_0)
s_blod_30_0 <- as.matrix(tf_lod_30*S_lod30_0)

l_blod_40_0 <- as.matrix(tf_lod_40*L_lod40_0)
s_blod_40_0 <- as.matrix(tf_lod_40*S_lod40_0)

l_blod_50_0 <- as.matrix(tf_lod_50*L_lod50_0)
s_blod_50_0 <- as.matrix(tf_lod_50*S_lod50_0)

#Subtract true values and divide by norm of true
less_diff_0 <- as_tibble(cbind(
      lod0 = norm((blod_0 - l_blod_0_0 - s_blod_0_0), type = "F"), #/norm((blod_0), type = "F"),
      lod10 = norm((blod_10 - l_blod_10_0 - s_blod_10_0), type = "F")/norm((blod_10), type = "F"),
      lod20 = norm((blod_20 - l_blod_20_0 - s_blod_20_0), type = "F")/norm((blod_20), type = "F"),
      lod30 = norm((blod_30 - l_blod_30_0 - s_blod_30_0), type = "F")/norm((blod_30), type = "F"),
      lod40 = norm((blod_40 - l_blod_40_0 - s_blod_40_0), type = "F")/norm((blod_40), type = "F"),
      lod50 = norm((blod_50 - l_blod_50_0 - s_blod_50_0), type = "F")/norm((blod_50), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "< LOD",
         Method = "PCP w/ 0")

l_above_blod_0_0 <- as.matrix((!tf_lod_0)*L_lod0_0)
s_above_blod_0_0 <- as.matrix((!tf_lod_0)*S_lod0_0)

l_above_blod_10_0 <- as.matrix((!tf_lod_10)*L_lod10_0)
s_above_blod_10_0 <- as.matrix((!tf_lod_10)*S_lod10_0)

l_above_blod_20_0 <- as.matrix((!tf_lod_20)*L_lod20_0)
s_above_blod_20_0 <- as.matrix((!tf_lod_20)*S_lod20_0)

l_above_blod_30_0 <- as.matrix((!tf_lod_30)*L_lod30_0)
s_above_blod_30_0 <- as.matrix((!tf_lod_30)*S_lod30_0)

l_above_blod_40_0 <- as.matrix((!tf_lod_40)*L_lod40_0)
s_above_blod_40_0 <- as.matrix((!tf_lod_40)*S_lod40_0)

l_above_blod_50_0 <- as.matrix((!tf_lod_50)*L_lod50_0)
s_above_blod_50_0 <- as.matrix((!tf_lod_50)*S_lod50_0)

#divide by true values
above_diff_0 <- as_tibble(cbind(
  lod0  = norm((mix  - l_above_blod_0_0  - s_above_blod_0_0),  type = "F")/norm(mix,  type = "F"),
  lod10 = norm((mix_data_lod_10_0 - l_above_blod_10_0 - s_above_blod_10_0), type = "F")/norm(mix_data_lod_10_0, type = "F"),
  lod20 = norm((mix_data_lod_20_0 - l_above_blod_20_0 - s_above_blod_20_0), type = "F")/norm(mix_data_lod_20_0, type = "F"),
  lod30 = norm((mix_data_lod_30_0 - l_above_blod_30_0 - s_above_blod_30_0), type = "F")/norm(mix_data_lod_30_0, type = "F"),
  lod40 = norm((mix_data_lod_40_0 - l_above_blod_40_0 - s_above_blod_40_0), type = "F")/norm(mix_data_lod_40_0, type = "F"),
  lod50 = norm((mix_data_lod_50_0 - l_above_blod_50_0 - s_above_blod_50_0), type = "F")/norm(mix_data_lod_50_0, type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "> LOD",
         Method = "PCP w/ 0")

L_blod_0_sqrt2 <- as.matrix(tf_lod_0*L_lod0_sqrt2)
S_blod_0_sqrt2 <- as.matrix(tf_lod_0*S_lod0_sqrt2)

L_blod_10_sqrt2 <- as.matrix(tf_lod_10*L_lod10_sqrt2)
S_blod_10_sqrt2 <- as.matrix(tf_lod_10*S_lod10_sqrt2)

L_blod_20_sqrt2 <- as.matrix(tf_lod_20*L_lod20_sqrt2)
S_blod_20_sqrt2 <- as.matrix(tf_lod_20*S_lod20_sqrt2)

L_blod_30_sqrt2 <- as.matrix(tf_lod_30*L_lod30_sqrt2)
S_blod_30_sqrt2 <- as.matrix(tf_lod_30*S_lod30_sqrt2)

L_blod_40_sqrt2 <- as.matrix(tf_lod_40*L_lod40_sqrt2)
S_blod_40_sqrt2 <- as.matrix(tf_lod_40*S_lod40_sqrt2)

L_blod_50_sqrt2 <- as.matrix(tf_lod_50*L_lod50_sqrt2)
S_blod_50_sqrt2 <- as.matrix(tf_lod_50*S_lod50_sqrt2)

less_diff_sqrt2 <- as_tibble(
  cbind(lod0  = norm((blod_0  - L_blod_0_sqrt2  - S_blod_0_sqrt2),  type = "F"), #/norm((blod_0), type = "F"),
        lod10 = norm((blod_10 - L_blod_10_sqrt2 - S_blod_10_sqrt2), type = "F")/norm((blod_10), type = "F"),
        lod20 = norm((blod_20 - L_blod_20_sqrt2 - S_blod_20_sqrt2), type = "F")/norm((blod_20), type = "F"),
        lod30 = norm((blod_30 - L_blod_30_sqrt2 - S_blod_30_sqrt2), type = "F")/norm((blod_30), type = "F"),
        lod40 = norm((blod_40 - L_blod_40_sqrt2 - S_blod_40_sqrt2), type = "F")/norm((blod_40), type = "F"),
        lod50 = norm((blod_50 - L_blod_50_sqrt2 - S_blod_50_sqrt2), type = "F")/norm((blod_50), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "< LOD",
         Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))

L_above_blod_0_sqrt2 <- as.matrix((!tf_lod_0)*L_lod0_sqrt2)
S_above_blod_0_sqrt2 <- as.matrix((!tf_lod_0)*S_lod0_sqrt2)

L_above_blod_10_sqrt2 <- as.matrix((!tf_lod_10)*L_lod10_sqrt2)
S_above_blod_10_sqrt2 <- as.matrix((!tf_lod_10)*S_lod10_sqrt2)

L_above_blod_20_sqrt2 <- as.matrix((!tf_lod_20)*L_lod20_sqrt2)
S_above_blod_20_sqrt2 <- as.matrix((!tf_lod_20)*S_lod20_sqrt2)

L_above_blod_30_sqrt2 <- as.matrix((!tf_lod_30)*L_lod30_sqrt2)
S_above_blod_30_sqrt2 <- as.matrix((!tf_lod_30)*S_lod30_sqrt2)

L_above_blod_40_sqrt2 <- as.matrix((!tf_lod_40)*L_lod40_sqrt2)
S_above_blod_40_sqrt2 <- as.matrix((!tf_lod_40)*S_lod40_sqrt2)

L_above_blod_50_sqrt2 <- as.matrix((!tf_lod_50)*L_lod50_sqrt2)
S_above_blod_50_sqrt2 <- as.matrix((!tf_lod_50)*S_lod50_sqrt2)

#divide by true values
above_diff_sqrt2 <- as_tibble(cbind(
  lod0  = norm((mix  - L_above_blod_0_sqrt2  - S_above_blod_0_sqrt2),  type = "F")/norm(mix,  type = "F"),
  lod10 = norm((mix_data_lod_10_0 - L_above_blod_10_sqrt2 - S_above_blod_10_sqrt2), type = "F")/norm(mix_data_lod_10_0, type = "F"),
  lod20 = norm((mix_data_lod_20_0 - L_above_blod_20_sqrt2 - S_above_blod_20_sqrt2), type = "F")/norm(mix_data_lod_20_0, type = "F"),
  lod30 = norm((mix_data_lod_30_0 - L_above_blod_30_sqrt2 - S_above_blod_30_sqrt2), type = "F")/norm(mix_data_lod_30_0, type = "F"),
  lod40 = norm((mix_data_lod_40_0 - L_above_blod_40_sqrt2 - S_above_blod_40_sqrt2), type = "F")/norm(mix_data_lod_40_0, type = "F"),
  lod50 = norm((mix_data_lod_50_0 - L_above_blod_50_sqrt2 - S_above_blod_50_sqrt2), type = "F")/norm(mix_data_lod_50_0, type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "> LOD",
         Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))
```

### Viz

```{r, fig.height = 5, fig.width = 5, fig.align = "center"}
rbind(above_diff, 
      less_diff,
      above_diff_0, 
      less_diff_0,
      above_diff_sqrt2, 
      less_diff_sqrt2) %>% 
  mutate(norm = ifelse(Values == "> LOD" & Method == "LOD PCP", norm + 0.005, norm),
         norm = ifelse(Values == "> LOD" & Method == "PCP w/ 0", norm - 0.005, norm)) %>% 
  ggplot(aes(x = percent_blod, y = norm, group = interaction(Values, Method), color = Method)) + 
  geom_point(aes()) + geom_path(aes(linetype = Values)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "\n(norm(X-L-S) / norm(X))",
       title = "Relative Error in Values < LOD & > LOD")
```

## SVD

```{r}
svd(L_lod0)$d

svd(L_lod50)$d
```

### Right singular vectors

```{r}
# Extract right singular vectors from each low rank solution matrix
V_lod0  <-  svd(L_lod0)$v[,1:5]
V_lod10 <- svd(L_lod10)$v[,1:5]
V_lod20 <- svd(L_lod20)$v[,1:5]
V_lod30 <- svd(L_lod30)$v[,1:5]
V_lod40 <- svd(L_lod40)$v[,1:5]
V_lod50 <- svd(L_lod50)$v[,1:5]

# Hack to flip singular vectos -- Use correlation
# cor(V_lod0, V_lod10)
# cor(V_lod0, V_lod20)
# cor(V_lod0, V_lod30)
# cor(V_lod0, V_lod40)
# cor(V_lod0, V_lod50)

# Hack -- Flip
V_lod10[,3] <- -V_lod10[,3]
V_lod10[,5] <- -V_lod10[,5]
V_lod20[,3] <- -V_lod20[,3]
V_lod20[,5] <- -V_lod20[,5]
V_lod30[,3] <- -V_lod30[,3]
V_lod30[,4] <- -V_lod30[,4]
V_lod30[,5] <- -V_lod30[,5]
V_lod40[,4] <- -V_lod40[,4]
V_lod40[,3] <- -V_lod40[,3]
V_lod50[,3] <- -V_lod50[,3]
V_lod50[,4] <- -V_lod50[,4]
V_lod50[,5] <- -V_lod50[,5]

V_diff <- as_tibble(cbind(lod0 =norm((V_lod0 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      lod10 =norm((V_lod10 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      lod20 =norm((V_lod20 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      lod30 =norm((V_lod30 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      lod40 =norm((V_lod40 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      lod50 =norm((V_lod50 - V_lod0), type = "F")/norm((V_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "LOD PCP")

#V_diff

# Extract right singular vectors from each low rank solution matrix
nn_V_lod0  <-  svd(nn_L_lod0)$v[,1:5]
nn_V_lod10 <- svd(nn_L_lod10)$v[,1:5]
nn_V_lod20 <- svd(nn_L_lod20)$v[,1:5]
nn_V_lod30 <- svd(nn_L_lod30)$v[,1:5]
nn_V_lod40 <- svd(nn_L_lod40)$v[,1:5]
nn_V_lod50 <- svd(nn_L_lod50)$v[,1:5]

# cor(nn_V_lod0, nn_V_lod10)
# cor(nn_V_lod0, nn_V_lod20)
# cor(nn_V_lod0, nn_V_lod30)
# cor(nn_V_lod0, nn_V_lod40)
# cor(nn_V_lod0, nn_V_lod50)

# Hack -- Flip
nn_V_lod10[,3] <- -nn_V_lod10[,3]
nn_V_lod10[,5] <- -nn_V_lod10[,5]
nn_V_lod20[,3] <- -nn_V_lod20[,3]
nn_V_lod20[,5] <- -nn_V_lod20[,5]
nn_V_lod30[,3] <- -nn_V_lod30[,3]
nn_V_lod30[,4] <- -nn_V_lod30[,4]
nn_V_lod30[,5] <- -nn_V_lod30[,5]
nn_V_lod40[,4] <- -nn_V_lod40[,4]
nn_V_lod40[,3] <- -nn_V_lod40[,3]
nn_V_lod50[,3] <- -nn_V_lod50[,3]
nn_V_lod50[,4] <- -nn_V_lod50[,4]
nn_V_lod50[,5] <- -nn_V_lod50[,5]

nn_V_diff <- as_tibble(cbind(lod0 =norm((nn_V_lod0 - nn_V_lod0), type = "F")/norm((nn_V_lod0), type = "F"),
      lod10 =norm((nn_V_lod10 - nn_V_lod0), type = "F")/norm((nn_V_lod0), type = "F"),
      lod20 =norm((nn_V_lod20 - nn_V_lod0), type = "F")/norm((nn_V_lod0), type = "F"),
      lod30 =norm((nn_V_lod30 - nn_V_lod0), type = "F")/norm((nn_V_lod0), type = "F"),
      lod40 =norm((nn_V_lod40 - nn_V_lod0), type = "F")/norm((nn_V_lod0), type = "F"),
      lod50 =norm((nn_V_lod50 - nn_V_lod0), type = "F")/norm((nn_V_lod0), type = "F"))) %>% 
  gather(percent_blod, norm)

#nn_V_diff

# Extract right singular vectors from each low rank solution matrix
V_lod0_0  <-  svd(L_lod0_0)$v[,1:5]
V_lod10_0 <- svd(L_lod10_0)$v[,1:5]
V_lod20_0 <- svd(L_lod20_0)$v[,1:5]
V_lod30_0 <- svd(L_lod30_0)$v[,1:5]
V_lod40_0 <- svd(L_lod40_0)$v[,1:5]
V_lod50_0 <- svd(L_lod50_0)$v[,1:5]

# cor(V_lod0_0, V_lod10_0)
# cor(V_lod0_0, V_lod20_0)
# cor(V_lod0_0, V_lod30_0)
# cor(V_lod0_0, V_lod40_0)
# cor(V_lod0_0, V_lod50_0)

# Hack -- Flip
V_lod10_0[,3] <- -V_lod10_0[,3]
V_lod10_0[,4] <- -V_lod10_0[,4]
V_lod10_0[,5] <- -V_lod10_0[,5]
V_lod20_0[,3] <- -V_lod20_0[,3]
V_lod20_0[,4] <- -V_lod20_0[,4]
V_lod30_0[,3] <- -V_lod30_0[,3]
V_lod30_0[,5] <- -V_lod30_0[,5]
V_lod40_0[,3] <- -V_lod40_0[,3]
V_lod50_0[,3] <- -V_lod50_0[,3]
V_lod50_0[,4] <- -V_lod50_0[,4]

V_diff_0 <- as_tibble(cbind(lod0 =norm((V_lod0_0 - V_lod0_0), type = "F")/norm((V_lod0_0), type = "F"),
      lod10 =norm((V_lod10_0 - V_lod0_0), type = "F")/norm((V_lod0_0), type = "F"),
      lod20 =norm((V_lod20_0 - V_lod0_0), type = "F")/norm((V_lod0_0), type = "F"),
      lod30 =norm((V_lod30_0 - V_lod0_0), type = "F")/norm((V_lod0_0), type = "F"),
      lod40 =norm((V_lod40_0 - V_lod0_0), type = "F")/norm((V_lod0_0), type = "F"),
      lod50 =norm((V_lod50_0 - V_lod0_0), type = "F")/norm((V_lod0_0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP w/ 0")

#V_diff_0

# Extract right singular vectors from each low rank solution matrix
V_lod0_sqrt2  <-  svd(L_lod0_sqrt2)$v[,1:5]
V_lod10_sqrt2 <- svd(L_lod10_sqrt2)$v[,1:5]
V_lod20_sqrt2 <- svd(L_lod20_sqrt2)$v[,1:5]
V_lod30_sqrt2 <- svd(L_lod30_sqrt2)$v[,1:5]
V_lod40_sqrt2 <- svd(L_lod40_sqrt2)$v[,1:5]
V_lod50_sqrt2 <- svd(L_lod50_sqrt2)$v[,1:5]

# cor(V_lod0_sqrt2, V_lod10_sqrt2)
# cor(V_lod0_sqrt2, V_lod20_sqrt2)
# cor(V_lod0_sqrt2, V_lod30_sqrt2)
# cor(V_lod0_sqrt2, V_lod40_sqrt2)
# cor(V_lod0_sqrt2, V_lod50_sqrt2)

# Hack -- Flip
V_lod10_sqrt2[,4] <- -V_lod10_sqrt2[,4]
V_lod10_sqrt2[,5] <- -V_lod10_sqrt2[,5]
V_lod20_sqrt2[,3] <- -V_lod20_sqrt2[,3]
V_lod20_sqrt2[,5] <- -V_lod20_sqrt2[,5]
V_lod30_sqrt2[,3] <- -V_lod30_sqrt2[,3]
V_lod30_sqrt2[,5] <- -V_lod30_sqrt2[,5]
V_lod50_sqrt2[,3] <- -V_lod50_sqrt2[,3]
V_lod50_sqrt2[,4] <- -V_lod50_sqrt2[,4]

V_diff_sqrt2 <- as_tibble(cbind(lod0 =norm((V_lod0_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"),
      lod10 =norm((V_lod10_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"),
      lod20 =norm((V_lod20_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"),
      lod30 =norm((V_lod30_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"),
      lod40 =norm((V_lod40_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"),
      lod50 =norm((V_lod50_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))

#V_diff_sqrt2
```

#### Viz

```{r, fig.height = 5, fig.width = 5, fig.align = "center"}
rbind(V_diff,
      V_diff_0,
      V_diff_sqrt2) %>% ggplot(aes(x = percent_blod, y = norm, group = Method, color = Method)) + 
  geom_point() + geom_path() + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "norm(SV - SV_lod0) / norm(SV_lod0)",
       title = "Relative Error in Low-Rank \nSolution Right Singular Vectors")
```

##### Loadings

```{r, message=FALSE, warning=FALSE}
as_tibble(V_lod0) %>% 
  mutate(PM = colnames(mix),
         LOD = "LOD 0") %>% 
  full_join(., as_tibble(V_lod10) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 10")) %>%
  full_join(., as_tibble(V_lod20) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 20")) %>%
  full_join(., as_tibble(V_lod30) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 30")) %>%
  full_join(., as_tibble(V_lod40) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 40")) %>%
  full_join(., as_tibble(V_lod50) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 50")) %>%
  gather(key = singular_vector, value = magnitude, V1:V5) %>%
  ggplot(aes(x = PM, y = magnitude)) + geom_point() + 
  geom_segment(aes(xend = PM, yend = 0)) +
  facet_grid(LOD ~ singular_vector) +
  geom_hline(yintercept = 0, linetype = "dashed", 
             color = "red") +
  theme_bw(base_size = 12) + labs(x = "", y = "Magnitude", title = "Jingkai's <LOD PCP") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.background = element_rect(fill = "white")) +
  geom_hline(yintercept = 0, size = 0.2) + 
  theme(legend.position = c(0.85, 0.10), 
                legend.background = element_rect(fill = "white", colour = NA),
        legend.text=element_text(size=15),
        legend.title = element_blank(),
        strip.text.x = element_text(size = 13),
        axis.title.y = element_text(size = 18))
```

```{r, message=FALSE}
as_tibble(nn_V_lod0) %>% 
  mutate(PM = colnames(mix),
         LOD = "LOD 0") %>% 
  full_join(., as_tibble(nn_V_lod10) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 10")) %>%
  full_join(., as_tibble(nn_V_lod20) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 20")) %>%
  full_join(., as_tibble(nn_V_lod30) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 30")) %>%
  full_join(., as_tibble(nn_V_lod40) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 40")) %>%
  full_join(., as_tibble(nn_V_lod50) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 50")) %>%
  gather(key = singular_vector, value = magnitude, V1:V5) %>%
  ggplot(aes(x = PM, y = magnitude)) + geom_point() + 
  geom_segment(aes(xend = PM, yend = 0)) +
  facet_grid(LOD ~ singular_vector) +
  geom_hline(yintercept = 0, linetype = "dashed", 
             color = "red") +
  theme_bw(base_size = 12) + labs(x = "", y = "Magnitude", title = "<LOD PCP with measured values") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.background = element_rect(fill = "white")) +
  geom_hline(yintercept = 0, size = 0.2) + 
  theme(legend.position = c(0.85, 0.10), 
                legend.background = element_rect(fill = "white", colour = NA),
        legend.text=element_text(size=15),
        legend.title = element_blank(),
        strip.text.x = element_text(size = 13),
        axis.title.y = element_text(size = 18))
```

```{r, message=FALSE}
as_tibble(V_lod0_0) %>% 
  mutate(PM = colnames(mix),
         LOD = "LOD 0") %>% 
  full_join(., as_tibble(V_lod10_0) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 10")) %>%
  full_join(., as_tibble(V_lod20_0) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 20")) %>%
  full_join(., as_tibble(V_lod30_0) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 30")) %>%
  full_join(., as_tibble(V_lod40_0) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 40")) %>%
  full_join(., as_tibble(V_lod50_0) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 50")) %>%
  gather(key = singular_vector, value = magnitude, V1:V5) %>%
  ggplot(aes(x = PM, y = magnitude)) + geom_point() + 
  geom_segment(aes(xend = PM, yend = 0)) +
  facet_grid(LOD ~ singular_vector) +
  geom_hline(yintercept = 0, linetype = "dashed", 
             color = "red") +
  theme_bw(base_size = 12) + labs(x = "", y = "Magnitude", title = "Original PCP with constant zero") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.background = element_rect(fill = "white")) +
  geom_hline(yintercept = 0, size = 0.2) + 
  theme(legend.position = c(0.85, 0.10), 
                legend.background = element_rect(fill = "white", colour = NA),
        legend.text=element_text(size=15),
        legend.title = element_blank(),
        strip.text.x = element_text(size = 13),
        axis.title.y = element_text(size = 18))
```

```{r, message=FALSE}
as_tibble(V_lod0_sqrt2) %>% 
  mutate(PM = colnames(mix),
         LOD = "LOD 0") %>% 
  full_join(., as_tibble(V_lod10_sqrt2) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 10")) %>%
  full_join(., as_tibble(V_lod20_sqrt2) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 20")) %>%
  full_join(., as_tibble(V_lod30_sqrt2) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 30")) %>%
  full_join(., as_tibble(V_lod40_sqrt2) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 40")) %>%
  full_join(., as_tibble(V_lod50_sqrt2) %>%
  mutate(PM = colnames(mix),
         LOD = "LOD 50")) %>%
  gather(key = singular_vector, value = magnitude, V1:V5) %>%
  ggplot(aes(x = PM, y = magnitude)) + geom_point() + 
  geom_segment(aes(xend = PM, yend = 0)) +
  facet_grid(LOD ~ singular_vector) +
  geom_hline(yintercept = 0, linetype = "dashed", 
             color = "red") +
  theme_bw(base_size = 12) + labs(x = "", y = "Magnitude", title = "Original PCP with LOD/sqrt(2)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.background = element_rect(fill = "white")) +
  geom_hline(yintercept = 0, size = 0.2) + 
  theme(legend.position = c(0.85, 0.10), 
                legend.background = element_rect(fill = "white", colour = NA),
        legend.text=element_text(size=15),
        legend.title = element_blank(),
        strip.text.x = element_text(size = 13),
        axis.title.y = element_text(size = 18))
```

### Left singular vectors

```{r}
u_lod0  <-  svd(L_lod0)$u[,1:5]
u_lod10 <- svd(L_lod10)$u[,1:5]
u_lod20 <- svd(L_lod20)$u[,1:5]
u_lod30 <- svd(L_lod30)$u[,1:5]
u_lod40 <- svd(L_lod40)$u[,1:5]
u_lod50 <- svd(L_lod50)$u[,1:5]

# Hack -- Flip
u_lod10[,3] <- -u_lod10[,3]
u_lod10[,5] <- -u_lod10[,5]
u_lod20[,3] <- -u_lod20[,3]
u_lod20[,5] <- -u_lod20[,5]
u_lod30[,3] <- -u_lod30[,3]
u_lod30[,4] <- -u_lod30[,4]
u_lod30[,5] <- -u_lod30[,5]
u_lod40[,4] <- -u_lod40[,4]
u_lod40[,3] <- -u_lod40[,3]
u_lod50[,3] <- -u_lod50[,3]
u_lod50[,4] <- -u_lod50[,4]
u_lod50[,5] <- -u_lod50[,5]

u_diff <- as_tibble(cbind(lod0 =norm((u_lod0 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      lod10 =norm((u_lod10 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      lod20 =norm((u_lod20 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      lod30 =norm((u_lod30 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      lod40 =norm((u_lod40 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      lod50 =norm((u_lod50 - u_lod0), type = "F")/norm((u_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
mutate(Method = "LOD PCP")

# u_diff

nn_u_lod0  <-  svd(nn_L_lod0)$u[,1:5]
nn_u_lod10 <- svd(nn_L_lod10)$u[,1:5]
nn_u_lod20 <- svd(nn_L_lod20)$u[,1:5]
nn_u_lod30 <- svd(nn_L_lod30)$u[,1:5]
nn_u_lod40 <- svd(nn_L_lod40)$u[,1:5]
nn_u_lod50 <- svd(nn_L_lod50)$u[,1:5]

# Hack -- Flip
nn_u_lod10[,3] <- -nn_u_lod10[,3]
nn_u_lod10[,5] <- -nn_u_lod10[,5]
nn_u_lod20[,3] <- -nn_u_lod20[,3]
nn_u_lod20[,5] <- -nn_u_lod20[,5]
nn_u_lod30[,3] <- -nn_u_lod30[,3]
nn_u_lod30[,4] <- -nn_u_lod30[,4]
nn_u_lod30[,5] <- -nn_u_lod30[,5]
nn_u_lod40[,4] <- -nn_u_lod40[,4]
nn_u_lod40[,3] <- -nn_u_lod40[,3]
nn_u_lod50[,3] <- -nn_u_lod50[,3]
nn_u_lod50[,4] <- -nn_u_lod50[,4]
nn_u_lod50[,5] <- -nn_u_lod50[,5]

nn_u_diff <- as_tibble(cbind(lod0 =norm((nn_u_lod0 - nn_u_lod0), type = "F")/norm((nn_u_lod0), type = "F"),
      lod10 =norm((nn_u_lod10 - nn_u_lod0), type = "F")/norm((nn_u_lod0), type = "F"),
      lod20 =norm((nn_u_lod20 - nn_u_lod0), type = "F")/norm((nn_u_lod0), type = "F"),
      lod30 =norm((nn_u_lod30 - nn_u_lod0), type = "F")/norm((nn_u_lod0), type = "F"),
      lod40 =norm((nn_u_lod40 - nn_u_lod0), type = "F")/norm((nn_u_lod0), type = "F"),
      lod50 =norm((nn_u_lod50 - nn_u_lod0), type = "F")/norm((nn_u_lod0), type = "F"))) %>% 
  gather(percent_blod, norm)

u_lod0_0  <-  svd(L_lod0_0)$u[,1:5]
u_lod10_0 <- svd(L_lod10_0)$u[,1:5]
u_lod20_0 <- svd(L_lod20_0)$u[,1:5]
u_lod30_0 <- svd(L_lod30_0)$u[,1:5]
u_lod40_0 <- svd(L_lod40_0)$u[,1:5]
u_lod50_0 <- svd(L_lod50_0)$u[,1:5]

# Hack -- Flip
u_lod10_0[,3] <- -u_lod10_0[,3]
u_lod10_0[,4] <- -u_lod10_0[,4]
u_lod10_0[,5] <- -u_lod10_0[,5]
u_lod20_0[,3] <- -u_lod20_0[,3]
u_lod20_0[,4] <- -u_lod20_0[,4]
u_lod30_0[,3] <- -u_lod30_0[,3]
u_lod30_0[,5] <- -u_lod30_0[,5]
u_lod40_0[,3] <- -u_lod40_0[,3]
u_lod50_0[,3] <- -u_lod50_0[,3]
u_lod50_0[,4] <- -u_lod50_0[,4]

u_diff_0 <- as_tibble(cbind(lod0 =norm((u_lod0_0 - u_lod0_0), type = "F")/norm((u_lod0_0), type = "F"),
      lod10 =norm((u_lod10_0 - u_lod0_0), type = "F")/norm((u_lod0_0), type = "F"),
      lod20 =norm((u_lod20_0 - u_lod0_0), type = "F")/norm((u_lod0_0), type = "F"),
      lod30 =norm((u_lod30_0 - u_lod0_0), type = "F")/norm((u_lod0_0), type = "F"),
      lod40 =norm((u_lod40_0 - u_lod0_0), type = "F")/norm((u_lod0_0), type = "F"),
      lod50 =norm((u_lod50_0 - u_lod0_0), type = "F")/norm((u_lod0_0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP w/ 0")

u_lod0_sqrt2  <-  svd(L_lod0_sqrt2)$u[,1:5]
u_lod10_sqrt2 <- svd(L_lod10_sqrt2)$u[,1:5]
u_lod20_sqrt2 <- svd(L_lod20_sqrt2)$u[,1:5]
u_lod30_sqrt2 <- svd(L_lod30_sqrt2)$u[,1:5]
u_lod40_sqrt2 <- svd(L_lod40_sqrt2)$u[,1:5]
u_lod50_sqrt2 <- svd(L_lod50_sqrt2)$u[,1:5]

# Hack -- Flip
u_lod10_sqrt2[,4] <- -u_lod10_sqrt2[,4]
u_lod10_sqrt2[,5] <- -u_lod10_sqrt2[,5]
u_lod20_sqrt2[,3] <- -u_lod20_sqrt2[,3]
u_lod20_sqrt2[,5] <- -u_lod20_sqrt2[,5]
u_lod30_sqrt2[,3] <- -u_lod30_sqrt2[,3]
u_lod30_sqrt2[,5] <- -u_lod30_sqrt2[,5]
u_lod50_sqrt2[,3] <- -u_lod50_sqrt2[,3]
u_lod50_sqrt2[,4] <- -u_lod50_sqrt2[,4]

u_diff_sqrt2 <- as_tibble(cbind(lod0 =norm((u_lod0_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"),
      lod10 =norm((u_lod10_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"),
      lod20 =norm((u_lod20_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"),
      lod30 =norm((u_lod30_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"),
      lod40 =norm((u_lod40_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"),
      lod50 =norm((u_lod50_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))
```

#### Viz

```{r, fig.height = 5, fig.width = 5, fig.align = "center"}
rbind(u_diff,
      u_diff_0,
      u_diff_sqrt2) %>% ggplot(aes(x = percent_blod, y = norm, group = Method, color = Method)) + 
  geom_point() + geom_path() + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "norm(SV - SV_lod0) / norm(SV_lod0)",
       title = "Relative Error in Low-Rank \nSolution Left Singular Vectors")
```

### Singular Values

```{r}
d_lod0  <- svd(L_lod0)$d[1:5]
d_lod10 <- svd(L_lod10)$d[1:5]
d_lod20 <- svd(L_lod20)$d[1:5]
d_lod30 <- svd(L_lod30)$d[1:5]
d_lod40 <- svd(L_lod40)$d[1:5]
d_lod50 <- svd(L_lod50)$d[1:5]

norm_vec <- function(x) sqrt(sum(x^2))

d_diff <- as_tibble(cbind(lod0 = norm_vec(d_lod0 - d_lod0)/norm_vec(d_lod0),
      lod10 = norm_vec(d_lod10 - d_lod0)/norm_vec(d_lod0),
      lod20 = norm_vec(d_lod20 - d_lod0)/norm_vec(d_lod0),
      lod30 = norm_vec(d_lod30 - d_lod0)/norm_vec(d_lod0),
      lod40 = norm_vec(d_lod40 - d_lod0)/norm_vec(d_lod0),
      lod50 = norm_vec(d_lod50 - d_lod0)/norm_vec(d_lod0))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "LOD PCP")

nn_d_lod0  <- svd(nn_L_lod0)$d[1:5]
nn_d_lod10 <- svd(nn_L_lod10)$d[1:5]
nn_d_lod20 <- svd(nn_L_lod20)$d[1:5]
nn_d_lod30 <- svd(nn_L_lod30)$d[1:5]
nn_d_lod40 <- svd(nn_L_lod40)$d[1:5]
nn_d_lod50 <- svd(nn_L_lod50)$d[1:5]

nn_d_diff <- as_tibble(cbind(lod0 = norm_vec(nn_d_lod0 - nn_d_lod0)/norm_vec(nn_d_lod0),
      lod10 = norm_vec(nn_d_lod10 - nn_d_lod0)/norm_vec(nn_d_lod0),
      lod20 = norm_vec(nn_d_lod20 - nn_d_lod0)/norm_vec(nn_d_lod0),
      lod30 = norm_vec(nn_d_lod30 - nn_d_lod0)/norm_vec(nn_d_lod0),
      lod40 = norm_vec(nn_d_lod40 - nn_d_lod0)/norm_vec(nn_d_lod0),
      lod50 = norm_vec(nn_d_lod50 - nn_d_lod0)/norm_vec(nn_d_lod0))) %>% 
  gather(percent_blod, norm)

d_lod0_0  <- svd(L_lod0_0)$d[1:5]
d_lod10_0 <- svd(L_lod10_0)$d[1:5]
d_lod20_0 <- svd(L_lod20_0)$d[1:5]
d_lod30_0 <- svd(L_lod30_0)$d[1:5]
d_lod40_0 <- svd(L_lod40_0)$d[1:5]
d_lod50_0 <- svd(L_lod50_0)$d[1:5]

d_diff_0 <- as_tibble(cbind(lod0 = norm_vec(d_lod0_0 - d_lod0_0)/norm_vec(d_lod0_0),
      lod10 = norm_vec(d_lod10_0 - d_lod0_0)/norm_vec(d_lod0_0),
      lod20 = norm_vec(d_lod20_0 - d_lod0_0)/norm_vec(d_lod0_0),
      lod30 = norm_vec(d_lod30_0 - d_lod0_0)/norm_vec(d_lod0_0),
      lod40 = norm_vec(d_lod40_0 - d_lod0_0)/norm_vec(d_lod0_0),
      lod50 = norm_vec(d_lod50_0 - d_lod0_0)/norm_vec(d_lod0_0))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP w/ 0")

d_lod0_sqrt2  <- svd(L_lod0_sqrt2)$d[1:5]
d_lod10_sqrt2 <- svd(L_lod10_sqrt2)$d[1:5]
d_lod20_sqrt2 <- svd(L_lod20_sqrt2)$d[1:5]
d_lod30_sqrt2 <- svd(L_lod30_sqrt2)$d[1:5]
d_lod40_sqrt2 <- svd(L_lod40_sqrt2)$d[1:5]
d_lod50_sqrt2 <- svd(L_lod50_sqrt2)$d[1:5]

d_diff_sqrt2 <- as_tibble(cbind(lod0 = norm_vec(d_lod0_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2),
      lod10 = norm_vec(d_lod10_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2),
      lod20 = norm_vec(d_lod20_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2),
      lod30 = norm_vec(d_lod30_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2),
      lod40 = norm_vec(d_lod40_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2),
      lod50 = norm_vec(d_lod50_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))
```

#### Viz

```{r, fig.height = 5, fig.width = 5, fig.align = "center"}
rbind(d_diff_sqrt2,
      d_diff,
      d_diff_0) %>% ggplot(aes(x = percent_blod, y = norm, group = Method, color = Method)) + 
  geom_point() + geom_path() + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "norm(SV - SV_lod0) / norm(SV_lod0)",
       title = "Relative Error in Low-Rank \nSolution Singular Values")
```


## PCA

```{r}
pca_0  <- prcomp(mix)
pca_10 <- prcomp(mix_data_lod_10_sqrt2)
pca_20 <- prcomp(mix_data_lod_20_sqrt2)
pca_30 <- prcomp(mix_data_lod_30_sqrt2)
pca_40 <- prcomp(mix_data_lod_40_sqrt2)
pca_50 <- prcomp(mix_data_lod_50_sqrt2)
```

```{r}
cor(pca_0$rotation[,1:7], pca_10$rotation[,1:7])
cor(pca_0$rotation[,1:7], pca_20$rotation[,1:7])
cor(pca_0$rotation[,1:7], pca_30$rotation[,1:7])
cor(pca_0$rotation[,1:7], pca_40$rotation[,1:7])
cor(pca_0$rotation[,1:7], pca_50$rotation[,1:7])

pca_40$rotation[,7] <- -pca_40$rotation[,7]
pca_50$rotation[,7] <- -pca_50$rotation[,7]

rotation_norm <- as_tibble(cbind(lod0 = norm((pca_0$rotation[,1:7] - pca_0$rotation[,1:7]), type = "F")/norm((pca_0$rotation[,1:7]), type = "F"),
      lod10 = norm((pca_0$rotation[,1:7] - pca_10$rotation[,1:7]), type = "F")/norm((pca_0$rotation[,1:7]), type = "F"),
      lod20 = norm((pca_0$rotation[,1:7] - pca_20$rotation[,1:7]), type = "F")/norm((pca_0$rotation[,1:7]), type = "F"),
      lod30 = norm((pca_0$rotation[,1:7] - pca_30$rotation[,1:7]), type = "F")/norm((pca_0$rotation[,1:7]), type = "F"),
      lod40 = norm((pca_0$rotation[,1:7] - pca_40$rotation[,1:7]), type = "F")/norm((pca_0$rotation[,1:7]), type = "F"),
      lod50 = norm((pca_0$rotation[,1:7] - pca_50$rotation[,1:7]), type = "F")/norm((pca_0$rotation[,1:7]), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCA")
```

```{r}
cor(pca_0$x[,1:7], pca_10$x[,1:7])
cor(pca_0$x[,1:7], pca_20$x[,1:7])
cor(pca_0$x[,1:7], pca_30$x[,1:7])
cor(pca_0$x[,1:7], pca_40$x[,1:7])
cor(pca_0$x[,1:7], pca_50$x[,1:7])

pca_40$x[,7] <- -pca_40$x[,7]
pca_50$x[,7] <- -pca_50$x[,7]

score_norm <- as_tibble(cbind(lod0 = norm((pca_0$x[,1:7] - pca_0$x[,1:7]), type = "F")/norm((pca_0$x[,1:7]), type = "F"),
      lod10 = norm((pca_0$x[,1:7] - pca_10$x[,1:7]), type = "F")/norm((pca_0$x[,1:7]), type = "F"),
      lod20 = norm((pca_0$x[,1:7] - pca_20$x[,1:7]), type = "F")/norm((pca_0$x[,1:7]), type = "F"),
      lod30 = norm((pca_0$x[,1:7] - pca_30$x[,1:7]), type = "F")/norm((pca_0$x[,1:7]), type = "F"),
      lod40 = norm((pca_0$x[,1:7] - pca_40$x[,1:7]), type = "F")/norm((pca_0$x[,1:7]), type = "F"),
      lod50 = norm((pca_0$x[,1:7] - pca_50$x[,1:7]), type = "F")/norm((pca_0$x[,1:7]), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCA")
```

```{r}
sdev_norm <- as_tibble(cbind(lod0 = norm_vec(pca_0$sdev[1:7] - pca_0$sdev[1:7])/norm_vec(pca_0$sdev[1:7]),
      lod10 = norm_vec(pca_0$sdev[1:7] - pca_10$sdev[1:7])/norm_vec(pca_0$sdev[1:7]),
      lod20 = norm_vec(pca_0$sdev[1:7] - pca_20$sdev[1:7])/norm_vec(pca_0$sdev[1:7]),
      lod30 = norm_vec(pca_0$sdev[1:7] - pca_30$sdev[1:7])/norm_vec(pca_0$sdev[1:7]),
      lod40 = norm_vec(pca_0$sdev[1:7] - pca_40$sdev[1:7])/norm_vec(pca_0$sdev[1:7]),
      lod50 = norm_vec(pca_0$sdev[1:7] - pca_50$sdev[1:7])/norm_vec(pca_0$sdev[1:7]))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCA")
```

```{r}
pcp_pca_0  <- prcomp(L_lod0)
pcp_pca_10 <- prcomp(L_lod10)
pcp_pca_20 <- prcomp(L_lod20)
pcp_pca_30 <- prcomp(L_lod30)
pcp_pca_40 <- prcomp(L_lod40)
pcp_pca_50 <- prcomp(L_lod50)
```

```{r}
cor(pcp_pca_0$rotation[,1:7], pcp_pca_10$rotation[,1:7])
cor(pcp_pca_0$rotation[,1:7], pcp_pca_20$rotation[,1:7])
cor(pcp_pca_0$rotation[,1:7], pcp_pca_30$rotation[,1:7])
cor(pcp_pca_0$rotation[,1:7], pcp_pca_40$rotation[,1:7])
cor(pcp_pca_0$rotation[,1:7], pcp_pca_50$rotation[,1:7])

pcp_pca_40$rotation[,4] <- -pcp_pca_40$rotation[,4]
pcp_pca_50$rotation[,7] <- -pcp_pca_50$rotation[,7]

pcp_rotation_norm <- as_tibble(cbind(lod0 = norm((pcp_pca_0$rotation[,1:7] - pcp_pca_0$rotation[,1:7]), type = "F")/norm((pcp_pca_0$rotation[,1:7]), type = "F"),
      lod10 = norm((pcp_pca_0$rotation[,1:7] - pcp_pca_10$rotation[,1:7]), type = "F")/norm((pcp_pca_0$rotation[,1:7]), type = "F"),
      lod20 = norm((pcp_pca_0$rotation[,1:7] - pcp_pca_20$rotation[,1:7]), type = "F")/norm((pcp_pca_0$rotation[,1:7]), type = "F"),
      lod30 = norm((pcp_pca_0$rotation[,1:7] - pcp_pca_30$rotation[,1:7]), type = "F")/norm((pcp_pca_0$rotation[,1:7]), type = "F"),
      lod40 = norm((pcp_pca_0$rotation[,1:7] - pcp_pca_40$rotation[,1:7]), type = "F")/norm((pcp_pca_0$rotation[,1:7]), type = "F"),
      lod50 = norm((pcp_pca_0$rotation[,1:7] - pcp_pca_50$rotation[,1:7]), type = "F")/norm((pcp_pca_0$rotation[,1:7]), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP")
```

```{r}
cor(pcp_pca_0$x[,1:7], pcp_pca_10$x[,1:7])
cor(pcp_pca_0$x[,1:7], pcp_pca_20$x[,1:7])
cor(pcp_pca_0$x[,1:7], pcp_pca_30$x[,1:7])
cor(pcp_pca_0$x[,1:7], pcp_pca_40$x[,1:7])
cor(pcp_pca_0$x[,1:7], pcp_pca_50$x[,1:7])

pcp_pca_40$x[,4] <- -pcp_pca_40$x[,4]
pcp_pca_50$x[,7] <- -pcp_pca_50$x[,7]

pcp_score_norm <- as_tibble(cbind(lod0 = norm((pcp_pca_0$x[,1:7] - pcp_pca_0$x[,1:7]), type = "F")/norm((pcp_pca_0$x[,1:7]), type = "F"),
      lod10 = norm((pcp_pca_0$x[,1:7] - pcp_pca_10$x[,1:7]), type = "F")/norm((pcp_pca_0$x[,1:7]), type = "F"),
      lod20 = norm((pcp_pca_0$x[,1:7] - pcp_pca_20$x[,1:7]), type = "F")/norm((pcp_pca_0$x[,1:7]), type = "F"),
      lod30 = norm((pcp_pca_0$x[,1:7] - pcp_pca_30$x[,1:7]), type = "F")/norm((pcp_pca_0$x[,1:7]), type = "F"),
      lod40 = norm((pcp_pca_0$x[,1:7] - pcp_pca_40$x[,1:7]), type = "F")/norm((pcp_pca_0$x[,1:7]), type = "F"),
      lod50 = norm((pcp_pca_0$x[,1:7] - pcp_pca_50$x[,1:7]), type = "F")/norm((pcp_pca_0$x[,1:7]), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP")
```

```{r}
pcp_sdev_norm <- as_tibble(cbind(lod0 = norm_vec(pcp_pca_0$sdev[1:7] - pcp_pca_0$sdev[1:7])/norm_vec(pcp_pca_0$sdev[1:7]),
      lod10 = norm_vec(pcp_pca_0$sdev[1:7] - pcp_pca_10$sdev[1:7])/norm_vec(pcp_pca_0$sdev[1:7]),
      lod20 = norm_vec(pcp_pca_0$sdev[1:7] - pcp_pca_20$sdev[1:7])/norm_vec(pcp_pca_0$sdev[1:7]),
      lod30 = norm_vec(pcp_pca_0$sdev[1:7] - pcp_pca_30$sdev[1:7])/norm_vec(pcp_pca_0$sdev[1:7]),
      lod40 = norm_vec(pcp_pca_0$sdev[1:7] - pcp_pca_40$sdev[1:7])/norm_vec(pcp_pca_0$sdev[1:7]),
      lod50 = norm_vec(pcp_pca_0$sdev[1:7] - pcp_pca_50$sdev[1:7])/norm_vec(pcp_pca_0$sdev[1:7]))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP")
```

### Viz

```{r, fig.height = 5, fig.width = 5, fig.align = "center"}
rbind(rotation_norm, pcp_rotation_norm) %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point(aes(color = Method)) + geom_path(aes(group = Method, color = Method)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(X-lod0) / norm(X)",
       title = "Relative Prediction Error")
```

```{r, fig.height = 5, fig.width = 5, fig.align = "center"}
rbind(score_norm, pcp_score_norm) %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point(aes(color = Method)) + geom_path(aes(group = Method, color = Method)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(X-lod0) / norm(X)",
       title = "Relative Prediction Error")
```

```{r, fig.height = 5, fig.width = 5, fig.align = "center"}
rbind(sdev_norm, pcp_sdev_norm) %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point(aes(color = Method)) + geom_path(aes(group = Method, color = Method)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(X-lod0) / norm(X)",
       title = "Relative Prediction Error")
```