---
title: "PCP-LOD: Increasing LOD in NHANES POPs"
author: "Lizzy Gibson"
date: "2/1/2020"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(ggcorrplot)
library(ggfortify)  
library(gridExtra)
library(factoextra)
library(knitr)
library(haven)
library(rlist)
library(Matrix)
library(matconv)
library(patchwork)
library(mvtnorm)
library(reshape2)
library(GGally)
library(grDevices)

options(scipen = 999)
```

# NHANES

CDC imputes values \<LOD as LOD/sqrt(2). Here, if comment code = "below detectable limit", set value to -1.

```{r}
nhanes <- read_sas(here::here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  mutate(lbx074la = ifelse(lbd074lc == 1, -1, lbx074la),
         lbx099la = ifelse(lbd099lc == 1, -1, lbx099la),
         lbx105la = ifelse(lbd105lc == 1, -1, lbx105la),
         lbx118la = ifelse(lbd118lc == 1, -1, lbx118la),
         lbx138la = ifelse(lbd138lc == 1, -1, lbx138la),
         lbx153la = ifelse(lbd153lc == 1, -1, lbx153la),
         lbx156la = ifelse(lbd156lc == 1, -1, lbx156la),
         lbx157la = ifelse(lbd157lc == 1, -1, lbx157la),
         lbx167la = ifelse(lbd167lc == 1, -1, lbx167la),
         lbx170la = ifelse(lbd170lc == 1, -1, lbx170la),
         lbx180la = ifelse(lbd180lc == 1, -1, lbx180la),
         lbx187la = ifelse(lbd187lc == 1, -1, lbx187la),
         lbxd01la = ifelse(lbdd01lc == 1, -1, lbxd01la),
         lbxd03la = ifelse(lbdd03lc == 1, -1, lbxd03la),
         lbxd04la = ifelse(lbdd04lc == 1, -1, lbxd04la),
         lbxd05la = ifelse(lbdd05lc == 1, -1, lbxd05la),
         lbxd07la = ifelse(lbdd07lc == 1, -1, lbxd07la),
         lbxf01la = ifelse(lbdf01lc == 1, -1, lbxf01la),
         lbxf02la = ifelse(lbdf02lc == 1, -1, lbxf02la),
         lbxf03la = ifelse(lbdf03lc == 1, -1, lbxf03la),
         lbxf04la = ifelse(lbdf04lc == 1, -1, lbxf04la),
         lbxf05la = ifelse(lbdf05lc == 1, -1, lbxf05la),
         lbxf06la = ifelse(lbdf06lc == 1, -1, lbxf06la),
         lbxf07la = ifelse(lbdf07lc == 1, -1, lbxf07la),
         lbxf08la = ifelse(lbdf08lc == 1, -1, lbxf08la),
         lbxpcbla = ifelse(lbdpcblc == 1, -1, lbxpcbla),
         lbxtcdla = ifelse(lbdtcdlc == 1, -1, lbxtcdla),
         lbxhxcla = ifelse(lbdhxclc == 1, -1, lbxhxcla),
         lbx189la = ifelse(lbd189lc == 1, -1, lbx189la),
         lbx194la = ifelse(lbd194lc == 1, -1, lbx194la),
         lbx196la = ifelse(lbd196lc == 1, -1, lbx196la),
         lbx199la = ifelse(lbd199lc == 1, -1, lbx199la),
         lbxd02la = ifelse(lbdd02lc == 1, -1, lbxd02la),
         lbxf09la = ifelse(lbdf09lc == 1, -1, lbxf09la))
```

```{r}
prop <- function (x) {1 - (sum(x, na.rm = TRUE)/nrow(nhanes))}

names <- nhanes %>% select(names(.)[grep("lc", names(.))]) %>% 
  summarize_all(prop) %>% select_if(~. > 0.2) %>% names() %>% str_sub(., 4, 6) %>% str_c("lbx", ., "la") %>% as.vector()

pops <- nhanes %>% 
  select(!!names) %>% na.omit(.)

names(pops) <- str_sub(names(pops), 1, 6)
names(pops) <- str_replace(names(pops), "lbxd", "D")
names(pops) <- str_replace(names(pops), "lbxf", "F")
names(pops) <- str_replace(names(pops), "lbx", "PCB")

#pops

ggcorr(pops, method = c("everything", "spearman"), limits = FALSE,
       label = TRUE, label_size = 3, label_alpha = TRUE,
       hjust = 0.85, size = 3, color = "grey50", layout.exp = 1) + ggtitle("Persistent organic pollutants \n in NHANES 2001-2002")
```

Here, make matrix of LODs to use in LOD PCP. Comment code = 1 means "below detectable limit". CDC imputes values <LOD as LOD/sqrt(2).

```{r}
# Matrix of 0/1
lod_names <- nhanes %>% select(names(.)[grep("lc", names(.))]) %>% 
  summarize_all(prop) %>% select_if(~. > 0.2) %>% names() %>% as.vector()

lods <- read_sas(here::here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  select(!!lod_names) %>% 
  na.omit()

# Matrix of all values (with CDC imputed values)
imputed <- read_sas(here::here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names() %>% 
  select(!!names) %>% 
  na.omit()

# Element-wise multiplication by 1/0
# Keep values <LOD
# Values >LOD == 0
# Multiply by sqrt(2) to get back LOD
lod_matrix <- (lods * imputed) * sqrt(2)
lod_matrix <- as.matrix(lod_matrix)
#summary(lod_matrix)
```

**Need to scale LODs, too!**

Need to scale PCBs because they have super different ranges. Need to get rid of values less than LOD to scale and then add them back.

```{r}
#summary(pops)

# make <LOD NA so they dont affect the scaling
pops[pops < 0] <- NA

# Get stand dev of values > LDO
pop_sd <- as.vector(apply(as.matrix(pops), 2, sd, na.rm = TRUE))

# head(pops[,5])
# head(pop_sd[5])
# head(pops[,5]/pop_sd[5])

# Scale bc way different ranges
# Scale by sd vector of length equal to the number of columns of x.
pops <- scale(pops, center = FALSE, scale = pop_sd)

# make <LOD negative again
pops[is.na(pops)] <- -1
mixture_data <- pops

#summary(mixture_data)
```

Also want to scale the LODS!

```{r}
# Scale lod matrix by stand dev of measurements
lod_matrix <- scale(lod_matrix, center = FALSE, scale = pop_sd)

summary(lod_matrix)
```

### >LOD PCP Function

```{r, jingkai}
loss_lod <- function(X, D, LOD) {

    X_lod <- ((X - D)     * (D >= 0)) +
             ((X - LOD)   * (D < 0 & (X > LOD))) +
              (X          * (D < 0 & X < 0))
  
  l <- sum(X_lod^2) / 2
  l
}

############################################################

pcp_lod <- function(D, lambda, mu, LOD) {
  
  m <- nrow(D)
  n <- ncol(D)
  rho <- 1 # Augmented Lagrangian coefficient (rate)
  
  L1 <- matrix(0, m, n)
  L2 <- matrix(0, m, n)
  L3 <- matrix(0, m, n)
  
  S1 <- matrix(0, m, n)
  S2 <- matrix(0, m, n)
  
  Z1 <- matrix(0, m, n)
  Z2 <- matrix(0, m, n)
  Z3 <- matrix(0, m, n)
  
  # Max iteration
  MAX_ITER <- 5000
  
  # Convergence Thresholds
  LOSS_THRESH <- 1e-5
  SAME_THRESH <- 1e-4
  
  if (is.vector(LOD)) {
    empty = matrix(1, nrow = nrow(D), ncol = ncol(D))
    LOD = t(t(empty) * LOD)
  }
  
  loss <- vector("numeric", MAX_ITER)
  
  for (i in 1:MAX_ITER) {
    
    nuc <- prox_nuclear( ((L2 + L3 - (Z1 + Z2)/rho)/2), 1/2/rho)
    L1 <- nuc[[1]]
    nuclearL1 <- nuc[[2]] #nuclearX
    
    S1 <- prox_l1((S2 - Z3/rho), lambda/rho)
    
      L2_opt1 <- (mu*rho*D     + (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)
      L2_opt2 <- L1 + Z1/rho
      L2_opt3 <- ((mu*rho*LOD + (((mu + rho)*Z1) - (mu*Z3) + ((mu + rho)*rho*L1) - (mu*rho*S1)))) / ((2*mu*rho) + (rho^2))
      L2_opt4 <- (               (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)

      L2_new <- (L2_opt1 * (D >= 0)) +
        (L2_opt2 * ((D < 0) & (((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
        (L2_opt3 * ((D < 0) & (((L2 + S2) > LOD)))) +
        (L2_opt4 * ((D < 0) & (((L2 + S2) < 0))))

      S2_opt1 <- (mu*rho*D     + (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)
      S2_opt2 <- S1 + (Z3/rho)
      S2_opt3 <- (((mu*rho*LOD) + (((mu + rho)*Z3) - (mu*Z1) + ((mu + rho)*rho*S1) - (mu*rho*L1)))) / ((2*mu*rho) + (rho^2))
      S2_opt4 <- (               (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)

      S2 <- (S2_opt1 * (D >= 0)) +
        (S2_opt2 * (((D < 0) & ((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
        (S2_opt3 * (((D < 0) & ((L2 + S2) > LOD)))) +
        (S2_opt4 * (((D < 0) & ((L2 + S2) < 0))))
   
    L2 <- L2_new
    
    L3 <- pmax(L1 + Z2/rho, 0, na.rm = TRUE)
    # % Non-Negativity constraint!
    
    Z1 <- Z1 + rho*(L1 - L2)
    Z2 <- Z2 + rho*(L1 - L3)
    Z3 <- Z3 + rho*(S1 - S2)
    # % Z accumulate differnces between L and L and between S and S
    
    loss[i] <- nuclearL1 + 
      (lambda*sum(abs(S1))) +
      (mu*loss_lod((L2 + S2), D, LOD)) +
      sum(Z1*(L1 - L2)) +
      sum(Z2*(L1 - L3)) +
      sum(Z3*(S1 - S2)) +
      (rho/2 * (sum((L1-L2)^2) + sum((L1 - L3)^2) + sum((S1 - S2)^2)))
    # % The code block above takes LOD into account.
    
    print(str_c(i, " Obj: ", loss[i]))
        
    if ((i != 1) && 
        (abs(loss[i-1] - loss[i]) < LOSS_THRESH) && 
        is_same(SAME_THRESH, L1, L2, L3) &&
        is_same(SAME_THRESH, S1, S2)) {
      break} # % Convergence criteria!
  }
  
  L <- L3 # (L1 + L2 + L3) / 3
  S <- S1 #(S1 + S2) / 2
  list(L = L, S = S, loss = loss)
}
```

## Run PCP

```{r}
m <- nrow(mixture_data)
p <- ncol(mixture_data)

lambda_mix <- 1/sqrt(m)
mu_mix <- sqrt(p/(2*log(m*p)))

results_0  <- lod_pcp(mixture_data, lambda_mix, mu_mix, Delta = lod_matrix)
results_0$loss

L_lod0 <- results_0[[1]]
S_lod0 <- results_0[[2]]
svd(L_lod0)$d

length(L_lod0[L_lod0 >= 0])
length(L_lod0)
```

## Vary $\mu$

Create function to output new low rank matrix, sparse matrix, singular values and rank of new low rank matrix, and $\lambda$ and $\mu$ parameters used

```{r mu_lam}
mu_value <- c(seq(0.01, 1/sqrt(n), by = 0.1), seq(1/sqrt(n), 10, by = 0.5))

make_L_mu <- function(mu){ 
  mixture_mu <- lod_pcp(as.matrix(mixture_data), 1/sqrt(m), mu, as.matrix(lod_matrix))
  L <- mixture_mu$L
  S <- mixture_mu$S
  sv_diag <- svd(L)$d # singular values on new low rank matrix
  sv_count <- sum(sv_diag > 0.001) # rank of new low rank matrix
  list(L = L, SV = sv_diag, S = S, Count = sv_count, Mu = mu, Lambda = 1/sqrt(m))
}
```

Loop over $\lambda$, $\mu$ pairs.

```{r looop, results = FALSE, cache = TRUE}
range_out <- map(.x = mu_value, ~make_L_mu(mu = .x))
```

### Changing Low Rank Matrix

Examine how rank of low rank matrix changes with varying $\lambda$ and $\mu$.

```{r rank_ml}
singular_value_count <- range_out %>% list.map(.[4]) %>% unlist() %>% 
  cbind(sv_count = ., mu = mu_value) %>% as_tibble() 
```

```{r rank2}
singular_value_count %>% summary()
```

```{r}
singular_value_count %>% 
  ggplot(aes(x = mu, y = sv_count)) +
  geom_point() + geom_line() +
  theme_bw() +
  labs(y = "Rank",
       x = expression(mu),
       title = expression(paste("Changing rank of low rank matrix with varying ", mu))) +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 70, hjust = 1))
```

### Changing Sparse Matrix

Examine how sparsity of sparse matrix changes with varying $\lambda$ and $\mu$.

```{r mu_sparse2}
sparse <- range_out %>% list.map(.[3])
# Extract all sparse matrices

loop.vector2 <- 1:length(mu_value)

cells <- m*n
prop_not_zero <- vector(length = length(mu_value))

for (i in loop.vector2) { # Loop over loop.vector2

 not_zeros <- sum(sparse[[i]]$S != 0)
  # Create proportion of non-zero values across all cells in sparse matrix
  prop_not_zero[i] <- not_zeros/cells
}

sparseness <- cbind(prop_not_zero, singular_value_count) %>% as_tibble()
```

```{r plot_sparse2}
sparseness %>% summary()
```

```{r}
sparseness %>%
  ggplot(aes(x = mu, y = prop_not_zero)) +
  geom_point() + geom_line() +
  theme_bw() +
  labs(y = "Proportion Non-Zero",
       x = expression(mu),
       title = expression(paste("Changing sparsity of sparse matrix with varying ", mu))) +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 70, hjust = 1))
```

## Error

Each PCP creates a low rank L matrix and a sparse matrix that sum to the original D matrix with some error. To choose the best value for $\mu$, we add the L and S matrices to form D', then subtract D - D' to get an error matrix for each $\mu$. We then take the RMSE of the low rank matrix and the F norm of each error matrix, divided by the norm of the original matrix, to get relative error.

```{r cv_both}
# low_rank and sparse are lists of L and S matrices for each 
mix <- as.matrix(mixture_data)

loop.vector2 <- 1:length(mu_value)
rmse <- vector(length = length(mu_value))
rel_error <- vector(length = length(mu_value))
new_ml <- list()

low_rank_ml <- range_out %>% list.map(.[1])
sparse_ml <- range_out %>% list.map(.[3])

for (i in loop.vector2) { # Loop over loop.vector
  new_ml[[i]]  <- low_rank_ml[[i]]$L + sparse_ml[[i]]$S
  rmse[i]      <- sqrt(mean((mix - new_ml[[i]])^2))
  rel_error[i] <- norm((mixture_data - new_ml[[i]]), type = "F")/norm(mix, type = "F")
  }

cv <- cbind(mu_value, rmse, rel_error) %>% as_tibble()
```

### Plot Error

```{r plot_both}
cv %>% summary()
```

Below is the cross-section at $\lambda = 1/\sqrt{n}$, same as only varying $\mu$.

```{r}
cv %>% 
  ggplot(aes(y = rmse, x = mu_value)) + 
  geom_point() + geom_line() +
  theme_bw() +
  labs(y = "Root Mean Squared Error",
       x = expression(mu),
       title = expression(paste("Changing RMSE with varying ", mu)))
```
