---
title: "NHANES POP Simulations"
author: "Lizzy Gibson"
date: "4/8/2020"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    toc_depth: 5
    code_folding: 'hide'
---

```{r setup, include=FALSE}
require("knitr")
opts_chunk$set(echo = TRUE)
options(scipen = 999)
library(R.matlab)
library(tidyverse)
library(gridExtra)
library(Matrix)
library(matconv)
library(patchwork)
library(janitor)
library(ggcorrplot)
library(ggfortify)  
library(factoextra)
library(knitr)
library(haven)
library(rlist)
library(mvtnorm)
library(reshape2)
library(GGally)
library(grDevices)
library(plotly)
library(Cairo)
```

## NHANES

NHANES 2001-2002 POP data.

```{r}
nhanes <- read_sas(here::here("./Data/studypop_lod.sas7bdat")) %>% 
  clean_names()

head(nhanes)[1:7]
```

LA = lipid adjusted  
LC = comment code  

### Select

CDC imputes values \<LOD as LOD/sqrt(2). Here, if comment code = "below detectable limit", LC = 1.

```{r}
prop <- function (x) {1 - (sum(x, na.rm = TRUE)/nrow(nhanes))}

names <- nhanes %>% select(names(.)[grep("lc", names(.))]) %>% 
  summarize_all(prop) %>% select_if(~. > 0.6) %>% names() %>% str_sub(., 4, 6) %>% str_c("lbx", ., "la") %>% as.vector()

pops <- nhanes %>% 
  select(!!names) %>% na.omit(.)

names(pops) <- str_sub(names(pops), 1, 6)
names(pops) <- str_replace(names(pops), "lbxd", "D")
names(pops) <- str_replace(names(pops), "lbxf", "F")
names(pops) <- str_replace(names(pops), "lbx", "PCB")
pops

ggcorr(pops, method = c("everything", "spearman"), limits = FALSE,
       label = TRUE, label_size = 3, label_alpha = TRUE,
       hjust = 0.85, size = 3, color = "grey50", layout.exp = 1) + ggtitle("Persistent organic pollutants \n in NHANES 2001-2002")
```

### Simulate

Remove comment codes for simulations.  
Remove NA for simulations.

```{r}
# Vector of NHANES means
# log to approx normal dist
means <- as_vector(map(log(pops), function(x) mean(x, na.rm = TRUE)))

# Covariance matrix from NHANES
# log to approx normal dist
covs <- cov(log(pops))

# Simulate with multivariate normal function
# exp multi-normal to get multi-log normal
set.seed(1988)
sim_all <- exp(rmvnorm(1000, mean = means, sigma = covs)) %>% as_tibble()
```

```{r}
ggcorr(sim_all, method = c("everything", "spearman"), limits = FALSE,
       label = TRUE, label_size = 3, label_alpha = TRUE,
       hjust = 0.85, size = 3, color = "grey50", layout.exp = 1) + ggtitle("Simulated Data")
```

### Scale Simulations

Divide by standard deviation, do not mean center.  

```{r}
sim_all <- sim_all %>% 
  mutate_all(scale, center = FALSE)
```

### Create \<LOD Datasets

```{r, neg}
# Create version with 10% lowest values for each variable as below the LOD
mix_data_lod_10 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .10), -1, .)) %>% as.matrix()

# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .20), -1, .)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .30), -1, .)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .40), -1, .)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .50), -1, .)) %>% as.matrix()

# Create version with 10% lowest values for each variable as below the LOD
mix_data_lod_10_0 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .10), 0, .)) %>% as.matrix()

# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20_0 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .20), 0, .)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30_0 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .30), 0, .)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40_0 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .40), 0, .)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50_0 <- sim_all %>% 
  mutate_all(~ifelse(. < quantile(., probs = .50), 0, .)) %>% as.matrix()

# Create version with 10% lowest values for each variable as below the LOD
mix_data_lod_10_sqrt2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .10), (quantile(., probs = .10)/sqrt(2)), .)) %>% as.matrix()

# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20_sqrt2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .20), (quantile(., probs = .20)/sqrt(2)), .)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30_sqrt2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .30), (quantile(., probs = .30)/sqrt(2)), .)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40_sqrt2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .40), (quantile(., probs = .40)/sqrt(2)), .)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50_sqrt2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .50), (quantile(., probs = .50)/sqrt(2)), .)) %>% as.matrix()

# Create version with 10% lowest values for each variable as below the LOD
mix_data_lod_10_2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .10), (quantile(., probs = .10)/2), .)) %>% as.matrix()

# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20_2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .20), (quantile(., probs = .20)/2), .)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30_2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .30), (quantile(., probs = .30)/2), .)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40_2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .40), (quantile(., probs = .40)/2), .)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50_2 <- sim_all %>% 
  mutate_all(~ifelse(. <= quantile(., probs = .50), (quantile(., probs = .50)/2), .)) %>% as.matrix()
```

### Quantiles = LOD

```{r}
delta10 <- sim_all %>% 
  summarise_all(quantile, probs = .10) %>% as_vector()

delta20 <- sim_all %>% 
  summarise_all(quantile, probs = .20) %>% as_vector()

delta30 <- sim_all %>% 
  summarise_all(quantile, probs = .30) %>% as_vector()

delta40 <- sim_all %>% 
  summarise_all(quantile, probs = .40) %>% as_vector()

delta50 <- sim_all %>% 
  summarise_all(quantile, probs = .50) %>% as_vector()
```

## Fuctions

```{r, nn_function}
prox_l1 <- function(Y, c) {
  
  myzero <- matrix(data = 0, ncol = ncol(Y), nrow = nrow(Y))
  X <- sign(Y) * pmax(abs(Y) - c, myzero, na.rm = TRUE)
  X
} 

############################################################

prox_nuclear <- function(Y, c) {
  
  USV <- svd(Y)
  U <- USV$u
  S <- USV$d
  V <- USV$v
  
  myzero <- vector("numeric", length = length(S))
  S_new <- sign(S) * pmax(abs(S) - c, myzero, na.rm = TRUE)
  X <- U %*% diag(S_new) %*% t(V)
  nuclearX  <- sum(abs(S_new))

    list(X = X, nuclearX = nuclearX)
}

############################################################

is_same <- function(SAME_THRESH, ...) {
  flag <- TRUE
  varargin <- list(...)
  if (length(varargin) == 2) {
    if (max(abs(varargin[[1]] - varargin[[2]])) > SAME_THRESH) {
      flag <- FALSE
    }
  }
  else if (length(varargin) == 3) {
    if ((max(abs(varargin[[1]] - varargin[[2]])) > SAME_THRESH) |
        (max(abs(varargin[[1]] - varargin[[3]])) > SAME_THRESH) |
        (max(abs(varargin[[2]] - varargin[[3]])) > SAME_THRESH)) {
      flag <- FALSE
    }
  }
  flag
}

############################################################

loss_lod_NN <- function(X, D, LOD) {

    X_lod <- ((X - D)     * (D >= LOD)) +
            ((X - LOD)  * ((D < LOD) & (X > LOD))) +
              (X          * ((D < LOD) & (X < 0)))
  
  l <- sum(X_lod^2) / 2
  l
}

############################################################

pcp_lod_NN <- function(D, lambda, mu, LOD) {
  
  if( any(D < matrix(0, nrow = nrow(D), ncol = ncol(D))) ) stop("Physical concentration measurements cannot be negative.")
  
  m <- nrow(D)
  n <- ncol(D)
  rho <- 1 # Augmented Lagrangian coefficient (rate)
  
  L1 <- matrix(0, m, n)
  L2 <- matrix(0, m, n)
  L3 <- matrix(0, m, n)
  
  S1 <- matrix(0, m, n)
  S2 <- matrix(0, m, n)
  
  Z1 <- matrix(0, m, n)
  Z2 <- matrix(0, m, n)
  Z3 <- matrix(0, m, n)
  
  # Max iteration
  MAX_ITER <- 5000
  
  # Convergence Thresholds
  LOSS_THRESH <- 1e-5
  SAME_THRESH <- 1e-4
  
  if (is.vector(LOD)) {
    empty = matrix(TRUE, nrow = nrow(D), ncol = ncol(D))
    LOD = t(t(empty) * LOD)
  }
  
  if( any(LOD < matrix(0, nrow = nrow(LOD), ncol = ncol(LOD))) ) stop("Physical Limits of Detection (LOD) cannot be negative.")
  
  loss <- vector("numeric", MAX_ITER)
  
  for (i in 1:MAX_ITER) {
    
    nuc <- prox_nuclear( ((L2 + L3 - (Z1 + Z2)/rho)/2), 1/2/rho)
    L1 <- nuc[[1]]
    nuclearL1 <- nuc[[2]] #nuclearX
    # % L, Z, S all start at zero, and change each iteration
    # % Prox_nuc is singular value thresholding
    # % L is low rank matrix
    
    S1 <- prox_l1((S2 - Z3/rho), lambda/rho)
    # % S is sparse matrix
    
      L2_opt1 <- (mu*rho*D     + (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)
      L2_opt2 <- L1 + Z1/rho
      L2_opt3 <- ((mu*rho*LOD + (((mu + rho)*Z1) - (mu*Z3) + ((mu + rho)*rho*L1) - (mu*rho*S1)))) / ((2*mu*rho) + (rho^2))
      L2_opt4 <- (               (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)

      L2_new <- (L2_opt1 * (( D >= LOD))) +
                (L2_opt2 * (((D < LOD) & ((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
                (L2_opt3 * (((D < LOD) & ((L2 + S2) > LOD)))) +
                (L2_opt4 * (((D < LOD) & ((L2 + S2) < 0))))

      S2_opt1 <- (mu*rho*D     + (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)
      S2_opt2 <- S1 + (Z3/rho)
      S2_opt3 <- (((mu*rho*LOD) + (((mu + rho)*Z3) - (mu*Z1) + ((mu + rho)*rho*S1) - (mu*rho*L1)))) / ((2*mu*rho) + (rho^2))
      S2_opt4 <- (               (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)

      S2 <- (S2_opt1 * (( D >= LOD))) +
            (S2_opt2 * (((D < LOD) & ((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
            (S2_opt3 * (((D < LOD) & ((L2 + S2) > LOD)))) +
            (S2_opt4 * (((D < LOD) & ((L2 + S2) < 0))))
   
    L2 <- L2_new
    
    L3 <- pmax(L1 + Z2/rho, 0, na.rm = TRUE)
    # % Non-Negativity constraint!
    
    Z1 <- Z1 + rho*(L1 - L2)
    Z2 <- Z2 + rho*(L1 - L3)
    Z3 <- Z3 + rho*(S1 - S2)
    # % Z accumulate differnces between L and L and between S and S
    
    loss[i] <- nuclearL1 + 
      (lambda*sum(abs(S1))) +
      (mu*loss_lod_NN((L2 + S2), D, LOD)) +
      sum(Z1*(L1 - L2)) +
      sum(Z2*(L1 - L3)) +
      sum(Z3*(S1 - S2)) +
      (rho/2 * (sum((L1-L2)^2) + sum((L1 - L3)^2) + sum((S1 - S2)^2)))
    # % The code block above takes LOD into account.
    
    print(str_c(i, " Obj: ", loss[i]))
      
    if ((i != 1) && 
        (abs(loss[i-1] - loss[i]) < LOSS_THRESH) && 
        is_same(SAME_THRESH, L1, L2, L3) &&
        is_same(SAME_THRESH, S1, S2)) {
      break} # % Convergence criteria!
  }
  
  L <- L3 # (L1 + L2 + L3) / 3
  S <- S1 #(S1 + S2) / 2
  list(L = L, S = S, loss = loss)
}
```

```{r, older}
loss_lod <- function(X, D, LOD) {

    X_lod <- ((X - D)     * (D >= 0)) +
             ((X - LOD)   * (D < 0 & (X > LOD))) +
              (X          * (D < 0 & X < 0))
  
  l <- sum(X_lod^2) / 2
  l
}

############################################################

pcp_lod <- function(D, lambda, mu, LOD) {
  
  m <- nrow(D)
  n <- ncol(D)
  rho <- 1 # Augmented Lagrangian coefficient (rate)
  
  L1 <- matrix(0, m, n)
  L2 <- matrix(0, m, n)
  L3 <- matrix(0, m, n)
  
  S1 <- matrix(0, m, n)
  S2 <- matrix(0, m, n)
  
  Z1 <- matrix(0, m, n)
  Z2 <- matrix(0, m, n)
  Z3 <- matrix(0, m, n)
  
  # Max iteration
  MAX_ITER <- 5000
  
  # Convergence Thresholds
  LOSS_THRESH <- 1e-5
  SAME_THRESH <- 1e-4
  
  if (is.vector(LOD)) {
    empty = matrix(1, nrow = nrow(D), ncol = ncol(D))
    LOD = t(t(empty) * LOD)
  }
  
  loss <- vector("numeric", MAX_ITER)
  
  for (i in 1:MAX_ITER) {
    
    nuc <- prox_nuclear( ((L2 + L3 - (Z1 + Z2)/rho)/2), 1/2/rho)
    L1 <- nuc[[1]]
    nuclearL1 <- nuc[[2]] #nuclearX
    
    S1 <- prox_l1((S2 - Z3/rho), lambda/rho)
    
      L2_opt1 <- (mu*rho*D     + (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)
      L2_opt2 <- L1 + Z1/rho
      L2_opt3 <- ((mu*rho*LOD + (((mu + rho)*Z1) - (mu*Z3) + ((mu + rho)*rho*L1) - (mu*rho*S1)))) / ((2*mu*rho) + (rho^2))
      L2_opt4 <- (               (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)

      L2_new <- (L2_opt1 * (D >= 0)) +
        (L2_opt2 * ((D < 0) & (((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
        (L2_opt3 * ((D < 0) & (((L2 + S2) > LOD)))) +
        (L2_opt4 * ((D < 0) & (((L2 + S2) < 0))))

      S2_opt1 <- (mu*rho*D     + (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)
      S2_opt2 <- S1 + (Z3/rho)
      S2_opt3 <- (((mu*rho*LOD) + (((mu + rho)*Z3) - (mu*Z1) + ((mu + rho)*rho*S1) - (mu*rho*L1)))) / ((2*mu*rho) + (rho^2))
      S2_opt4 <- (               (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)

      S2 <- (S2_opt1 * (D >= 0)) +
        (S2_opt2 * (((D < 0) & ((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
        (S2_opt3 * (((D < 0) & ((L2 + S2) > LOD)))) +
        (S2_opt4 * (((D < 0) & ((L2 + S2) < 0))))
   
    L2 <- L2_new
    
    L3 <- pmax(L1 + Z2/rho, 0, na.rm = TRUE)
    # % Non-Negativity constraint!
    
    Z1 <- Z1 + rho*(L1 - L2)
    Z2 <- Z2 + rho*(L1 - L3)
    Z3 <- Z3 + rho*(S1 - S2)
    # % Z accumulate differnces between L and L and between S and S
    
    loss[i] <- nuclearL1 + 
      (lambda*sum(abs(S1))) +
      (mu*loss_lod((L2 + S2), D, LOD)) +
      sum(Z1*(L1 - L2)) +
      sum(Z2*(L1 - L3)) +
      sum(Z3*(S1 - S2)) +
      (rho/2 * (sum((L1-L2)^2) + sum((L1 - L3)^2) + sum((S1 - S2)^2)))
    # % The code block above takes LOD into account.
    
    print(str_c(i, " Obj: ", loss[i]))
        
    if ((i != 1) && 
        (abs(loss[i-1] - loss[i]) < LOSS_THRESH) && 
        is_same(SAME_THRESH, L1, L2, L3) &&
        is_same(SAME_THRESH, S1, S2)) {
      break} # % Convergence criteria!
  }
  
  L <- L3 # (L1 + L2 + L3) / 3
  S <- S1 #(S1 + S2) / 2
  list(L = L, S = S, loss = loss)
}
```

```{r}
soft_thresholding <- function(v, lambda) {
  myzero <- matrix(data = 0, ncol = ncol(v), nrow = nrow(v))
  w <- sign(v) * pmax(abs(v) - lambda, myzero)
  w
} 

soft_thresholding_diag <- function(v, lambda) {
  myzero <- vector("numeric", length = length(v))
  w <- sign(v) * pmax(abs(v) - lambda, myzero)
  w
} 

singular_value_threshold <- function(M, lambda) {
  
  USV <- svd(M)
  U <- USV$u
  S <- USV$d
  V <- USV$v
    
  N <- U %*% diag(soft_thresholding_diag(S, lambda)) %*% t(V)
  
  v  <- sum(soft_thresholding_diag(S, lambda))
  
  svt <- list(N = N, v = v) 
  svt
}

original_pcp <- function(D, lambda, mu) {
  
  m <- nrow(D)
  n <- ncol(D)
  
  S <- matrix(0, nrow = m, ncol = n)
  L <- matrix(0, nrow = m, ncol = n)
  
  iter <- 0
  MAX_ITER <- 5000
  done <- FALSE
  
  # Convergence Thresholds
  LOSS_THRESH <- 1e-4
  loss <- vector("numeric", MAX_ITER)
  
  while (!done) {
    
    iter <- iter + 1
    
    svt <- singular_value_threshold((D - S), 1/mu)
    L <- svt[[1]] #svt$N
    v <- svt[[2]]
    
    S <- soft_thresholding((D - L), lambda/mu)
    
    obj <- v + lambda * sum(abs(S)) + (mu/2) * norm((D - L - S), type = "F")^2
    loss[iter] <- obj
    
    print(str_c(iter, " Obj: ", obj))
    
    if (iter >= MAX_ITER | 
        (iter != 1) && (abs(loss[iter-1] - loss[iter]) < LOSS_THRESH)) {done <- TRUE}
    
  }
  list(L = L, S = S, Lambda = lambda, Mu = mu, obj_value = obj)
}
```

```{r, functionnnS}
pcp_lod_nnS <- function(D, lambda, mu, LOD) {
  
  m <- nrow(D)
  n <- ncol(D)
  rho <- 1 # Augmented Lagrangian coefficient (rate)
  
  L1 <- matrix(0, m, n)
  L2 <- matrix(0, m, n)
  L3 <- matrix(0, m, n)
  
  S1 <- matrix(0, m, n)
  S2 <- matrix(0, m, n)
  S3 <- matrix(0, m, n) # ADDED
  
  Z1 <- matrix(0, m, n)
  Z2 <- matrix(0, m, n)
  Z3 <- matrix(0, m, n)
  Z4 <- matrix(0, m, n) # ADDED
  
  # Max iteration
  MAX_ITER <- 5000
  
  # Convergence Thresholds
  LOSS_THRESH <- 1e-5
  SAME_THRESH <- 1e-4
  
  if (is.vector(LOD)) {
  #tf = ifelse(D < 0, TRUE, FALSE)
  #LOD = t(t(tf) * LOD)
    empty = matrix(1, nrow = nrow(D), ncol = ncol(D))
    LOD = t(t(empty) * LOD)
    }
  
  loss <- vector("numeric", MAX_ITER)
  
  for (i in 1:MAX_ITER) {
    
    nuc <- prox_nuclear(((L2 + L3 - (Z1 + Z2)/rho)/2), 1/2/rho)
    L1 <- nuc[[1]]
    nuclearL1 <- nuc[[2]] #nuclearX
    
    S1 <- prox_l1(((S2 + S3 - (Z3 + Z4)/rho)/2), lambda/rho) # ADDED
      #prox_l1(S2 - Z3/rho, lambda/rho)
      #prox_l1(((S2 + S3 - (Z3 + Z4)/rho)), lambda/rho) # ADDED
    
    L2_opt1 <- (mu*rho*D     + (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)
    L2_opt2 <- L1 + Z1/rho
    L2_opt3 <- ((mu*rho*LOD + (((mu + rho)*Z1) - (mu*Z3) + ((mu + rho)*rho*L1) - (mu*rho*S1)))) / ((2*mu*rho) + (rho^2))
    L2_opt4 <- (               (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)

    L2 <- (L2_opt1 * (D >= 0)) +
        (L2_opt2 * ((D < 0) & (((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
        (L2_opt3 * ((D < 0) & (((L2 + S2) > LOD)))) +
        (L2_opt4 * ((D < 0) & (((L2 + S2) < 0))))

    S2_opt1 <- (mu*rho*D     + (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)
    S2_opt2 <- S1 + (Z3/rho)
    S2_opt3 <- (((mu*rho*LOD) + (((mu + rho)*Z3) - (mu*Z1) + ((mu + rho)*rho*S1) - (mu*rho*L1)))) / ((2*mu*rho) + (rho^2))
    S2_opt4 <- (               (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)

    S2 <- (S2_opt1 * (D >= 0)) +
        (S2_opt2 * (((D < 0) & ((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
        (S2_opt3 * (((D < 0) & ((L2 + S2) > LOD)))) +
        (S2_opt4 * (((D < 0) & ((L2 + S2) < 0))))
      
    L3 <- pmax(L1 + Z2/rho, 0, na.rm = TRUE)
    # % Non-Negativity constraint!
    
    ## ADDED
    S3 <- pmax(S1 + Z4/rho, 0, na.rm = TRUE)
    
    Z1 <- Z1 + rho*(L1 - L2)
    Z2 <- Z2 + rho*(L1 - L3)
    Z3 <- Z3 + rho*(S1 - S2)
    Z4 <- Z4 + rho*(S1 - S3) # ADDED
    # % Z accumulate differnces between L and L and between S and S
    
    loss[i] <- nuclearL1 + 
      (lambda*sum(abs(S1))) +
      (mu*loss_lod((L2 + S2), D, LOD)) +
      sum(Z1*(L1 - L2)) +
      sum(Z2*(L1 - L3)) +
      sum(Z3*(S1 - S2)) +
      sum(Z4*(S1 - S3)) + # ADDED
      (rho/2 * (sum((L1-L2)^2) + sum((L1 - L3)^2) + sum((S1 - S2)^2)) + sum((S1 - S3)^2)) # ADDED
    # % The code block above takes LOD into account.
    
    print(str_c(i, " Obj: ", loss[i]))
        
    if ((i != 1) && 
        (abs(loss[i-1] - loss[i]) < LOSS_THRESH) && 
        is_same(SAME_THRESH, L1, L2, L3) &&
        is_same(SAME_THRESH, S1, S2, S3)) { # ADDED
      break} # % Convergence criteria!
  }
  
  L <- L3 # (L1 + L2 + L3) / 3
  S <- S3 # (S1 + S2 + S3) / 2
  list(L = L, S = S, loss = loss)
}
```

## PCP

```{r, jingkai_leave, cache = TRUE}
m <- nrow(sim_all)
p <- ncol(sim_all)

lambda_mix <- 1/sqrt(m)
mu_mix <- sqrt(p/(2*log(m*p)))

mix <- as.matrix(sim_all)
  
results_0  <- pcp_lod(mix,             lambda_mix, mu_mix, 0)
results_10 <- pcp_lod(mix_data_lod_10, lambda_mix, mu_mix, delta10)
results_20 <- pcp_lod(mix_data_lod_20, lambda_mix, mu_mix, delta20)
results_30 <- pcp_lod(mix_data_lod_30, lambda_mix, mu_mix, delta30)
results_40 <- pcp_lod(mix_data_lod_40, lambda_mix, mu_mix, delta40)
results_50 <- pcp_lod(mix_data_lod_50, lambda_mix, mu_mix, delta50)

nn_results_0  <- pcp_lod_NN(mix, lambda_mix, mu_mix, 0)
nn_results_10 <- pcp_lod_NN(mix, lambda_mix, mu_mix, delta10)
nn_results_20 <- pcp_lod_NN(mix, lambda_mix, mu_mix, delta20)
nn_results_30 <- pcp_lod_NN(mix, lambda_mix, mu_mix, delta30)
nn_results_40 <- pcp_lod_NN(mix, lambda_mix, mu_mix, delta40)
nn_results_50 <- pcp_lod_NN(mix, lambda_mix, mu_mix, delta50)

L_lod0 <- results_0[[1]]
S_lod0 <- results_0[[2]]
L_lod10 <- results_10[[1]]
S_lod10 <- results_10[[2]]
L_lod20 <- results_20[[1]]
S_lod20 <- results_20[[2]]
L_lod30 <- results_30[[1]]
S_lod30 <- results_30[[2]]
L_lod40 <- results_40[[1]]
S_lod40 <- results_40[[2]]
L_lod50 <- results_50[[1]]
S_lod50 <- results_50[[2]]

nn_L_lod0 <- nn_results_0[[1]]
nn_S_lod0 <- nn_results_0[[2]]
nn_L_lod10 <- nn_results_10[[1]]
nn_S_lod10 <- nn_results_10[[2]]
nn_L_lod20 <- nn_results_20[[1]]
nn_S_lod20 <- nn_results_20[[2]]
nn_L_lod30 <- nn_results_30[[1]]
nn_S_lod30 <- nn_results_30[[2]]
nn_L_lod40 <- nn_results_40[[1]]
nn_S_lod40 <- nn_results_40[[2]]
nn_L_lod50 <- nn_results_50[[1]]
nn_S_lod50 <- nn_results_50[[2]]

# all_equal(nn_L_lod0, L_lod0)
# all_equal(nn_L_lod10, L_lod10)
# all_equal(nn_L_lod20, L_lod20)
# all_equal(nn_L_lod30, L_lod30)
# all_equal(nn_L_lod40, L_lod40)
# all_equal(nn_L_lod50, L_lod50)
```

```{r, subzero_old, cache = TRUE}
results_0_0  <- original_pcp(mix,               lambda_mix, mu_mix)
results_10_0 <- original_pcp(mix_data_lod_10_0, lambda_mix, mu_mix)
results_20_0 <- original_pcp(mix_data_lod_20_0, lambda_mix, mu_mix)
results_30_0 <- original_pcp(mix_data_lod_30_0, lambda_mix, mu_mix)
results_40_0 <- original_pcp(mix_data_lod_40_0, lambda_mix, mu_mix)
results_50_0 <- original_pcp(mix_data_lod_50_0, lambda_mix, mu_mix)

L_lod0_0 <- results_0_0[[1]]
S_lod0_0 <- results_0_0[[2]]
L_lod10_0 <- results_10_0[[1]]
S_lod10_0 <- results_10_0[[2]]
L_lod20_0 <- results_20_0[[1]]
S_lod20_0 <- results_20_0[[2]]
L_lod30_0 <- results_30_0[[1]]
S_lod30_0 <- results_30_0[[2]]
L_lod40_0 <- results_40_0[[1]]
S_lod40_0 <- results_40_0[[2]]
L_lod50_0 <- results_50_0[[1]]
S_lod50_0 <- results_50_0[[2]]

results_0_sqrt2  <- original_pcp(mix,                   lambda_mix, mu_mix)
results_10_sqrt2 <- original_pcp(mix_data_lod_10_sqrt2, lambda_mix, mu_mix)
results_20_sqrt2 <- original_pcp(mix_data_lod_20_sqrt2, lambda_mix, mu_mix)
results_30_sqrt2 <- original_pcp(mix_data_lod_30_sqrt2, lambda_mix, mu_mix)
results_40_sqrt2 <- original_pcp(mix_data_lod_40_sqrt2, lambda_mix, mu_mix)
results_50_sqrt2 <- original_pcp(mix_data_lod_50_sqrt2, lambda_mix, mu_mix)

L_lod0_sqrt2 <- results_0_sqrt2[[1]]
S_lod0_sqrt2 <- results_0_sqrt2[[2]]
L_lod10_sqrt2 <- results_10_sqrt2[[1]]
S_lod10_sqrt2 <- results_10_sqrt2[[2]]
L_lod20_sqrt2 <- results_20_sqrt2[[1]]
S_lod20_sqrt2 <- results_20_sqrt2[[2]]
L_lod30_sqrt2 <- results_30_sqrt2[[1]]
S_lod30_sqrt2 <- results_30_sqrt2[[2]]
L_lod40_sqrt2 <- results_40_sqrt2[[1]]
S_lod40_sqrt2 <- results_40_sqrt2[[2]]
L_lod50_sqrt2 <- results_50_sqrt2[[1]]
S_lod50_sqrt2 <- results_50_sqrt2[[2]]
```

```{r, two, cache = TRUE}
results_0_2  <- original_pcp(mix,                   lambda_mix, mu_mix)
results_10_2 <- original_pcp(mix_data_lod_10_2, lambda_mix, mu_mix)
results_20_2 <- original_pcp(mix_data_lod_20_2, lambda_mix, mu_mix)
results_30_2 <- original_pcp(mix_data_lod_30_2, lambda_mix, mu_mix)
results_40_2 <- original_pcp(mix_data_lod_40_2, lambda_mix, mu_mix)
results_50_2 <- original_pcp(mix_data_lod_50_2, lambda_mix, mu_mix)

L_lod0_2 <- results_0_2[[1]]
S_lod0_2 <- results_0_2[[2]]
L_lod10_2 <- results_10_2[[1]]
S_lod10_2 <- results_10_2[[2]]
L_lod20_2 <- results_20_2[[1]]
S_lod20_2 <- results_20_2[[2]]
L_lod30_2 <- results_30_2[[1]]
S_lod30_2 <- results_30_2[[2]]
L_lod40_2 <- results_40_2[[1]]
S_lod40_2 <- results_40_2[[2]]
L_lod50_2 <- results_50_2[[1]]
S_lod50_2 <- results_50_2[[2]]
```

```{r pcpnns, cache = TRUE}
results_0_nnS  <- pcp_lod_nnS(mix,             lambda_mix, mu_mix, 0)
results_10_nnS <- pcp_lod_nnS(mix_data_lod_10, lambda_mix, mu_mix, delta10)
results_20_nnS <- pcp_lod_nnS(mix_data_lod_20, lambda_mix, mu_mix, delta20)
results_30_nnS <- pcp_lod_nnS(mix_data_lod_30, lambda_mix, mu_mix, delta30)
results_40_nnS <- pcp_lod_nnS(mix_data_lod_40, lambda_mix, mu_mix, delta40)
results_50_nnS <- pcp_lod_nnS(mix_data_lod_50, lambda_mix, mu_mix, delta50)

L_lod0_nnS <- results_0_nnS[[1]]
S_lod0_nnS <- results_0_nnS[[2]]
L_lod10_nnS <- results_10_nnS[[1]]
S_lod10_nnS <- results_10_nnS[[2]]
L_lod20_nnS <- results_20_nnS[[1]]
S_lod20_nnS <- results_20_nnS[[2]]
L_lod30_nnS <- results_30_nnS[[1]]
S_lod30_nnS <- results_30_nnS[[2]]
L_lod40_nnS <- results_40_nnS[[1]]
S_lod40_nnS <- results_40_nnS[[2]]
L_lod50_nnS <- results_50_nnS[[1]]
S_lod50_nnS <- results_50_nnS[[2]]
```

## X - L - S

```{r}
F_norm <- as_tibble(cbind(`0%` = norm((mix - L_lod0 - S_lod0), type = "F")/norm((mix), type = "F"),
      `10%` = norm((mix - L_lod10 - S_lod10), type = "F")/norm((mix), type = "F"),
      `20%` = norm((mix - L_lod20 - S_lod20), type = "F")/norm((mix), type = "F"),
      `30%` = norm((mix - L_lod30 - S_lod30), type = "F")/norm((mix), type = "F"),
      `40%` = norm((mix - L_lod40 - S_lod40), type = "F")/norm((mix), type = "F"),
      `50%` = norm((mix - L_lod50 - S_lod50), type = "F")/norm((mix), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "LOD PCP")

nn_F_norm <- as_tibble(cbind(`0%` = norm((mix - nn_L_lod0 - nn_S_lod0), type = "F")/norm((mix), type = "F"),
      `10%` = norm((mix - nn_L_lod10 - nn_S_lod10), type = "F")/norm((mix), type = "F"),
      `20%` = norm((mix - nn_L_lod20 - nn_S_lod20), type = "F")/norm((mix), type = "F"),
      `30%` = norm((mix - nn_L_lod30 - nn_S_lod30), type = "F")/norm((mix), type = "F"),
      `40%` = norm((mix - nn_L_lod40 - nn_S_lod40), type = "F")/norm((mix), type = "F"),
      `50%` = norm((mix - nn_L_lod50 - nn_S_lod50), type = "F")/norm((mix), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Both")

F_norm_0 <- as_tibble(cbind(`0%` = norm((mix - L_lod0_0 - S_lod0_0), type = "F")/norm((mix), type = "F"),
      `10%` = norm((mix - L_lod10_0 - S_lod10_0), type = "F")/norm((mix), type = "F"),
      `20%` = norm((mix - L_lod20_0 - S_lod20_0), type = "F")/norm((mix), type = "F"),
      `30%` = norm((mix - L_lod30_0 - S_lod30_0), type = "F")/norm((mix), type = "F"),
      `40%` = norm((mix - L_lod40_0 - S_lod40_0), type = "F")/norm((mix), type = "F"),
      `50%` = norm((mix - L_lod50_0 - S_lod50_0), type = "F")/norm((mix), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP w/ 0")

F_norm_sqrt2 <- as_tibble(cbind(`0%` = norm((mix - L_lod0_sqrt2 - S_lod0_sqrt2), type = "F")/norm((mix), type = "F"),
      `10%` = norm((mix - L_lod10_sqrt2 - S_lod10_sqrt2), type = "F")/norm((mix), type = "F"),
      `20%` = norm((mix - L_lod20_sqrt2 - S_lod20_sqrt2), type = "F")/norm((mix), type = "F"),
      `30%` = norm((mix - L_lod30_sqrt2 - S_lod30_sqrt2), type = "F")/norm((mix), type = "F"),
      `40%` = norm((mix - L_lod40_sqrt2 - S_lod40_sqrt2), type = "F")/norm((mix), type = "F"),
      `50%` = norm((mix - L_lod50_sqrt2 - S_lod50_sqrt2), type = "F")/norm((mix), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))

F_norm_2 <- as_tibble(cbind(`0%` = norm((mix - L_lod0_2 - S_lod0_2), type = "F")/norm((mix), type = "F"),
                                `10%` = norm((mix - L_lod10_2 - S_lod10_2), type = "F")/norm((mix), type = "F"),
                                `20%` = norm((mix - L_lod20_2 - S_lod20_2), type = "F")/norm((mix), type = "F"),
                                `30%` = norm((mix - L_lod30_2 - S_lod30_2), type = "F")/norm((mix), type = "F"),
                                `40%` = norm((mix - L_lod40_2 - S_lod40_2), type = "F")/norm((mix), type = "F"),
                                `50%` = norm((mix - L_lod50_2 - S_lod50_2), type = "F")/norm((mix), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP w/ LOD/2")
```

```{r}
F_norm_nnS <- as_tibble(cbind(`0%` = norm((mix - L_lod0_nnS - S_lod0_nnS), type = "F")/norm((mix), type = "F"),
      `10%` = norm((mix - L_lod10_nnS - S_lod10_nnS), type = "F")/norm((mix), type = "F"),
      `20%` = norm((mix - L_lod20_nnS - S_lod20_nnS), type = "F")/norm((mix), type = "F"),
      `30%` = norm((mix - L_lod30_nnS - S_lod30_nnS), type = "F")/norm((mix), type = "F"),
      `40%` = norm((mix - L_lod40_nnS - S_lod40_nnS), type = "F")/norm((mix), type = "F"),
      `50%` = norm((mix - L_lod50_nnS - S_lod50_nnS), type = "F")/norm((mix), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "LOD PCP nnS")
```

### Viz

```{r, fig.height = 5, fig.width = 4, fig.align = "center"}
rbind(F_norm_2, F_norm_sqrt2, F_norm_0, F_norm, F_norm_nnS) %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point(aes(color = Method)) + geom_path(aes(group = Method, color = Method)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(X-L-S) / norm(X)",
       title = "Relative Prediction Error")
```

## Individual Solution Matrices

```{r}
L_diff <- as_tibble(cbind(`0%` = norm((L_lod0 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      `10%` = norm((L_lod10 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      `20%` = norm((L_lod20 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      `30%` = norm((L_lod30 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      `40%` = norm((L_lod40 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      `50%` = norm((L_lod50 - L_lod0), type = "F")/norm((L_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank",
         Method = "LOD PCP")

S_diff <- as_tibble(cbind(`0%` = norm((S_lod0 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      `10%` = norm((S_lod10 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      `20%` = norm((S_lod20 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      `30%` = norm((S_lod30 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      `40%` = norm((S_lod40 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      `50%` = norm((S_lod50 - S_lod0), type = "F")/norm((S_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse",
         Method = "LOD PCP")

nn_L_diff <- as_tibble(cbind(`0%` = norm((nn_L_lod0 - nn_L_lod0), type = "F")/norm((nn_L_lod0), type = "F"),
      `10%` = norm((nn_L_lod10 - nn_L_lod0), type = "F")/norm((nn_L_lod0), type = "F"),
      `20%` = norm((nn_L_lod20 - nn_L_lod0), type = "F")/norm((nn_L_lod0), type = "F"),
      `30%` = norm((nn_L_lod30 - nn_L_lod0), type = "F")/norm((nn_L_lod0), type = "F"),
      `40%` = norm((nn_L_lod40 - nn_L_lod0), type = "F")/norm((nn_L_lod0), type = "F"),
      `50%` = norm((nn_L_lod50 - nn_L_lod0), type = "F")/norm((nn_L_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank")

nn_S_diff <- as_tibble(cbind(`0%` = norm((nn_S_lod0 - nn_S_lod0), type = "F")/norm((nn_S_lod0), type = "F"),
      `10%` = norm((nn_S_lod10 - nn_S_lod0), type = "F")/norm((nn_S_lod0), type = "F"),
      `20%` = norm((nn_S_lod20 - nn_S_lod0), type = "F")/norm((nn_S_lod0), type = "F"),
      `30%` = norm((nn_S_lod30 - nn_S_lod0), type = "F")/norm((nn_S_lod0), type = "F"),
      `40%` = norm((nn_S_lod40 - nn_S_lod0), type = "F")/norm((nn_S_lod0), type = "F"),
      `50%` = norm((nn_S_lod50 - nn_S_lod0), type = "F")/norm((nn_S_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse")

L_diff_0 <- as_tibble(cbind(`0%` = norm((L_lod0_0 - L_lod0_0), type = "F")/norm((L_lod0_0), type = "F"),
      `10%` = norm((L_lod10_0 - L_lod0_0), type = "F")/norm((L_lod0_0), type = "F"),
      `20%` = norm((L_lod20_0 - L_lod0_0), type = "F")/norm((L_lod0_0), type = "F"),
      `30%` = norm((L_lod30_0 - L_lod0_0), type = "F")/norm((L_lod0_0), type = "F"),
      `40%` = norm((L_lod40_0 - L_lod0_0), type = "F")/norm((L_lod0_0), type = "F"),
      `50%` = norm((L_lod50_0 - L_lod0_0), type = "F")/norm((L_lod0_0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank",
         Method = "PCP w/ 0")

S_diff_0 <- as_tibble(cbind(`0%` = norm((S_lod0_0 - S_lod0_0), type = "F")/norm((S_lod0_0), type = "F"),
      `10%` = norm((S_lod10_0 - S_lod0_0), type = "F")/norm((S_lod0_0), type = "F"),
      `20%` = norm((S_lod20_0 - S_lod0_0), type = "F")/norm((S_lod0_0), type = "F"),
      `30%` = norm((S_lod30_0 - S_lod0_0), type = "F")/norm((S_lod0_0), type = "F"),
      `40%` = norm((S_lod40_0 - S_lod0_0), type = "F")/norm((S_lod0_0), type = "F"),
      `50%` = norm((S_lod50_0 - S_lod0_0), type = "F")/norm((S_lod0_0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse",
         Method = "PCP w/ 0")

L_diff_sqrt2 <- as_tibble(cbind(`0%` = norm((L_lod0_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"),
      `10%` = norm((L_lod10_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"),
      `20%` = norm((L_lod20_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"),
      `30%` = norm((L_lod30_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"),
      `40%` = norm((L_lod40_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"),
      `50%` = norm((L_lod50_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank",
         Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))

S_diff_sqrt2 <- as_tibble(cbind(`0%` = norm((S_lod0_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"),
      `10%` = norm((S_lod10_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"),
      `20%` = norm((S_lod20_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"),
      `30%` = norm((S_lod30_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"),
      `40%` = norm((S_lod40_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"),
      `50%` = norm((S_lod50_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse",
         Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))

L_diff_2 <- as_tibble(cbind(`0%` = norm((L_lod0_2 - L_lod0_2), type = "F")/norm((L_lod0_2), type = "F"),
                                `10%` = norm((L_lod10_2 - L_lod0_2), type = "F")/norm((L_lod0_2), type = "F"),
                                `20%` = norm((L_lod20_2 - L_lod0_2), type = "F")/norm((L_lod0_2), type = "F"),
                                `30%` = norm((L_lod30_2 - L_lod0_2), type = "F")/norm((L_lod0_2), type = "F"),
                                `40%` = norm((L_lod40_2 - L_lod0_2), type = "F")/norm((L_lod0_2), type = "F"),
                                `50%` = norm((L_lod50_2 - L_lod0_2), type = "F")/norm((L_lod0_2), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank",
         Method = "PCP w/ LOD/2")

S_diff_2 <- as_tibble(cbind(`0%` = norm((S_lod0_2 - S_lod0_2), type = "F")/norm((S_lod0_2), type = "F"),
                                `10%` = norm((S_lod10_2 - S_lod0_2), type = "F")/norm((S_lod0_2), type = "F"),
                                `20%` = norm((S_lod20_2 - S_lod0_2), type = "F")/norm((S_lod0_2), type = "F"),
                                `30%` = norm((S_lod30_2 - S_lod0_2), type = "F")/norm((S_lod0_2), type = "F"),
                                `40%` = norm((S_lod40_2 - S_lod0_2), type = "F")/norm((S_lod0_2), type = "F"),
                                `50%` = norm((S_lod50_2 - S_lod0_2), type = "F")/norm((S_lod0_2), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse",
         Method = "PCP w/ LOD/2")
```

```{r}
L_diff_nnS <- as_tibble(cbind(`0%` = norm((L_lod0_nnS - L_lod0_nnS), type = "F")/norm((L_lod0_nnS), type = "F"),
      `10%` = norm((L_lod10_nnS - L_lod0_nnS), type = "F")/norm((L_lod0_nnS), type = "F"),
      `20%` = norm((L_lod20_nnS - L_lod0_nnS), type = "F")/norm((L_lod0_nnS), type = "F"),
      `30%` = norm((L_lod30_nnS - L_lod0_nnS), type = "F")/norm((L_lod0_nnS), type = "F"),
      `40%` = norm((L_lod40_nnS - L_lod0_nnS), type = "F")/norm((L_lod0_nnS), type = "F"),
      `50%` = norm((L_lod50_nnS - L_lod0_nnS), type = "F")/norm((L_lod0_nnS), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank",
         Method = "LOD PCP nnS")

S_diff_nnS <- as_tibble(cbind(`0%` = norm((S_lod0_nnS - S_lod0_nnS), type = "F")/norm((S_lod0_nnS), type = "F"),
      `10%` = norm((S_lod10_nnS - S_lod0_nnS), type = "F")/norm((S_lod0_nnS), type = "F"),
      `20%` = norm((S_lod20_nnS - S_lod0_nnS), type = "F")/norm((S_lod0_nnS), type = "F"),
      `30%` = norm((S_lod30_nnS - S_lod0_nnS), type = "F")/norm((S_lod0_nnS), type = "F"),
      `40%` = norm((S_lod40_nnS - S_lod0_nnS), type = "F")/norm((S_lod0_nnS), type = "F"),
      `50%` = norm((S_lod50_nnS - S_lod0_nnS), type = "F")/norm((S_lod0_nnS), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse",
         Method = "LOD PCP nnS")
```

### Viz

```{r, fig.height = 5, fig.width = 4, fig.align = "center"}
rbind(L_diff_2, S_diff_2,
      L_diff_sqrt2, S_diff_sqrt2,
      L_diff, S_diff,
      L_diff_0, S_diff_0,
      L_diff_nnS, S_diff_nnS) %>% ggplot(aes(x = percent_blod, y = norm, group = interaction(Matrix,Method), color = Method)) + 
  geom_point() + geom_path(aes(linetype = Matrix)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(difference) / norm(lod0))",
       title = "Relative Error in \nSolution Matrices")
```

## Values \<LOD vs \>LOD

```{r}
# BELOW LOD
# TRUE = <LOD
tf_lod_0 <- sim_all %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_0 <- as.matrix(tf_lod_0*L_lod0)
s_blod_0 <- as.matrix(tf_lod_0*S_lod0)
blod_0 <- as.matrix(sim_all*tf_lod_0)

tf_lod_10 <- mix_data_lod_10 %>% 
  as_tibble() %>%
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_10 <- as.matrix(tf_lod_10*L_lod10)
s_blod_10 <- as.matrix(tf_lod_10*S_lod10)
blod_10 <- as.matrix(sim_all*tf_lod_10)

tf_lod_20 <- mix_data_lod_20 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_20 <- as.matrix(tf_lod_20*L_lod20)
s_blod_20 <- as.matrix(tf_lod_20*S_lod20)
blod_20 <- as.matrix(sim_all*tf_lod_20)

tf_lod_30 <- mix_data_lod_30 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_30 <- as.matrix(tf_lod_30*L_lod30)
s_blod_30 <- as.matrix(tf_lod_30*S_lod30)
blod_30 <- as.matrix(sim_all*tf_lod_30)

tf_lod_40 <- mix_data_lod_40 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_40 <- as.matrix(tf_lod_40*L_lod40)
s_blod_40 <- as.matrix(tf_lod_40*S_lod40)
blod_40 <- as.matrix(sim_all*tf_lod_40)

tf_lod_50 <- mix_data_lod_50 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_50 <- as.matrix(tf_lod_50*L_lod50)
s_blod_50 <- as.matrix(tf_lod_50*S_lod50)
blod_50 <- as.matrix(sim_all*tf_lod_50) 

#Subtract true values and divide by norm of true
less_diff <- as_tibble(cbind(`0%` = norm((blod_0 - l_blod_0 - s_blod_0), type = "F"), #/norm((mix), type = "F"),
      `10%` = norm((blod_10 - l_blod_10 - s_blod_10), type = "F")/norm((blod_10), type = "F"),
      `20%` = norm((blod_20 - l_blod_20 - s_blod_20), type = "F")/norm((blod_20), type = "F"),
      `30%` = norm((blod_30 - l_blod_30 - s_blod_30), type = "F")/norm((blod_30), type = "F"),
      `40%` = norm((blod_40 - l_blod_40 - s_blod_40), type = "F")/norm((blod_40), type = "F"),
      `50%` = norm((blod_50 - l_blod_50 - s_blod_50), type = "F")/norm((blod_50), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "< LOD",
         Method = "LOD PCP")

l_above_blod_0 <- as.matrix((!tf_lod_0)*L_lod0)
s_above_blod_0 <- as.matrix((!tf_lod_0)*S_lod0)

l_above_blod_10 <- as.matrix((!tf_lod_10)*L_lod10)
s_above_blod_10 <- as.matrix((!tf_lod_10)*S_lod10)

l_above_blod_20 <- as.matrix((!tf_lod_20)*L_lod20)
s_above_blod_20 <- as.matrix((!tf_lod_20)*S_lod20)

l_above_blod_30 <- as.matrix((!tf_lod_30)*L_lod30)
s_above_blod_30 <- as.matrix((!tf_lod_30)*S_lod30)

l_above_blod_40 <- as.matrix((!tf_lod_40)*L_lod40)
s_above_blod_40 <- as.matrix((!tf_lod_40)*S_lod40)

l_above_blod_50 <- as.matrix((!tf_lod_50)*L_lod50)
s_above_blod_50 <- as.matrix((!tf_lod_50)*S_lod50)

#divide by true values
# mix_data_lod_##_0 datasets replaced <LOD with zero, so use them as reference for >LOD
above_diff <- as_tibble(cbind(
  `0%`  = norm((mix  - l_above_blod_0  - s_above_blod_0),  type = "F")/norm(mix,  type = "F"),
  `10%` = norm((mix_data_lod_10_0 - l_above_blod_10 - s_above_blod_10), type = "F")/norm(mix_data_lod_10_0, type = "F"),
  `20%` = norm((mix_data_lod_20_0 - l_above_blod_20 - s_above_blod_20), type = "F")/norm(mix_data_lod_20_0, type = "F"),
  `30%` = norm((mix_data_lod_30_0 - l_above_blod_30 - s_above_blod_30), type = "F")/norm(mix_data_lod_30_0, type = "F"),
  `40%` = norm((mix_data_lod_40_0 - l_above_blod_40 - s_above_blod_40), type = "F")/norm(mix_data_lod_40_0, type = "F"),
  `50%` = norm((mix_data_lod_50_0 - l_above_blod_50 - s_above_blod_50), type = "F")/norm(mix_data_lod_50_0, type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "> LOD",
         Method = "LOD PCP")

l_blod_0_0 <- as.matrix(tf_lod_0*L_lod0_0)
s_blod_0_0 <- as.matrix(tf_lod_0*S_lod0_0)

l_blod_10_0 <- as.matrix(tf_lod_10*L_lod10_0)
s_blod_10_0 <- as.matrix(tf_lod_10*S_lod10_0)

l_blod_20_0 <- as.matrix(tf_lod_20*L_lod20_0)
s_blod_20_0 <- as.matrix(tf_lod_20*S_lod20_0)

l_blod_30_0 <- as.matrix(tf_lod_30*L_lod30_0)
s_blod_30_0 <- as.matrix(tf_lod_30*S_lod30_0)

l_blod_40_0 <- as.matrix(tf_lod_40*L_lod40_0)
s_blod_40_0 <- as.matrix(tf_lod_40*S_lod40_0)

l_blod_50_0 <- as.matrix(tf_lod_50*L_lod50_0)
s_blod_50_0 <- as.matrix(tf_lod_50*S_lod50_0)

#Subtract true values and divide by norm of true
less_diff_0 <- as_tibble(cbind(
      `0%` = norm((blod_0 - l_blod_0_0 - s_blod_0_0), type = "F"), #/norm((blod_0), type = "F"),
      `10%` = norm((blod_10 - l_blod_10_0 - s_blod_10_0), type = "F")/norm((blod_10), type = "F"),
      `20%` = norm((blod_20 - l_blod_20_0 - s_blod_20_0), type = "F")/norm((blod_20), type = "F"),
      `30%` = norm((blod_30 - l_blod_30_0 - s_blod_30_0), type = "F")/norm((blod_30), type = "F"),
      `40%` = norm((blod_40 - l_blod_40_0 - s_blod_40_0), type = "F")/norm((blod_40), type = "F"),
      `50%` = norm((blod_50 - l_blod_50_0 - s_blod_50_0), type = "F")/norm((blod_50), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "< LOD",
         Method = "PCP w/ 0")

l_above_blod_0_0 <- as.matrix((!tf_lod_0)*L_lod0_0)
s_above_blod_0_0 <- as.matrix((!tf_lod_0)*S_lod0_0)

l_above_blod_10_0 <- as.matrix((!tf_lod_10)*L_lod10_0)
s_above_blod_10_0 <- as.matrix((!tf_lod_10)*S_lod10_0)

l_above_blod_20_0 <- as.matrix((!tf_lod_20)*L_lod20_0)
s_above_blod_20_0 <- as.matrix((!tf_lod_20)*S_lod20_0)

l_above_blod_30_0 <- as.matrix((!tf_lod_30)*L_lod30_0)
s_above_blod_30_0 <- as.matrix((!tf_lod_30)*S_lod30_0)

l_above_blod_40_0 <- as.matrix((!tf_lod_40)*L_lod40_0)
s_above_blod_40_0 <- as.matrix((!tf_lod_40)*S_lod40_0)

l_above_blod_50_0 <- as.matrix((!tf_lod_50)*L_lod50_0)
s_above_blod_50_0 <- as.matrix((!tf_lod_50)*S_lod50_0)

#divide by true values
above_diff_0 <- as_tibble(cbind(
  `0%`  = norm((mix  - l_above_blod_0_0  - s_above_blod_0_0),  type = "F")/norm(mix,  type = "F"),
  `10%` = norm((mix_data_lod_10_0 - l_above_blod_10_0 - s_above_blod_10_0), type = "F")/norm(mix_data_lod_10_0, type = "F"),
  `20%` = norm((mix_data_lod_20_0 - l_above_blod_20_0 - s_above_blod_20_0), type = "F")/norm(mix_data_lod_20_0, type = "F"),
  `30%` = norm((mix_data_lod_30_0 - l_above_blod_30_0 - s_above_blod_30_0), type = "F")/norm(mix_data_lod_30_0, type = "F"),
  `40%` = norm((mix_data_lod_40_0 - l_above_blod_40_0 - s_above_blod_40_0), type = "F")/norm(mix_data_lod_40_0, type = "F"),
  `50%` = norm((mix_data_lod_50_0 - l_above_blod_50_0 - s_above_blod_50_0), type = "F")/norm(mix_data_lod_50_0, type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "> LOD",
         Method = "PCP w/ 0")

L_blod_0_sqrt2 <- as.matrix(tf_lod_0*L_lod0_sqrt2)
S_blod_0_sqrt2 <- as.matrix(tf_lod_0*S_lod0_sqrt2)

L_blod_10_sqrt2 <- as.matrix(tf_lod_10*L_lod10_sqrt2)
S_blod_10_sqrt2 <- as.matrix(tf_lod_10*S_lod10_sqrt2)

L_blod_20_sqrt2 <- as.matrix(tf_lod_20*L_lod20_sqrt2)
S_blod_20_sqrt2 <- as.matrix(tf_lod_20*S_lod20_sqrt2)

L_blod_30_sqrt2 <- as.matrix(tf_lod_30*L_lod30_sqrt2)
S_blod_30_sqrt2 <- as.matrix(tf_lod_30*S_lod30_sqrt2)

L_blod_40_sqrt2 <- as.matrix(tf_lod_40*L_lod40_sqrt2)
S_blod_40_sqrt2 <- as.matrix(tf_lod_40*S_lod40_sqrt2)

L_blod_50_sqrt2 <- as.matrix(tf_lod_50*L_lod50_sqrt2)
S_blod_50_sqrt2 <- as.matrix(tf_lod_50*S_lod50_sqrt2)

less_diff_sqrt2 <- as_tibble(
  cbind(`0%`  = norm((blod_0  - L_blod_0_sqrt2  - S_blod_0_sqrt2),  type = "F"), #/norm((blod_0), type = "F"),
        `10%` = norm((blod_10 - L_blod_10_sqrt2 - S_blod_10_sqrt2), type = "F")/norm((blod_10), type = "F"),
        `20%` = norm((blod_20 - L_blod_20_sqrt2 - S_blod_20_sqrt2), type = "F")/norm((blod_20), type = "F"),
        `30%` = norm((blod_30 - L_blod_30_sqrt2 - S_blod_30_sqrt2), type = "F")/norm((blod_30), type = "F"),
        `40%` = norm((blod_40 - L_blod_40_sqrt2 - S_blod_40_sqrt2), type = "F")/norm((blod_40), type = "F"),
        `50%` = norm((blod_50 - L_blod_50_sqrt2 - S_blod_50_sqrt2), type = "F")/norm((blod_50), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "< LOD",
         Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))

L_above_blod_0_sqrt2 <- as.matrix((!tf_lod_0)*L_lod0_sqrt2)
S_above_blod_0_sqrt2 <- as.matrix((!tf_lod_0)*S_lod0_sqrt2)

L_above_blod_10_sqrt2 <- as.matrix((!tf_lod_10)*L_lod10_sqrt2)
S_above_blod_10_sqrt2 <- as.matrix((!tf_lod_10)*S_lod10_sqrt2)

L_above_blod_20_sqrt2 <- as.matrix((!tf_lod_20)*L_lod20_sqrt2)
S_above_blod_20_sqrt2 <- as.matrix((!tf_lod_20)*S_lod20_sqrt2)

L_above_blod_30_sqrt2 <- as.matrix((!tf_lod_30)*L_lod30_sqrt2)
S_above_blod_30_sqrt2 <- as.matrix((!tf_lod_30)*S_lod30_sqrt2)

L_above_blod_40_sqrt2 <- as.matrix((!tf_lod_40)*L_lod40_sqrt2)
S_above_blod_40_sqrt2 <- as.matrix((!tf_lod_40)*S_lod40_sqrt2)

L_above_blod_50_sqrt2 <- as.matrix((!tf_lod_50)*L_lod50_sqrt2)
S_above_blod_50_sqrt2 <- as.matrix((!tf_lod_50)*S_lod50_sqrt2)

#divide by true values
above_diff_sqrt2 <- as_tibble(cbind(
  `0%`  = norm((mix  - L_above_blod_0_sqrt2  - S_above_blod_0_sqrt2),  type = "F")/norm(mix,  type = "F"),
  `10%` = norm((mix_data_lod_10_0 - L_above_blod_10_sqrt2 - S_above_blod_10_sqrt2), type = "F")/norm(mix_data_lod_10_0, type = "F"),
  `20%` = norm((mix_data_lod_20_0 - L_above_blod_20_sqrt2 - S_above_blod_20_sqrt2), type = "F")/norm(mix_data_lod_20_0, type = "F"),
  `30%` = norm((mix_data_lod_30_0 - L_above_blod_30_sqrt2 - S_above_blod_30_sqrt2), type = "F")/norm(mix_data_lod_30_0, type = "F"),
  `40%` = norm((mix_data_lod_40_0 - L_above_blod_40_sqrt2 - S_above_blod_40_sqrt2), type = "F")/norm(mix_data_lod_40_0, type = "F"),
  `50%` = norm((mix_data_lod_50_0 - L_above_blod_50_sqrt2 - S_above_blod_50_sqrt2), type = "F")/norm(mix_data_lod_50_0, type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "> LOD",
         Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))
```

```{r, ls2}
L_blod_0_2 <- as.matrix(tf_lod_0*L_lod0_2)
S_blod_0_2 <- as.matrix(tf_lod_0*S_lod0_2)

L_blod_10_2 <- as.matrix(tf_lod_10*L_lod10_2)
S_blod_10_2 <- as.matrix(tf_lod_10*S_lod10_2)

L_blod_20_2 <- as.matrix(tf_lod_20*L_lod20_2)
S_blod_20_2 <- as.matrix(tf_lod_20*S_lod20_2)

L_blod_30_2 <- as.matrix(tf_lod_30*L_lod30_2)
S_blod_30_2 <- as.matrix(tf_lod_30*S_lod30_2)

L_blod_40_2 <- as.matrix(tf_lod_40*L_lod40_2)
S_blod_40_2 <- as.matrix(tf_lod_40*S_lod40_2)

L_blod_50_2 <- as.matrix(tf_lod_50*L_lod50_2)
S_blod_50_2 <- as.matrix(tf_lod_50*S_lod50_2)

less_diff_2 <- as_tibble(
  cbind(`0%`  = norm((blod_0  - L_blod_0_2  - S_blod_0_2),  type = "F"), #/norm((blod_0), type = "F"),
        `10%` = norm((blod_10 - L_blod_10_2 - S_blod_10_2), type = "F")/norm((blod_10), type = "F"),
        `20%` = norm((blod_20 - L_blod_20_2 - S_blod_20_2), type = "F")/norm((blod_20), type = "F"),
        `30%` = norm((blod_30 - L_blod_30_2 - S_blod_30_2), type = "F")/norm((blod_30), type = "F"),
        `40%` = norm((blod_40 - L_blod_40_2 - S_blod_40_2), type = "F")/norm((blod_40), type = "F"),
        `50%` = norm((blod_50 - L_blod_50_2 - S_blod_50_2), type = "F")/norm((blod_50), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "< LOD",
         Method = "PCP w/ LOD/2")

L_above_blod_0_2 <- as.matrix((!tf_lod_0)*L_lod0_2)
S_above_blod_0_2 <- as.matrix((!tf_lod_0)*S_lod0_2)

L_above_blod_10_2 <- as.matrix((!tf_lod_10)*L_lod10_2)
S_above_blod_10_2 <- as.matrix((!tf_lod_10)*S_lod10_2)

L_above_blod_20_2 <- as.matrix((!tf_lod_20)*L_lod20_2)
S_above_blod_20_2 <- as.matrix((!tf_lod_20)*S_lod20_2)

L_above_blod_30_2 <- as.matrix((!tf_lod_30)*L_lod30_2)
S_above_blod_30_2 <- as.matrix((!tf_lod_30)*S_lod30_2)

L_above_blod_40_2 <- as.matrix((!tf_lod_40)*L_lod40_2)
S_above_blod_40_2 <- as.matrix((!tf_lod_40)*S_lod40_2)

L_above_blod_50_2 <- as.matrix((!tf_lod_50)*L_lod50_2)
S_above_blod_50_2 <- as.matrix((!tf_lod_50)*S_lod50_2)

#divide by true values
above_diff_2 <- as_tibble(cbind(
  `0%`  = norm((mix  - L_above_blod_0_2  - S_above_blod_0_2),  type = "F")/norm(mix,  type = "F"),
  `10%` = norm((mix_data_lod_10_0 - L_above_blod_10_2 - S_above_blod_10_2), type = "F")/norm(mix_data_lod_10_0, type = "F"),
  `20%` = norm((mix_data_lod_20_0 - L_above_blod_20_2 - S_above_blod_20_2), type = "F")/norm(mix_data_lod_20_0, type = "F"),
  `30%` = norm((mix_data_lod_30_0 - L_above_blod_30_2 - S_above_blod_30_2), type = "F")/norm(mix_data_lod_30_0, type = "F"),
  `40%` = norm((mix_data_lod_40_0 - L_above_blod_40_2 - S_above_blod_40_2), type = "F")/norm(mix_data_lod_40_0, type = "F"),
  `50%` = norm((mix_data_lod_50_0 - L_above_blod_50_2 - S_above_blod_50_2), type = "F")/norm(mix_data_lod_50_0, type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "> LOD",
         Method = "PCP w/ LOD/2")
```


```{r}
l_above_blod_0_nnS <- as.matrix((!tf_lod_0)*L_lod0_nnS)
s_above_blod_0_nnS <- as.matrix((!tf_lod_0)*S_lod0_nnS)

l_above_blod_10_nnS <- as.matrix((!tf_lod_10)*L_lod10_nnS)
s_above_blod_10_nnS <- as.matrix((!tf_lod_10)*S_lod10_nnS)

l_above_blod_20_nnS <- as.matrix((!tf_lod_20)*L_lod20_nnS)
s_above_blod_20_nnS <- as.matrix((!tf_lod_20)*S_lod20_nnS)

l_above_blod_30_nnS <- as.matrix((!tf_lod_30)*L_lod30_nnS)
s_above_blod_30_nnS <- as.matrix((!tf_lod_30)*S_lod30_nnS)

l_above_blod_40_nnS <- as.matrix((!tf_lod_40)*L_lod40)
s_above_blod_40_nnS <- as.matrix((!tf_lod_40)*S_lod40)

l_above_blod_50_nnS <- as.matrix((!tf_lod_50)*L_lod50_nnS)
s_above_blod_50_nnS <- as.matrix((!tf_lod_50)*S_lod50_nnS)

#divide by true values
above_diff_nnS <- as_tibble(cbind(
  `0%`  = norm((mix  - l_above_blod_0_nnS  - s_above_blod_0_nnS),  type = "F")/
    norm(mix,  type = "F"),
  `10%` = norm((mix_data_lod_10_0 - l_above_blod_10_nnS - s_above_blod_10_nnS), type = "F")/
    norm(mix_data_lod_10_0, type = "F"),
  `20%` = norm((mix_data_lod_20_0 - l_above_blod_20_nnS - s_above_blod_20_nnS), type = "F")/
    norm(mix_data_lod_20_0, type = "F"),
  `30%` = norm((mix_data_lod_30_0 - l_above_blod_30_nnS - s_above_blod_30_nnS), type = "F")/
    norm(mix_data_lod_30_0, type = "F"),
  `40%` = norm((mix_data_lod_40_0 - l_above_blod_40_nnS - s_above_blod_40_nnS), type = "F")/
    norm(mix_data_lod_40_0, type = "F"),
  `50%` = norm((mix_data_lod_50_0 - l_above_blod_50_nnS - s_above_blod_50_nnS), type = "F")/
    norm(mix_data_lod_50_0, type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "> LOD",
         Method = "LOD PCP nnS")

l_blod_0_nnS <- as.matrix(tf_lod_0*L_lod0_nnS)
s_blod_0_nnS <- as.matrix(tf_lod_0*S_lod0_nnS)

l_blod_10_nnS <- as.matrix(tf_lod_10*L_lod10_nnS)
s_blod_10_nnS <- as.matrix(tf_lod_10*S_lod10_nnS)

l_blod_20_nnS <- as.matrix(tf_lod_20*L_lod20_nnS)
s_blod_20_nnS <- as.matrix(tf_lod_20*S_lod20_nnS)

l_blod_30_nnS <- as.matrix(tf_lod_30*L_lod30_nnS)
s_blod_30_nnS <- as.matrix(tf_lod_30*S_lod30_nnS)

l_blod_40_nnS <- as.matrix(tf_lod_40*L_lod40_nnS)
s_blod_40_nnS <- as.matrix(tf_lod_40*S_lod40_nnS)

l_blod_50_nnS <- as.matrix(tf_lod_50*L_lod50_nnS)
s_blod_50_nnS <- as.matrix(tf_lod_50*S_lod50_nnS)

#Subtract true values and divide by norm of true
less_diff_nnS <- as_tibble(cbind(`0%` = norm((blod_0 - l_blod_0_nnS - s_blod_0_nnS), type = "F"), #/norm((mix), type = "F"),
      `10%` = norm((blod_10 - l_blod_10_nnS - s_blod_10_nnS), type = "F")/
        norm((blod_10), type = "F"),
      `20%` = norm((blod_20 - l_blod_20_nnS - s_blod_20_nnS), type = "F")/
        norm((blod_20), type = "F"),
      `30%` = norm((blod_30 - l_blod_30_nnS - s_blod_30_nnS), type = "F")/
        norm((blod_30), type = "F"),
      `40%` = norm((blod_40 - l_blod_40_nnS - s_blod_40_nnS), type = "F")/
        norm((blod_40), type = "F"),
      `50%` = norm((blod_50 - l_blod_50_nnS - s_blod_50_nnS), type = "F")/
        norm((blod_50), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "< LOD",
         Method = "LOD PCP nnS")
```

### Viz

```{r, fig.height = 5, fig.width = 4, fig.align = "center"}
rbind(above_diff, 
      less_diff,
      above_diff_0, 
      less_diff_0,
      above_diff_sqrt2, 
      less_diff_sqrt2,
      above_diff_2,
      less_diff_2,
      above_diff_nnS,
      less_diff_nnS) %>% 
  mutate(norm = ifelse(Values == "> LOD" & Method == "LOD PCP", norm + 0.005, norm),
         norm = ifelse(Values == "> LOD" & Method == "PCP w/ 0", norm - 0.005, norm)) %>% 
  ggplot(aes(x = percent_blod, y = norm, group = interaction(Values, Method), color = Method)) + 
  geom_point(aes()) + geom_path(aes(linetype = Values)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "(norm(X-L-S) / norm(X)",
       title = "Relative Error in \nValues < LOD & > LOD")
```

## SVD

```{r}
svd(L_lod0)$d

svd(L_lod50)$d
```

### Right singular vectors

```{r}
# Extract right singular vectors from each low rank solution matrix
V_lod0  <-  svd(L_lod0)$v[,1:7]
V_lod10 <- svd(L_lod10)$v[,1:7]
V_lod20 <- svd(L_lod20)$v[,1:7]
V_lod30 <- svd(L_lod30)$v[,1:7]
V_lod40 <- svd(L_lod40)$v[,1:7]
V_lod50 <- svd(L_lod50)$v[,1:7]

# Hack to flip singular vectos -- Use correlation
# cor(V_lod0, V_lod10)
# cor(V_lod0, V_lod20)
# cor(V_lod0, V_lod30)
# cor(V_lod0, V_lod40)
# cor(V_lod0, V_lod50)

# Hack -- Flip
V_lod10[,3] <- -V_lod10[,3]
V_lod10[,5:7] <- -V_lod10[,5:7]
V_lod20[,3] <- -V_lod20[,3]
V_lod20[,5:7] <- -V_lod20[,5:7]
V_lod30[,3:6] <- -V_lod30[,3:6]
V_lod40[,3:4] <- -V_lod40[,3:4]
V_lod40[,7] <- -V_lod40[,7]
V_lod50[,3:7] <- -V_lod50[,3:7]

V_diff <- as_tibble(cbind(`0%` =norm((V_lod0 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      `10%` =norm((V_lod10 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      `20%` =norm((V_lod20 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      `30%` =norm((V_lod30 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      `40%` =norm((V_lod40 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      `50%` =norm((V_lod50 - V_lod0), type = "F")/norm((V_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "LOD PCP")

#V_diff

# Extract right singular vectors from each low rank solution matrix
nn_V_lod0  <-  svd(nn_L_lod0)$v[,1:7]
nn_V_lod10 <- svd(nn_L_lod10)$v[,1:7]
nn_V_lod20 <- svd(nn_L_lod20)$v[,1:7]
nn_V_lod30 <- svd(nn_L_lod30)$v[,1:7]
nn_V_lod40 <- svd(nn_L_lod40)$v[,1:7]
nn_V_lod50 <- svd(nn_L_lod50)$v[,1:7]

# cor(nn_V_lod0, nn_V_lod10)
# cor(nn_V_lod0, nn_V_lod20)
# cor(nn_V_lod0, nn_V_lod30)
# cor(nn_V_lod0, nn_V_lod40)
# cor(nn_V_lod0, nn_V_lod50)

# Hack -- Flip
nn_V_lod10[,3] <- -nn_V_lod10[,3]
nn_V_lod10[,5] <- -nn_V_lod10[,5]
nn_V_lod20[,3] <- -nn_V_lod20[,3]
nn_V_lod20[,5] <- -nn_V_lod20[,5]
nn_V_lod30[,3] <- -nn_V_lod30[,3]
nn_V_lod30[,4] <- -nn_V_lod30[,4]
nn_V_lod30[,5] <- -nn_V_lod30[,5]
nn_V_lod40[,4] <- -nn_V_lod40[,4]
nn_V_lod40[,3] <- -nn_V_lod40[,3]
nn_V_lod50[,3] <- -nn_V_lod50[,3]
nn_V_lod50[,4] <- -nn_V_lod50[,4]
nn_V_lod50[,5] <- -nn_V_lod50[,5]

nn_V_diff <- as_tibble(cbind(`0%` =norm((nn_V_lod0 - nn_V_lod0), type = "F")/norm((nn_V_lod0), type = "F"),
      `10%` =norm((nn_V_lod10 - nn_V_lod0), type = "F")/norm((nn_V_lod0), type = "F"),
      `20%` =norm((nn_V_lod20 - nn_V_lod0), type = "F")/norm((nn_V_lod0), type = "F"),
      `30%` =norm((nn_V_lod30 - nn_V_lod0), type = "F")/norm((nn_V_lod0), type = "F"),
      `40%` =norm((nn_V_lod40 - nn_V_lod0), type = "F")/norm((nn_V_lod0), type = "F"),
      `50%` =norm((nn_V_lod50 - nn_V_lod0), type = "F")/norm((nn_V_lod0), type = "F"))) %>% 
  gather(percent_blod, norm)

#nn_V_diff

# Extract right singular vectors from each low rank solution matrix
V_lod0_0  <-  svd(L_lod0_0)$v[,1:7]
V_lod10_0 <- svd(L_lod10_0)$v[,1:7]
V_lod20_0 <- svd(L_lod20_0)$v[,1:7]
V_lod30_0 <- svd(L_lod30_0)$v[,1:7]
V_lod40_0 <- svd(L_lod40_0)$v[,1:7]
V_lod50_0 <- svd(L_lod50_0)$v[,1:7]

# cor(V_lod0_0, V_lod10_0)
# cor(V_lod0_0, V_lod20_0)
# cor(V_lod0_0, V_lod30_0)
# cor(V_lod0_0, V_lod40_0)
# cor(V_lod0_0, V_lod50_0)

# Hack -- Flip
V_lod10_0[,3:7] <- -V_lod10_0[,3:7]
V_lod20_0[,3:4] <- -V_lod20_0[,3:4]
V_lod20_0[,7] <- -V_lod20_0[,7]
V_lod30_0[,3] <- -V_lod30_0[,3]
V_lod30_0[,5] <- -V_lod30_0[,5]
V_lod30_0[,7] <- -V_lod30_0[,7]
V_lod40_0[,3] <- -V_lod40_0[,3]
V_lod50_0[,3:4] <- -V_lod50_0[,3:4]
V_lod50_0[,7] <- -V_lod50_0[,7]

V_diff_0 <- as_tibble(cbind(`0%` =norm((V_lod0_0 - V_lod0_0), type = "F")/norm((V_lod0_0), type = "F"),
      `10%` =norm((V_lod10_0 - V_lod0_0), type = "F")/norm((V_lod0_0), type = "F"),
      `20%` =norm((V_lod20_0 - V_lod0_0), type = "F")/norm((V_lod0_0), type = "F"),
      `30%` =norm((V_lod30_0 - V_lod0_0), type = "F")/norm((V_lod0_0), type = "F"),
      `40%` =norm((V_lod40_0 - V_lod0_0), type = "F")/norm((V_lod0_0), type = "F"),
      `50%` =norm((V_lod50_0 - V_lod0_0), type = "F")/norm((V_lod0_0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP w/ 0")

#V_diff_0

# Extract right singular vectors from each low rank solution matrix
V_lod0_sqrt2  <-  svd(L_lod0_sqrt2)$v[,1:7]
V_lod10_sqrt2 <- svd(L_lod10_sqrt2)$v[,1:7]
V_lod20_sqrt2 <- svd(L_lod20_sqrt2)$v[,1:7]
V_lod30_sqrt2 <- svd(L_lod30_sqrt2)$v[,1:7]
V_lod40_sqrt2 <- svd(L_lod40_sqrt2)$v[,1:7]
V_lod50_sqrt2 <- svd(L_lod50_sqrt2)$v[,1:7]

# cor(V_lod0_sqrt2, V_lod10_sqrt2)
# cor(V_lod0_sqrt2, V_lod20_sqrt2)
# cor(V_lod0_sqrt2, V_lod30_sqrt2)
# cor(V_lod0_sqrt2, V_lod40_sqrt2)
# cor(V_lod0_sqrt2, V_lod50_sqrt2)

# Hack -- Flip
V_lod10_sqrt2[,4:5] <- -V_lod10_sqrt2[,4:5]
V_lod10_sqrt2[,7] <- -V_lod10_sqrt2[,7]

V_lod20_sqrt2[,3] <- -V_lod20_sqrt2[,3]
V_lod20_sqrt2[,5:7] <- -V_lod20_sqrt2[,5:7]

V_lod30_sqrt2[,3] <- -V_lod30_sqrt2[,3]
V_lod30_sqrt2[,5:6] <- -V_lod30_sqrt2[,5:6]

V_lod40_sqrt2[,7] <- -V_lod40_sqrt2[,7]

V_lod50_sqrt2[,3:4] <- -V_lod50_sqrt2[,3:4]
V_lod50_sqrt2[,6:7] <- -V_lod50_sqrt2[,6:7]

V_diff_sqrt2 <- as_tibble(cbind(`0%` =norm((V_lod0_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"),
      `10%` =norm((V_lod10_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"),
      `20%` =norm((V_lod20_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"),
      `30%` =norm((V_lod30_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"),
      `40%` =norm((V_lod40_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"),
      `50%` =norm((V_lod50_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))

#V_diff_sqrt2
```

```{r, vdiff2}
# Extract right singular vectors from each low rank solution matrix
V_lod0_2  <-  svd(L_lod0_2)$v[,1:7]
V_lod10_2 <- svd(L_lod10_2)$v[,1:7]
V_lod20_2 <- svd(L_lod20_2)$v[,1:7]
V_lod30_2 <- svd(L_lod30_2)$v[,1:7]
V_lod40_2 <- svd(L_lod40_2)$v[,1:7]
V_lod50_2 <- svd(L_lod50_2)$v[,1:7]

# cor(V_lod0_2, V_lod10_2)
# cor(V_lod0_2, V_lod20_2)
# cor(V_lod0_2, V_lod30_2)
# cor(V_lod0_2, V_lod40_2)
# cor(V_lod0_2, V_lod50_2)

# Hack -- Flip
V_lod10_2[,3] <- -V_lod10_2[,3]
V_lod10_2[,5] <- -V_lod10_2[,5]
V_lod10_2[,7] <- -V_lod10_2[,7]
V_lod20_2[,3] <- -V_lod20_2[,3]
V_lod20_2[,5] <- -V_lod20_2[,5]
V_lod30_2[,3] <- -V_lod30_2[,3]
V_lod30_2[,5] <- -V_lod30_2[,5]
V_lod40_2[,3:5] <- -V_lod40_2[,3:5]
V_lod50_2[,3:5] <- -V_lod50_2[,3:5]
V_lod50_2[,7] <- -V_lod50_2[,7]

V_diff_2 <- as_tibble(cbind(`0%` =norm((V_lod0_2 - V_lod0_2), type = "F")/norm((V_lod0_2), type = "F"),
                                `10%` =norm((V_lod10_2 - V_lod0_2), type = "F")/norm((V_lod0_2), type = "F"),
                                `20%` =norm((V_lod20_2 - V_lod0_2), type = "F")/norm((V_lod0_2), type = "F"),
                                `30%` =norm((V_lod30_2 - V_lod0_2), type = "F")/norm((V_lod0_2), type = "F"),
                                `40%` =norm((V_lod40_2 - V_lod0_2), type = "F")/norm((V_lod0_2), type = "F"),
                                `50%` =norm((V_lod50_2 - V_lod0_2), type = "F")/norm((V_lod0_2), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP w/ LOD/2")

#V_diff_2
```

```{r}
# Extract right singular vectors from each low rank solution matrix
V_lod0_nnS  <-  svd(L_lod0_nnS)$v[,1:7]
V_lod10_nnS <- svd(L_lod10_nnS)$v[,1:7]
V_lod20_nnS <- svd(L_lod20_nnS)$v[,1:7]
V_lod30_nnS <- svd(L_lod30_nnS)$v[,1:7]
V_lod40_nnS <- svd(L_lod40_nnS)$v[,1:7]
V_lod50_nnS <- svd(L_lod50_nnS)$v[,1:7]

# Hack to flip singular vectos -- Use correlation
# cor(V_lod0_nnS, V_lod10_nnS)
# cor(V_lod0_nnS, V_lod20_nnS)
# cor(V_lod0_nnS, V_lod30_nnS)
# cor(V_lod0_nnS, V_lod40_nnS)
# cor(V_lod0_nnS, V_lod50_nnS)

# Hack -- Flip
V_lod30_nnS[,6] <- -V_lod30_nnS[,6]
V_lod40_nnS[,6] <- -V_lod40_nnS[,6]
V_lod50_nnS[,6] <- -V_lod50_nnS[,6]

V_diff_nnS<- as_tibble(cbind(`0%` =norm((V_lod0_nnS - V_lod0_nnS), type = "F")/norm((V_lod0_nnS), type = "F"),
      `10%` =norm((V_lod10_nnS - V_lod0_nnS), type = "F")/norm((V_lod0_nnS), type = "F"),
      `20%` =norm((V_lod20_nnS - V_lod0_nnS), type = "F")/norm((V_lod0_nnS), type = "F"),
      `30%` =norm((V_lod30_nnS - V_lod0_nnS), type = "F")/norm((V_lod0_nnS), type = "F"),
      `40%` =norm((V_lod40_nnS - V_lod0_nnS), type = "F")/norm((V_lod0_nnS), type = "F"),
      `50%` =norm((V_lod50_nnS - V_lod0_nnS), type = "F")/norm((V_lod0_nnS), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "LOD PCP nnS")

#V_diff_nnS
```

#### Viz

```{r, fig.height = 5, fig.width = 4, fig.align = "center"}
rbind(V_diff,
      V_diff_0,
      V_diff_sqrt2,
      V_diff_2,
      V_diff_nnS) %>% ggplot(aes(x = percent_blod, y = norm, group = Method, color = Method)) + 
  geom_point() + geom_path() + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "norm(SV - SV_lod0) / norm(SV_lod0)",
       title = "Relative Error in Low-Rank \nSolution Right Singular Vectors")
```

### Left singular vectors

```{r}
u_lod0  <-  svd(L_lod0)$u[,1:7]
u_lod10 <- svd(L_lod10)$u[,1:7]
u_lod20 <- svd(L_lod20)$u[,1:7]
u_lod30 <- svd(L_lod30)$u[,1:7]
u_lod40 <- svd(L_lod40)$u[,1:7]
u_lod50 <- svd(L_lod50)$u[,1:7]

# Hack -- Flip
u_lod10[,3] <- -u_lod10[,3]
u_lod10[,5:7] <- -u_lod10[,5:7]
u_lod20[,3] <- -u_lod20[,3]
u_lod20[,5:7] <- -u_lod20[,5:7]
u_lod30[,3:6] <- -u_lod30[,3:6]
u_lod40[,3:4] <- -u_lod40[,3:4]
u_lod40[,7] <- -u_lod40[,7]
u_lod50[,3:7] <- -u_lod50[,3:7]

u_diff <- as_tibble(cbind(`0%` =norm((u_lod0 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      `10%` =norm((u_lod10 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      `20%` =norm((u_lod20 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      `30%` =norm((u_lod30 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      `40%` =norm((u_lod40 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      `50%` =norm((u_lod50 - u_lod0), type = "F")/norm((u_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
mutate(Method = "LOD PCP")

# u_diff

nn_u_lod0  <-  svd(nn_L_lod0)$u[,1:7]
nn_u_lod10 <- svd(nn_L_lod10)$u[,1:7]
nn_u_lod20 <- svd(nn_L_lod20)$u[,1:7]
nn_u_lod30 <- svd(nn_L_lod30)$u[,1:7]
nn_u_lod40 <- svd(nn_L_lod40)$u[,1:7]
nn_u_lod50 <- svd(nn_L_lod50)$u[,1:7]

# Hack -- Flip
nn_u_lod10[,3] <- -nn_u_lod10[,3]
nn_u_lod10[,5] <- -nn_u_lod10[,5]
nn_u_lod20[,3] <- -nn_u_lod20[,3]
nn_u_lod20[,5] <- -nn_u_lod20[,5]
nn_u_lod30[,3] <- -nn_u_lod30[,3]
nn_u_lod30[,4] <- -nn_u_lod30[,4]
nn_u_lod30[,5] <- -nn_u_lod30[,5]
nn_u_lod40[,4] <- -nn_u_lod40[,4]
nn_u_lod40[,3] <- -nn_u_lod40[,3]
nn_u_lod50[,3] <- -nn_u_lod50[,3]
nn_u_lod50[,4] <- -nn_u_lod50[,4]
nn_u_lod50[,5] <- -nn_u_lod50[,5]

nn_u_diff <- as_tibble(cbind(`0%` =norm((nn_u_lod0 - nn_u_lod0), type = "F")/norm((nn_u_lod0), type = "F"),
      `10%` =norm((nn_u_lod10 - nn_u_lod0), type = "F")/norm((nn_u_lod0), type = "F"),
      `20%` =norm((nn_u_lod20 - nn_u_lod0), type = "F")/norm((nn_u_lod0), type = "F"),
      `30%` =norm((nn_u_lod30 - nn_u_lod0), type = "F")/norm((nn_u_lod0), type = "F"),
      `40%` =norm((nn_u_lod40 - nn_u_lod0), type = "F")/norm((nn_u_lod0), type = "F"),
      `50%` =norm((nn_u_lod50 - nn_u_lod0), type = "F")/norm((nn_u_lod0), type = "F"))) %>% 
  gather(percent_blod, norm)

u_lod0_0  <-  svd(L_lod0_0)$u[,1:7]
u_lod10_0 <- svd(L_lod10_0)$u[,1:7]
u_lod20_0 <- svd(L_lod20_0)$u[,1:7]
u_lod30_0 <- svd(L_lod30_0)$u[,1:7]
u_lod40_0 <- svd(L_lod40_0)$u[,1:7]
u_lod50_0 <- svd(L_lod50_0)$u[,1:7]

# Hack -- Flip
u_lod10_0[,3:7] <- -u_lod10_0[,3:7]
u_lod20_0[,3:4] <- -u_lod20_0[,3:4]
u_lod20_0[,7] <- -u_lod20_0[,7]
u_lod30_0[,3] <- -u_lod30_0[,3]
u_lod30_0[,5] <- -u_lod30_0[,5]
u_lod30_0[,7] <- -u_lod30_0[,7]
u_lod40_0[,3] <- -u_lod40_0[,3]
u_lod50_0[,3:4] <- -u_lod50_0[,3:4]
u_lod50_0[,7] <- -u_lod50_0[,7]

u_diff_0 <- as_tibble(cbind(`0%` =norm((u_lod0_0 - u_lod0_0), type = "F")/norm((u_lod0_0), type = "F"),
      `10%` =norm((u_lod10_0 - u_lod0_0), type = "F")/norm((u_lod0_0), type = "F"),
      `20%` =norm((u_lod20_0 - u_lod0_0), type = "F")/norm((u_lod0_0), type = "F"),
      `30%` =norm((u_lod30_0 - u_lod0_0), type = "F")/norm((u_lod0_0), type = "F"),
      `40%` =norm((u_lod40_0 - u_lod0_0), type = "F")/norm((u_lod0_0), type = "F"),
      `50%` =norm((u_lod50_0 - u_lod0_0), type = "F")/norm((u_lod0_0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP w/ 0")

u_lod0_sqrt2  <-  svd(L_lod0_sqrt2)$u[,1:7]
u_lod10_sqrt2 <- svd(L_lod10_sqrt2)$u[,1:7]
u_lod20_sqrt2 <- svd(L_lod20_sqrt2)$u[,1:7]
u_lod30_sqrt2 <- svd(L_lod30_sqrt2)$u[,1:7]
u_lod40_sqrt2 <- svd(L_lod40_sqrt2)$u[,1:7]
u_lod50_sqrt2 <- svd(L_lod50_sqrt2)$u[,1:7]

# Hack -- Flip
u_lod10_sqrt2[,4:5] <- -u_lod10_sqrt2[,4:5]
u_lod10_sqrt2[,7] <- -u_lod10_sqrt2[,7]
u_lod20_sqrt2[,3] <- -u_lod20_sqrt2[,3]
u_lod20_sqrt2[,5:7] <- -u_lod20_sqrt2[,5:7]
u_lod30_sqrt2[,3] <- -u_lod30_sqrt2[,3]
u_lod30_sqrt2[,5:6] <- -u_lod30_sqrt2[,5:6]
u_lod40_sqrt2[,7] <- -u_lod40_sqrt2[,7]
u_lod50_sqrt2[,3:4] <- -u_lod50_sqrt2[,3:4]
u_lod50_sqrt2[,6:7] <- -u_lod50_sqrt2[,6:7]

u_diff_sqrt2 <- as_tibble(cbind(`0%` =norm((u_lod0_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"),
      `10%` =norm((u_lod10_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"),
      `20%` =norm((u_lod20_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"),
      `30%` =norm((u_lod30_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"),
      `40%` =norm((u_lod40_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"),
      `50%` =norm((u_lod50_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))
```

```{r, udiff2}
u_lod0_2  <-  svd(L_lod0_2)$u[,1:7]
u_lod10_2 <- svd(L_lod10_2)$u[,1:7]
u_lod20_2 <- svd(L_lod20_2)$u[,1:7]
u_lod30_2 <- svd(L_lod30_2)$u[,1:7]
u_lod40_2 <- svd(L_lod40_2)$u[,1:7]
u_lod50_2 <- svd(L_lod50_2)$u[,1:7]

# Hack -- Flip
u_lod10_2[,3] <- -u_lod10_2[,3]
u_lod10_2[,5] <- -u_lod10_2[,5]
u_lod10_2[,7] <- -u_lod10_2[,7]
u_lod20_2[,3] <- -u_lod20_2[,3]
u_lod20_2[,5] <- -u_lod20_2[,5]
u_lod30_2[,3] <- -u_lod30_2[,3]
u_lod30_2[,5] <- -u_lod30_2[,5]
u_lod40_2[,3:5] <- -u_lod40_2[,3:5]
u_lod50_2[,3:5] <- -u_lod50_2[,3:5]
u_lod50_2[,7] <- -u_lod50_2[,7]

u_diff_2 <- as_tibble(cbind(`0%` =norm((u_lod0_2 - u_lod0_2), type = "F")/norm((u_lod0_2), type = "F"),
                                `10%` =norm((u_lod10_2 - u_lod0_2), type = "F")/norm((u_lod0_2), type = "F"),
                                `20%` =norm((u_lod20_2 - u_lod0_2), type = "F")/norm((u_lod0_2), type = "F"),
                                `30%` =norm((u_lod30_2 - u_lod0_2), type = "F")/norm((u_lod0_2), type = "F"),
                                `40%` =norm((u_lod40_2 - u_lod0_2), type = "F")/norm((u_lod0_2), type = "F"),
                                `50%` =norm((u_lod50_2 - u_lod0_2), type = "F")/norm((u_lod0_2), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP w/ LOD/2")
```

```{r}
u_lod0_nnS  <-  svd(L_lod0_nnS)$u[,1:7]
u_lod10_nnS <- svd(L_lod10_nnS)$u[,1:7]
u_lod20_nnS <- svd(L_lod20_nnS)$u[,1:7]
u_lod30_nnS <- svd(L_lod30_nnS)$u[,1:7]
u_lod40_nnS <- svd(L_lod40_nnS)$u[,1:7]
u_lod50_nnS <- svd(L_lod50_nnS)$u[,1:7]

# Hack -- Flip
u_lod30_nnS[,6] <- -u_lod30_nnS[,6]
u_lod40_nnS[,6] <- -u_lod40_nnS[,6]
u_lod50_nnS[,6] <- -u_lod50_nnS[,6]

u_diff_nnS<- as_tibble(cbind(`0%` =norm((u_lod0_nnS - u_lod0_nnS), type = "F")/norm((u_lod0_nnS), type = "F"),
      `10%` =norm((u_lod10_nnS - u_lod0_nnS), type = "F")/norm((u_lod0_nnS), type = "F"),
      `20%` =norm((u_lod20_nnS - u_lod0_nnS), type = "F")/norm((u_lod0_nnS), type = "F"),
      `30%` =norm((u_lod30_nnS - u_lod0_nnS), type = "F")/norm((u_lod0_nnS), type = "F"),
      `40%` =norm((u_lod40_nnS - u_lod0_nnS), type = "F")/norm((u_lod0_nnS), type = "F"),
      `50%` =norm((u_lod50_nnS - u_lod0_nnS), type = "F")/norm((u_lod0_nnS), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
mutate(Method = "LOD PCP nnS")

# u_diff_nnS
```

#### Viz

```{r, fig.height = 5, fig.width = 4, fig.align = "center"}
rbind(u_diff,
      u_diff_0,
      u_diff_sqrt2,
      u_diff_2,
      u_diff_nnS) %>% ggplot(aes(x = percent_blod, y = norm, group = Method, color = Method)) + 
  geom_point() + geom_path() + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "norm(SV - SV_lod0) / norm(SV_lod0)",
       title = "Relative Error in Low-Rank \nSolution Left Singular Vectors")
```

### Singular Values

```{r}
d_lod0  <- svd(L_lod0)$d[1:7]
d_lod10 <- svd(L_lod10)$d[1:7]
d_lod20 <- svd(L_lod20)$d[1:7]
d_lod30 <- svd(L_lod30)$d[1:7]
d_lod40 <- svd(L_lod40)$d[1:7]
d_lod50 <- svd(L_lod50)$d[1:7]

norm_vec <- function(x) sqrt(sum(x^2))

d_diff <- as_tibble(cbind(`0%` = norm_vec(d_lod0 - d_lod0)/norm_vec(d_lod0),
      `10%` = norm_vec(d_lod10 - d_lod0)/norm_vec(d_lod0),
      `20%` = norm_vec(d_lod20 - d_lod0)/norm_vec(d_lod0),
      `30%` = norm_vec(d_lod30 - d_lod0)/norm_vec(d_lod0),
      `40%` = norm_vec(d_lod40 - d_lod0)/norm_vec(d_lod0),
      `50%` = norm_vec(d_lod50 - d_lod0)/norm_vec(d_lod0))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "LOD PCP")

nn_d_lod0  <- svd(nn_L_lod0)$d[1:7]
nn_d_lod10 <- svd(nn_L_lod10)$d[1:7]
nn_d_lod20 <- svd(nn_L_lod20)$d[1:7]
nn_d_lod30 <- svd(nn_L_lod30)$d[1:7]
nn_d_lod40 <- svd(nn_L_lod40)$d[1:7]
nn_d_lod50 <- svd(nn_L_lod50)$d[1:7]

nn_d_diff <- as_tibble(cbind(`0%` = norm_vec(nn_d_lod0 - nn_d_lod0)/norm_vec(nn_d_lod0),
      `10%` = norm_vec(nn_d_lod10 - nn_d_lod0)/norm_vec(nn_d_lod0),
      `20%` = norm_vec(nn_d_lod20 - nn_d_lod0)/norm_vec(nn_d_lod0),
      `30%` = norm_vec(nn_d_lod30 - nn_d_lod0)/norm_vec(nn_d_lod0),
      `40%` = norm_vec(nn_d_lod40 - nn_d_lod0)/norm_vec(nn_d_lod0),
      `50%` = norm_vec(nn_d_lod50 - nn_d_lod0)/norm_vec(nn_d_lod0))) %>% 
  gather(percent_blod, norm)

d_lod0_0  <- svd(L_lod0_0)$d[1:7]
d_lod10_0 <- svd(L_lod10_0)$d[1:7]
d_lod20_0 <- svd(L_lod20_0)$d[1:7]
d_lod30_0 <- svd(L_lod30_0)$d[1:7]
d_lod40_0 <- svd(L_lod40_0)$d[1:7]
d_lod50_0 <- svd(L_lod50_0)$d[1:7]

d_diff_0 <- as_tibble(cbind(`0%` = norm_vec(d_lod0_0 - d_lod0_0)/norm_vec(d_lod0_0),
      `10%` = norm_vec(d_lod10_0 - d_lod0_0)/norm_vec(d_lod0_0),
      `20%` = norm_vec(d_lod20_0 - d_lod0_0)/norm_vec(d_lod0_0),
      `30%` = norm_vec(d_lod30_0 - d_lod0_0)/norm_vec(d_lod0_0),
      `40%` = norm_vec(d_lod40_0 - d_lod0_0)/norm_vec(d_lod0_0),
      `50%` = norm_vec(d_lod50_0 - d_lod0_0)/norm_vec(d_lod0_0))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP w/ 0")

d_lod0_sqrt2  <- svd(L_lod0_sqrt2)$d[1:7]
d_lod10_sqrt2 <- svd(L_lod10_sqrt2)$d[1:7]
d_lod20_sqrt2 <- svd(L_lod20_sqrt2)$d[1:7]
d_lod30_sqrt2 <- svd(L_lod30_sqrt2)$d[1:7]
d_lod40_sqrt2 <- svd(L_lod40_sqrt2)$d[1:7]
d_lod50_sqrt2 <- svd(L_lod50_sqrt2)$d[1:7]

d_diff_sqrt2 <- as_tibble(cbind(`0%` = norm_vec(d_lod0_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2),
      `10%` = norm_vec(d_lod10_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2),
      `20%` = norm_vec(d_lod20_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2),
      `30%` = norm_vec(d_lod30_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2),
      `40%` = norm_vec(d_lod40_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2),
      `50%` = norm_vec(d_lod50_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))
```

```{r, ddiff2}
d_lod0_2  <- svd(L_lod0_2)$d[1:7]
d_lod10_2 <- svd(L_lod10_2)$d[1:7]
d_lod20_2 <- svd(L_lod20_2)$d[1:7]
d_lod30_2 <- svd(L_lod30_2)$d[1:7]
d_lod40_2 <- svd(L_lod40_2)$d[1:7]
d_lod50_2 <- svd(L_lod50_2)$d[1:7]

d_diff_2 <- as_tibble(cbind(`0%` = norm_vec(d_lod0_2 - d_lod0_2)/norm_vec(d_lod0_2),
                                `10%` = norm_vec(d_lod10_2 - d_lod0_2)/norm_vec(d_lod0_2),
                                `20%` = norm_vec(d_lod20_2 - d_lod0_2)/norm_vec(d_lod0_2),
                                `30%` = norm_vec(d_lod30_2 - d_lod0_2)/norm_vec(d_lod0_2),
                                `40%` = norm_vec(d_lod40_2 - d_lod0_2)/norm_vec(d_lod0_2),
                                `50%` = norm_vec(d_lod50_2 - d_lod0_2)/norm_vec(d_lod0_2))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP w/ LOD/2")
```

```{r}
d_lod0_nnS  <- svd(L_lod0_nnS)$d[1:7]
d_lod10_nnS <- svd(L_lod10_nnS)$d[1:7]
d_lod20_nnS <- svd(L_lod20_nnS)$d[1:7]
d_lod30_nnS <- svd(L_lod30_nnS)$d[1:7]
d_lod40_nnS <- svd(L_lod40_nnS)$d[1:7]
d_lod50_nnS <- svd(L_lod50_nnS)$d[1:7]

norm_vec <- function(x) sqrt(sum(x^2))

d_diff_nnS<- as_tibble(cbind(`0%` = norm_vec(d_lod0_nnS - d_lod0_nnS)/norm_vec(d_lod0_nnS),
      `10%` = norm_vec(d_lod10_nnS - d_lod0_nnS)/norm_vec(d_lod0_nnS),
      `20%` = norm_vec(d_lod20_nnS - d_lod0_nnS)/norm_vec(d_lod0_nnS),
      `30%` = norm_vec(d_lod30_nnS - d_lod0_nnS)/norm_vec(d_lod0_nnS),
      `40%` = norm_vec(d_lod40_nnS - d_lod0_nnS)/norm_vec(d_lod0_nnS),
      `50%` = norm_vec(d_lod50_nnS - d_lod0_nnS)/norm_vec(d_lod0_nnS))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "LOD PCP nnS")
```

#### Viz

```{r, fig.height = 5, fig.width = 4, fig.align = "center"}
rbind(d_diff_sqrt2,
      d_diff,
      d_diff_0,
      d_diff_2,
      d_diff_nnS) %>% ggplot(aes(x = percent_blod, y = norm, group = Method, color = Method)) + 
  geom_point() + geom_path() + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "norm(SV - SV_lod0) / norm(SV_lod0)",
       title = "Relative Error in Low-Rank \nSolution Singular Values")
```

## PCA

```{r}
pca_0  <- prcomp(mix)
pca_10 <- prcomp(mix_data_lod_10_sqrt2)
pca_20 <- prcomp(mix_data_lod_20_sqrt2)
pca_30 <- prcomp(mix_data_lod_30_sqrt2)
pca_40 <- prcomp(mix_data_lod_40_sqrt2)
pca_50 <- prcomp(mix_data_lod_50_sqrt2)
```

```{r}
# cor(pca_0$rotation[,1:7], pca_10$rotation[,1:7])
# cor(pca_0$rotation[,1:7], pca_20$rotation[,1:7])
# cor(pca_0$rotation[,1:7], pca_30$rotation[,1:7])
# cor(pca_0$rotation[,1:7], pca_40$rotation[,1:7])
# cor(pca_0$rotation[,1:7], pca_50$rotation[,1:7])

pca_10$rotation[,6:7] <- -pca_10$rotation[,6:7]
pca_20$rotation[,6:7] <- -pca_20$rotation[,6:7]
pca_40$rotation[,6:7] <- -pca_40$rotation[,6:7]
pca_50$rotation[,3:5] <- -pca_50$rotation[,3:5]

rotation_norm <- as_tibble(cbind(`0%` = norm((pca_0$rotation[,1:7] - pca_0$rotation[,1:7]), type = "F")/norm((pca_0$rotation[,1:7]), type = "F"),
      `10%` = norm((pca_0$rotation[,1:7] - pca_10$rotation[,1:7]), type = "F")/norm((pca_0$rotation[,1:7]), type = "F"),
      `20%` = norm((pca_0$rotation[,1:7] - pca_20$rotation[,1:7]), type = "F")/norm((pca_0$rotation[,1:7]), type = "F"),
      `30%` = norm((pca_0$rotation[,1:7] - pca_30$rotation[,1:7]), type = "F")/norm((pca_0$rotation[,1:7]), type = "F"),
      `40%` = norm((pca_0$rotation[,1:7] - pca_40$rotation[,1:7]), type = "F")/norm((pca_0$rotation[,1:7]), type = "F"),
      `50%` = norm((pca_0$rotation[,1:7] - pca_50$rotation[,1:7]), type = "F")/norm((pca_0$rotation[,1:7]), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCA")
```

```{r}
# cor(pca_0$x[,1:7], pca_10$x[,1:7])
# cor(pca_0$x[,1:7], pca_20$x[,1:7])
# cor(pca_0$x[,1:7], pca_30$x[,1:7])
# cor(pca_0$x[,1:7], pca_40$x[,1:7])
# cor(pca_0$x[,1:7], pca_50$x[,1:7])

pca_10$x[,6:7] <- -pca_10$x[,6:7]
pca_20$x[,6:7] <- -pca_20$x[,6:7]
pca_40$x[,6:7] <- -pca_40$x[,6:7]
pca_50$x[,3:5] <- -pca_50$x[,3:5]

score_norm <- as_tibble(cbind(`0%` = norm((pca_0$x[,1:7] - pca_0$x[,1:7]), type = "F")/norm((pca_0$x[,1:7]), type = "F"),
      `10%` = norm((pca_0$x[,1:7] - pca_10$x[,1:7]), type = "F")/norm((pca_0$x[,1:7]), type = "F"),
      `20%` = norm((pca_0$x[,1:7] - pca_20$x[,1:7]), type = "F")/norm((pca_0$x[,1:7]), type = "F"),
      `30%` = norm((pca_0$x[,1:7] - pca_30$x[,1:7]), type = "F")/norm((pca_0$x[,1:7]), type = "F"),
      `40%` = norm((pca_0$x[,1:7] - pca_40$x[,1:7]), type = "F")/norm((pca_0$x[,1:7]), type = "F"),
      `50%` = norm((pca_0$x[,1:7] - pca_50$x[,1:7]), type = "F")/norm((pca_0$x[,1:7]), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCA")
```

```{r}
sdev_norm <- as_tibble(cbind(`0%` = norm_vec(pca_0$sdev[1:7] - pca_0$sdev[1:7])/norm_vec(pca_0$sdev[1:7]),
      `10%` = norm_vec(pca_0$sdev[1:7] - pca_10$sdev[1:7])/norm_vec(pca_0$sdev[1:7]),
      `20%` = norm_vec(pca_0$sdev[1:7] - pca_20$sdev[1:7])/norm_vec(pca_0$sdev[1:7]),
      `30%` = norm_vec(pca_0$sdev[1:7] - pca_30$sdev[1:7])/norm_vec(pca_0$sdev[1:7]),
      `40%` = norm_vec(pca_0$sdev[1:7] - pca_40$sdev[1:7])/norm_vec(pca_0$sdev[1:7]),
      `50%` = norm_vec(pca_0$sdev[1:7] - pca_50$sdev[1:7])/norm_vec(pca_0$sdev[1:7]))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCA")
```

```{r}
pcp_pca_0  <- prcomp(L_lod0)
pcp_pca_10 <- prcomp(L_lod10)
pcp_pca_20 <- prcomp(L_lod20)
pcp_pca_30 <- prcomp(L_lod30)
pcp_pca_40 <- prcomp(L_lod40)
pcp_pca_50 <- prcomp(L_lod50)
```

```{r}
# cor(pcp_pca_0$rotation[,1:7], pcp_pca_10$rotation[,1:7])
# cor(pcp_pca_0$rotation[,1:7], pcp_pca_20$rotation[,1:7])
# cor(pcp_pca_0$rotation[,1:7], pcp_pca_30$rotation[,1:7])
# cor(pcp_pca_0$rotation[,1:7], pcp_pca_40$rotation[,1:7])
# cor(pcp_pca_0$rotation[,1:7], pcp_pca_50$rotation[,1:7])

pcp_pca_10$rotation[,7] <- -pcp_pca_10$rotation[,7]
pcp_pca_20$rotation[,3:4] <- -pcp_pca_20$rotation[,3:4]
pcp_pca_20$rotation[,6] <- -pcp_pca_20$rotation[,6]
pcp_pca_30$rotation[,3:4] <- -pcp_pca_30$rotation[,3:4]
pcp_pca_30$rotation[,6:7] <- -pcp_pca_30$rotation[,6:7]
pcp_pca_40$rotation[,6] <- -pcp_pca_40$rotation[,6]
pcp_pca_50$rotation[,3:6] <- -pcp_pca_50$rotation[,3:6]

pcp_rotation_norm <- as_tibble(cbind(`0%` = norm((pcp_pca_0$rotation[,1:7] - pcp_pca_0$rotation[,1:7]), type = "F")/norm((pcp_pca_0$rotation[,1:7]), type = "F"),
      `10%` = norm((pcp_pca_0$rotation[,1:7] - pcp_pca_10$rotation[,1:7]), type = "F")/norm((pcp_pca_0$rotation[,1:7]), type = "F"),
      `20%` = norm((pcp_pca_0$rotation[,1:7] - pcp_pca_20$rotation[,1:7]), type = "F")/norm((pcp_pca_0$rotation[,1:7]), type = "F"),
      `30%` = norm((pcp_pca_0$rotation[,1:7] - pcp_pca_30$rotation[,1:7]), type = "F")/norm((pcp_pca_0$rotation[,1:7]), type = "F"),
      `40%` = norm((pcp_pca_0$rotation[,1:7] - pcp_pca_40$rotation[,1:7]), type = "F")/norm((pcp_pca_0$rotation[,1:7]), type = "F"),
      `50%` = norm((pcp_pca_0$rotation[,1:7] - pcp_pca_50$rotation[,1:7]), type = "F")/norm((pcp_pca_0$rotation[,1:7]), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP")
```

```{r}
# cor(pcp_pca_0$x[,1:7], pcp_pca_10$x[,1:7])
# cor(pcp_pca_0$x[,1:7], pcp_pca_20$x[,1:7])
# cor(pcp_pca_0$x[,1:7], pcp_pca_30$x[,1:7])
# cor(pcp_pca_0$x[,1:7], pcp_pca_40$x[,1:7])
# cor(pcp_pca_0$x[,1:7], pcp_pca_50$x[,1:7])

pcp_pca_10$x[,7] <- -pcp_pca_10$x[,7]
pcp_pca_20$x[,3:4] <- -pcp_pca_20$x[,3:4]
pcp_pca_20$x[,6] <- -pcp_pca_20$x[,6]
pcp_pca_30$x[,3:4] <- -pcp_pca_30$x[,3:4]
pcp_pca_30$x[,6:7] <- -pcp_pca_30$x[,6:7]
pcp_pca_40$x[,6] <- -pcp_pca_40$x[,6]
pcp_pca_50$x[,3:6] <- -pcp_pca_50$x[,3:6]

pcp_score_norm <- as_tibble(cbind(`0%` = norm((pcp_pca_0$x[,1:7] - pcp_pca_0$x[,1:7]), type = "F")/norm((pcp_pca_0$x[,1:7]), type = "F"),
      `10%` = norm((pcp_pca_0$x[,1:7] - pcp_pca_10$x[,1:7]), type = "F")/norm((pcp_pca_0$x[,1:7]), type = "F"),
      `20%` = norm((pcp_pca_0$x[,1:7] - pcp_pca_20$x[,1:7]), type = "F")/norm((pcp_pca_0$x[,1:7]), type = "F"),
      `30%` = norm((pcp_pca_0$x[,1:7] - pcp_pca_30$x[,1:7]), type = "F")/norm((pcp_pca_0$x[,1:7]), type = "F"),
      `40%` = norm((pcp_pca_0$x[,1:7] - pcp_pca_40$x[,1:7]), type = "F")/norm((pcp_pca_0$x[,1:7]), type = "F"),
      `50%` = norm((pcp_pca_0$x[,1:7] - pcp_pca_50$x[,1:7]), type = "F")/norm((pcp_pca_0$x[,1:7]), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP")
```

```{r}
pcp_sdev_norm <- as_tibble(cbind(`0%` = norm_vec(pcp_pca_0$sdev[1:7] - pcp_pca_0$sdev[1:7])/norm_vec(pcp_pca_0$sdev[1:7]),
      `10%` = norm_vec(pcp_pca_0$sdev[1:7] - pcp_pca_10$sdev[1:7])/norm_vec(pcp_pca_0$sdev[1:7]),
      `20%` = norm_vec(pcp_pca_0$sdev[1:7] - pcp_pca_20$sdev[1:7])/norm_vec(pcp_pca_0$sdev[1:7]),
      `30%` = norm_vec(pcp_pca_0$sdev[1:7] - pcp_pca_30$sdev[1:7])/norm_vec(pcp_pca_0$sdev[1:7]),
      `40%` = norm_vec(pcp_pca_0$sdev[1:7] - pcp_pca_40$sdev[1:7])/norm_vec(pcp_pca_0$sdev[1:7]),
      `50%` = norm_vec(pcp_pca_0$sdev[1:7] - pcp_pca_50$sdev[1:7])/norm_vec(pcp_pca_0$sdev[1:7]))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "PCP")
```

### Viz

```{r, fig.height = 5, fig.width = 4, fig.align = "center"}
rbind(rotation_norm, pcp_rotation_norm) %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point(aes(color = Method)) + geom_path(aes(group = Method, color = Method)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(X-lod0) / norm(X)",
       title = "Relative Error in Rotations")
```

```{r, fig.height = 5, fig.width = 4, fig.align = "center"}
rbind(score_norm, pcp_score_norm) %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point(aes(color = Method)) + geom_path(aes(group = Method, color = Method)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(X-lod0) / norm(X)",
       title = "Relative Error in Scores")
```

```{r, fig.height = 5, fig.width = 4, fig.align = "center"}
rbind(sdev_norm, pcp_sdev_norm) %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point(aes(color = Method)) + geom_path(aes(group = Method, color = Method)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(X-lod0) / norm(X)",
       title = "Relative Error in Singular Values")
```

### Variance Explained

```{r}
PCP_0 <- pcp_pca_0$sdev^2/sum(pcp_pca_0$sdev^2) *100
PCA_0 <- pca_0$sdev^2/sum(pca_0$sdev^2) *100

PCP_50 <- pcp_pca_50$sdev^2/sum(pcp_pca_50$sdev^2) *100
PCA_50 <- pca_50$sdev^2/sum(pca_50$sdev^2) *100

round(cbind(Component = 1:18, PCP_0, PCA_0, PCP_50, PCA_50), 4) %>% kable()
```

```{r, include=FALSE}
round(cbind(Component = 1:18, PCP_0, PCA_0, PCP_50, PCA_50), 4) %>% stargazer::stargazer(., summary = NULL)
```

## Values \<LOD

```{r, l22s}
t_na_lod_0 <- sim_all %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_0_na <- as_tibble(t_na_lod_0*L_lod0)
s_blod_0_na <- as_tibble(t_na_lod_0*S_lod0)
blod_0_na <- as_tibble(sim_all*t_na_lod_0)

t_na_lod_10 <- mix_data_lod_10 %>% 
  as_tibble() %>%
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_10_na <- as_tibble(t_na_lod_10*L_lod10)
s_blod_10_na <- as_tibble(t_na_lod_10*S_lod10)
blod_10_na <- as_tibble(sim_all*t_na_lod_10)

t_na_lod_20 <- mix_data_lod_20 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_20_na <- as_tibble(t_na_lod_20*L_lod20)
s_blod_20_na <- as_tibble(t_na_lod_20*S_lod20)
blod_20_na <- as_tibble(sim_all*t_na_lod_20)

t_na_lod_30 <- mix_data_lod_30 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_30_na <- as_tibble(t_na_lod_30*L_lod30)
s_blod_30_na <- as_tibble(t_na_lod_30*S_lod30)
blod_30_na <- as_tibble(sim_all*t_na_lod_30)

t_na_lod_40 <- mix_data_lod_40 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_40_na <- as_tibble(t_na_lod_40*L_lod40)
s_blod_40_na <- as_tibble(t_na_lod_40*S_lod40)
blod_40_na <- as_tibble(sim_all*t_na_lod_40)

t_na_lod_50 <- mix_data_lod_50 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_50_na <- as_tibble(t_na_lod_50*L_lod50)
s_blod_50_na <- as_tibble(t_na_lod_50*S_lod50)
blod_50_na <- as_tibble(sim_all*t_na_lod_50) 
```

```{r}
l_blod_0_0_na <- as_tibble(t_na_lod_0*L_lod0_0)
s_blod_0_0_na <- as_tibble(t_na_lod_0*S_lod0_0)

l_blod_10_0_na <- as_tibble(t_na_lod_10*L_lod10_0)
s_blod_10_0_na <- as_tibble(t_na_lod_10*S_lod10_0)

l_blod_20_0_na <- as_tibble(t_na_lod_20*L_lod20_0)
s_blod_20_0_na <- as_tibble(t_na_lod_20*S_lod20_0)

l_blod_30_0_na <- as_tibble(t_na_lod_30*L_lod30_0)
s_blod_30_0_na <- as_tibble(t_na_lod_30*S_lod30_0)

l_blod_40_0_na <- as_tibble(t_na_lod_40*L_lod40_0)
s_blod_40_0_na <- as_tibble(t_na_lod_40*S_lod40_0)

l_blod_50_0_na <- as_tibble(t_na_lod_50*L_lod50_0)
s_blod_50_0_na <- as_tibble(t_na_lod_50*S_lod50_0)

L_blod_0_sqrt2_na <- as_tibble(t_na_lod_0*L_lod0_sqrt2)
S_blod_0_sqrt2_na <- as_tibble(t_na_lod_0*S_lod0_sqrt2)

L_blod_10_sqrt2_na <- as_tibble(t_na_lod_10*L_lod10_sqrt2)
S_blod_10_sqrt2_na <- as_tibble(t_na_lod_10*S_lod10_sqrt2)

L_blod_20_sqrt2_na <- as_tibble(t_na_lod_20*L_lod20_sqrt2)
S_blod_20_sqrt2_na <- as_tibble(t_na_lod_20*S_lod20_sqrt2)

L_blod_30_sqrt2_na <- as_tibble(t_na_lod_30*L_lod30_sqrt2)
S_blod_30_sqrt2_na <- as_tibble(t_na_lod_30*S_lod30_sqrt2)

L_blod_40_sqrt2_na <- as_tibble(t_na_lod_40*L_lod40_sqrt2)
S_blod_40_sqrt2_na <- as_tibble(t_na_lod_40*S_lod40_sqrt2)

L_blod_50_sqrt2_na <- as_tibble(t_na_lod_50*L_lod50_sqrt2)
S_blod_50_sqrt2_na <- as_tibble(t_na_lod_50*S_lod50_sqrt2)
```

```{r, ls22}
L_blod_0_2_na <- as_tibble(t_na_lod_0*L_lod0_2)
S_blod_0_2_na <- as_tibble(t_na_lod_0*S_lod0_2)

L_blod_10_2_na <- as_tibble(t_na_lod_10*L_lod10_2)
S_blod_10_2_na <- as_tibble(t_na_lod_10*S_lod10_2)

L_blod_20_2_na <- as_tibble(t_na_lod_20*L_lod20_2)
S_blod_20_2_na <- as_tibble(t_na_lod_20*S_lod20_2)

L_blod_30_2_na <- as_tibble(t_na_lod_30*L_lod30_2)
S_blod_30_2_na <- as_tibble(t_na_lod_30*S_lod30_2)

L_blod_40_2_na <- as_tibble(t_na_lod_40*L_lod40_2)
S_blod_40_2_na <- as_tibble(t_na_lod_40*S_lod40_2)

L_blod_50_2_na <- as_tibble(t_na_lod_50*L_lod50_2)
S_blod_50_2_na <- as_tibble(t_na_lod_50*S_lod50_2)
```

```{r}
LOD10 <- delta10 %>% as.matrix() %>% t() %>% as_tibble() %>% rename_all(., list(~str_sub(., start = 1, end = -5))) %>% gather(POP, LOD) %>% mutate(Percent = "10%")
LOD20 <- delta20 %>% as.matrix() %>% t() %>% as_tibble() %>% rename_all(., list(~str_sub(., start = 1, end = -5))) %>% gather(POP, LOD) %>% mutate(Percent = "20%")
LOD30 <- delta30 %>% as.matrix() %>% t() %>% as_tibble() %>% rename_all(., list(~str_sub(., start = 1, end = -5))) %>% gather(POP, LOD) %>% mutate(Percent = "30%")
LOD40 <- delta40 %>% as.matrix() %>% t() %>% as_tibble() %>% rename_all(., list(~str_sub(., start = 1, end = -5))) %>% gather(POP, LOD) %>% mutate(Percent = "40%")
LOD50 <- delta50 %>% as.matrix() %>% t() %>% as_tibble() %>% rename_all(., list(~str_sub(., start = 1, end = -5))) %>% gather(POP, LOD) %>% mutate(Percent = "50%")
LODall <- rbind(LOD10, LOD20, LOD30, LOD40, LOD50)
  
plot_10 <- blod_10_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Original, -rowid) %>% mutate(Percent = "10%")
plotl_10 <- l_blod_10_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))
plots_10 <- s_blod_10_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))
plotall_10 <- (l_blod_10_na + s_blod_10_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))

plot_20 <- blod_20_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Original, -rowid) %>% mutate(Percent = "20%") 
plotl_20 <- l_blod_20_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent"))
plots_20 <- s_blod_20_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent"))
plotall_20 <- (l_blod_20_na + s_blod_20_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent")) 

plot_30 <- blod_30_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Original, -rowid) %>% mutate(Percent = "30%")
plotl_30 <- l_blod_30_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent"))
plots_30 <- s_blod_30_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent")) 
plotall_30 <- (l_blod_30_na + s_blod_30_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent")) 

plot_40 <- blod_40_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Original, -rowid) %>% mutate(Percent = "40%") 
plotl_40 <- l_blod_40_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))
plots_40 <- s_blod_40_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))
plotall_40 <- (l_blod_40_na + s_blod_40_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))

plot_50 <- blod_50_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Original, -rowid) %>% mutate(Percent = "50%") 
plotl_50 <- l_blod_50_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent"))
plots_50 <- s_blod_50_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent")) 
plotall_50 <- (l_blod_50_na + s_blod_50_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent"))

org <- rbind(plot_10,
        plot_20,
        plot_30,
        plot_40,
        plot_50) %>% rename(Value = Original) %>% 
  mutate(Compare = "Original") %>% 
  left_join(., LODall, by = c("POP", "Percent"))

plotall <- rbind(plotl_10,
      plots_10,
      plotall_10,
      plotl_20,
      plots_20,
      plotall_20,
      plotl_30,
      plots_30,
      plotall_30, 
      plotl_40,
      plots_40,
      plotall_40,
      plotl_50,
      plots_50,
      plotall_50)
```

```{r, l22s2}
l_blod_0_nnS_na <- as_tibble(t_na_lod_0*L_lod0_nnS)
s_blod_0_nnS_na <- as_tibble(t_na_lod_0*S_lod0_nnS)

l_blod_10_nnS_na <- as_tibble(t_na_lod_10*L_lod10_nnS)
s_blod_10_nnS_na <- as_tibble(t_na_lod_10*S_lod10_nnS)

l_blod_20_nnS_na <- as_tibble(t_na_lod_20*L_lod20_nnS)
s_blod_20_nnS_na <- as_tibble(t_na_lod_20*S_lod20_nnS)

l_blod_30_nnS_na <- as_tibble(t_na_lod_30*L_lod30_nnS)
s_blod_30_nnS_na <- as_tibble(t_na_lod_30*S_lod30_nnS)

l_blod_40_nnS_na <- as_tibble(t_na_lod_40*L_lod40_nnS)
s_blod_40_nnS_na <- as_tibble(t_na_lod_40*S_lod40_nnS)

l_blod_50_nnS_na <- as_tibble(t_na_lod_50*L_lod50_nnS)
s_blod_50_nnS_na <- as_tibble(t_na_lod_50*S_lod50_nnS)
```

```{r}
plotl_10_nnS <- l_blod_10_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))
plots_10_nnS <- s_blod_10_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))
plotall_10_nnS <- (l_blod_10_nnS_na + s_blod_10_nnS_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))

plotl_20_nnS <- l_blod_20_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent"))
plots_20_nnS <- s_blod_20_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent"))
plotall_20_nnS <- (l_blod_20_nnS_na + s_blod_20_nnS_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent")) 

plotl_30_nnS <- l_blod_30_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent"))
plots_30_nnS <- s_blod_30_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent")) 
plotall_30_nnS <- (l_blod_30_nnS_na + s_blod_30_nnS_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent")) 

plotl_40_nnS <- l_blod_40_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))
plots_40_nnS <- s_blod_40_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))
plotall_40_nnS <- (l_blod_40_nnS_na + s_blod_40_nnS_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))

plotl_50_nnS <- l_blod_50_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent"))
plots_50_nnS <- s_blod_50_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent")) 
plotall_50_nnS <- (l_blod_50_nnS_na + s_blod_50_nnS_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent"))

plotall_nns <- rbind(plotl_10_nnS,
      plots_10_nnS,
      plotall_10_nnS,
      plotl_20_nnS,
      plots_20_nnS,
      plotall_20_nnS,
      plotl_30_nnS,
      plots_30_nnS,
      plotall_30_nnS, 
      plotl_40_nnS,
      plots_40_nnS,
      plotall_40_nnS,
      plotl_50_nnS,
      plots_50_nnS,
      plotall_50_nnS)
```

```{r}
plotall %>% 
  drop_na(.) %>% 
  mutate(above_lod = ifelse(Value > LOD, 1, 0)) %>%
  group_by(Compare, Percent) %>% 
  summarise(above = sum(above_lod),
            total = n()) %>% 
  mutate(above_prop = above/total) %>% 
  select(-above, -total) %>% 
  kable(.)

rbind(plots_10,
      plots_20,
      plots_30,
      plots_40,
      plots_50) %>% 
  drop_na(.) %>% 
  group_by(Compare, Percent) %>% 
  summarise(Min = min (Value),
            Ave = mean(Value),
            Max = max(Value)) %>% kable(.)
```

```{r}
plotall_nns %>% 
  drop_na(.) %>% 
  mutate(above_lod = ifelse(Value > LOD, 1, 0)) %>%
  group_by(Compare, Percent) %>% 
  summarise(above = sum(above_lod),
            total = n()) %>% 
  mutate(above_prop = above/total) %>% 
  select(-above, -total) %>% 
  kable(.)

rbind(plots_10_nnS,
      plots_20_nnS,
      plots_30_nnS,
      plots_40_nnS,
      plots_50_nnS) %>% 
  drop_na(.) %>% 
  group_by(Compare, Percent) %>% 
  summarise(Min = min (Value),
            Ave = mean(Value),
            Max = max(Value)) %>% kable(.)
```

### Correlation

```{r}
cor(as.matrix(blod_50_na), use = "complete.obs", method = "spearman")
cor(as.matrix(l_blod_50_na), use = "complete.obs", method = "spearman")
cor(as.matrix(s_blod_50_na), use = "complete.obs", method = "spearman")
```

```{r}
cor(as.matrix(l_blod_50_nnS_na), use = "complete.obs", method = "spearman")
cor(as.matrix(s_blod_50_nnS_na), use = "complete.obs", method = "spearman")
```

### Viz

```{r}
plotall %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  #filter(Compare != "Original") %>% 
  # with and without Original
  mutate(Compare = fct_relevel(Compare, "Low Rank Solution",
                            "Sparse Solution",
                            "Model Prediction",
                            "Original")) %>% 
  ggplot(aes(x = POP, y = Value)) + 
  geom_jitter(aes(color = Compare), alpha = 0.1, width = 0.3, height = 0) + 
  theme_bw() +
  geom_point(aes(y = LOD), shape = 3, size = 0.5) +
  facet_wrap(.~Percent) +
  labs(x = "POP", 
       y = "Solution Value",
       title = "Solution Values <LOD + Original Values") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, hjust = 1))

plotall %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  filter(Compare != "Original") %>% 
  # with and without Original
  mutate(Compare = fct_relevel(Compare, "Low Rank Solution",
                            "Sparse Solution",
                            "Model Prediction")) %>% 
  ggplot(aes(x = POP, y = Value)) + 
  geom_jitter(aes(color = Compare), alpha = 0.1, width = 0.3, height = 0) + 
  theme_bw() +
  geom_point(aes(y = LOD), shape = 3, size = 0.5) +
  facet_wrap(.~Percent) +
  labs(x = "POP", 
       y = "Solution Value",
       title = "Solution Values <LOD") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
plotall %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  mutate(Value_SD = Value - LOD) %>%
  #filter(Compare != "Sparse Solution") %>% 
  ggplot(aes(x = Value)) + 
  geom_histogram(aes(fill = Compare, color = Compare), alpha = 0.25) + 
  theme_bw() +
  facet_wrap(.~Percent, scales = "free") +
  labs(x = "Solution Value", 
       y = "Density",
       title = "Values <LOD") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, hjust = 1))

plotall %>% 
  drop_na(.) %>% 
  filter(Compare != "Sparse Solution") %>% 
  select(-Original, -LOD) %>% 
  spread(key = Compare, value = Value) %>% 
  mutate(Sparse = `Model Prediction` - `Low Rank Solution`) %>% 
  summarise(max_sparse = max(Sparse),
            min_sparse = min(Sparse))
```

```{r}
plotall_nns %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  #filter(Compare != "Original") %>% 
  # with and without Original
  mutate(Compare = fct_relevel(Compare, "Low Rank Solution",
                            "Sparse Solution",
                            "Model Prediction",
                            "Original")) %>% 
  ggplot(aes(x = POP, y = Value)) + 
  geom_jitter(aes(color = Compare), alpha = 0.1, width = 0.3, height = 0) + 
  theme_bw() +
  geom_point(aes(y = LOD), shape = 3, size = 0.5) +
  facet_wrap(.~Percent) +
  labs(x = "POP", 
       y = "Solution Value",
       title = "nnS Solution Values <LOD + Original Values") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, hjust = 1))

plotall_nns %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  filter(Compare != "Original") %>% 
  # with and without Original
  mutate(Compare = fct_relevel(Compare, "Low Rank Solution",
                            "Sparse Solution",
                            "Model Prediction")) %>% 
  ggplot(aes(x = POP, y = Value)) + 
  geom_jitter(aes(color = Compare), alpha = 0.1, width = 0.3, height = 0) + 
  theme_bw() +
  geom_point(aes(y = LOD), shape = 3, size = 0.5) +
  facet_wrap(.~Percent) +
  labs(x = "POP", 
       y = "Solution Value",
       title = "nnS Solution Values <LOD") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
plotall_nns %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  #filter(Compare != "Sparse Solution") %>% 
  ggplot(aes(x = Value)) + 
  geom_histogram(aes(fill = Compare, color = Compare), alpha = 0.25) + 
  theme_bw() +
  facet_wrap(.~Percent, scales = "free") +
  labs(x = "Solution Value", 
       y = "Count",
       title = "nnS Solution Values <LOD + Original Values") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, hjust = 1))
```