---
title: "Independent Sims"
author: "Lizzy Gibson"
date: "6/09/2020"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    toc_depth: 5
---

```{r setup, include=FALSE}
require("knitr")
opts_chunk$set(echo = FALSE, messages = FALSE)
options(scipen = 999)
library(R.matlab)
library(tidyverse)
library(gridExtra)
library(Matrix)
library(matconv)
library(patchwork)
library(janitor)
library(ggcorrplot)
library(ggfortify)  
library(factoextra)
library(knitr)
library(haven)
library(rlist)
library(mvtnorm)
library(reshape2)
library(GGally)
library(grDevices)
library(plotly)
library(Cairo)
```

## Simulate

```{r, scores}
# Simulate scores
seeds <- 1:10
sim_scores <- matrix(NA, nrow = 100, ncol = 10)
for (i in 1:length(seeds)) {
  set.seed(seeds[i])
  sim_scores[,i] <- exp(rnorm(100, mean = 1))
}

summary(sim_scores)
sim_scores <- as_tibble(sim_scores)
sim_scores
```

```{r, score_hist}
sim_scores %>%
  mutate(id = 1:nrow(.)) %>% 
  gather(key = pop, value = value, -id) %>% 
  ggplot(aes(x = value)) +
  geom_histogram() + facet_wrap(~pop) +
  theme_minimal()
```

```{r}
# Simulate 1 pattern
```


```{r, select, include=FALSE}
prop <- function (x) {1 - (sum(x, na.rm = TRUE)/nrow(nhanes))}

names <- nhanes %>% select(names(.)[grep("lc", names(.))]) %>% 
  summarize_all(prop) %>% select_if(~. > 0.8) %>% names() %>% str_sub(., 4, 6) %>% str_c("lbx", ., "la") %>% as.vector()

pops <- nhanes %>% 
  select(!!names) %>% na.omit(.)

names(pops) <- str_sub(names(pops), 1, 6)
names(pops) <- str_replace(names(pops), "lbxd", "D")
names(pops) <- str_replace(names(pops), "lbxf", "F")
names(pops) <- str_replace(names(pops), "lbx", "PCB")
pops

ggcorr(pops, method = c("everything", "spearman"), limits = FALSE,
       label = TRUE, label_size = 3, label_alpha = TRUE,
       hjust = 0.85, size = 3, color = "grey50", layout.exp = 1) + ggtitle("Persistent organic pollutants \n in NHANES 2001-2002")
```

```{r, sim1, include=FALSE}
# Vector of NHANES means
# log to approx normal dist
means <- as_vector(map(log(pops), function(x) mean(x, na.rm = TRUE)))

sim_chem <- matrix(NA, nrow = 100, ncol = 10)
for (i in 1:length(means)) {
  sim_chem[,i] <- exp(rnorm(100, mean = means[i]))
  
}
summary(sim_chem)
colnames(sim_chem) <- colnames(pops)
sim_all <- as_tibble(sim_chem)
```

```{r, sim2, include=FALSE}
ggcorr(sim_all, method = c("everything", "spearman"), limits = FALSE,
       label = TRUE, label_size = 3, label_alpha = TRUE,
       hjust = 0.85, size = 3, color = "grey50", layout.exp = 1) + ggtitle("Simulated Data")
```

```{r, scale1, include=FALSE}
sim_all <- as_tibble(apply(sim_all, 2, scale, center = FALSE))
summary(sim_all)
```

```{r, scale2, include=FALSE}
sim_all %>%
  mutate(id = 1:nrow(.)) %>% 
  gather(key = pop, value = value, -id) %>% 
  ggplot(aes(x = value)) +
  geom_histogram() + facet_wrap(~pop) +
  theme_minimal()
```

```{r, neg, include=FALSE}
mix_data_lod_10 <- sim_all %>%
  mutate(F08 = ifelse(F08 < quantile(F08, probs = .10), -1, F08)) %>% as.matrix()
  
# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20 <- sim_all %>% 
  mutate(F08 = ifelse(F08 < quantile(F08, probs = .20), -1, F08)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30 <- sim_all %>% 
  mutate(F08 = ifelse(F08 < quantile(F08, probs = .30), -1, F08)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40 <- sim_all %>% 
  mutate(F08 = ifelse(F08 < quantile(F08, probs = .40), -1, F08)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50 <- sim_all %>% 
  mutate(F08 = ifelse(F08 < quantile(F08, probs = .50), -1, F08)) %>% as.matrix()

# Create version with 10% lowest values for each variable as below the LOD
mix_data_lod_10_sqrt2 <- sim_all %>% 
  mutate(F08 = ifelse(F08 < quantile(F08, probs = .10), (quantile(F08, probs = .10)/sqrt(2)), F08)) %>% as.matrix()

# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20_sqrt2 <- sim_all %>% 
  mutate(F08 = ifelse(F08 < quantile(F08, probs = .20), (quantile(F08, probs = .20)/sqrt(2)), F08)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30_sqrt2 <- sim_all %>% 
  mutate(F08 = ifelse(F08 < quantile(F08, probs = .30), (quantile(F08, probs = .30)/sqrt(2)), F08)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40_sqrt2 <- sim_all %>% 
  mutate(F08 = ifelse(F08 < quantile(F08, probs = .40), (quantile(F08, probs = .40)/sqrt(2)), F08)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50_sqrt2 <- sim_all %>% 
  mutate(F08 = ifelse(F08 < quantile(F08, probs = .50), (quantile(F08, probs = .50)/sqrt(2)), F08)) %>% as.matrix()
```

```{r, quant, include=FALSE}
delta10 <- c(rep(0, times = 6), quantile(sim_all$F08, probs = 0.10), 0, 0)

delta20 <- c(rep(0, times = 6), quantile(sim_all$F08, probs = 0.20), 0, 0)

delta30 <- c(rep(0, times = 6), quantile(sim_all$F08, probs = 0.30), 0, 0)

delta40 <- c(rep(0, times = 6), quantile(sim_all$F08, probs = 0.40), 0, 0)

delta50 <- c(rep(0, times = 6), quantile(sim_all$F08, probs = 0.50), 0, 0)
```

```{r, lod_function, include=FALSE}
prox_l1 <- function(Y, c) {
  
  myzero <- matrix(data = 0, ncol = ncol(Y), nrow = nrow(Y))
  X <- sign(Y) * pmax(abs(Y) - c, myzero, na.rm = TRUE)
  X
} 

############################################################

prox_nuclear <- function(Y, c) {
  
  USV <- svd(Y)
  U <- USV$u
  S <- USV$d
  V <- USV$v
  
  myzero <- vector("numeric", length = length(S))
  S_new <- sign(S) * pmax(abs(S) - c, myzero, na.rm = TRUE)
  X <- U %*% diag(S_new) %*% t(V)
  nuclearX  <- sum(abs(S_new))

    list(X = X, nuclearX = nuclearX)
}

############################################################

is_same <- function(SAME_THRESH, ...) {
  flag <- TRUE
  varargin <- list(...)
  if (length(varargin) == 2) {
    if (max(abs(varargin[[1]] - varargin[[2]])) > SAME_THRESH) {
      flag <- FALSE
    }
  }
  else if (length(varargin) == 3) {
    if ((max(abs(varargin[[1]] - varargin[[2]])) > SAME_THRESH) |
        (max(abs(varargin[[1]] - varargin[[3]])) > SAME_THRESH) |
        (max(abs(varargin[[2]] - varargin[[3]])) > SAME_THRESH)) {
      flag <- FALSE
    }
  }
  flag
}

############################################################

loss_lod <- function(X, D, LOD) {

    X_lod <- ((X - D)     * (D >= 0)) +
             ((X - LOD)   * (D < 0 & (X > LOD))) +
              (X          * (D < 0 & X < 0))
  
  l <- sum(X_lod^2) / 2
  l
}

############################################################

pcp_lod <- function(D, lambda, mu, LOD) {
  
  m <- nrow(D)
  n <- ncol(D)
  rho <- 1 # Augmented Lagrangian coefficient (rate)
  
  L1 <- matrix(0, m, n)
  L2 <- matrix(0, m, n)
  L3 <- matrix(0, m, n)
  
  S1 <- matrix(0, m, n)
  S2 <- matrix(0, m, n)
  
  Z1 <- matrix(0, m, n)
  Z2 <- matrix(0, m, n)
  Z3 <- matrix(0, m, n)
  
  # Max iteration
  MAX_ITER <- 5000
  
  # Convergence Thresholds
  LOSS_THRESH <- 1e-5
  SAME_THRESH <- 1e-4
  
  if (is.vector(LOD)) {
    empty = matrix(1, nrow = nrow(D), ncol = ncol(D))
    LOD = t(t(empty) * LOD)
  }
  
  loss <- vector("numeric", MAX_ITER)
  
  for (i in 1:MAX_ITER) {
    
    nuc <- prox_nuclear( ((L2 + L3 - (Z1 + Z2)/rho)/2), 1/2/rho)
    L1 <- nuc[[1]]
    nuclearL1 <- nuc[[2]] #nuclearX
    
    S1 <- prox_l1((S2 - Z3/rho), lambda/rho)
    
      L2_opt1 <- (mu*rho*D     + (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)
      L2_opt2 <- L1 + Z1/rho
      L2_opt3 <- ((mu*rho*LOD + (((mu + rho)*Z1) - (mu*Z3) + ((mu + rho)*rho*L1) - (mu*rho*S1)))) / ((2*mu*rho) + (rho^2))
      L2_opt4 <- (               (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)

      L2_new <- (L2_opt1 * (D >= 0)) +
        (L2_opt2 * ((D < 0) & (((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
        (L2_opt3 * ((D < 0) & (((L2 + S2) > LOD)))) +
        (L2_opt4 * ((D < 0) & (((L2 + S2) < 0))))

      S2_opt1 <- (mu*rho*D     + (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)
      S2_opt2 <- S1 + (Z3/rho)
      S2_opt3 <- (((mu*rho*LOD) + (((mu + rho)*Z3) - (mu*Z1) + ((mu + rho)*rho*S1) - (mu*rho*L1)))) / ((2*mu*rho) + (rho^2))
      S2_opt4 <- (               (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)

      S2 <- (S2_opt1 * (D >= 0)) +
        (S2_opt2 * (((D < 0) & ((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
        (S2_opt3 * (((D < 0) & ((L2 + S2) > LOD)))) +
        (S2_opt4 * (((D < 0) & ((L2 + S2) < 0))))
   
    L2 <- L2_new
    
    L3 <- pmax(L1 + Z2/rho, 0, na.rm = TRUE)
    # % Non-Negativity constraint!
    
    Z1 <- Z1 + rho*(L1 - L2)
    Z2 <- Z2 + rho*(L1 - L3)
    Z3 <- Z3 + rho*(S1 - S2)
    # % Z accumulate differnces between L and L and between S and S
    
    loss[i] <- nuclearL1 + 
      (lambda*sum(abs(S1))) +
      (mu*loss_lod((L2 + S2), D, LOD)) +
      sum(Z1*(L1 - L2)) +
      sum(Z2*(L1 - L3)) +
      sum(Z3*(S1 - S2)) +
      (rho/2 * (sum((L1-L2)^2) + sum((L1 - L3)^2) + sum((S1 - S2)^2)))
    # % The code block above takes LOD into account.
    
    print(str_c(i, " Obj: ", loss[i]))
        
    if ((i != 1) && 
        (abs(loss[i-1] - loss[i]) < LOSS_THRESH) && 
        is_same(SAME_THRESH, L1, L2, L3) &&
        is_same(SAME_THRESH, S1, S2)) {
      break} # % Convergence criteria!
  }
  
  L <- L3 # (L1 + L2 + L3) / 3
  S <- S1 #(S1 + S2) / 2
  list(L = L, S = S, loss = loss)
}
```

```{r, old_function, include=FALSE}
soft_thresholding <- function(v, lambda) {
  myzero <- matrix(data = 0, ncol = ncol(v), nrow = nrow(v))
  w <- sign(v) * pmax(abs(v) - lambda, myzero)
  w
} 

soft_thresholding_diag <- function(v, lambda) {
  myzero <- vector("numeric", length = length(v))
  w <- sign(v) * pmax(abs(v) - lambda, myzero)
  w
} 

singular_value_threshold <- function(M, lambda) {
  
  USV <- svd(M)
  U <- USV$u
  S <- USV$d
  V <- USV$v
    
  N <- U %*% diag(soft_thresholding_diag(S, lambda)) %*% t(V)
  
  v  <- sum(soft_thresholding_diag(S, lambda))
  
  svt <- list(N = N, v = v) 
  svt
}

original_pcp <- function(D, lambda, mu) {
  
  m <- nrow(D)
  n <- ncol(D)
  
  S <- matrix(0, nrow = m, ncol = n)
  L <- matrix(0, nrow = m, ncol = n)
  
  iter <- 0
  MAX_ITER <- 5000
  done <- FALSE
  
  # Convergence Thresholds
  LOSS_THRESH <- 1e-4
  loss <- vector("numeric", MAX_ITER)
  
  while (!done) {
    
    iter <- iter + 1
    
    svt <- singular_value_threshold((D - S), 1/mu)
    L <- svt[[1]] #svt$N
    v <- svt[[2]]
    
    S <- soft_thresholding((D - L), lambda/mu)
    
    obj <- v + lambda * sum(abs(S)) + (mu/2) * norm((D - L - S), type = "F")^2
    loss[iter] <- obj
    
    print(str_c(iter, " Obj: ", obj))
    
    if (iter >= MAX_ITER | 
        (iter != 1) && (abs(loss[iter-1] - loss[iter]) < LOSS_THRESH)) {done <- TRUE}
    
  }
  list(L = L, S = S, Lambda = lambda, Mu = mu, obj_value = obj)
}
```

```{r, nns_function, include=FALSE}
pcp_lod_nnS <- function(D, lambda, mu, LOD) {
  
  m <- nrow(D)
  n <- ncol(D)
  rho <- 1 # Augmented Lagrangian coefficient (rate)
  
  L1 <- matrix(0, m, n)
  L2 <- matrix(0, m, n)
  L3 <- matrix(0, m, n)
  
  S1 <- matrix(0, m, n)
  S2 <- matrix(0, m, n)
  S3 <- matrix(0, m, n) # ADDED
  
  Z1 <- matrix(0, m, n)
  Z2 <- matrix(0, m, n)
  Z3 <- matrix(0, m, n)
  Z4 <- matrix(0, m, n) # ADDED
  
  # Max iteration
  MAX_ITER <- 5000
  
  # Convergence Thresholds
  LOSS_THRESH <- 1e-5
  SAME_THRESH <- 1e-4
  
  if (is.vector(LOD)) {
  #tf = ifelse(D < 0, TRUE, FALSE)
  #LOD = t(t(tf) * LOD)
    empty = matrix(1, nrow = nrow(D), ncol = ncol(D))
    LOD = t(t(empty) * LOD)
    }
  
  loss <- vector("numeric", MAX_ITER)
  
  for (i in 1:MAX_ITER) {
    
    nuc <- prox_nuclear(((L2 + L3 - (Z1 + Z2)/rho)/2), 1/2/rho)
    L1 <- nuc[[1]]
    nuclearL1 <- nuc[[2]] #nuclearX
    
    S1 <- prox_l1(((S2 + S3 - (Z3 + Z4)/rho)/2), lambda/rho) # ADDED
      #prox_l1(S2 - Z3/rho, lambda/rho)
    
    L2_opt1 <- (mu*rho*D     + (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)
    L2_opt2 <- L1 + Z1/rho
    L2_opt3 <- ((mu*rho*LOD + (((mu + rho)*Z1) - (mu*Z3) + ((mu + rho)*rho*L1) - (mu*rho*S1)))) / ((2*mu*rho) + (rho^2))
    L2_opt4 <- (               (mu + rho)*Z1 - mu*Z3 + (mu + rho)*rho*L1 - mu*rho*S1) / (2*mu*rho + rho^2)

    L2 <- (L2_opt1 * (D >= 0)) +
        (L2_opt2 * ((D < 0) & (((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
        (L2_opt3 * ((D < 0) & (((L2 + S2) > LOD)))) +
        (L2_opt4 * ((D < 0) & (((L2 + S2) < 0))))

    S2_opt1 <- (mu*rho*D     + (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)
    S2_opt2 <- S1 + (Z3/rho)
    S2_opt3 <- (((mu*rho*LOD) + (((mu + rho)*Z3) - (mu*Z1) + ((mu + rho)*rho*S1) - (mu*rho*L1)))) / ((2*mu*rho) + (rho^2))
    S2_opt4 <- (               (mu + rho)*Z3 - (mu*Z1) + (mu + rho)*rho*S1 - mu*rho*L1) / (2*mu*rho + rho^2)

    S2 <- (S2_opt1 * (D >= 0)) +
        (S2_opt2 * (((D < 0) & ((L2 + S2) >= 0) & ((L2 + S2) <= LOD)))) +
        (S2_opt3 * (((D < 0) & ((L2 + S2) > LOD)))) +
        (S2_opt4 * (((D < 0) & ((L2 + S2) < 0))))
      
    L3 <- pmax(L1 + Z2/rho, 0, na.rm = TRUE)
    # % Non-Negativity constraint!
    
    ## ADDED
    S3 <- pmax(S1 + Z4/rho, 0, na.rm = TRUE)
    
    Z1 <- Z1 + rho*(L1 - L2)
    Z2 <- Z2 + rho*(L1 - L3)
    Z3 <- Z3 + rho*(S1 - S2)
    Z4 <- Z4 + rho*(S1 - S3) # ADDED
    # % Z accumulate differnces between L and L and between S and S
    
    loss[i] <- nuclearL1 + 
      (lambda*sum(abs(S1))) +
      (mu*loss_lod((L2 + S2), D, LOD)) +
      sum(Z1*(L1 - L2)) +
      sum(Z2*(L1 - L3)) +
      sum(Z3*(S1 - S2)) +
      sum(Z4*(S1 - S3)) + # ADDED
      (rho/2 * (sum((L1-L2)^2) + sum((L1 - L3)^2) + sum((S1 - S2)^2)) + sum((S1 - S3)^2)) # ADDED
    # % The code block above takes LOD into account.
    
    print(str_c(i, " Obj: ", loss[i]))
        
    if ((i != 1) && 
        (abs(loss[i-1] - loss[i]) < LOSS_THRESH) && 
        is_same(SAME_THRESH, L1, L2, L3) &&
        is_same(SAME_THRESH, S1, S2, S3)) { # ADDED
      break} # % Convergence criteria!
  }
  
  L <- L3 #(L1 + L2 + L3) / 3
  S <- S3 #(S1 + S2 + S3) / 3
  list(L = L, S = S, loss = loss)
}
```

```{r, jingkai_leave, include=FALSE, cache = TRUE}
m <- nrow(sim_all)
p <- ncol(sim_all)

lambda_mix <- 1/sqrt(m)
mu_mix <- sqrt(p/(2*log(m*p)))

mix <- as.matrix(sim_all)
  
results_0  <- pcp_lod(mix,             lambda_mix, mu_mix, 0)
results_10 <- pcp_lod(mix_data_lod_10, lambda_mix, mu_mix, delta10)
results_20 <- pcp_lod(mix_data_lod_20, lambda_mix, mu_mix, delta20)
results_30 <- pcp_lod(mix_data_lod_30, lambda_mix, mu_mix, delta30)
results_40 <- pcp_lod(mix_data_lod_40, lambda_mix, mu_mix, delta40)
results_50 <- pcp_lod(mix_data_lod_50, lambda_mix, mu_mix, delta50)

L_lod0 <- results_0[[1]]
S_lod0 <- results_0[[2]]
L_lod10 <- results_10[[1]]
S_lod10 <- results_10[[2]]
L_lod20 <- results_20[[1]]
S_lod20 <- results_20[[2]]
L_lod30 <- results_30[[1]]
S_lod30 <- results_30[[2]]
L_lod40 <- results_40[[1]]
S_lod40 <- results_40[[2]]
L_lod50 <- results_50[[1]]
S_lod50 <- results_50[[2]]
```

```{r, nns, include=FALSE, cache = TRUE}
results_0_nnS  <- pcp_lod_nnS(mix,             lambda_mix, mu_mix, 0)
results_10_nnS <- pcp_lod_nnS(mix_data_lod_10, lambda_mix, mu_mix, delta10)
results_20_nnS <- pcp_lod_nnS(mix_data_lod_20, lambda_mix, mu_mix, delta20)
results_30_nnS <- pcp_lod_nnS(mix_data_lod_30, lambda_mix, mu_mix, delta30)
results_40_nnS <- pcp_lod_nnS(mix_data_lod_40, lambda_mix, mu_mix, delta40)
results_50_nnS <- pcp_lod_nnS(mix_data_lod_50, lambda_mix, mu_mix, delta50)

L_lod0_nnS <- results_0_nnS[[1]]
S_lod0_nnS <- results_0_nnS[[2]]
L_lod10_nnS <- results_10_nnS[[1]]
S_lod10_nnS <- results_10_nnS[[2]]
L_lod20_nnS <- results_20_nnS[[1]]
S_lod20_nnS <- results_20_nnS[[2]]
L_lod30_nnS <- results_30_nnS[[1]]
S_lod30_nnS <- results_30_nnS[[2]]
L_lod40_nnS <- results_40_nnS[[1]]
S_lod40_nnS <- results_40_nnS[[2]]
L_lod50_nnS <- results_50_nnS[[1]]
S_lod50_nnS <- results_50_nnS[[2]]
```

```{r, original, include=FALSE, cache = TRUE}
results_0_sqrt2  <- original_pcp(mix,                   lambda_mix, mu_mix)
results_10_sqrt2 <- original_pcp(mix_data_lod_10_sqrt2, lambda_mix, mu_mix)
results_20_sqrt2 <- original_pcp(mix_data_lod_20_sqrt2, lambda_mix, mu_mix)
results_30_sqrt2 <- original_pcp(mix_data_lod_30_sqrt2, lambda_mix, mu_mix)
results_40_sqrt2 <- original_pcp(mix_data_lod_40_sqrt2, lambda_mix, mu_mix)
results_50_sqrt2 <- original_pcp(mix_data_lod_50_sqrt2, lambda_mix, mu_mix)

L_lod0_sqrt2 <- results_0_sqrt2[[1]]
S_lod0_sqrt2 <- results_0_sqrt2[[2]]
L_lod10_sqrt2 <- results_10_sqrt2[[1]]
S_lod10_sqrt2 <- results_10_sqrt2[[2]]
L_lod20_sqrt2 <- results_20_sqrt2[[1]]
S_lod20_sqrt2 <- results_20_sqrt2[[2]]
L_lod30_sqrt2 <- results_30_sqrt2[[1]]
S_lod30_sqrt2 <- results_30_sqrt2[[2]]
L_lod40_sqrt2 <- results_40_sqrt2[[1]]
S_lod40_sqrt2 <- results_40_sqrt2[[2]]
L_lod50_sqrt2 <- results_50_sqrt2[[1]]
S_lod50_sqrt2 <- results_50_sqrt2[[2]]
```

## X - L - S

```{r, xls, include=FALSE}
F_norm <- as_tibble(cbind(`0%` = norm((mix - L_lod0 - S_lod0), type = "F")/norm((mix), type = "F"),
      `10%` = norm((mix - L_lod10 - S_lod10), type = "F")/norm((mix), type = "F"),
      `20%` = norm((mix - L_lod20 - S_lod20), type = "F")/norm((mix), type = "F"),
      `30%` = norm((mix - L_lod30 - S_lod30), type = "F")/norm((mix), type = "F"),
      `40%` = norm((mix - L_lod40 - S_lod40), type = "F")/norm((mix), type = "F"),
      `50%` = norm((mix - L_lod50 - S_lod50), type = "F")/norm((mix), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "LOD PCP")

F_norm_sqrt2 <- as_tibble(cbind(`0%` = norm((mix - L_lod0_sqrt2 - S_lod0_sqrt2), type = "F")/norm((mix), type = "F"),
      `10%` = norm((mix - L_lod10_sqrt2 - S_lod10_sqrt2), type = "F")/norm((mix), type = "F"),
      `20%` = norm((mix - L_lod20_sqrt2 - S_lod20_sqrt2), type = "F")/norm((mix), type = "F"),
      `30%` = norm((mix - L_lod30_sqrt2 - S_lod30_sqrt2), type = "F")/norm((mix), type = "F"),
      `40%` = norm((mix - L_lod40_sqrt2 - S_lod40_sqrt2), type = "F")/norm((mix), type = "F"),
      `50%` = norm((mix - L_lod50_sqrt2 - S_lod50_sqrt2), type = "F")/norm((mix), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))

F_norm_nnS <- as_tibble(cbind(`0%` = norm((mix - L_lod0_nnS - S_lod0_nnS), type = "F")/norm((mix), type = "F"),
      `10%` = norm((mix - L_lod10_nnS - S_lod10_nnS), type = "F")/norm((mix), type = "F"),
      `20%` = norm((mix - L_lod20_nnS - S_lod20_nnS), type = "F")/norm((mix), type = "F"),
      `30%` = norm((mix - L_lod30_nnS - S_lod30_nnS), type = "F")/norm((mix), type = "F"),
      `40%` = norm((mix - L_lod40_nnS - S_lod40_nnS), type = "F")/norm((mix), type = "F"),
      `50%` = norm((mix - L_lod50_nnS - S_lod50_nnS), type = "F")/norm((mix), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "LOD PCP nnS")
```

* X = simulated dataset
* L = low rank solution matrix
* S = sparse solution matrix

```{r, fig.align = "center"}
rbind(F_norm_sqrt2, F_norm, F_norm_nnS) %>% ggplot(aes(x = percent_blod, y = norm)) + 
  geom_point(aes(color = Method)) + geom_path(aes(group = Method, color = Method)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(X-L-S) / norm(X)",
       title = "Relative Prediction Error")
```

## Individual Solution Matrices

```{r, ind, include=FALSE}
L_diff <- as_tibble(cbind(`0%` = norm((L_lod0 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      `10%` = norm((L_lod10 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      `20%` = norm((L_lod20 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      `30%` = norm((L_lod30 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      `40%` = norm((L_lod40 - L_lod0), type = "F")/norm((L_lod0), type = "F"),
      `50%` = norm((L_lod50 - L_lod0), type = "F")/norm((L_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank",
         Method = "LOD PCP")

S_diff <- as_tibble(cbind(`0%` = norm((S_lod0 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      `10%` = norm((S_lod10 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      `20%` = norm((S_lod20 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      `30%` = norm((S_lod30 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      `40%` = norm((S_lod40 - S_lod0), type = "F")/norm((S_lod0), type = "F"),
      `50%` = norm((S_lod50 - S_lod0), type = "F")/norm((S_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse",
         Method = "LOD PCP")

L_diff_sqrt2 <- as_tibble(cbind(`0%` = norm((L_lod0_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"),
      `10%` = norm((L_lod10_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"),
      `20%` = norm((L_lod20_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"),
      `30%` = norm((L_lod30_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"),
      `40%` = norm((L_lod40_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"),
      `50%` = norm((L_lod50_sqrt2 - L_lod0_sqrt2), type = "F")/norm((L_lod0_sqrt2), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank",
         Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))

S_diff_sqrt2 <- as_tibble(cbind(`0%` = norm((S_lod0_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"),
      `10%` = norm((S_lod10_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"),
      `20%` = norm((S_lod20_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"),
      `30%` = norm((S_lod30_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"),
      `40%` = norm((S_lod40_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"),
      `50%` = norm((S_lod50_sqrt2 - S_lod0_sqrt2), type = "F")/norm((S_lod0_sqrt2), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse",
         Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))

L_diff_nnS <- as_tibble(cbind(`0%` = norm((L_lod0_nnS - L_lod0_nnS), type = "F")/norm((L_lod0_nnS), type = "F"),
      `10%` = norm((L_lod10_nnS - L_lod0_nnS), type = "F")/norm((L_lod0_nnS), type = "F"),
      `20%` = norm((L_lod20_nnS - L_lod0_nnS), type = "F")/norm((L_lod0_nnS), type = "F"),
      `30%` = norm((L_lod30_nnS - L_lod0_nnS), type = "F")/norm((L_lod0_nnS), type = "F"),
      `40%` = norm((L_lod40_nnS - L_lod0_nnS), type = "F")/norm((L_lod0_nnS), type = "F"),
      `50%` = norm((L_lod50_nnS - L_lod0_nnS), type = "F")/norm((L_lod0_nnS), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Low-Rank",
         Method = "LOD PCP nnS")

S_diff_nnS <- as_tibble(cbind(`0%` = norm((S_lod0_nnS - S_lod0_nnS), type = "F")/norm((S_lod0_nnS), type = "F"),
      `10%` = norm((S_lod10_nnS - S_lod0_nnS), type = "F")/norm((S_lod0_nnS), type = "F"),
      `20%` = norm((S_lod20_nnS - S_lod0_nnS), type = "F")/norm((S_lod0_nnS), type = "F"),
      `30%` = norm((S_lod30_nnS - S_lod0_nnS), type = "F")/norm((S_lod0_nnS), type = "F"),
      `40%` = norm((S_lod40_nnS - S_lod0_nnS), type = "F")/norm((S_lod0_nnS), type = "F"),
      `50%` = norm((S_lod50_nnS - S_lod0_nnS), type = "F")/norm((S_lod0_nnS), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Matrix = "Sparse",
         Method = "LOD PCP nnS")
```

* Reference is solution matix with 0\% \<LOD  
* Low rank solution matrices compared with low rank solution with 0\% \<LOD
* Sparse solution matrices compared with sparse solution with 0\% \<LOD

```{r, fig.align = "center"}
rbind(L_diff_sqrt2, S_diff_sqrt2,
      L_diff, S_diff,
      L_diff_nnS, S_diff_nnS) %>%
  ggplot(aes(x = percent_blod, y = norm, group = interaction(Matrix,Method), color = Method)) + 
  geom_point() + geom_path(aes(linetype = Matrix)) + theme_bw() +
  labs(x = "Percent Below LOD", y = "norm(difference) / norm(lod0))",
       title = "Relative Error in Solution Matrices")
```

## Values \<LOD vs \>LOD

```{r, delt_0, include=FALSE}
mix_data_lod_10_0 <- sim_all %>%
  mutate(F08 = ifelse(F08 < quantile(F08, probs = .10), 0, F08)) %>% as.matrix()
  
# Create version with 20% lowest values for each variable as below the LOD
mix_data_lod_20_0 <- sim_all %>% 
  mutate(F08 = ifelse(F08 < quantile(F08, probs = .20), 0, F08)) %>% as.matrix()

# Create version with 30% lowest values for each variable as below the LOD
mix_data_lod_30_0 <- sim_all %>% 
  mutate(F08 = ifelse(F08 < quantile(F08, probs = .30), 0, F08)) %>% as.matrix()

# Create version with 40% lowest values for each variable as below the LOD
mix_data_lod_40_0 <- sim_all %>% 
  mutate(F08 = ifelse(F08 < quantile(F08, probs = .40), 0, F08)) %>% as.matrix()

# Create version with 50% lowest values for each variable as below the LOD
mix_data_lod_50_0 <- sim_all %>% 
  mutate(F08 = ifelse(F08 < quantile(F08, probs = .50), 0, F08)) %>% as.matrix()
```

```{r, above_below, include=FALSE}
# BELOW LOD
# TRUE = <LOD
tf_lod_0 <- sim_all %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_0 <- as.matrix(tf_lod_0*L_lod0)
s_blod_0 <- as.matrix(tf_lod_0*S_lod0)
blod_0 <- as.matrix(sim_all*tf_lod_0)

tf_lod_10 <- mix_data_lod_10 %>% 
  as_tibble() %>%
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_10 <- as.matrix(tf_lod_10*L_lod10)
s_blod_10 <- as.matrix(tf_lod_10*S_lod10)
blod_10 <- as.matrix(sim_all*tf_lod_10)

tf_lod_20 <- mix_data_lod_20 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_20 <- as.matrix(tf_lod_20*L_lod20)
s_blod_20 <- as.matrix(tf_lod_20*S_lod20)
blod_20 <- as.matrix(sim_all*tf_lod_20)

tf_lod_30 <- mix_data_lod_30 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_30 <- as.matrix(tf_lod_30*L_lod30)
s_blod_30 <- as.matrix(tf_lod_30*S_lod30)
blod_30 <- as.matrix(sim_all*tf_lod_30)

tf_lod_40 <- mix_data_lod_40 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_40 <- as.matrix(tf_lod_40*L_lod40)
s_blod_40 <- as.matrix(tf_lod_40*S_lod40)
blod_40 <- as.matrix(sim_all*tf_lod_40)

tf_lod_50 <- mix_data_lod_50 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, FALSE))
l_blod_50 <- as.matrix(tf_lod_50*L_lod50)
s_blod_50 <- as.matrix(tf_lod_50*S_lod50)
blod_50 <- as.matrix(sim_all*tf_lod_50) 

#Subtract true values and divide by norm of true
less_diff <- as_tibble(cbind(`0%` = norm((blod_0 - l_blod_0 - s_blod_0), type = "F"), #/norm((mix), type = "F"),
      `10%` = norm((blod_10 - l_blod_10 - s_blod_10), type = "F")/norm((blod_10), type = "F"),
      `20%` = norm((blod_20 - l_blod_20 - s_blod_20), type = "F")/norm((blod_20), type = "F"),
      `30%` = norm((blod_30 - l_blod_30 - s_blod_30), type = "F")/norm((blod_30), type = "F"),
      `40%` = norm((blod_40 - l_blod_40 - s_blod_40), type = "F")/norm((blod_40), type = "F"),
      `50%` = norm((blod_50 - l_blod_50 - s_blod_50), type = "F")/norm((blod_50), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "< LOD",
         Method = "LOD PCP")

l_above_blod_0 <- as.matrix((!tf_lod_0)*L_lod0)
s_above_blod_0 <- as.matrix((!tf_lod_0)*S_lod0)

l_above_blod_10 <- as.matrix((!tf_lod_10)*L_lod10)
s_above_blod_10 <- as.matrix((!tf_lod_10)*S_lod10)

l_above_blod_20 <- as.matrix((!tf_lod_20)*L_lod20)
s_above_blod_20 <- as.matrix((!tf_lod_20)*S_lod20)

l_above_blod_30 <- as.matrix((!tf_lod_30)*L_lod30)
s_above_blod_30 <- as.matrix((!tf_lod_30)*S_lod30)

l_above_blod_40 <- as.matrix((!tf_lod_40)*L_lod40)
s_above_blod_40 <- as.matrix((!tf_lod_40)*S_lod40)

l_above_blod_50 <- as.matrix((!tf_lod_50)*L_lod50)
s_above_blod_50 <- as.matrix((!tf_lod_50)*S_lod50)

#divide by true values
# mix_data_lod_##_0 datasets replaced <LOD with zero, so use them as reference for >LOD
above_diff <- as_tibble(cbind(
  `0%`  = norm((mix  - l_above_blod_0  - s_above_blod_0),  type = "F")/norm(mix,  type = "F"),
  `10%` = norm((mix_data_lod_10_0 - l_above_blod_10 - s_above_blod_10), type = "F")/norm(mix_data_lod_10_0, type = "F"),
  `20%` = norm((mix_data_lod_20_0 - l_above_blod_20 - s_above_blod_20), type = "F")/norm(mix_data_lod_20_0, type = "F"),
  `30%` = norm((mix_data_lod_30_0 - l_above_blod_30 - s_above_blod_30), type = "F")/norm(mix_data_lod_30_0, type = "F"),
  `40%` = norm((mix_data_lod_40_0 - l_above_blod_40 - s_above_blod_40), type = "F")/norm(mix_data_lod_40_0, type = "F"),
  `50%` = norm((mix_data_lod_50_0 - l_above_blod_50 - s_above_blod_50), type = "F")/norm(mix_data_lod_50_0, type = "F"))) %>%
  gather(percent_blod, norm) %>% 
  mutate(Values = "> LOD",
         Method = "LOD PCP")

L_blod_0_sqrt2 <- as.matrix(tf_lod_0*L_lod0_sqrt2)
S_blod_0_sqrt2 <- as.matrix(tf_lod_0*S_lod0_sqrt2)

L_blod_10_sqrt2 <- as.matrix(tf_lod_10*L_lod10_sqrt2)
S_blod_10_sqrt2 <- as.matrix(tf_lod_10*S_lod10_sqrt2)

L_blod_20_sqrt2 <- as.matrix(tf_lod_20*L_lod20_sqrt2)
S_blod_20_sqrt2 <- as.matrix(tf_lod_20*S_lod20_sqrt2)

L_blod_30_sqrt2 <- as.matrix(tf_lod_30*L_lod30_sqrt2)
S_blod_30_sqrt2 <- as.matrix(tf_lod_30*S_lod30_sqrt2)

L_blod_40_sqrt2 <- as.matrix(tf_lod_40*L_lod40_sqrt2)
S_blod_40_sqrt2 <- as.matrix(tf_lod_40*S_lod40_sqrt2)

L_blod_50_sqrt2 <- as.matrix(tf_lod_50*L_lod50_sqrt2)
S_blod_50_sqrt2 <- as.matrix(tf_lod_50*S_lod50_sqrt2)

less_diff_sqrt2 <- as_tibble(
  cbind(`0%`  = norm((blod_0  - L_blod_0_sqrt2  - S_blod_0_sqrt2),  type = "F"), #/norm((blod_0), type = "F"),
        `10%` = norm((blod_10 - L_blod_10_sqrt2 - S_blod_10_sqrt2), type = "F")/norm((blod_10), type = "F"),
        `20%` = norm((blod_20 - L_blod_20_sqrt2 - S_blod_20_sqrt2), type = "F")/norm((blod_20), type = "F"),
        `30%` = norm((blod_30 - L_blod_30_sqrt2 - S_blod_30_sqrt2), type = "F")/norm((blod_30), type = "F"),
        `40%` = norm((blod_40 - L_blod_40_sqrt2 - S_blod_40_sqrt2), type = "F")/norm((blod_40), type = "F"),
        `50%` = norm((blod_50 - L_blod_50_sqrt2 - S_blod_50_sqrt2), type = "F")/norm((blod_50), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "< LOD",
         Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))

L_above_blod_0_sqrt2 <- as.matrix((!tf_lod_0)*L_lod0_sqrt2)
S_above_blod_0_sqrt2 <- as.matrix((!tf_lod_0)*S_lod0_sqrt2)

L_above_blod_10_sqrt2 <- as.matrix((!tf_lod_10)*L_lod10_sqrt2)
S_above_blod_10_sqrt2 <- as.matrix((!tf_lod_10)*S_lod10_sqrt2)

L_above_blod_20_sqrt2 <- as.matrix((!tf_lod_20)*L_lod20_sqrt2)
S_above_blod_20_sqrt2 <- as.matrix((!tf_lod_20)*S_lod20_sqrt2)

L_above_blod_30_sqrt2 <- as.matrix((!tf_lod_30)*L_lod30_sqrt2)
S_above_blod_30_sqrt2 <- as.matrix((!tf_lod_30)*S_lod30_sqrt2)

L_above_blod_40_sqrt2 <- as.matrix((!tf_lod_40)*L_lod40_sqrt2)
S_above_blod_40_sqrt2 <- as.matrix((!tf_lod_40)*S_lod40_sqrt2)

L_above_blod_50_sqrt2 <- as.matrix((!tf_lod_50)*L_lod50_sqrt2)
S_above_blod_50_sqrt2 <- as.matrix((!tf_lod_50)*S_lod50_sqrt2)

#divide by true values
above_diff_sqrt2 <- as_tibble(cbind(
  `0%`  = norm((mix  - L_above_blod_0_sqrt2  - S_above_blod_0_sqrt2),  type = "F")/norm(mix,  type = "F"),
  `10%` = norm((mix_data_lod_10_0 - L_above_blod_10_sqrt2 - S_above_blod_10_sqrt2), type = "F")/norm(mix_data_lod_10_0, type = "F"),
  `20%` = norm((mix_data_lod_20_0 - L_above_blod_20_sqrt2 - S_above_blod_20_sqrt2), type = "F")/norm(mix_data_lod_20_0, type = "F"),
  `30%` = norm((mix_data_lod_30_0 - L_above_blod_30_sqrt2 - S_above_blod_30_sqrt2), type = "F")/norm(mix_data_lod_30_0, type = "F"),
  `40%` = norm((mix_data_lod_40_0 - L_above_blod_40_sqrt2 - S_above_blod_40_sqrt2), type = "F")/norm(mix_data_lod_40_0, type = "F"),
  `50%` = norm((mix_data_lod_50_0 - L_above_blod_50_sqrt2 - S_above_blod_50_sqrt2), type = "F")/norm(mix_data_lod_50_0, type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "> LOD",
         Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))

l_above_blod_0_nnS <- as.matrix((!tf_lod_0)*L_lod0_nnS)
s_above_blod_0_nnS <- as.matrix((!tf_lod_0)*S_lod0_nnS)

l_above_blod_10_nnS <- as.matrix((!tf_lod_10)*L_lod10_nnS)
s_above_blod_10_nnS <- as.matrix((!tf_lod_10)*S_lod10_nnS)

l_above_blod_20_nnS <- as.matrix((!tf_lod_20)*L_lod20_nnS)
s_above_blod_20_nnS <- as.matrix((!tf_lod_20)*S_lod20_nnS)

l_above_blod_30_nnS <- as.matrix((!tf_lod_30)*L_lod30_nnS)
s_above_blod_30_nnS <- as.matrix((!tf_lod_30)*S_lod30_nnS)

l_above_blod_40_nnS <- as.matrix((!tf_lod_40)*L_lod40)
s_above_blod_40_nnS <- as.matrix((!tf_lod_40)*S_lod40)

l_above_blod_50_nnS <- as.matrix((!tf_lod_50)*L_lod50_nnS)
s_above_blod_50_nnS <- as.matrix((!tf_lod_50)*S_lod50_nnS)

#divide by true values
above_diff_nnS <- as_tibble(cbind(
  `0%`  = norm((mix  - l_above_blod_0_nnS  - s_above_blod_0_nnS),  type = "F")/
    norm(mix,  type = "F"),
  `10%` = norm((mix_data_lod_10_0 - l_above_blod_10_nnS - s_above_blod_10_nnS), type = "F")/
    norm(mix_data_lod_10_0, type = "F"),
  `20%` = norm((mix_data_lod_20_0 - l_above_blod_20_nnS - s_above_blod_20_nnS), type = "F")/
    norm(mix_data_lod_20_0, type = "F"),
  `30%` = norm((mix_data_lod_30_0 - l_above_blod_30_nnS - s_above_blod_30_nnS), type = "F")/
    norm(mix_data_lod_30_0, type = "F"),
  `40%` = norm((mix_data_lod_40_0 - l_above_blod_40_nnS - s_above_blod_40_nnS), type = "F")/
    norm(mix_data_lod_40_0, type = "F"),
  `50%` = norm((mix_data_lod_50_0 - l_above_blod_50_nnS - s_above_blod_50_nnS), type = "F")/
    norm(mix_data_lod_50_0, type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "> LOD",
         Method = "LOD PCP nnS")

l_blod_0_nnS <- as.matrix(tf_lod_0*L_lod0_nnS)
s_blod_0_nnS <- as.matrix(tf_lod_0*S_lod0_nnS)

l_blod_10_nnS <- as.matrix(tf_lod_10*L_lod10_nnS)
s_blod_10_nnS <- as.matrix(tf_lod_10*S_lod10_nnS)

l_blod_20_nnS <- as.matrix(tf_lod_20*L_lod20_nnS)
s_blod_20_nnS <- as.matrix(tf_lod_20*S_lod20_nnS)

l_blod_30_nnS <- as.matrix(tf_lod_30*L_lod30_nnS)
s_blod_30_nnS <- as.matrix(tf_lod_30*S_lod30_nnS)

l_blod_40_nnS <- as.matrix(tf_lod_40*L_lod40_nnS)
s_blod_40_nnS <- as.matrix(tf_lod_40*S_lod40_nnS)

l_blod_50_nnS <- as.matrix(tf_lod_50*L_lod50_nnS)
s_blod_50_nnS <- as.matrix(tf_lod_50*S_lod50_nnS)

#Subtract true values and divide by norm of true
less_diff_nnS <- as_tibble(cbind(`0%` = norm((blod_0 - l_blod_0_nnS - s_blod_0_nnS), type = "F"), #/norm((mix), type = "F"),
      `10%` = norm((blod_10 - l_blod_10_nnS - s_blod_10_nnS), type = "F")/
        norm((blod_10), type = "F"),
      `20%` = norm((blod_20 - l_blod_20_nnS - s_blod_20_nnS), type = "F")/
        norm((blod_20), type = "F"),
      `30%` = norm((blod_30 - l_blod_30_nnS - s_blod_30_nnS), type = "F")/
        norm((blod_30), type = "F"),
      `40%` = norm((blod_40 - l_blod_40_nnS - s_blod_40_nnS), type = "F")/
        norm((blod_40), type = "F"),
      `50%` = norm((blod_50 - l_blod_50_nnS - s_blod_50_nnS), type = "F")/
        norm((blod_50), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Values = "< LOD",
         Method = "LOD PCP nnS")
```

* Values \> and \< LOD stratified
* Sum of low rank and sparse solution matrices (L \+ S) compared to simulated data (X)

```{r, fig.align = "center"}
rbind(above_diff, 
      less_diff,
      above_diff_sqrt2, 
      less_diff_sqrt2,
      above_diff_nnS,
      less_diff_nnS) %>% 
  mutate(norm = ifelse(Values == "> LOD" & Method == "LOD PCP", norm - 0.005, norm)) %>% 
  ggplot(aes(x = percent_blod, y = norm, group = interaction(Values, Method), color = Method)) + 
  geom_point(aes()) + geom_path(aes(linetype = Values)) + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "norm(X-L-S) / norm(X)",
       title = "Relative Error in Values < LOD & > LOD")
```

## SVD

### Right singular vectors

```{r, svdv, include=FALSE}
# Extract right singular vectors from each low rank solution matrix
V_lod0  <-  svd(L_lod0)$v[,1:2]
V_lod10 <- svd(L_lod10)$v[,1:2]
V_lod20 <- svd(L_lod20)$v[,1:2]
V_lod30 <- svd(L_lod30)$v[,1:2]
V_lod40 <- svd(L_lod40)$v[,1:2]
V_lod50 <- svd(L_lod50)$v[,1:2]

# Hack to flip singular vectos -- Use correlation
# cor(V_lod0, V_lod10)
# cor(V_lod0, V_lod20)
# cor(V_lod0, V_lod30)
# cor(V_lod0, V_lod40)
# cor(V_lod0, V_lod50)

V_diff <- as_tibble(cbind(`0%` =norm((V_lod0 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      `10%` =norm((V_lod10 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      `20%` =norm((V_lod20 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      `30%` =norm((V_lod30 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      `40%` =norm((V_lod40 - V_lod0), type = "F")/norm((V_lod0), type = "F"),
      `50%` =norm((V_lod50 - V_lod0), type = "F")/norm((V_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "LOD PCP")

#V_diff

# Extract right singular vectors from each low rank solution matrix
V_lod0_sqrt2  <-  svd(L_lod0_sqrt2)$v[,1:2]
V_lod10_sqrt2 <- svd(L_lod10_sqrt2)$v[,1:2]
V_lod20_sqrt2 <- svd(L_lod20_sqrt2)$v[,1:2]
V_lod30_sqrt2 <- svd(L_lod30_sqrt2)$v[,1:2]
V_lod40_sqrt2 <- svd(L_lod40_sqrt2)$v[,1:2]
V_lod50_sqrt2 <- svd(L_lod50_sqrt2)$v[,1:2]

# cor(V_lod0_sqrt2, V_lod10_sqrt2)
# cor(V_lod0_sqrt2, V_lod20_sqrt2)
# cor(V_lod0_sqrt2, V_lod30_sqrt2)
# cor(V_lod0_sqrt2, V_lod40_sqrt2)
# cor(V_lod0_sqrt2, V_lod50_sqrt2)

V_diff_sqrt2 <- as_tibble(cbind(`0%` =norm((V_lod0_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"),
      `10%` =norm((V_lod10_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"),
      `20%` =norm((V_lod20_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"),
      `30%` =norm((V_lod30_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"),
      `40%` =norm((V_lod40_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"),
      `50%` =norm((V_lod50_sqrt2 - V_lod0_sqrt2), type = "F")/norm((V_lod0_sqrt2), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))

#V_diff_sqrt2

# Extract right singular vectors from each low rank solution matrix
V_lod0_nnS  <-  svd(L_lod0_nnS)$v[,1:2]
V_lod10_nnS <- svd(L_lod10_nnS)$v[,1:2]
V_lod20_nnS <- svd(L_lod20_nnS)$v[,1:2]
V_lod30_nnS <- svd(L_lod30_nnS)$v[,1:2]
V_lod40_nnS <- svd(L_lod40_nnS)$v[,1:2]
V_lod50_nnS <- svd(L_lod50_nnS)$v[,1:2]

# Hack to flip singular vectos -- Use correlation
# cor(V_lod0_nnS, V_lod10_nnS)
# cor(V_lod0_nnS, V_lod20_nnS)
# cor(V_lod0_nnS, V_lod30_nnS)
# cor(V_lod0_nnS, V_lod40_nnS)
# cor(V_lod0_nnS, V_lod50_nnS)

V_diff_nnS<- as_tibble(cbind(`0%` =norm((V_lod0_nnS - V_lod0_nnS), type = "F")/norm((V_lod0_nnS), type = "F"),
      `10%` =norm((V_lod10_nnS - V_lod0_nnS), type = "F")/norm((V_lod0_nnS), type = "F"),
      `20%` =norm((V_lod20_nnS - V_lod0_nnS), type = "F")/norm((V_lod0_nnS), type = "F"),
      `30%` =norm((V_lod30_nnS - V_lod0_nnS), type = "F")/norm((V_lod0_nnS), type = "F"),
      `40%` =norm((V_lod40_nnS - V_lod0_nnS), type = "F")/norm((V_lod0_nnS), type = "F"),
      `50%` =norm((V_lod50_nnS - V_lod0_nnS), type = "F")/norm((V_lod0_nnS), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "LOD PCP nnS")

#V_diff_nnS
```

* Reference is right singular vector matrix of SVD of low rank solution matix with 0\% \<LOD

```{r, fig.align = "center"}
rbind(V_diff,
      V_diff_sqrt2,
      V_diff_nnS) %>% ggplot(aes(x = percent_blod, y = norm, group = Method, color = Method)) + 
  geom_point() + geom_path() + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "norm(SV - SV_lod0) / norm(SV_lod0)",
       title = "Relative Error in Low-Rank Solution Right Singular Vectors")
```

### Left singular vectors

```{r, svdu, include=FALSE}
u_lod0  <-  svd(L_lod0)$u[,1:2]
u_lod10 <- svd(L_lod10)$u[,1:2]
u_lod20 <- svd(L_lod20)$u[,1:2]
u_lod30 <- svd(L_lod30)$u[,1:2]
u_lod40 <- svd(L_lod40)$u[,1:2]
u_lod50 <- svd(L_lod50)$u[,1:2]

u_diff <- as_tibble(cbind(`0%` =norm((u_lod0 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      `10%` =norm((u_lod10 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      `20%` =norm((u_lod20 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      `30%` =norm((u_lod30 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      `40%` =norm((u_lod40 - u_lod0), type = "F")/norm((u_lod0), type = "F"),
      `50%` =norm((u_lod50 - u_lod0), type = "F")/norm((u_lod0), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
mutate(Method = "LOD PCP")

# u_diff

u_lod0_sqrt2  <-  svd(L_lod0_sqrt2)$u[,1:2]
u_lod10_sqrt2 <- svd(L_lod10_sqrt2)$u[,1:2]
u_lod20_sqrt2 <- svd(L_lod20_sqrt2)$u[,1:2]
u_lod30_sqrt2 <- svd(L_lod30_sqrt2)$u[,1:2]
u_lod40_sqrt2 <- svd(L_lod40_sqrt2)$u[,1:2]
u_lod50_sqrt2 <- svd(L_lod50_sqrt2)$u[,1:2]

u_diff_sqrt2 <- as_tibble(cbind(`0%` =norm((u_lod0_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"),
      `10%` =norm((u_lod10_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"),
      `20%` =norm((u_lod20_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"),
      `30%` =norm((u_lod30_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"),
      `40%` =norm((u_lod40_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"),
      `50%` =norm((u_lod50_sqrt2 - u_lod0_sqrt2), type = "F")/norm((u_lod0_sqrt2), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))

u_lod0_nnS  <-  svd(L_lod0_nnS)$u[,1:2]
u_lod10_nnS <- svd(L_lod10_nnS)$u[,1:2]
u_lod20_nnS <- svd(L_lod20_nnS)$u[,1:2]
u_lod30_nnS <- svd(L_lod30_nnS)$u[,1:2]
u_lod40_nnS <- svd(L_lod40_nnS)$u[,1:2]
u_lod50_nnS <- svd(L_lod50_nnS)$u[,1:2]

u_diff_nnS<- as_tibble(cbind(`0%` =norm((u_lod0_nnS - u_lod0_nnS), type = "F")/norm((u_lod0_nnS), type = "F"),
      `10%` =norm((u_lod10_nnS - u_lod0_nnS), type = "F")/norm((u_lod0_nnS), type = "F"),
      `20%` =norm((u_lod20_nnS - u_lod0_nnS), type = "F")/norm((u_lod0_nnS), type = "F"),
      `30%` =norm((u_lod30_nnS - u_lod0_nnS), type = "F")/norm((u_lod0_nnS), type = "F"),
      `40%` =norm((u_lod40_nnS - u_lod0_nnS), type = "F")/norm((u_lod0_nnS), type = "F"),
      `50%` =norm((u_lod50_nnS - u_lod0_nnS), type = "F")/norm((u_lod0_nnS), type = "F"))) %>% 
  gather(percent_blod, norm) %>% 
mutate(Method = "LOD PCP nnS")

# u_diff_nnS
```

* Reference is left singular vector matrix of SVD of low rank solution matix with 0\% \<LOD

```{r, fig.align = "center"}
rbind(u_diff,
      u_diff_sqrt2,
      u_diff_nnS) %>% ggplot(aes(x = percent_blod, y = norm, group = Method, color = Method)) + 
  geom_point() + geom_path() + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "norm(SV - SV_lod0) / norm(SV_lod0)",
       title = "Relative Error in Low-Rank Solution Left Singular Vectors")
```

### Singular Values

```{r, include=FALSE}
d_lod0  <- svd(L_lod0)$d[1:2]
d_lod10 <- svd(L_lod10)$d[1:2]
d_lod20 <- svd(L_lod20)$d[1:2]
d_lod30 <- svd(L_lod30)$d[1:2]
d_lod40 <- svd(L_lod40)$d[1:2]
d_lod50 <- svd(L_lod50)$d[1:2]

norm_vec <- function(x) sqrt(sum(x^2))

d_diff <- as_tibble(cbind(`0%` = norm_vec(d_lod0 - d_lod0)/norm_vec(d_lod0),
      `10%` = norm_vec(d_lod10 - d_lod0)/norm_vec(d_lod0),
      `20%` = norm_vec(d_lod20 - d_lod0)/norm_vec(d_lod0),
      `30%` = norm_vec(d_lod30 - d_lod0)/norm_vec(d_lod0),
      `40%` = norm_vec(d_lod40 - d_lod0)/norm_vec(d_lod0),
      `50%` = norm_vec(d_lod50 - d_lod0)/norm_vec(d_lod0))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "LOD PCP")

d_lod0_sqrt2  <- svd(L_lod0_sqrt2)$d[1:2]
d_lod10_sqrt2 <- svd(L_lod10_sqrt2)$d[1:2]
d_lod20_sqrt2 <- svd(L_lod20_sqrt2)$d[1:2]
d_lod30_sqrt2 <- svd(L_lod30_sqrt2)$d[1:2]
d_lod40_sqrt2 <- svd(L_lod40_sqrt2)$d[1:2]
d_lod50_sqrt2 <- svd(L_lod50_sqrt2)$d[1:2]

d_diff_sqrt2 <- as_tibble(cbind(`0%` = norm_vec(d_lod0_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2),
      `10%` = norm_vec(d_lod10_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2),
      `20%` = norm_vec(d_lod20_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2),
      `30%` = norm_vec(d_lod30_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2),
      `40%` = norm_vec(d_lod40_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2),
      `50%` = norm_vec(d_lod50_sqrt2 - d_lod0_sqrt2)/norm_vec(d_lod0_sqrt2))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = paste0("PCP w/ LOD/", intToUtf8(8730),2))

d_lod0_nnS  <- svd(L_lod0_nnS)$d[1:2]
d_lod10_nnS <- svd(L_lod10_nnS)$d[1:2]
d_lod20_nnS <- svd(L_lod20_nnS)$d[1:2]
d_lod30_nnS <- svd(L_lod30_nnS)$d[1:2]
d_lod40_nnS <- svd(L_lod40_nnS)$d[1:2]
d_lod50_nnS <- svd(L_lod50_nnS)$d[1:2]

norm_vec <- function(x) sqrt(sum(x^2))

d_diff_nnS<- as_tibble(cbind(`0%` = norm_vec(d_lod0_nnS - d_lod0_nnS)/norm_vec(d_lod0_nnS),
      `10%` = norm_vec(d_lod10_nnS - d_lod0_nnS)/norm_vec(d_lod0_nnS),
      `20%` = norm_vec(d_lod20_nnS - d_lod0_nnS)/norm_vec(d_lod0_nnS),
      `30%` = norm_vec(d_lod30_nnS - d_lod0_nnS)/norm_vec(d_lod0_nnS),
      `40%` = norm_vec(d_lod40_nnS - d_lod0_nnS)/norm_vec(d_lod0_nnS),
      `50%` = norm_vec(d_lod50_nnS - d_lod0_nnS)/norm_vec(d_lod0_nnS))) %>% 
  gather(percent_blod, norm) %>% 
  mutate(Method = "LOD PCP nnS")
```

* Reference is singular value vector of SVD of low rank solution matix with 0\% \<LOD

```{r, fig.align = "center"}
rbind(d_diff_sqrt2,
      d_diff,
      d_diff_nnS) %>% ggplot(aes(x = percent_blod, y = norm, group = Method, color = Method)) + 
  geom_point() + geom_path() + theme_bw() +
  labs(x = "Percent Below LOD", 
       y = "norm(SV - SV_lod0) / norm(SV_lod0)",
       title = "Relative Error in Low-Rank Solution Singular Values")
```


## True v. Predicted

```{r, tp_lod, include=FALSE}
true_pred <- as_tibble(cbind(Simulated = mix[,8],
                          `0%` = L_lod0[,8] + S_lod0[,8],
                          `10%` = L_lod10[,8] + S_lod10[,8],
                          `20%` = L_lod20[,8] + S_lod20[,8],
                          `30%` = L_lod30[,8] + S_lod30[,8],
                          `40%` = L_lod30[,8] + S_lod30[,8],
                          `50%` = L_lod30[,8] + S_lod30[,8],
          id = 1:100)) %>% gather(key = Percent_BLOD, value = Predicted, -Simulated, -id) %>% 
  mutate(LOD = c(rep(0, 100), rep(quantile(mix[,8], .10), 100),
                 rep(quantile(mix[,8], .20), 100),
                 rep(quantile(mix[,8], .30), 100),
                 rep(quantile(mix[,8], .40), 100),
                 rep(quantile(mix[,8], .50), 100)))
```

```{r, fig.align="center"}
true_pred %>% 
  ggplot(aes(x = Simulated, y = Predicted)) + 
  geom_hline(yintercept = 0, color = 'grey', linetype = 'dashed') +
  geom_rect(aes(xmin = 0, xmax = LOD, ymin = 0, ymax = LOD),
                   fill = "pink", alpha = 0.03) +
  geom_abline(intercept = 0, slope = 1, color = 'grey', linetype = 'dashed') +
  geom_point(aes(color = Percent_BLOD)) +
  facet_wrap(~Percent_BLOD) +
  theme_bw() + theme(legend.position = "none") +
  labs(title= "PCP-LOD Simulated v. Predicted Values (L + S) for POP F08")
```

```{r, fig.align="center"}
true_pred %>% 
  filter(Simulated <= LOD) %>% 
  ggplot(aes(x = Simulated, y = Predicted)) + 
  geom_hline(yintercept = 0, color = 'grey', linetype = 'dashed') +
  geom_rect(aes(xmin = 0, xmax = LOD, ymin = 0, ymax = LOD),
                   fill = "pink", alpha = 0.03) +
  geom_abline(intercept = 0, slope = 1, color = 'grey', linetype = 'dashed') +
  geom_point(aes(color = Percent_BLOD)) +
  facet_wrap(~Percent_BLOD) +
  theme_bw() + theme(legend.position = "none") +
  labs(title= "PCP-LOD Simulated v. Predicted Values (L + S) for POP F08 <LOD")
```

```{r, sqrt2_tp_lod, include=FALSE}
true_pred_sqrt2 <- as_tibble(cbind(Simulated = mix[,8],
                          `0%` = L_lod0_sqrt2[,8] + S_lod0_sqrt2[,8],
                          `10%` = L_lod10_sqrt2[,8] + S_lod10_sqrt2[,8],
                          `20%` = L_lod20_sqrt2[,8] + S_lod20_sqrt2[,8],
                          `30%` = L_lod30_sqrt2[,8] + S_lod30_sqrt2[,8],
                          `40%` = L_lod30_sqrt2[,8] + S_lod30_sqrt2[,8],
                          `50%` = L_lod30_sqrt2[,8] + S_lod30_sqrt2[,8],
          id = 1:100)) %>% gather(key = Percent_BLOD, value = Predicted, -Simulated, -id) %>% 
  mutate(LOD = c(rep(0, 100), rep(quantile(mix[,8], .10), 100),
                 rep(quantile(mix[,8], .20), 100),
                 rep(quantile(mix[,8], .30), 100),
                 rep(quantile(mix[,8], .40), 100),
                 rep(quantile(mix[,8], .50), 100)))
```

```{r, fig.align="center"}
true_pred_sqrt2 %>% 
  ggplot(aes(x = Simulated, y = Predicted)) + 
  geom_hline(yintercept = 0, color = 'grey', linetype = 'dashed') +
  geom_rect(aes(xmin = 0, xmax = LOD, ymin = 0, ymax = LOD),
                   fill = "pink", alpha = 0.03) +
  geom_abline(intercept = 0, slope = 1, color = 'grey', linetype = 'dashed') +
  geom_point(aes(color = Percent_BLOD)) +
  facet_wrap(~Percent_BLOD) +
  theme_bw() + theme(legend.position = "none") +
  labs(title= "Original PCP w/ LOD/sqrt(2) Simulated v. Predicted Values (L + S) for POP F08")
```

```{r, fig.align="center"}
true_pred_sqrt2 %>% 
  filter(Simulated <= LOD) %>% 
  ggplot(aes(x = Simulated, y = Predicted)) + 
  geom_hline(yintercept = 0, color = 'grey', linetype = 'dashed') +
  geom_rect(aes(xmin = 0, xmax = LOD, ymin = 0, ymax = LOD),
                   fill = "pink", alpha = 0.03) +
  geom_abline(intercept = 0, slope = 1, color = 'grey', linetype = 'dashed') +
  geom_point(aes(color = Percent_BLOD)) +
  facet_wrap(~Percent_BLOD) +
  theme_bw() + theme(legend.position = "none") +
  labs(title= "Original PCP w/ LOD/sqrt(2) Simulated v. Predicted Values (L + S) for POP F08 <LOD")
```

```{r, nns_tp_lod, include=FALSE}
true_pred_nnS <- as_tibble(cbind(Simulated = mix[,8],
                          `0%` = L_lod0_nnS[,8] + S_lod0_nnS[,8],
                          `10%` = L_lod10_nnS[,8] + S_lod10_nnS[,8],
                          `20%` = L_lod20_nnS[,8] + S_lod20_nnS[,8],
                          `30%` = L_lod30_nnS[,8] + S_lod30_nnS[,8],
                          `40%` = L_lod30_nnS[,8] + S_lod30_nnS[,8],
                          `50%` = L_lod30_nnS[,8] + S_lod30_nnS[,8],
          id = 1:100)) %>% gather(key = Percent_BLOD, value = Predicted, -Simulated, -id) %>% 
  mutate(LOD = c(rep(0, 100), rep(quantile(mix[,8], .10), 100),
                 rep(quantile(mix[,8], .20), 100),
                 rep(quantile(mix[,8], .30), 100),
                 rep(quantile(mix[,8], .40), 100),
                 rep(quantile(mix[,8], .50), 100)))
```

```{r, fig.align="center"}
true_pred_nnS %>% 
  ggplot(aes(x = Simulated, y = Predicted)) + 
  geom_hline(yintercept = 0, color = 'grey', linetype = 'dashed') +
  geom_rect(aes(xmin = 0, xmax = LOD, ymin = 0, ymax = LOD),
                   fill = "pink", alpha = 0.03) +
  geom_abline(intercept = 0, slope = 1, color = 'grey', linetype = 'dashed') +
  geom_point(aes(color = Percent_BLOD)) +
  facet_wrap(~Percent_BLOD) +
  theme_bw() + theme(legend.position = "none") +
  labs(title= "nnS PCP-LOD Simulated v. Predicted Values (L + S) for POP F08")
```

```{r, fig.align="center"}
true_pred_nnS %>% 
  filter(Simulated <= LOD) %>% 
  ggplot(aes(x = Simulated, y = Predicted)) + 
  geom_hline(yintercept = 0, color = 'grey', linetype = 'dashed') +
  geom_rect(aes(xmin = 0, xmax = LOD, ymin = 0, ymax = LOD),
                   fill = "pink", alpha = 0.03) +
  geom_abline(intercept = 0, slope = 1, color = 'grey', linetype = 'dashed') +
  geom_point(aes(color = Percent_BLOD)) +
  facet_wrap(~Percent_BLOD) +
  theme_bw() + theme(legend.position = "none") +
  labs(title= "nnS PCP-LOD Simulated v. Predicted Values (L + S) for POP F08 <LOD")
```

## Values \<LOD

```{r, l22s, include=FALSE}
t_na_lod_0 <- sim_all %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_0_na <- as_tibble(t_na_lod_0*L_lod0)
s_blod_0_na <- as_tibble(t_na_lod_0*S_lod0)
blod_0_na <- as_tibble(sim_all*t_na_lod_0)

t_na_lod_10 <- mix_data_lod_10 %>% 
  as_tibble() %>%
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_10_na <- as_tibble(t_na_lod_10*L_lod10)
s_blod_10_na <- as_tibble(t_na_lod_10*S_lod10)
blod_10_na <- as_tibble(sim_all*t_na_lod_10)

t_na_lod_20 <- mix_data_lod_20 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_20_na <- as_tibble(t_na_lod_20*L_lod20)
s_blod_20_na <- as_tibble(t_na_lod_20*S_lod20)
blod_20_na <- as_tibble(sim_all*t_na_lod_20)

t_na_lod_30 <- mix_data_lod_30 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_30_na <- as_tibble(t_na_lod_30*L_lod30)
s_blod_30_na <- as_tibble(t_na_lod_30*S_lod30)
blod_30_na <- as_tibble(sim_all*t_na_lod_30)

t_na_lod_40 <- mix_data_lod_40 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_40_na <- as_tibble(t_na_lod_40*L_lod40)
s_blod_40_na <- as_tibble(t_na_lod_40*S_lod40)
blod_40_na <- as_tibble(sim_all*t_na_lod_40)

t_na_lod_50 <- mix_data_lod_50 %>% 
  as_tibble() %>% 
  mutate_all(function(x) ifelse(x == -1, TRUE, NA))
l_blod_50_na <- as_tibble(t_na_lod_50*L_lod50)
s_blod_50_na <- as_tibble(t_na_lod_50*S_lod50)
blod_50_na <- as_tibble(sim_all*t_na_lod_50) 

L_blod_0_sqrt2_na <- as_tibble(t_na_lod_0*L_lod0_sqrt2)
S_blod_0_sqrt2_na <- as_tibble(t_na_lod_0*S_lod0_sqrt2)

L_blod_10_sqrt2_na <- as_tibble(t_na_lod_10*L_lod10_sqrt2)
S_blod_10_sqrt2_na <- as_tibble(t_na_lod_10*S_lod10_sqrt2)

L_blod_20_sqrt2_na <- as_tibble(t_na_lod_20*L_lod20_sqrt2)
S_blod_20_sqrt2_na <- as_tibble(t_na_lod_20*S_lod20_sqrt2)

L_blod_30_sqrt2_na <- as_tibble(t_na_lod_30*L_lod30_sqrt2)
S_blod_30_sqrt2_na <- as_tibble(t_na_lod_30*S_lod30_sqrt2)

L_blod_40_sqrt2_na <- as_tibble(t_na_lod_40*L_lod40_sqrt2)
S_blod_40_sqrt2_na <- as_tibble(t_na_lod_40*S_lod40_sqrt2)

L_blod_50_sqrt2_na <- as_tibble(t_na_lod_50*L_lod50_sqrt2)
S_blod_50_sqrt2_na <- as_tibble(t_na_lod_50*S_lod50_sqrt2)

LOD10 <- delta10 %>% as.matrix() %>% t() %>% as_tibble() %>% rename(F08 = 7) %>% gather(POP, LOD) %>% mutate(Percent = "10%")
LOD20 <- delta20 %>% as.matrix() %>% t() %>% as_tibble() %>% rename(F08 = 7) %>% gather(POP, LOD) %>% mutate(Percent = "20%")
LOD30 <- delta30 %>% as.matrix() %>% t() %>% as_tibble() %>% rename(F08 = 7) %>% gather(POP, LOD) %>% mutate(Percent = "30%")
LOD40 <- delta40 %>% as.matrix() %>% t() %>% as_tibble() %>% rename(F08 = 7) %>% gather(POP, LOD) %>% mutate(Percent = "40%")
LOD50 <- delta50 %>% as.matrix() %>% t() %>% as_tibble() %>% rename(F08 = 7) %>% gather(POP, LOD) %>% mutate(Percent = "50%")
LODall <- rbind(LOD10, LOD20, LOD30, LOD40, LOD50)
  
plot_10 <- blod_10_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Original, -rowid) %>% mutate(Percent = "10%")
plotl_10 <- l_blod_10_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))
plots_10 <- s_blod_10_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))
plotall_10 <- (l_blod_10_na + s_blod_10_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))

plot_20 <- blod_20_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Original, -rowid) %>% mutate(Percent = "20%") 
plotl_20 <- l_blod_20_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent"))
plots_20 <- s_blod_20_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent"))
plotall_20 <- (l_blod_20_na + s_blod_20_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent")) 

plot_30 <- blod_30_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Original, -rowid) %>% mutate(Percent = "30%")
plotl_30 <- l_blod_30_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent"))
plots_30 <- s_blod_30_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent")) 
plotall_30 <- (l_blod_30_na + s_blod_30_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent")) 

plot_40 <- blod_40_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Original, -rowid) %>% mutate(Percent = "40%") 
plotl_40 <- l_blod_40_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))
plots_40 <- s_blod_40_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))
plotall_40 <- (l_blod_40_na + s_blod_40_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))

plot_50 <- blod_50_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Original, -rowid) %>% mutate(Percent = "50%") 
plotl_50 <- l_blod_50_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent"))
plots_50 <- s_blod_50_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent")) 
plotall_50 <- (l_blod_50_na + s_blod_50_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent"))

org <- rbind(plot_10,
        plot_20,
        plot_30,
        plot_40,
        plot_50) %>% rename(Value = Original) %>% 
  mutate(Compare = "Original") %>% 
  left_join(., LODall, by = c("POP", "Percent"))

plotall <- rbind(plotl_10,
      plots_10,
      plotall_10,
      plotl_20,
      plots_20,
      plotall_20,
      plotl_30,
      plots_30,
      plotall_30, 
      plotl_40,
      plots_40,
      plotall_40,
      plotl_50,
      plots_50,
      plotall_50)

l_blod_0_nnS_na <- as_tibble(t_na_lod_0*L_lod0_nnS)
s_blod_0_nnS_na <- as_tibble(t_na_lod_0*S_lod0_nnS)

l_blod_10_nnS_na <- as_tibble(t_na_lod_10*L_lod10_nnS)
s_blod_10_nnS_na <- as_tibble(t_na_lod_10*S_lod10_nnS)

l_blod_20_nnS_na <- as_tibble(t_na_lod_20*L_lod20_nnS)
s_blod_20_nnS_na <- as_tibble(t_na_lod_20*S_lod20_nnS)

l_blod_30_nnS_na <- as_tibble(t_na_lod_30*L_lod30_nnS)
s_blod_30_nnS_na <- as_tibble(t_na_lod_30*S_lod30_nnS)

l_blod_40_nnS_na <- as_tibble(t_na_lod_40*L_lod40_nnS)
s_blod_40_nnS_na <- as_tibble(t_na_lod_40*S_lod40_nnS)

l_blod_50_nnS_na <- as_tibble(t_na_lod_50*L_lod50_nnS)
s_blod_50_nnS_na <- as_tibble(t_na_lod_50*S_lod50_nnS)

plotl_10_nnS <- l_blod_10_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))
plots_10_nnS <- s_blod_10_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))
plotall_10_nnS <- (l_blod_10_nnS_na + s_blod_10_nnS_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))

plotl_20_nnS <- l_blod_20_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent"))
plots_20_nnS <- s_blod_20_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent"))
plotall_20_nnS <- (l_blod_20_nnS_na + s_blod_20_nnS_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent")) 

plotl_30_nnS <- l_blod_30_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent"))
plots_30_nnS <- s_blod_30_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent")) 
plotall_30_nnS <- (l_blod_30_nnS_na + s_blod_30_nnS_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent")) 

plotl_40_nnS <- l_blod_40_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))
plots_40_nnS <- s_blod_40_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))
plotall_40_nnS <- (l_blod_40_nnS_na + s_blod_40_nnS_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))

plotl_50_nnS <- l_blod_50_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent"))
plots_50_nnS <- s_blod_50_nnS_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent")) 
plotall_50_nnS <- (l_blod_50_nnS_na + s_blod_50_nnS_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent"))

plotall_nnS <- rbind(plotl_10_nnS,
      plots_10_nnS,
      plotall_10_nnS,
      plotl_20_nnS,
      plots_20_nnS,
      plotall_20_nnS,
      plotl_30_nnS,
      plots_30_nnS,
      plotall_30_nnS, 
      plotl_40_nnS,
      plots_40_nnS,
      plotall_40_nnS,
      plotl_50_nnS,
      plots_50_nnS,
      plotall_50_nnS)

plotl_10_sqrt2 <- L_blod_10_sqrt2_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))
plots_10_sqrt2 <- S_blod_10_sqrt2_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))
plotall_10_sqrt2 <- (L_blod_10_sqrt2_na + S_blod_10_sqrt2_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "10%") %>% left_join(., plot_10, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD10, by = c("POP", "Percent"))

plotl_20_sqrt2 <- L_blod_20_sqrt2_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent"))
plots_20_sqrt2 <- S_blod_20_sqrt2_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent"))
plotall_20_sqrt2 <- (L_blod_20_sqrt2_na + S_blod_20_sqrt2_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "20%") %>% left_join(., plot_20, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD20, by = c("POP", "Percent")) 

plotl_30_sqrt2 <- L_blod_30_sqrt2_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent"))
plots_30_sqrt2 <- S_blod_30_sqrt2_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent")) 
plotall_30_sqrt2 <- (L_blod_30_sqrt2_na + S_blod_30_sqrt2_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "30%") %>% left_join(., plot_30, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD30, by = c("POP", "Percent")) 

plotl_40_sqrt2 <- L_blod_40_sqrt2_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))
plots_40_sqrt2 <- S_blod_40_sqrt2_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))
plotall_40_sqrt2 <- (L_blod_40_sqrt2_na + S_blod_40_sqrt2_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "40%") %>% left_join(., plot_40, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD40, by = c("POP", "Percent"))

plotl_50_sqrt2 <- L_blod_50_sqrt2_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Low Rank Solution", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent"))
plots_50_sqrt2 <- S_blod_50_sqrt2_na %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Sparse Solution", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent")) 
plotall_50_sqrt2 <- (L_blod_50_sqrt2_na + S_blod_50_sqrt2_na) %>% as_tibble(.) %>% rowid_to_column(.) %>% gather(key = POP, value = Value, -rowid) %>% mutate(Compare = "Model Prediction", Percent = "50%") %>% left_join(., plot_50, by = c("rowid", "POP", "Percent")) %>% left_join(., LOD50, by = c("POP", "Percent"))

plotall_sqrt2 <- rbind(plotl_10_sqrt2,
      plots_10_sqrt2,
      plotall_10_sqrt2,
      plotl_20_sqrt2,
      plots_20_sqrt2,
      plotall_20_sqrt2,
      plotl_30_sqrt2,
      plots_30_sqrt2,
      plotall_30_sqrt2, 
      plotl_40_sqrt2,
      plots_40_sqrt2,
      plotall_40_sqrt2,
      plotl_50_sqrt2,
      plots_50_sqrt2,
      plotall_50_sqrt2)
```

```{r}
plotall %>% 
  filter(Compare == "Low Rank Solution") %>% 
  drop_na(.) %>% 
  mutate(above_lod = ifelse(Value > LOD, 1, 0)) %>%
  group_by(Compare, Percent) %>% 
  summarise(above = sum(above_lod),
            total = n()) %>% 
  mutate(Proportion = round(above/total, 2)) %>% 
  ungroup(.) %>% 
  select(Percent, Proportion) %>% 
  kable(., caption = "LOD PCP Low Rank Solution Values >LOD for POP F08")

plotall_nnS %>% 
  filter(Compare == "Low Rank Solution") %>% 
  drop_na(.) %>% 
  mutate(above_lod = ifelse(Value > LOD, 1, 0)) %>%
  group_by(Compare, Percent) %>% 
  summarise(above = sum(above_lod),
            total = n()) %>% 
  mutate(Proportion = round(above/total, 2)) %>% 
  ungroup(.) %>% 
  select(Percent, Proportion) %>% 
  kable(., caption = "nnS LOD PCP Low Rank Solution Values >LOD for POP F08")

plotall_sqrt2 %>% 
  filter(Compare == "Low Rank Solution") %>% 
  drop_na(.) %>% 
  mutate(above_lod = ifelse(Value > LOD, 1, 0)) %>%
  group_by(Compare, Percent) %>% 
  summarise(above = sum(above_lod),
            total = n()) %>% 
  mutate(Proportion = round(above/total, 2)) %>% 
  ungroup(.) %>% 
  select(Percent, Proportion) %>% 
  kable(., caption = "Original PCP w/ LOD/sqrt(2) Low Rank Solution Values >LOD for POP F08")

rbind(plots_10,
      plots_20,
      plots_30,
      plots_40,
      plots_50) %>% 
  drop_na(.) %>% 
  group_by(Compare, Percent) %>% 
  summarise(Min = min(Value),
            Ave = mean(Value),
            Max = max(Value)) %>% 
  ungroup(.) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  select(-Compare) %>% kable(., caption = "LOD PCP Sparse Solutions for POP F08")

rbind(plots_10_nnS,
      plots_20_nnS,
      plots_30_nnS,
      plots_40_nnS,
      plots_50_nnS) %>% 
  drop_na(.) %>% 
  group_by(Compare, Percent) %>%
  summarise(Min = min (Value),
            Mean = mean(Value),
            Max = max(Value)) %>% 
  ungroup(.) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  select(-Compare) %>% kable(., caption = "nnS LOD PCP Sparse Solutions for POP F08")

rbind(plots_10_sqrt2,
      plots_20_sqrt2,
      plots_30_sqrt2,
      plots_40_sqrt2,
      plots_50_sqrt2) %>% 
  drop_na(.) %>% 
  group_by(Compare, Percent) %>%
  summarise(Min = min (Value),
            Mean = mean(Value),
            Max = max(Value)) %>% 
  ungroup(.) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  select(-Compare) %>% kable(., caption = "Original PCP w/ LOD/sqrt(2) Sparse Solutions for POP F08")
```

* Plus sign (\+) indicates LOD for each chemical

```{r, fig.align = "center"}
plotall %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  #filter(Compare != "Original") %>% 
  # with and without Original
  mutate(Compare = fct_relevel(Compare, "Low Rank Solution",
                            "Sparse Solution",
                            "Model Prediction",
                            "Original")) %>% 
  ggplot(aes(x = Percent, y = Value)) + 
  geom_jitter(aes(color = Compare), alpha = 0.75, width = 0.10, height = 0) + 
  theme_bw() +
  geom_point(aes(y = LOD), shape = 3, size = 2) +
  #facet_wrap(.~Percent) +
  labs(x = "% < LOD", 
       y = "Solution Value",
       title = "LOD PCP Solution Values <LOD + Original Values for POP F08") +
  theme(legend.position = "bottom")
```

* Plus sign (\+) indicates LOD for each chemical

```{r, fig.align = "center"}
plotall %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  filter(Compare != "Original") %>% 
  # with and without Original
  mutate(Compare = fct_relevel(Compare, "Low Rank Solution",
                            "Sparse Solution",
                            "Model Prediction")) %>% 
  ggplot(aes(x = Percent, y = Value)) + 
  geom_jitter(aes(color = Compare), alpha = 0.75, width = 0.10, height = 0) + 
  theme_bw() +
  geom_point(aes(y = LOD), shape = 3, size = 2) +
  #facet_wrap(.~Percent) +
  labs(x = "% < LOD", 
       y = "Solution Value",
       title = "LOD PCP Solution Values <LOD for POP F08") +
  theme(legend.position = "bottom")
```

* Plus sign (\+) indicates LOD for each chemical

```{r, fig.align = "center"}
plotall_nnS %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  #filter(Compare != "Original") %>% 
  # with and without Original
  mutate(Compare = fct_relevel(Compare, "Low Rank Solution",
                            "Sparse Solution",
                            "Model Prediction",
                            "Original")) %>% 
  ggplot(aes(x = Percent, y = Value)) + 
  geom_jitter(aes(color = Compare), alpha = 0.75, width = 0.10, height = 0) + 
  theme_bw() +
  geom_point(aes(y = LOD), shape = 3, size = 2) +
  #facet_wrap(.~Percent) +
  labs(x = "% < LOD", 
       y = "Solution Value",
       title = "nnS LOD PCP Solution Values <LOD + Original Values for POP F08") +
  theme(legend.position = "bottom")
```

* Plus sign (\+) indicates LOD for each chemical

```{r, fig.align = "center"}
plotall_nnS %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  filter(Compare != "Original") %>% 
  # with and without Original
  mutate(Compare = fct_relevel(Compare, "Low Rank Solution",
                            "Sparse Solution",
                            "Model Prediction")) %>% 
  ggplot(aes(x = Percent, y = Value)) + 
  geom_jitter(aes(color = Compare), alpha = 0.75, width = 0.10, height = 0) + 
  theme_bw() +
  geom_point(aes(y = LOD), shape = 3, size = 2) +
  #facet_wrap(.~Percent) +
  labs(x = "% < LOD", 
       y = "Solution Value",
       title = "nnS LOD PCP Solution Values <LOD for POP F08") +
  theme(legend.position = "bottom")
```

* Plus sign (\+) indicates LOD for each chemical

```{r, fig.align = "center"}
plotall_sqrt2 %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  #filter(Compare != "Original") %>% 
  # with and without Original
  mutate(Compare = fct_relevel(Compare, "Low Rank Solution",
                            "Sparse Solution",
                            "Model Prediction",
                            "Original")) %>% 
  ggplot(aes(x = Percent, y = Value)) + 
  geom_jitter(aes(color = Compare), alpha = 0.75, width = 0.10, height = 0) + 
  theme_bw() +
  geom_point(aes(y = LOD), shape = 3, size = 2) +
  #facet_wrap(.~Percent) +
  labs(x = "% < LOD", 
       y = "Solution Value",
       title = "Original PCP w/ LOD/sqrt(2) Solution Values <LOD + Original Values for POP F08") +
  theme(legend.position = "bottom")
```

* Plus sign (\+) indicates LOD for each chemical

```{r, fig.align = "center"}
plotall_sqrt2 %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  filter(Compare != "Original") %>% 
  # with and without Original
  mutate(Compare = fct_relevel(Compare, "Low Rank Solution",
                            "Sparse Solution",
                            "Model Prediction")) %>% 
    ggplot(aes(x = Percent, y = Value)) + 
  geom_jitter(aes(color = Compare), alpha = 0.75, width = 0.10, height = 0) + 
  theme_bw() +
  geom_point(aes(y = LOD), shape = 3, size = 2) +
  #facet_wrap(.~Percent) +
  labs(x = "% < LOD", 
       y = "Solution Value",
       title = "Original PCP w/ LOD/sqrt(2) Solution Values <LOD for POP F08") +
  theme(legend.position = "bottom")
```

```{r, message=FALSE, fig.align = "center"}
plotall %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  mutate(Value_SD = Value - LOD) %>%
  #filter(Compare != "Sparse Solution") %>% 
  ggplot(aes(x = Value)) + 
  geom_histogram(aes(fill = Compare, color = Compare), alpha = 0.25) + 
  theme_bw() +
  facet_wrap(.~Percent, scales = "free") +
  labs(x = "Solution Value", 
       y = "Count",
       title = "LOD PCP Solution Values <LOD + Original Values for POP F08") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, hjust = 1))

plotall_nnS %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  #filter(Compare != "Sparse Solution") %>% 
  ggplot(aes(x = Value)) + 
  geom_histogram(aes(fill = Compare, color = Compare), alpha = 0.25) + 
  theme_bw() +
  facet_wrap(.~Percent, scales = "free") +
  labs(x = "Solution Value", 
       y = "Count",
       title = "nnS LOD PCP Solution Values <LOD + Original Values for POP F08") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, hjust = 1))

plotall_sqrt2 %>% 
  select(-Original) %>% 
  rbind(., org) %>% 
  drop_na(.) %>% 
  #filter(Compare != "Sparse Solution") %>% 
  ggplot(aes(x = Value)) + 
  geom_histogram(aes(fill = Compare, color = Compare), alpha = 0.25) + 
  theme_bw() +
  facet_wrap(.~Percent, scales = "free") +
  labs(x = "Solution Value", 
       y = "Count",
       title = "Original PCP w/ LOD/sqrt(2) Solution Values <LOD + Original Values for POP F08") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, hjust = 1))
```

